---
#title: "2025 Licensed Angler Survey — Preferred Species"
#date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  officedown::rdocx_document:
    toc: false
always_allow_html: yes
---

```{r setup, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, fig.width=7.5, fig.height=7}
knitr::opts_chunk$set(echo=FALSE, include=TRUE, warning=FALSE, error=FALSE, message=FALSE, ft.align="left")
library(tictoc)
tic("Report Took ")
options(stringsAsFactors = FALSE)
library(officedown)
library(officer)
library(rmarkdown)
library(tidyverse)
library(knitr)
library(flextable)
library(stringr)
library(survey)

setwd("F:/Survey/Analysis/PreferredSpecies/")

source("..\\BaseFunctions_2025_UPDATED.R") #load file of common functions
# Sourced read-only to inherit the crosstab report's caption text and table
# wrappers verbatim rather than duplicating them. Nothing in CrossTabTables/ is
# modified. PreferredSpeciesFunctions.R is sourced last so it wins any conflict.
source("..\\CrossTabTables\\CrossTabTableFunctions.R")
source("PreferredSpeciesFunctions.R") #load file of preferred species report functions
# Chapter 5 is the latent profile analysis (D140-D156). Ch5LPA.R replaced
# Ch5Functions.R (k-means, D120), which was deleted and is in git history.
source("Ch5LPA.R")
```

```{r getData, echo=FALSE}
load(file="../../Data/DataAggregation1/aggregateData_20260624.rData")

# D76: 2018 snapshot for the Chapter 2 D4 slope figures, taken before d is
# filtered to 2025. Same !is.na(B1) rule as the 2025 universe (D23); "No
# preference" stays in d2018 here and is excluded later, item-by-item, only
# from the slope comparison itself (D4SlopeData), not from this snapshot.
d2018 <- d %>% filter(surveyYear == 2018, !is.na(B1))

d <- d %>% filter(surveyYear==2025)

# Population total over ALL 2025 respondents, captured before the B1 filter
# because the expansion column is reported on the full-population basis (D29).
popTotalAll <- sum(d$postWeight)
nAll2025 <- nrow(d)
nNoB1 <- sum(is.na(d$B1))

# Captured before the B1 filter so Chapter 2 can report how many respondents
# answered the D4 battery but are outside this report's universe (F12).
nD4AnyAll2025 <- sum(rowSums(!is.na(d[, d4.items])) > 0)
nD4AnyNoB1 <- sum(rowSums(!is.na(d[, d4.items])) > 0 & is.na(d$B1))

# D23: the B1 filter is the first analytic filter. Respondents who left B1
# blank are out of the report entirely, not merely out of the banner.
d <- d %>% filter(!is.na(B1))

# Rebuild scale/subscale scores from raw item factors, applying reversals
# flagged in Scales.csv (single source of truth) at report time.
d <- add_scale_scores(d)

d$B1banner <- AssignBannerGroup(d$B1)

q <- read.csv(file="../../Data/DataAggregation1/FactorLevels_aggregated.csv") %>% filter(Year==2025)
l <- read.csv(file="../../Data/DataAggregation1/Labels.csv")
```

```{r dataChecks, echo=FALSE}
# Checks after the universe is fixed. These stop the render rather than letting
# a silent miscount propagate into every table.
stopifnot(
  nrow(d) == nAll2025 - nNoB1,
  sum(is.na(d$B1)) == 0,
  sum(!is.na(d$B1banner)) + sum(is.na(d$B1banner)) == nrow(d)
)

# D76: the 2018 snapshot must carry every species name the banner uses and
# the same five D4 response levels, or D4SlopeData's cross-year join would
# silently miss species rather than erroring.
stopifnot(
  all(unique(d2018$surveyYear) == 2018),
  sum(is.na(d2018$B1)) == 0,
  length(setdiff(unlist(banner.definition$Members), as.character(d2018$B1))) == 0,
  identical(levels(d2018$D4a), levels(d$D4a))
)

sizeTbl <- SpeciesSizeTable(d, popTotalAll)

stopifnot(
  abs(sum(sizeTbl$Percent) - 100) < 1e-8,
  sum(sizeTbl$Respondents) == nrow(d),
  abs(sum(sizeTbl$TotalAnglers) - popTotalAll) < 1e-6
)

nBanner <- sum(InBannerColumn(d$B1))
nBannerExcluded <- nrow(d) - nBanner

# Sum of the banner column counts. Exceeds nBanner because family columns
# contain their own species columns; quoted in Appendix B so the overlap is
# documented with a live figure rather than a hardcoded one.
nBannerCellSum <- sum(vapply(
  banner.definition$Members,
  function(m) sum(as.character(d$B1) %in% m),
  integer(1)
))

popTotalAnalysis <- sum(d$postWeight)
```

<!--
D33: page 1 is intentionally left blank for a hand-built title page, and the
table of contents is placed explicitly rather than via the YAML `toc` option so
that it follows the title page instead of preceding it.
-->

&nbsp;

`r run_pagebreak()`

```{r toc}
block_toc()
```

`r run_pagebreak()`

# Chapter 1: Determining Species Groupings

`r paste0("This report covers only anglers who answered the preferred-species question. Of the ", format(nAll2025, big.mark=","), " anglers who responded to the 2025 survey, ", format(nNoB1, big.mark=","), " left that question blank, leaving an analysis sample of ", format(nrow(d), big.mark=","), ".")`

`r paste0("Because of that restriction, the Overall column of this report describes anglers who stated a species preference rather than all licensed anglers, and it will therefore not match the Overall column of the 2025 Crosstabs report. The preferred-species distribution in the next table is the one quantity unaffected by the restriction, and it does match the Crosstabs report exactly.")`

```{r ch1Helpers, echo=FALSE}
# Small accessors for the Chapter 1 narrative so every quoted figure is live.
Pc <- function(sp) round(sizeTbl$Percent[sizeTbl$Species == sp])
Rn <- function(sp) sizeTbl$Respondents[sizeTbl$Species == sp]
FamRow <- function(g) family.disp[family.disp$Group == g, ]
FamP <- function(fam, out) {
  FmtP(min(family.tests$PFamily[family.tests$Family == fam & family.tests$Outcome == out]))
}
top3 <- c("Walleye / Sauger", "Largemouth bass", "I do not prefer any particular type of fish")
```

The 2025 questionnaire offered `r nrow(sizeTbl)` answer categories for preferred species, and anglers concentrate on a few of them: `r sum(sizeTbl$Respondents < min.group.n & sizeTbl$Respondents > 0)` categories drew fewer than `r min.group.n` respondents and Sturgeon drew none. A species-by-species breakdown of the rest of the survey is therefore not supportable across the whole list. This chapter builds the set of preferred groups that organises every later chapter. Related species are combined into a family group only where their anglers cannot be distinguished on motivations, attitudes and effort, and a species keeps its own column wherever it has enough respondents to be reported on its own. Anglers who prefer no particular type of fish are kept as a group in their own right rather than set aside: they are roughly one in six of the sample, and their answers describe a segment of licence holders that species-specific management does not reach directly.

## Question Text

`r paste0("*", trimws(GetQuestion(q, B1, 2025)), "*")`

## Sample Sizes and Population Estimates by Species

`r paste(caption.sizes, "  ", caption.raked, sep="")`

```{r speciesSizes}
CreateFlex(ArrangeSpeciesSizeTable(sizeTbl))
```

`r paste0("Total anglers applies each species percentage to the full weighted 2025 angler population of ", format(round(popTotalAll), big.mark=","), ", so the column sums to that population. This assumes that leaving the preferred-species question blank is unrelated to which species an angler prefers. The weights carried by the ", format(nrow(d), big.mark=","), " respondents in the analysis sample themselves total ", format(round(sum(d$postWeight)), big.mark=","), ".")`

Three categories account for about `r round(sum(sizeTbl$Percent[sizeTbl$Species %in% top3]))` percent of the weighted angler population: Walleye / Sauger (`r Pc("Walleye / Sauger")` percent), Largemouth bass (`r Pc("Largemouth bass")` percent) and anglers with no particular preference (`r Pc("I do not prefer any particular type of fish")` percent). Crappie and Channel catfish follow at `r Pc("Crappie")` and `r Pc("Channel catfish")` percent, and no other species reaches 5 percent. The practical consequence for managers is that walleye, largemouth bass, crappie and channel catfish programmes each speak to a measurable share of the angling public, while preferences for species such as paddlefish, yellow perch, common carp and muskellunge are held by too few surveyed anglers to describe with confidence, however locally important those fisheries may be.

## Selection Rules

`r paste0("The list of preferred groups used in the rest of this report is produced by the rules below, applied in this order. (1) Five candidate families are proposed in the next section; a species that is not in a candidate family is never combined. (2) Every pair of species inside a candidate family is compared on nine outcomes (four motivation scales, four attitude scales, and days fished), and the p-values are Bonferroni-adjusted across all of the tests in that family. A family may be combined only if none of its adjusted p-values is below ", family.alpha, ". (3) Walleye / Sauger, Trout and No preference are single-member groups; they are not tested. (4) A group or species needs at least ", min.group.n, " raw respondents to receive a column. All species in a candidate family are tested before the size rule is applied, and a species that meets the size rule receives its own column whether or not its family is combined.")`

`r paste0("Overlapping confidence intervals are weak evidence that two species are similar, and the comparisons for the smaller species are underpowered. A dagger on the n column of a contrast table marks a comparison in which one species has fewer than ", min.group.n, " respondents.")`

The rules answer a practical question: when a family label such as "catfish" or "bass" is used as a management unit, does it describe one angling constituency or several? Combining species whose anglers behave alike buys precision, because the pooled column has narrower confidence intervals than any of its members; combining species whose anglers differ hides the very distinctions a species-specific programme depends on. The Bonferroni adjustment leans toward combining, since it is difficult for any single contrast to clear the threshold, so a family that fails the test does so on strong evidence. The reverse does not hold. With as few as `r Rn("Muskellunge / Tiger musky")` respondents in some species, a family that passes may still contain differences the survey is too small to detect, and the family columns should be read as "no measurable difference among these anglers", not as proof that the species are interchangeable.

## Proposed Family Groupings

`r paste0("Candidate families and their member species. Species that are in no candidate family are not listed. Respondents is the raw unweighted count. ", caption.raked)`

```{r familyProposal}
CreateFlex(FamilyProposalTable(d))
```

```{r familyTests, echo=FALSE}
# All within-family tests are computed once and shared by every contrast table,
# the disposition table and the banner check below.
family.tests <- purrr::map_dfr(
  unique(family.candidates$Family),
  function(f) FamilyTests(d, f)
)
family.disp <- FamilyDisposition(d, family.tests)
```

## Comparisons Within Proposed Families

`r paste0("Each candidate family with more than one species is shown broken out by species alongside the family as a whole. These are the comparisons used to decide whether a family may be combined.")`

### Bass

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, "  ", caption.comparison, sep="")`

```{r bassMotivation}
CreateFlex(GenusMeansTable(d, "Bass", motivation.vars, l))
```

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.raked, "  ", caption.reversed, sep="")`

```{r bassAttitude}
CreateFlex(GenusMeansTable(d, "Bass", attitude.vars, l))
```

`r paste("Total days fished in Nebraska during 2025.", "  ", caption.means, "  ", caption.medians, "  ", caption.raked, sep="")`

```{r bassEffort}
CreateFlex(GenusEffortTable(d, "Bass"))
```

`r paste(caption.contrasts, sep="")`

```{r bassContrasts}
CreateFlex(ContrastTable(dplyr::filter(family.tests, Family == "Bass"), c(motivation.vars, attitude.vars), l))
```

`r paste("Days fished, same species comparisons.", "  ", caption.contrasts, sep="")`

```{r bassEffortContrasts}
CreateFlex(EffortContrastTable(dplyr::filter(family.tests, Family == "Bass")))
```

None of the `r FamRow("Bass")$Tests` largemouth-versus-smallmouth contrasts approached the adjusted threshold (smallest adjusted p = `r FmtP(FamRow("Bass")$MinP)`). Smallmouth anglers are few (`r Rn("Smallmouth bass")` respondents), so the comparison has limited power, but the point estimates for the two species sit close together on every motivation and attitude scale and on days fished. The Bass family is combined, and Largemouth bass and Smallmouth bass each keep a species column because both exceed the size floor.

### Panfish / Sunfish

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, "  ", caption.comparison, sep="")`

```{r panfishMotivation}
CreateFlex(GenusMeansTable(d, "Panfish / Sunfish", motivation.vars, l))
```

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.raked, "  ", caption.reversed, sep="")`

```{r panfishAttitude}
CreateFlex(GenusMeansTable(d, "Panfish / Sunfish", attitude.vars, l))
```

`r paste("Total days fished in Nebraska during 2025.", "  ", caption.means, "  ", caption.medians, "  ", caption.raked, sep="")`

```{r panfishEffort}
CreateFlex(GenusEffortTable(d, "Panfish / Sunfish"))
```

`r paste(caption.contrasts, sep="")`

```{r panfishContrasts}
CreateFlex(ContrastTable(dplyr::filter(family.tests, Family == "Panfish / Sunfish"), c(motivation.vars, attitude.vars), l))
```

`r paste("Days fished, same species comparisons.", "  ", caption.contrasts, sep="")`

```{r panfishEffortContrasts}
CreateFlex(EffortContrastTable(dplyr::filter(family.tests, Family == "Panfish / Sunfish")))
```

Crappie, Bluegill / Sunfish and Yellow perch produced no adjusted difference in `r FamRow("Panfish / Sunfish")$Tests` contrasts (smallest adjusted p = `r FmtP(FamRow("Panfish / Sunfish")$MinP)`). Yellow perch contributes only `r Rn("Yellow perch")` respondents and is the least informative member; its inclusion rests on the absence of contrary evidence rather than on a precise estimate. Crappie dominates the family numerically (`r Rn("Crappie")` of `r FamRow("Panfish / Sunfish")$Respondents` respondents), so the Panfish / Sunfish column will largely reflect crappie anglers. The separate Crappie and Bluegill / Sunfish columns let the reader check whether that matters for any given question.

### Catfish

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, "  ", caption.comparison, sep="")`

```{r catfishMotivation}
CreateFlex(GenusMeansTable(d, "Catfish", motivation.vars, l))
```

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.raked, "  ", caption.reversed, sep="")`

```{r catfishAttitude}
CreateFlex(GenusMeansTable(d, "Catfish", attitude.vars, l))
```

`r paste("Total days fished in Nebraska during 2025.", "  ", caption.means, "  ", caption.medians, "  ", caption.raked, sep="")`

```{r catfishEffort}
CreateFlex(GenusEffortTable(d, "Catfish"))
```

`r paste(caption.contrasts, sep="")`

```{r catfishContrasts}
CreateFlex(ContrastTable(dplyr::filter(family.tests, Family == "Catfish"), c(motivation.vars, attitude.vars), l))
```

`r paste("Days fished, same species comparisons.", "  ", caption.contrasts, sep="")`

```{r catfishEffortContrasts}
CreateFlex(EffortContrastTable(dplyr::filter(family.tests, Family == "Catfish")))
```

The three catfish species were the most homogeneous family tested (smallest adjusted p = `r FmtP(FamRow("Catfish")$MinP)` across `r FamRow("Catfish")$Tests` contrasts). Channel, blue and flathead catfish anglers report similar motivations, attitudes and effort, which supports treating catfish as a single constituency for programme-level purposes. Blue catfish (`r Rn("Blue catfish")` respondents) falls below the size floor and appears only within the family column; Channel catfish and Flathead catfish are also reported separately.

### Moronides

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, "  ", caption.comparison, sep="")`

```{r moronidesMotivation}
CreateFlex(GenusMeansTable(d, "Moronides", motivation.vars, l))
```

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.raked, "  ", caption.reversed, sep="")`

```{r moronidesAttitude}
CreateFlex(GenusMeansTable(d, "Moronides", attitude.vars, l))
```

`r paste("Total days fished in Nebraska during 2025.", "  ", caption.means, "  ", caption.medians, "  ", caption.raked, sep="")`

```{r moronidesEffort}
CreateFlex(GenusEffortTable(d, "Moronides"))
```

`r paste(caption.contrasts, sep="")`

```{r moronidesContrasts}
CreateFlex(ContrastTable(dplyr::filter(family.tests, Family == "Moronides"), c(motivation.vars, attitude.vars), l))
```

`r paste("Days fished, same species comparisons.", "  ", caption.contrasts, sep="")`

```{r moronidesEffortContrasts}
CreateFlex(EffortContrastTable(dplyr::filter(family.tests, Family == "Moronides")))
```

Striped bass, Wiper and White bass were not combined. Wiper and White bass anglers differ on `r FamRow("Moronides")$Differences` of the nine outcomes after adjustment: wiper anglers place more importance on the fishery-resource motivations (adjusted p = `r FamP("Moronides", "motivation_resource")`), agree more strongly with the size-of-fish attitude items (`r FamP("Moronides", "attitude_size")`), and agree less with the harvest items (`r FamP("Moronides", "attitude_harvest")`). The pattern is of wiper anglers as a size-oriented, release-inclined group and white bass anglers as a more harvest-oriented one, a distinction a combined Moronid column would erase. Wiper and White bass each exceed the size floor and receive their own columns; Striped bass (`r Rn("Striped bass")` respondents) does not, and appears in no column.

### Esocids

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, "  ", caption.comparison, sep="")`

```{r esocidMotivation}
CreateFlex(GenusMeansTable(d, "Esocids", motivation.vars, l))
```

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.raked, "  ", caption.reversed, sep="")`

```{r esocidAttitude}
CreateFlex(GenusMeansTable(d, "Esocids", attitude.vars, l))
```

`r paste("Total days fished in Nebraska during 2025.", "  ", caption.means, "  ", caption.medians, "  ", caption.raked, sep="")`

```{r esocidEffort}
CreateFlex(GenusEffortTable(d, "Esocids"))
```

`r paste(caption.contrasts, sep="")`

```{r esocidContrasts}
CreateFlex(ContrastTable(dplyr::filter(family.tests, Family == "Esocids"), c(motivation.vars, attitude.vars), l))
```

`r paste("Days fished, same species comparisons.", "  ", caption.contrasts, sep="")`

```{r esocidEffortContrasts}
CreateFlex(EffortContrastTable(dplyr::filter(family.tests, Family == "Esocids")))
```

Northern pike and Muskellunge / Tiger musky were not combined. Muskellunge anglers score higher on the physical and psychological motivations (adjusted p = `r FamP("Esocids", "motivation_pp")`), the fishery-resource motivations (`r FamP("Esocids", "motivation_resource")`) and the size-of-fish attitudes (`r FamP("Esocids", "attitude_size")`). With only `r Rn("Muskellunge / Tiger musky")` muskellunge respondents these estimates are imprecise, but the differences are large enough to clear the adjusted threshold regardless, and they point the same way: a small, highly engaged, size-focused muskellunge constituency that pike anglers do not describe well. Northern pike (`r Rn("Northern pike")` respondents) receives its own column; Muskellunge / Tiger musky does not meet the size floor and appears in no column.

## Group Selection Results

`r paste0("Test results and size rule for every candidate group. Tests is the number of species pairs times nine outcomes. Differences counts the tests with a family p below ", family.alpha, ". Family column is Yes only when the group may be combined and has at least ", min.group.n, " respondents.")`

```{r familyDisposition}
CreateFlex(FamilyDispositionTable(family.disp))
```

`r paste0("Size rule for each species in a candidate family. A species column is independent of whether its family is combined.")`

```{r speciesDisposition}
CreateFlex(SpeciesDispositionTable(d))
```

```{r bannerRuleCheck, echo=FALSE}
# D190: the hand-typed banner must equal what the rules produce. This stops the
# render rather than letting the two drift apart.
derived.banner <- DeriveBanner(d, family.disp)
stopifnot(
  identical(derived.banner$Column, banner.definition$Column),
  identical(derived.banner$Type, banner.definition$Type),
  identical(derived.banner$Members, banner.definition$Members)
)
```

```{r ch1Summary, echo=FALSE}
fd <- family.disp |> dplyr::filter(Multi)
fd_comb <- fd |> dplyr::filter(Combines)
fd_split <- fd |> dplyr::filter(!Combines)
Fam <- function(g) fd[fd$Group == g, ]
FamList <- function(x) paste0(x$Group, " (", x$Tests, " tests)", collapse = ", ")
MinPList <- function(x) paste(FmtP(x$MinP), collapse = ", ")
below_min <- sizeTbl |>
  dplyr::filter(Species %in% c("Striped bass", "Muskellunge / Tiger musky", "Blue catfish", "Yellow perch"))
stopifnot(nrow(below_min) == 4, all(below_min$Respondents < min.group.n))
```

Of the `r nrow(fd)` candidate families, `r nrow(fd_comb)` were combined: `r FamList(fd_comb)`, with smallest Bonferroni-adjusted p-values of `r MinPList(fd_comb)`. The `r nrow(fd_split)` that were not, `r fd_split$Group[1]` (`r fd_split$Differences[1]` of `r fd_split$Tests[1]` contrasts below `r family.alpha`, smallest `r FmtP(fd_split$MinP[1])`) and `r fd_split$Group[2]` (`r fd_split$Differences[2]` of `r fd_split$Tests[2]`, smallest `r FmtP(fd_split$MinP[2])`), failed for a similar reason: in each, one member (Wiper, Muskellunge) is more size-focused and places more importance on fishery-resource motivations than its relative. Wiper (`r Rn("Wiper")` respondents), White bass (`r Rn("White bass")`) and Northern pike (`r Rn("Northern pike")`) meet the `r min.group.n`-respondent minimum and stand alone. Striped bass (`r Rn("Striped bass")`) and Muskellunge / Tiger musky (`r Rn("Muskellunge / Tiger musky")`) do not, and because their families were not combined they appear in no column; their respondents remain in the Overall column only. Blue catfish (`r Rn("Blue catfish")`) and Yellow perch (`r Rn("Yellow perch")`) also fall below the minimum but are carried within the Catfish and Panfish / Sunfish family columns. The final banner has `r nrow(banner.definition)` columns: `r sum(banner.definition$Type == "Family")` family columns and `r sum(banner.definition$Type != "Family")` species columns.

## Final Preferred Groups

`r paste0("There are ", nrow(banner.definition), " preferred groups: ", sum(banner.definition$Type == "Family"), " family groups, ", sum(banner.definition$Type == "Species"), " species reported alongside the family group that contains them, and ", sum(banner.definition$Type == "Split"), " species whose family was not combined. Every table in the chapters that follow uses these columns. Respondents outside every column keep their place in the Overall column of every table.")`

`r paste(caption.banner, "  ", caption.raked, sep="")`

```{r bannerSizes}
CreateFlex(FinalGroupsTable(d, popTotalAll))
```

`r paste0("Preferred species outside every preferred group. These ", nBannerExcluded, " respondents remain in the Overall column of every table but receive no preferred-group column.")`

```{r bannerExclusions}
CreateFlex(BannerExclusionTable(d))
```

`r paste0("The preferred groups cover ", format(nBanner, big.mark=","), " distinct respondents of the ", format(nrow(d), big.mark=","), " in the analysis sample; ", nBannerExcluded, " do not appear in any preferred-group column. Because family columns contain their own species columns, the respondent counts in the table above add to more than ", format(nBanner, big.mark=","), " and should not be totalled.")`

The family columns are the appropriate reference for programme-level questions, where the aim is to characterise catfish or panfish anglers as a whole; they carry the largest samples and the narrowest confidence intervals. The species columns nested beneath them show whether the family average conceals variation worth acting on: where a species column departs from its family, the family figure is a blend and should be quoted with that in mind. Wiper, White bass and Northern pike stand alone because the evidence in this chapter says their anglers should not be merged with their relatives. Because a respondent can appear in both a family column and a species column, columns are not additive across the banner, and a difference between a species and its own family is damped by the respondents they share and should not be over-read.

`r run_pagebreak()`

# Chapter 2: Species-Linked Scale Questions

```{r d4Setup}
# Universe for the battery: the report universe, with each item keeping its own
# non-missing filter as the crosstab report does (2025CrossTabReport.rmd L768).
nD4Any <- sum(rowSums(!is.na(d[, d4.items])) > 0)
d4.categories <- levels(d[[d4.items[1]]])

stopifnot(
  length(d4.items) == 13,
  all(d4.items %in% names(d)),
  length(d4.categories) == 5
)
```

`r paste0("*", trimws(GetQuestion(q, D4, 2025)), "*")`

`r paste0("Each item is reported in its own table. Rows are the preferred groups from Chapter 1, with individual species indented beneath the family group that contains them; family rows include the respondents in their species rows, so rows overlap and must not be totalled. Of the analysis sample of ", format(nrow(d), big.mark=","), " anglers, ", format(nD4Any, big.mark=","), " answered at least one item in this battery.")`

`r paste0("This battery diverges from the 2025 Crosstabs report by more than the rest of the report does. The preferred-species question was not a strict gate on the battery in the delivered data: across all ", format(nAll2025, big.mark=","), " respondents to the 2025 survey, ", format(nD4AnyAll2025, big.mark=","), " answered at least one item in this battery, of whom ", format(nD4AnyNoB1, big.mark=","), " left the preferred-species question blank. Those respondents are outside this report's universe, so the Overall row here rests on fewer respondents than the corresponding Crosstabs report table.")`

```{r ch2Helpers, echo=FALSE}
# Group-by-item means for the chapter narrative, from the same builder as the
# tables, so every quoted figure is live. The closing section claims a group
# differs from the overall only when the group's 95% interval lies entirely
# outside the Overall interval (D4SepHi / D4SepLo); every claim is asserted
# here so the render stops if the data stop supporting it.
d4.tt <- setNames(
  lapply(d4.items, function(i) D4MeansLong(d, i, includeOverall = TRUE)),
  d4.items
)
d4.mat <- sapply(d4.tt, function(x) setNames(x$Mean, x$RawLabel))
d4.grp <- d4.mat[rownames(d4.mat) != "Overall", , drop = FALSE]
D4M <- function(g, i) sprintf("%.1f", d4.mat[g, i])
D4Rng <- function(i) sprintf("%.1f to %.1f", min(d4.grp[, i]), max(d4.grp[, i]))
D4Top <- function(i, k = 1) names(sort(d4.grp[, i], decreasing = TRUE))[k]
D4Bot <- function(i, k = 1) names(sort(d4.grp[, i]))[k]
D4N <- function(g) { x <- d4.tt$D4a; x$N[x$RawLabel == g] }
D4SepHi <- function(i) {
  t <- d4.tt[[i]]; ov <- t[t$RawLabel == "Overall", ]; g <- t[t$RawLabel != "Overall", ]
  g$RawLabel[g$Mean - g$CI > ov$Mean + ov$CI]
}
D4SepLo <- function(i) {
  t <- d4.tt[[i]]; ov <- t[t$RawLabel == "Overall", ]; g <- t[t$RawLabel != "Overall", ]
  g$RawLabel[g$Mean + g$CI < ov$Mean - ov$CI]
}
d4.claim <- function(i, hi = character(), lo = character(),
                     hi_only = FALSE, lo_only = FALSE) {
  stopifnot(all(hi %in% D4SepHi(i)), all(lo %in% D4SepLo(i)))
  if (hi_only) stopifnot(setequal(D4SepHi(i), hi))
  if (lo_only) stopifnot(setequal(D4SepLo(i), lo))
  invisible(TRUE)
}
# Overall mean of one item above the overall mean of another, intervals apart
D4OvApart <- function(iHi, iLo) {
  a <- d4.tt[[iHi]][d4.tt[[iHi]]$RawLabel == "Overall", ]
  b <- d4.tt[[iLo]][d4.tt[[iLo]]$RawLabel == "Overall", ]
  a$Mean - a$CI > b$Mean + b$CI
}

stopifnot(
  setequal(names(sort(d4.mat["Overall", ]))[1:2], c("D4b", "D4h")),
  D4OvApart("D4d", "D4c"), D4OvApart("D4e", "D4b"),
  all(d4.grp[, "D4c"] > 3), all(d4.grp[, "D4d"] > 3),
  d4.mat["Walleye / Sauger", "D4a"] < 3
)
d4.claim("D4c", hi = "Wiper", hi_only = TRUE, lo_only = TRUE)
d4.claim("D4d", hi_only = TRUE, lo_only = TRUE)
d4.claim("D4a", hi = c("Channel catfish", "White bass", "Trout"), lo = "Walleye / Sauger",
         hi_only = TRUE, lo_only = TRUE)
d4.claim("D4f", hi = "Walleye / Sauger", lo = "Bluegill / Sunfish", hi_only = TRUE)
d4.claim("D4g", hi = "Walleye / Sauger", lo = c("Bass", "Wiper"), hi_only = TRUE)
d4.claim("D4h", hi = c("Walleye / Sauger", "Wiper"), lo = c("Bass", "Bluegill / Sunfish"),
         hi_only = TRUE)
d4.claim("D4e", hi = c("Bass", "Wiper"))
d4.claim("D4i", hi = "Wiper", hi_only = TRUE)
d4.claim("D4j", hi = "Bluegill / Sunfish", lo = c("Northern pike", "No preference"),
         hi_only = TRUE, lo_only = TRUE)
d4.claim("D4b", lo = "Northern pike", lo_only = TRUE)
d4.claim("D4l", hi = "Bluegill / Sunfish")
d4.claim("D4m", lo = "Bluegill / Sunfish")
# Non-separations the text relies on
stopifnot(
  !("Walleye / Sauger" %in% unlist(lapply(c("D4i", "D4j", "D4k", "D4l"),
                                          function(i) c(D4SepHi(i), D4SepLo(i))))),
  !("Northern pike" %in% c(D4SepHi("D4c"), D4SepHi("D4m"))),
  !any(c("White bass", "Trout", "Channel catfish") %in%
         unlist(lapply(c("D4b", "D4c", "D4d", "D4e", "D4g"),
                       function(i) c(D4SepHi(i), D4SepLo(i))))),
  sum(vapply(d4.items,
             function(i) "No preference" %in% c(D4SepHi(i), D4SepLo(i)),
             logical(1))) == 1,
  "No preference" %in% D4SepLo("D4j"),
  D4N("No preference") < 0.2 * Rn("I do not prefer any particular type of fish")
)
```

The thirteen statements fall into three themes. Five ask about satisfaction: with fishing success (D4a) and with the size and number of fish caught and the size and number allowed to be harvested (D4i to D4l); Chapter 4 returns to those five as a set. Five ask about regulation and the trade-off between size and harvest: support for regulations that increase size (D4c) or numbers (D4d), willingness to take smaller fish for more of them (D4b) or fewer fish for larger ones (D4e), and whether harvest opportunity matters more than size (D4g). Three ask about the fishery and access to it: whether the preferred fish is becoming harder to catch (D4f), whether the angler travels too far (D4h) and whether there are enough places to fish (D4m). Each item is presented with its table, a stacked-percentage figure, a figure of group means ordered from lowest to highest, and a comparison with 2018 for any group whose change is large enough to show. The closing section of the chapter reads across the items by preferred group.

`r paste(caption.d4gate, sep="")`

## `r ItemQuestionText("D4a", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4a}
CreateFlex(D4ItemTable(d, "D4a", d4.categories))
```

```{r d4aPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4a", d4.categories, titleText = ItemQuestionText("D4a", q))
```

```{r d4aMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4a", titleText = ItemQuestionText("D4a", q))
```

```{r d4aSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4a", titleText = ItemQuestionText("D4a", q))
```

`r paste0("For this item, White bass, Trout, and Channel catfish anglers report the highest satisfaction, averaging 3.7, 3.6, and 3.6 on the five-point scale, with 62%, 58%, and 57% agreeing or strongly agreeing and no more than 17% disagreeing. Walleye/Sauger anglers -- the largest single preferred group in the survey -- report the lowest satisfaction, averaging 2.8, and are the only group where more anglers disagree (40%) than agree (28%); Flathead catfish anglers, at 3.0, divide evenly (36% each way). The gap between Walleye/Sauger and the three highest groups is roughly three-quarters of a point or more, and may point to a difference in how reliably each species can be caught rather than a difference in how much anglers enjoy the pursuit itself. Within families the widest contrast is among catfish, where Channel catfish anglers (3.6) are considerably more satisfied than Flathead catfish anglers (3.0); the two bass species and the two panfish species each fall within about a tenth of a point of each other.")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. Within 2025, one further pattern stands out: anglers with no single preferred species report above-average satisfaction (3.4, against 3.2 overall) and the largest neutral share of any group (45%), and neutral responses are common across the board -- roughly three in ten anglers in most groups take neither side -- so the group differences described above rest on the balance between agreement and disagreement rather than on lopsided views within any group.")`

## `r ItemQuestionText("D4b", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4b}
CreateFlex(D4ItemTable(d, "D4b", d4.categories))
```

```{r d4bPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4b", d4.categories, titleText = ItemQuestionText("D4b", q))
```

```{r d4bMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4b", titleText = ItemQuestionText("D4b", q))
```

```{r d4bSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4b", titleText = ItemQuestionText("D4b", q))
```

`r paste0("Willingness to harvest smaller fish in exchange for more of them is low overall, averaging 2.8, with 38% disagreeing and 24% agreeing. Smallmouth bass and White bass anglers report the highest agreement (3.05 each), and Smallmouth bass anglers are the only group where more agree (40%) than disagree (33%). Northern pike anglers report the lowest (2.4), with 59% disagreeing and only 8% agreeing; Wiper anglers (58% disagree, 31% agree) and Flathead catfish anglers (51% disagree, 27% agree) also disagree far more often than they agree. The bass family shows the widest within-family spread, with Smallmouth bass anglers (3.1) well above Largemouth bass anglers (2.7).")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. Within 2025, what separates some groups is how many take no side: 58% of anglers with no single preferred species and 48% of Bluegill/Sunfish anglers are neutral, against 11% of Wiper anglers, so a middling average can reflect very different response patterns.")`

## `r ItemQuestionText("D4c", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4c}
CreateFlex(D4ItemTable(d, "D4c", d4.categories))
```

```{r d4cPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4c", d4.categories, titleText = ItemQuestionText("D4c", q))
```

```{r d4cMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4c", titleText = ItemQuestionText("D4c", q))
```

```{r d4cSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4c", titleText = ItemQuestionText("D4c", q))
```

`r paste0("Support for regulations to increase the size of the preferred fish is high in every group, averaging 3.8 overall, with 66% agreeing and 12% disagreeing. Wiper anglers report the highest support (4.3; 87% agree, 5% disagree), followed by Northern pike anglers (4.05; 77% agree). Trout anglers report the lowest (3.6), alongside Walleye/Sauger and Flathead catfish anglers (3.6 each), though even in these groups more than half agree.")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. What distinguishes the groups in 2025 is the firmness of the support: in every group, supporters outnumber opponents by at least three to one, and Wiper and Northern pike anglers are the least likely to take neither side (8% and 9% neutral), while 35% of anglers with no single preferred species and 31% of Channel catfish anglers do.")`

## `r ItemQuestionText("D4d", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4d}
CreateFlex(D4ItemTable(d, "D4d", d4.categories))
```

```{r d4dPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4d", d4.categories, titleText = ItemQuestionText("D4d", q))
```

```{r d4dMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4d", titleText = ItemQuestionText("D4d", q))
```

```{r d4dSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4d", titleText = ItemQuestionText("D4d", q))
```

`r paste0("Support for regulations to increase the numbers of the preferred fish is high in every group, averaging 3.9 overall, with 73% agreeing and 7% disagreeing. The spread across groups is narrow: Wiper anglers report the highest support (4.1; 81% agree), while Crappie (3.7) and Panfish/Sunfish anglers (3.8) report the lowest, though 69% and 71% of them agree. Set against the previous item, most groups support numbers-focused regulation more strongly than size-focused regulation; Wiper and Northern pike anglers are the exceptions, backing size rules somewhat more strongly, and Crappie anglers rate the two about equally. That tilt toward numbers over size may indicate that, for most anglers, catching fish at all matters more than catching bigger ones.")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. Within 2025, the share who disagree is 0% after rounding among both Smallmouth bass anglers and anglers with no single preferred species, against 12% of Northern pike and Flathead catfish anglers, so the differences in averages reflect differences in how strongly anglers agree more than any split between supporters and opponents.")`

## `r ItemQuestionText("D4e", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4e}
CreateFlex(D4ItemTable(d, "D4e", d4.categories))
```

```{r d4ePercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4e", d4.categories, titleText = ItemQuestionText("D4e", q))
```

```{r d4eMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4e", titleText = ItemQuestionText("D4e", q))
```

```{r d4eSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4e", titleText = ItemQuestionText("D4e", q))
```

`r paste0("Willingness to harvest fewer fish in exchange for larger fish averages 3.6 overall, with 52% agreeing and 14% disagreeing. Wiper anglers report the highest willingness (4.2; 82% agree, 3% disagree), followed by the bass groups (Smallmouth bass 3.9, Largemouth bass 3.8; 63% to 67% agree). Bluegill/Sunfish and White bass anglers report the lowest (3.2 each), though for both the difference is mostly neutral rather than opposed responses: 49% and 56% of them take neither side, and 37% and 29% agree.")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. The 2025 pattern is internally consistent with the harvest-versus-size question two items later: the groups most willing to sacrifice numbers for size here -- Wiper and both bass species -- are the same ones that lean toward size over harvest opportunity there, while Walleye/Sauger anglers, among the least willing here, lean toward harvest opportunity. No group falls below neutral on average, so the differences are in degree of willingness, not direction.")`

## `r ItemQuestionText("D4f", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4f}
CreateFlex(D4ItemTable(d, "D4f", d4.categories))
```

```{r d4fPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4f", d4.categories, titleText = ItemQuestionText("D4f", q))
```

```{r d4fMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4f", titleText = ItemQuestionText("D4f", q))
```

```{r d4fSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4f", titleText = ItemQuestionText("D4f", q))
```

`r paste0("Agreement that the preferred fish is becoming harder to catch averages 3.3 overall, with 45% agreeing and 20% disagreeing. Walleye/Sauger anglers report the highest agreement (3.6; 56% agree), followed by Flathead catfish (3.5) and Northern pike anglers (3.5; 60% agree, the highest agree share of any group). Bluegill/Sunfish anglers report the lowest (2.6; 46% disagree, 16% agree) and are joined below the scale midpoint only by Channel catfish anglers (3.0). The within-family spreads are wide for panfish (Bluegill/Sunfish 2.6, Crappie 3.3) and catfish (Channel catfish 3.0, Flathead catfish 3.5).")`

`r paste0("Agreement that the preferred fish has become harder to catch rose modestly across all anglers between 2018 and 2025, from 3.2 to 3.3 -- one of only two items in this battery, along with the places-to-fish item at the end, where the change across all anglers is what stands out between years. No individual preferred group's change was large enough to appear in the figure above, which suggests a broad, shallow drift toward agreement rather than a sharp movement concentrated in any one group.")`

## `r ItemQuestionText("D4g", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4g}
CreateFlex(D4ItemTable(d, "D4g", d4.categories))
```

```{r d4gPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4g", d4.categories, titleText = ItemQuestionText("D4g", q))
```

```{r d4gMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4g", titleText = ItemQuestionText("D4g", q))
```

```{r d4gSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4g", titleText = ItemQuestionText("D4g", q))
```

`r paste0("Views on whether harvest opportunity matters more than fish size are divided, averaging 3.0 overall, with 36% agreeing and 30% disagreeing. Trout (3.3) and Walleye/Sauger anglers (3.3) lean furthest toward harvest opportunity. Wiper anglers lean furthest toward size (2.3; 60% disagree, 25% agree), followed by Smallmouth bass anglers (2.4; 53% disagree, 13% agree) and the bass family as a whole (2.7; 41% disagree, 24% agree).")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. Within 2025, half of the anglers with no single preferred species (50%) take neither side, the largest neutral share of any group, against 15% of Wiper anglers; the two groups' averages sit at different ends of the range for different reasons, with a majority of Wiper anglers disagreeing (60%) and the no-preference group split between disagreeing (28%) and agreeing (22%).")`

## `r ItemQuestionText("D4h", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4h}
CreateFlex(D4ItemTable(d, "D4h", d4.categories))
```

```{r d4hPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4h", d4.categories, titleText = ItemQuestionText("D4h", q))
```

```{r d4hMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4h", titleText = ItemQuestionText("D4h", q))
```

```{r d4hSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4h", titleText = ItemQuestionText("D4h", q))
```

`r paste0("Agreement that the angler has to travel too far to fish for the preferred fish averages 2.8 overall, with 43% disagreeing and 25% agreeing. Wiper anglers report the highest agreement (3.4; 55% agree, 18% disagree), with the widest margin of agreement over disagreement of any group; Northern pike (3.1), White bass (3.1), and Trout anglers (3.1) follow. Bluegill/Sunfish anglers report the lowest (2.1; 75% disagree, 12% agree), followed by Flathead catfish (2.4), Channel catfish (2.4), and Largemouth bass anglers (2.5).")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. The travel pattern partly lines up with the places-to-fish item at the end of this battery: Northern pike, Wiper, and Trout anglers sit at or near the top of both, while Bluegill/Sunfish and Channel catfish anglers sit at or near the bottom of both, suggesting that travel distance and the perceived shortage of places to fish may be two readings of the same underlying access picture for these species. Flathead catfish anglers are the exception, near the bottom on travel (2.4) but second from the top on places to fish (3.3).")`

## `r ItemQuestionText("D4i", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4i}
CreateFlex(D4ItemTable(d, "D4i", d4.categories))
```

```{r d4iPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4i", d4.categories, titleText = ItemQuestionText("D4i", q))
```

```{r d4iMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4i", titleText = ItemQuestionText("D4i", q))
```

```{r d4iSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4i", titleText = ItemQuestionText("D4i", q))
```

`r paste0("Satisfaction with the size of the preferred fish caught averages 3.3 overall, with 46% agreeing and 21% disagreeing. Wiper anglers report the highest satisfaction (4.0; 80% agree, 7% disagree), followed by White bass anglers (3.6). Northern pike anglers report the lowest (3.0), the only group averaging below the scale midpoint, followed by Largemouth bass anglers (3.0).")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. Within 2025, how the groups arrive at their averages differs as much as the averages themselves: Northern pike anglers split into opposing camps (43% agree, 37% disagree, only a fifth neutral), while half of the anglers with no single preferred species (50%), 44% of White bass anglers, and four in ten Trout anglers (41%) take no side at all.")`

## `r ItemQuestionText("D4j", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4j}
CreateFlex(D4ItemTable(d, "D4j", d4.categories))
```

```{r d4jPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4j", d4.categories, titleText = ItemQuestionText("D4j", q))
```

```{r d4jMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4j", titleText = ItemQuestionText("D4j", q))
```

```{r d4jSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4j", titleText = ItemQuestionText("D4j", q))
```

`r paste0("Satisfaction with the size of the preferred fish that may be harvested averages 3.5 overall, with 56% agreeing and 10% disagreeing. Bluegill/Sunfish anglers report the highest satisfaction (3.9; 69% agree, 3% disagree), followed by White bass anglers (3.8) and Smallmouth bass anglers (3.7). Northern pike anglers report the lowest (3.0; 38% agree, 40% disagree) and are the only group where disagreement is at least as common as agreement; anglers with no single preferred species (3.2) and Wiper anglers (3.3) follow.")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. Compared with the previous item, nearly every group rates the size they are allowed to harvest at least as favorably as the size they actually catch; Wiper anglers are the one clear exception, rating the size they catch (4.0) above the size they are allowed to keep (3.3), while Northern pike anglers rate the two about equally (3.0 each), which may hint that where Wiper anglers have a complaint, it is with the rules rather than the fish.")`

## `r ItemQuestionText("D4k", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4k}
CreateFlex(D4ItemTable(d, "D4k", d4.categories))
```

```{r d4kPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4k", d4.categories, titleText = ItemQuestionText("D4k", q))
```

```{r d4kMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4k", titleText = ItemQuestionText("D4k", q))
```

```{r d4kSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4k", titleText = ItemQuestionText("D4k", q))
```

`r paste0("Satisfaction with the number of the preferred fish caught averages 3.2 overall, with 46% agreeing and 27% disagreeing. Bluegill/Sunfish anglers report the highest satisfaction (3.6; 70% agree, 20% disagree), followed by Channel catfish and Wiper anglers (3.4 each). Flathead catfish anglers report the lowest (2.8; 50% disagree, 38% agree), the only group averaging below the scale midpoint, followed by Walleye/Sauger anglers (3.0).")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. The 2025 ranking partly mirrors the overall fishing-success item at the top of this battery -- Channel catfish, White bass, and Trout anglers in the upper part of both, Walleye/Sauger and Flathead catfish anglers near the bottom of both -- which may indicate that when anglers judge their overall success, the number of fish caught weighs at least as heavily as their size.")`

## `r ItemQuestionText("D4l", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4l}
CreateFlex(D4ItemTable(d, "D4l", d4.categories))
```

```{r d4lPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4l", d4.categories, titleText = ItemQuestionText("D4l", q))
```

```{r d4lMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4l", titleText = ItemQuestionText("D4l", q))
```

```{r d4lSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4l", titleText = ItemQuestionText("D4l", q))
```

`r paste0("Satisfaction with the number of the preferred fish that may be harvested averages 3.5 overall, with 56% agreeing and 10% disagreeing. Bluegill/Sunfish anglers report the highest satisfaction (3.9; 66% agree, 5% disagree), followed by Crappie, Smallmouth bass, and White bass anglers (3.7 each). Northern pike anglers report the lowest (3.15; 47% agree, 30% disagree), followed by Wiper anglers (3.2), 46% of whom take neither side.")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. Compared with the number caught in the previous item, every group rates the number it is allowed to harvest at least as favorably except Wiper anglers (3.2 allowed, against 3.4 caught) and, marginally, Northern pike anglers (3.15 allowed, against 3.21 caught); Wiper anglers also rate the size they may keep below the size they catch, so their lower ratings for what may be kept appear on both size and number.")`

## `r ItemQuestionText("D4m", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4m}
CreateFlex(D4ItemTable(d, "D4m", d4.categories))
```

```{r d4mPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4m", d4.categories, titleText = ItemQuestionText("D4m", q))
```

```{r d4mMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4m", titleText = ItemQuestionText("D4m", q))
```

```{r d4mSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4m", titleText = ItemQuestionText("D4m", q))
```

`r paste0("Agreement that there are not enough places to fish for the preferred fish averages 3.1 overall, with 36% agreeing and 34% disagreeing. Northern pike anglers report the highest agreement (3.5; 62% agree, 28% disagree), followed by Flathead catfish (3.3), Wiper (3.3), Trout, and Smallmouth bass anglers (3.3 each). Bluegill/Sunfish anglers report the lowest (2.6; 56% disagree, 24% agree), followed by Channel catfish anglers (2.6).")`

`r paste0("Flathead catfish anglers' agreement rose sharply between 2018 and 2025, from 2.5 to 3.3 -- the only group whose change appears in any of the 2018-2025 figures for this battery. Agreement across all anglers also crept upward between the two years, from 2.9 to 3.1, another instance, like the difficulty-of-catching item earlier, where the shift shows up broadly rather than only within individual preferred groups.")`

## Reading Across the Items

This section reads across the thirteen items by preferred group, under the same rule as Chapters 3 and 4: a group is described as differing from the overall only when its 95 percent confidence interval lies entirely outside the Overall interval. The per-item paragraphs above describe the printed means without that screen.

Support for regulation is the most uniform result in the battery. Every preferred group's mean sits on the agree side for regulations to increase the size of its preferred fish (group means `r D4Rng("D4c")`, overall `r D4M("Overall", "D4c")`) and for regulations to increase their numbers (`r D4Rng("D4d")`, overall `r D4M("Overall", "D4d")`). Overall, number regulations draw more support than size regulations, with the two intervals apart, and the only group to separate from the overall on either item is Wiper, above it on size regulations. The trade-off items are less generous. Willingness to accept smaller fish in exchange for more of them (`r D4M("Overall", "D4b")`) is, with travelling too far, one of the two lowest-scoring statements in the battery, while willingness to harvest fewer fish for larger ones scores `r D4M("Overall", "D4e")`, again with the intervals apart. Anglers want more and bigger fish, and will give up harvest to gain size more readily than they will give up size to gain harvest.

Walleye / Sauger anglers, the largest preferred group, are the only group below the overall on satisfaction with fishing success (`r D4M("Walleye / Sauger", "D4a")` against `r D4M("Overall", "D4a")` overall, and below the neutral point) and the only group above it on saying their preferred fish is becoming harder to catch (`r D4M("Walleye / Sauger", "D4f")`). They are above the overall on travelling too far (`r D4M("Walleye / Sauger", "D4h")`) and are the only group above it on ranking harvest opportunity ahead of size (`r D4M("Walleye / Sauger", "D4g")`). On none of the four size and number satisfaction items do they separate from the overall, so the discontent is with catch rates and access rather than with harvest rules; the paired comparison in Chapter 4 places it more precisely, in the number of fish caught. For a group of this size, a success-satisfaction mean below the neutral point is the most consequential single figure in the chapter.

Wiper anglers are the battery's size-oriented outlier. They are the only group above the overall on support for size regulations (`r D4M("Wiper", "D4c")`) and on satisfaction with the size of fish they catch (`r D4M("Wiper", "D4i")`), above it on willingness to harvest fewer fish for larger ones (`r D4M("Wiper", "D4e")`) and on travelling too far (`r D4M("Wiper", "D4h")`), and below it on ranking harvest opportunity ahead of size (`r D4M("Wiper", "D4g")`). Their rating of the size they are allowed to harvest (`r D4M("Wiper", "D4j")`) does not separate from the overall by this screen, but the sharper paired comparison in Chapter 4 shows them to be the only group that rates the size it catches above the size it may keep. Read with Chapter 1, where Wiper anglers separated from White bass anglers on exactly these attitudes, this is a constituency that strongly supports size regulation and rates what the rules let it keep below what it catches, a tension worth having in view when wiper length limits are reviewed. The group has `r D4N("Wiper")` respondents in this battery, so its intervals are wide.

Northern pike anglers are below the overall on satisfaction with the size they are allowed to harvest (`r D4M("Northern pike", "D4j")` against `r D4M("Overall", "D4j")`) and are the only group below it on willingness to trade size for numbers (`r D4M("Northern pike", "D4b")`). Their means on size regulations (`r D4M("Northern pike", "D4c")`) and on not having enough places to fish (`r D4M("Northern pike", "D4m")`) are among the highest printed, but on `r D4N("Northern pike")` respondents neither clears the interval screen. What the screen does support is a size-focused reading: a group unwilling to give up size and dissatisfied with the size the rules let it keep.

Bass anglers, the second-largest preferred group, favour size over harvest: above the overall on harvesting fewer fish for larger ones (`r D4M("Bass", "D4e")`) and below it on ranking harvest ahead of size (`r D4M("Bass", "D4g")`). They are also below the overall on travelling too far (`r D4M("Bass", "D4h")` against `r D4M("Overall", "D4h")`). Bluegill / Sunfish anglers are the battery's least constrained constituency: above the overall on satisfaction with the size (`r D4M("Bluegill / Sunfish", "D4j")`) and number (`r D4M("Bluegill / Sunfish", "D4l")`) they are allowed to harvest, and below it on travelling too far (`r D4M("Bluegill / Sunfish", "D4h")`), on lacking places to fish (`r D4M("Bluegill / Sunfish", "D4m")`) and on finding their fish harder to catch (`r D4M("Bluegill / Sunfish", "D4f")`), on `r D4N("Bluegill / Sunfish")` respondents. White bass, Trout and Channel catfish anglers are above the overall on satisfaction with fishing success (`r D4M("White bass", "D4a")`, `r D4M("Trout", "D4a")` and `r D4M("Channel catfish", "D4a")`) without separating on any of the regulation items.

Anglers with no single preferred fish separate from the overall on one item only, below it on satisfaction with the size they are allowed to harvest (`r D4M("No preference", "D4j")`), and, as the item paragraphs note, carry the largest neutral shares. Their row deserves a caution of its own: because the statements presuppose a preferred fish, only `r D4N("No preference")` of the `r Rn("I do not prefer any particular type of fish")` anglers in this group answered the first item, so the row describes a small, self-selected subset of them rather than the group as a whole.

# Chapter 3: Crosstabs by Preferred Species

```{r ch3Setup}
# Layout helpers. In officedown a block_section describes the section that ENDS
# at that point, so a wide table is bracketed by a portrait break before it and
# a landscape break after it (D43).
sect_portrait <- function() {
  block_section(prop_section(
    page_size = page_size(orient = "portrait"),
    type = "nextPage"
  ))
}
sect_landscape <- function() {
  block_section(prop_section(
    page_size = page_size(orient = "landscape"),
    type = "nextPage"
  ))
}

# Select-all field sets, selected exactly as 2025CrossTabReport.rmd L247 does.
# Several A4 fields carry no 2025 data; they contribute nothing and drop out of
# the percentage calculation on their own, as they do in the crosstab report.
a4.fields <- d %>% dplyr::select(contains("A4")) %>% select(-contains("Answered")) %>% names()
a5.fields <- d %>% dplyr::select(contains("A5")) %>% select(-contains("Answered")) %>% names()
a6.fields <- d %>% dplyr::select(contains("A6")) %>% select(-contains("Answered")) %>% names()

# Sub-scale membership drives the battery tables (D88). Read here rather than
# in getData so Chapter 3's inputs stay in one place.
s <- read.csv(file = "../../Data/DataAggregation1/Scales.csv")

# The tournament count is relabeled exactly as 2025CrossTabReport.rmd L205 does.
dTourney <- d %>%
  mutate(fishedTourney = factor(
    if_else(fishedTourney, "Fished Tournaments", "No Tournaments"),
    levels = c("No Tournaments", "Fished Tournaments")
  ))

# Daggers mark items reversed within the named scale, read from Scales.csv.
Ch3ItemLabels <- function(fields, scaleName = NULL) {
  rev <- if (is.null(scaleName)) {
    character(0)
  } else {
    unique(s$Field[s$ScaleName == scaleName & s$Reversed])
  }
  vapply(
    fields, Ch3ItemLabel, character(1),
    codebook = q, reversedFields = rev, USE.NAMES = FALSE
  )
}

c2.fields <- d %>% dplyr::select(contains("C2")) %>% select(-contains("Answered")) %>% names()
q31.fields <- d %>% dplyr::select(contains("Q31")) %>% select(-contains("Answered")) %>% names()
e1.fields <- d %>% dplyr::select(contains("E1")) %>% select(-contains("Answered")) %>% names()

stopifnot(
  all(c(a4.fields, a5.fields, a6.fields) %in% names(d)),
  nrow(s) > 0,
  sum(!is.na(dTourney$fishedTourney)) == sum(!is.na(d$fishedTourney)),
  # Every battery item must land in exactly one table: a sub-scale table or
  # the unassigned-items table that follows it.
  length(c2.fields) == 17,
  length(q31.fields) == 12,
  length(e1.fields) == 16
)
```

`r paste0("This chapter crosstabs the remaining survey questions by preferred group. Questions appear in the order they are reported in the 2025 Crosstabs report, and each question keeps the universe and the derived variables that report uses; only the columns of the original crosstabs -- residency, gender, and age -- are replaced by the preferred groups. ", caption.ch3rows)`

`r paste0("Two conventions for the sample size are used. Where every response column of a table shares one denominator, a single N column reports it. Where each column carries its own universe -- a battery item with its own missingness, a scale score with its completeness gate, or an indicator computed on its own subset -- the count appears inside each cell after the confidence interval. N is the raw unweighted respondent count in both cases.")`

<!--
There is no visualizations chapter. Step 4 of the plan produces figures that are
interspersed within Chapters 1-3 next to the questions they illustrate (D34).
Chapter 3 figures are held until the tables have been reviewed (D91).
-->

In the text of this chapter, a difference between a preferred group and the overall estimate is described only when the group's 95 percent confidence interval lies entirely outside the Overall interval. That screen is conservative: modest differences, and most differences involving small groups, will fail it, so an unmentioned group is not shown to be typical — it is merely not shown to differ.

```{r ch3TextHelpers, echo=FALSE}
# Universes shared by the section narratives and the section tables. Moved here
# from their section chunks so the narrative, which precedes each table, can
# quote live values from the same objects.

# Universe for the A17 combination columns copied from 2025CrossTabReport.rmd
# L317: respondents who answered both parts and used at least one area type.
dAccess <- d %>%
  filter(!is.na(A17Pub_corrected) & !is.na(A17Priv_corrected)) %>%
  filter(!(A17Pub_corrected == "No" & A17Priv_corrected == "No"))

# Guided-trip indicator construction copied from 2025CrossTabReport.rmd L563.
dHiredGuide <- d %>%
  mutate(
    hiredNE      = if_else(is.na(hiredGuide), NA, !is.na(Q18a) & Q18a > 0),
    hiredOutside = if_else(is.na(hiredGuide), NA, !is.na(Q18b) & Q18b > 0),
    hiredNEonly  = if_else(is.na(hiredGuide), NA, hiredNE & !hiredOutside),
    hiredOutOnly = if_else(is.na(hiredGuide), NA, hiredOutside & !hiredNE),
    hiredBoth    = if_else(is.na(hiredGuide), NA, hiredNE & hiredOutside),
    hiredAny     = if_else(is.na(hiredGuide), NA, hiredNE | hiredOutside)
  )

# Days universe copied from 2025CrossTabReport.rmd L976: a total is only used
# when every month was answered.
dDays <- d %>% filter(!is.na(C1Total_days) & C1_AnsweredAll == TRUE)

# Long tables behind the narratives, built by the same functions as the
# tables. A difference is claimed in the text only when the group interval
# lies entirely outside the Overall interval (SepHi / SepLo); every claim is
# asserted below, by rule rather than by value, so the render stops if the
# data stop supporting the text.
ch3.t <- list(
  a11      = Ch3RateLong(d, "A11", "Yes"),
  a12      = Ch3RateLong(d %>% filter(A11 == "Yes"), "A12", "Yes"),
  a10      = Ch3RateLong(d, "A10", "Yes"),
  tourn    = Ch3RateLong(dTourney, "fishedTourney", "Fished Tournaments"),
  tournmean = Ch3MeanLong(d %>% filter(A13_corrected > 0), "A13_corrected"),
  q11o     = Ch3RateLong(d %>% filter(!is.na(Q11)), "Q11", "Often"),
  q11n     = Ch3RateLong(d %>% filter(!is.na(Q11)), "Q11", "Never"),
  pub      = Ch3RateLong(dAccess, "A17justPub", "Yes"),
  both     = Ch3RateLong(dAccess, "A17both", "Yes"),
  a7med    = Ch3MedianLong(d, "A7_miles"),
  a8med    = Ch3MedianLong(d, "A8_miles"),
  a9       = Ch3MeanLong(d, "A9"),
  q16      = Ch3RateLong(d %>% filter(!is.na(Q16)), "Q16", "Yes"),
  e7       = Ch3RateLong(d, "E7", "Yes"),
  guide    = Ch3RateLong(dHiredGuide, "hiredAny", "TRUE"),
  daysmean = Ch3MeanLong(dDays, "C1Total_days"),
  daysmed  = Ch3MedianLong(dDays, "C1Total_days"),
  q26      = Ch3RateLong(d %>% filter(!is.na(Q26)), "Q26", "Yes"),
  e2f      = Ch3RateLong(d %>% filter(!is.na(E2)), "E2", "Female"),
  age      = Ch3MeanLong(d, "Age"),
  mn = Ch3MeanLong(d, "motivation_natural", gate = "motivation_natural_AnsweredAll"),
  mp = Ch3MeanLong(d, "motivation_pp", gate = "motivation_pp_AnsweredAll"),
  ms = Ch3MeanLong(d, "motivation_social", gate = "motivation_social_AnsweredAll"),
  mr = Ch3MeanLong(d, "motivation_resource", gate = "motivation_resource_AnsweredAll"),
  rc = Ch3MeanLong(d, "reg_comprehension", gate = "reg_comprehension_AnsweredAll"),
  rs = Ch3MeanLong(d, "reg_sitesupport", gate = "reg_sitesupport_AnsweredAll"),
  ru = Ch3MeanLong(d, "reg_uniform", gate = "reg_uniform_AnsweredAll"),
  ac = Ch3MeanLong(d, "attitude_catch", gate = "attitude_catch_AnsweredAll"),
  an = Ch3MeanLong(d, "attitude_numbers", gate = "attitude_numbers_AnsweredAll"),
  asz = Ch3MeanLong(d, "attitude_size", gate = "attitude_size_AnsweredAll"),
  ah = Ch3MeanLong(d, "attitude_harvest", gate = "attitude_harvest_AnsweredAll")
)

Ch3SAList <- function(fields, gate) {
  out <- list()
  for (f in fields) {
    v <- setdiff(levels(d[[f]]), "Unchecked")
    if (length(v) == 1 && any(d[[f]] == v, na.rm = TRUE)) {
      out[[v]] <- Ch3RateLong(d, f, v, gate = gate)
    }
  }
  out
}
sa4 <- Ch3SAList(a4.fields, "A4_Answered")
sa5 <- Ch3SAList(a5.fields, "A5_Answered")
sa6 <- Ch3SAList(a6.fields, "A6_Answered")

Ch3Bounds <- function(t) {
  if ("CI" %in% names(t)) {
    data.frame(RawLabel = t$RawLabel, lo = t$Value - t$CI, hi = t$Value + t$CI)
  } else {
    data.frame(RawLabel = t$RawLabel, lo = unname(t$Lower), hi = unname(t$Upper))
  }
}
SepHi <- function(t) {
  b <- Ch3Bounds(t); ov <- b[b$RawLabel == "Overall", ]
  g <- b[b$RawLabel != "Overall" & !is.na(b$lo), ]
  g$RawLabel[g$lo > ov$hi]
}
SepLo <- function(t) {
  b <- Ch3Bounds(t); ov <- b[b$RawLabel == "Overall", ]
  g <- b[b$RawLabel != "Overall" & !is.na(b$hi), ]
  g$RawLabel[g$hi < ov$lo]
}
V3 <- function(t, g) t$Value[t$RawLabel == g]
P3 <- function(t, g) sprintf("%.0f%%", V3(t, g))
M3 <- function(t, g) sprintf("%.1f", V3(t, g))
D3 <- function(t, g) sprintf("%.0f", V3(t, g))
N3 <- function(t, g) t$N[t$RawLabel == g]

ch3.claim <- function(t, hi = character(), lo = character(),
                      hi_only = FALSE, lo_only = FALSE) {
  stopifnot(all(hi %in% SepHi(t)), all(lo %in% SepLo(t)))
  if (hi_only) stopifnot(setequal(SepHi(t), hi))
  if (lo_only) stopifnot(setequal(SepLo(t), lo))
  invisible(TRUE)
}

ch3.claim(ch3.t$a11, hi = c("Wiper", "Northern pike"), lo = c("White bass", "No preference"))
ch3.claim(ch3.t$a12, hi = "Walleye / Sauger", lo = c("White bass", "No preference"))
ch3.claim(ch3.t$a10, hi = c("Wiper", "Walleye / Sauger"), lo = "No preference")
stopifnot(length(SepHi(ch3.t$tourn)) == 0)
stopifnot(all(V3(ch3.t$tourn, "Flathead catfish") == 0, V3(ch3.t$tourn, "Wiper") == 0,
              V3(ch3.t$tourn, "White bass") == 0, V3(ch3.t$tourn, "No preference") == 0))
ch3.claim(ch3.t$tournmean, lo = "Panfish / Sunfish")
ch3.claim(ch3.t$q11o, lo = "No preference")
stopifnot(length(SepHi(ch3.t$q11n)) == 0, length(SepLo(ch3.t$q11n)) == 0)
stopifnot(V3(ch3.t$q11o, "Northern pike") == 0)
ch3.claim(ch3.t$pub, hi = "Northern pike")
ch3.claim(ch3.t$both, lo = "Northern pike")
ch3.claim(ch3.t$a7med, hi = c("Walleye / Sauger", "Wiper", "Northern pike"))
stopifnot(length(SepLo(ch3.t$a7med)) == 0)
ch3.claim(ch3.t$a8med, hi = c("Wiper", "Northern pike"),
          lo = c("Bass", "Panfish / Sunfish", "Catfish"))
ch3.claim(ch3.t$a9, hi = "Walleye / Sauger",
          lo = c("Wiper", "Bluegill / Sunfish", "Trout"), hi_only = TRUE)
ch3.claim(ch3.t$q16, hi = c("Wiper", "Walleye / Sauger"), lo = c("Catfish", "No preference"))
ch3.claim(ch3.t$e7, hi = "Walleye / Sauger", lo = "No preference",
          hi_only = TRUE, lo_only = TRUE)
ch3.claim(ch3.t$guide, hi = "Walleye / Sauger", hi_only = TRUE)
ch3.claim(ch3.t$daysmean, hi = "Bass", lo = c("Northern pike", "No preference"))
ch3.claim(ch3.t$daysmed, hi = c("Bass", "Catfish"), lo = "No preference")
ch3.claim(ch3.t$q26,
          hi = c("Northern pike", "Crappie", "Panfish / Sunfish", "Walleye / Sauger"),
          lo = c("White bass", "Trout", "No preference", "Largemouth bass"))
ch3.claim(ch3.t$e2f, hi = "No preference", lo = "Wiper", hi_only = TRUE, lo_only = TRUE)
ch3.claim(ch3.t$age, hi = c("Walleye / Sauger", "Panfish / Sunfish"),
          lo = c("Bass", "Smallmouth bass", "Wiper"))
ch3.claim(ch3.t$mn, hi = "Wiper", lo = "No preference")
ch3.claim(ch3.t$mp, lo = "No preference")
stopifnot(length(SepHi(ch3.t$ms)) == 0, length(SepLo(ch3.t$ms)) == 0)
ch3.claim(ch3.t$mr, hi = c("Wiper", "Walleye / Sauger", "Catfish"), lo = "No preference")
ch3.claim(ch3.t$rc, hi = c("Bass", "Smallmouth bass"))
ch3.claim(ch3.t$rs, hi = "Smallmouth bass", hi_only = TRUE)
ch3.claim(ch3.t$ru, lo = "Northern pike", lo_only = TRUE)
ch3.claim(ch3.t$ac, hi = "Walleye / Sauger", lo = "No preference", hi_only = TRUE)
ch3.claim(ch3.t$an, hi = "Walleye / Sauger", lo = c("Trout", "No preference"), hi_only = TRUE)
ch3.claim(ch3.t$asz, hi = c("Wiper", "Northern pike", "Bass"),
          lo = c("Bluegill / Sunfish", "Panfish / Sunfish", "No preference"))
ch3.claim(ch3.t$ah, hi = c("White bass", "Walleye / Sauger", "Channel catfish"), lo = "Bass")
ch3.claim(sa4[["Ponds and sandpits"]], hi = "Bass", lo = "Walleye / Sauger")
ch3.claim(sa4[["Lakes and Reservoirs"]], hi = c("Walleye / Sauger", "Wiper"), lo = "Trout")
ch3.claim(sa4[["Sandhill lakes"]], hi = "Northern pike", hi_only = TRUE)
ch3.claim(sa4[["Missouri River"]], hi = c("Catfish", "Flathead catfish"))
ch3.claim(sa4[["Platte River"]], hi = "Catfish")
ch3.claim(sa4[["Other streams, rivers, and canals"]], hi = c("Catfish", "Trout"))
ch3.claim(sa5[["Bank/wading"]], hi = "Catfish", lo = "Walleye / Sauger", lo_only = TRUE)
ch3.claim(sa5[["Wading"]], hi = "Trout", hi_only = TRUE)
ch3.claim(sa5[["Motorized boat"]], hi = "Walleye / Sauger",
          lo = c("Bluegill / Sunfish", "Trout", "No preference"), hi_only = TRUE)
ch3.claim(sa5[["Kayak/Canoe"]], hi = "Bass")
ch3.claim(sa5[["Ice fishing"]],
          hi = c("Panfish / Sunfish", "Crappie", "Walleye / Sauger"),
          lo = c("Bass", "White bass", "No preference"))
ch3.claim(sa6[["Rod & reel"]], lo = "Trout")
ch3.claim(sa6[["Fly-fishing"]], hi = "Trout", lo = "Catfish", hi_only = TRUE)
for (nm in setdiff(names(sa6), c("Rod & reel", "Fly-fishing"))) {
  stopifnot(length(SepHi(sa6[[nm]])) == 0)
}
```

`r run_pagebreak()`

## Fish Out-Of-State

Just under half of anglers (`r P3(ch3.t$a11, "Overall")`) also fished outside Nebraska in 2025. Northern pike (`r P3(ch3.t$a11, "Northern pike")`) and Wiper (`r P3(ch3.t$a11, "Wiper")`) anglers did so at rates above the overall, consistent with the travel distances they report later in this chapter, while White bass (`r P3(ch3.t$a11, "White bass")`) and No preference (`r P3(ch3.t$a11, "No preference")`) anglers fell below it.

`r paste(trimws(GetQuestion(q, A11, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3A11}
CreateFlex(Ch3SelectOneTable(d, "A11"))
```

```{r ch3A11Plot, fig.width=6.5, fig.height=5}
Ch3RatePlot(
  d, "A11", "Yes", "Percent answering Yes",
  titleText = trimws(GetQuestion(q, A11, 2025))
)
```

`r run_pagebreak()`

## Boat Out-Of-State

Among anglers who fished out of state, `r P3(ch3.t$a12, "Overall")` took a boat with them. Walleye / Sauger anglers (`r P3(ch3.t$a12, "Walleye / Sauger")`) sit above the overall rate and anglers with no preferred type (`r P3(ch3.t$a12, "No preference")`) below it. White bass anglers' rate (`r P3(ch3.t$a12, "White bass")`) is also below, though it rests on only `r N3(ch3.t$a12, "White bass")` respondents.

`r paste(trimws(GetQuestion(q, A12, 2025)), "  ", caption.ch3selectone, "  Only respondents who fished out of state are included in this calculation.", "  ", caption.raked, sep="")`

```{r ch3A12}
CreateFlex(Ch3SelectOneTable(d %>% filter(A11 == "Yes"), "A12"))
```

```{r ch3A12Plot, fig.width=6.5, fig.height=5}
Ch3RatePlot(
  d %>% filter(A11 == "Yes"), "A12", "Yes", "Percent answering Yes",
  titleText = trimws(GetQuestion(q, A12, 2025))
)
```

`r run_pagebreak()`

## Park Entry Permit

`r P3(ch3.t$a10, "Overall")` of anglers held a park entry permit. Wiper (`r P3(ch3.t$a10, "Wiper")`) and Walleye / Sauger (`r P3(ch3.t$a10, "Walleye / Sauger")`) anglers exceed the overall rate and No preference anglers (`r P3(ch3.t$a10, "No preference")`) fall below it, a separation that tracks the boat-oriented groups in the Methods section.

`r paste(trimws(GetQuestion(q, A10, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3A10}
CreateFlex(Ch3SelectOneTable(d, "A10"))
```

`r run_pagebreak()`

## Fishing Tournaments

Tournament fishing is rare: `r P3(ch3.t$tourn, "Overall")` of anglers fished at least one tournament, and no group sits above the overall rate by the interval screen. Flathead catfish, Wiper, White bass and No preference anglers reported no tournament participation at all. Among the anglers who did fish tournaments, the mean was `r M3(ch3.t$tournmean, "Overall")` tournaments; Panfish / Sunfish anglers averaged `r M3(ch3.t$tournmean, "Panfish / Sunfish")`, below the overall mean.

`r paste("Percent of respondents who participated in at least one fishing tournament (derived from ", trimws(GetQuestion(q, A13, 2025)), ").", "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3Tourney}
CreateFlex(Ch3SelectOneTable(dTourney, "fishedTourney"))
```

```{r ch3TourneyPlot, fig.width=6.5, fig.height=5}
Ch3RatePlot(
  dTourney, "fishedTourney", "Fished Tournaments",
  "Percent fishing at least one tournament",
  titleText = "Fishing tournament participation"
)
```

`r paste(trimws(GetQuestion(q, A13, 2025)), "  ", caption.ch3means, "  Only respondents who participated in at least one tournament are included in this calculation.", "  ", caption.raked, sep="")`

```{r ch3TourneyMean}
CreateFlex(Ch3MeansTable(
  d %>% filter(A13_corrected > 0),
  "A13_corrected",
  "Mean tournaments fished"
))
```

`r run_pagebreak()`

`r sect_portrait()`

## Waterbody Types

Lakes and reservoirs are the dominant water type for every group (`r P3(sa4[["Lakes and Reservoirs"]], "Overall")` overall), but the remaining types carry distinct group signatures. Bass anglers use ponds and sandpits most (`r P3(sa4[["Ponds and sandpits"]], "Bass")` against `r P3(sa4[["Ponds and sandpits"]], "Overall")` overall), while Walleye / Sauger anglers use them least (`r P3(sa4[["Ponds and sandpits"]], "Walleye / Sauger")`) and are heaviest on lakes and reservoirs (`r P3(sa4[["Lakes and Reservoirs"]], "Walleye / Sauger")`). Northern pike anglers are the only group above the overall on Sandhill lakes (`r P3(sa4[["Sandhill lakes"]], "Northern pike")` against `r P3(sa4[["Sandhill lakes"]], "Overall")`). Catfish anglers separate upward on the rivers: the Missouri (`r P3(sa4[["Missouri River"]], "Catfish")` against `r P3(sa4[["Missouri River"]], "Overall")` overall, and `r P3(sa4[["Missouri River"]], "Flathead catfish")` among Flathead catfish anglers), the Platte (`r P3(sa4[["Platte River"]], "Catfish")` against `r P3(sa4[["Platte River"]], "Overall")`) and other streams, rivers and canals (`r P3(sa4[["Other streams, rivers, and canals"]], "Catfish")`). Trout anglers fall below the overall on lakes and reservoirs (`r P3(sa4[["Lakes and Reservoirs"]], "Trout")`) and sit above it on other streams, rivers and canals (`r P3(sa4[["Other streams, rivers, and canals"]], "Trout")` against `r P3(sa4[["Other streams, rivers, and canals"]], "Overall")`).

`r paste(trimws(GetQuestion(q, A4, 2025)), "  ", caption.ch3selectall, "  ", caption.raked, sep="")`

```{r ch3A4}
CreateFlex(Ch3SelectAllTable(d, a4.fields, "A4_Answered"))
```

`r run_pagebreak()`

## Methods

Bank or wading fishing is the most common method (`r P3(sa5[["Bank/wading"]], "Overall")` overall), led by Catfish anglers (`r P3(sa5[["Bank/wading"]], "Catfish")`); Walleye / Sauger anglers are the one group below the overall on it (`r P3(sa5[["Bank/wading"]], "Walleye / Sauger")`) and far above on motorized boats (`r P3(sa5[["Motorized boat"]], "Walleye / Sauger")` against `r P3(sa5[["Motorized boat"]], "Overall")` overall), where Bluegill / Sunfish (`r P3(sa5[["Motorized boat"]], "Bluegill / Sunfish")`), Trout (`r P3(sa5[["Motorized boat"]], "Trout")`) and No preference (`r P3(sa5[["Motorized boat"]], "No preference")`) anglers fall below. Trout anglers stand alone above the overall on wading (`r P3(sa5[["Wading"]], "Trout")` against `r P3(sa5[["Wading"]], "Overall")`), and Bass anglers separate upward on kayaks and canoes (`r P3(sa5[["Kayak/Canoe"]], "Bass")` against `r P3(sa5[["Kayak/Canoe"]], "Overall")`). Ice fishing separates Crappie (`r P3(sa5[["Ice fishing"]], "Crappie")`), Panfish / Sunfish (`r P3(sa5[["Ice fishing"]], "Panfish / Sunfish")`) and Walleye / Sauger (`r P3(sa5[["Ice fishing"]], "Walleye / Sauger")`) anglers upward and Bass, White bass and No preference anglers downward, matching the ice-fishing question later in this chapter.

`r paste(trimws(GetQuestion(q, A5, 2025)), "  ", caption.ch3selectall, "  ", caption.raked, sep="")`

```{r ch3A5}
CreateFlex(Ch3SelectAllTable(d, a5.fields, "A5_Answered"))
```

`r sect_landscape()`

## Techniques

Rod and reel is near-universal (`r P3(sa6[["Rod & reel"]], "Overall")` overall); Trout anglers are the only group below the overall on it (`r P3(sa6[["Rod & reel"]], "Trout")`), while `r P3(sa6[["Fly-fishing"]], "Trout")` of them fly-fish against `r P3(sa6[["Fly-fishing"]], "Overall")` overall — the largest technique separation in the table. Catfish anglers fall below the overall on fly-fishing (`r P3(sa6[["Fly-fishing"]], "Catfish")`). No other technique lifts any group above its overall rate by the interval screen.

`r paste(trimws(GetQuestion(q, A6, 2025)), "  ", caption.ch3selectall, "  ", caption.raked, sep="")`

```{r ch3A6}
CreateFlex(Ch3SelectAllTable(d, a6.fields, "A6_Answered"))
```

`r sect_landscape()`

## Crowding

Crowding perceptions barely differ by preferred species: `r P3(ch3.t$q11n, "Overall")` of anglers never feel crowded and `r P3(ch3.t$q11o, "Overall")` often do, and no group separates from the overall on the Never response. No preference anglers report feeling crowded Often less than the overall (`r P3(ch3.t$q11o, "No preference")`), and no Northern pike angler chose Often, though the latter rests on `r N3(ch3.t$q11o, "Northern pike")` respondents.

`r paste(trimws(GetQuestion(q, Q11, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3Q11}
CreateFlex(Ch3SelectOneTable(d %>% filter(!is.na(Q11)), "Q11"))
```

```{r ch3Q11Plot, fig.width=6.5, fig.height=6}
Ch3StackPlot(
  d %>% filter(!is.na(Q11)), "Q11",
  titleText = trimws(GetQuestion(q, Q11, 2025))
)
```

`r sect_portrait()`

## Access

Of the anglers who fished at least one of the two area types, `r P3(ch3.t$pub, "Overall")` fished public areas only and `r P3(ch3.t$both, "Overall")` fished both. Northern pike anglers are the one departure: `r P3(ch3.t$pub, "Northern pike")` public-only and `r P3(ch3.t$both, "Northern pike")` both, on `r N3(ch3.t$pub, "Northern pike")` respondents — little private-water access in this group.

`r paste(trimws(GetQuestion(q, A17, 2025)), "  ", caption.ch3indicator, "  The first two columns are computed on everyone who answered the question; the last three are computed on respondents who used at least one of the two area types, matching the 2025 Crosstabs report.", "  ", caption.raked, sep="")`

```{r ch3A17}
# dAccess is built in ch3TextHelpers, above, so the section narrative can
# quote it before this table renders.
A17Label <- function(key) l$Label[l$Response == key]

CreateFlex(Ch3IndicatorTable(list(
  list(label = A17Label("A17pub"),      data = d,       var = "A17Pub_corrected",  value = "Yes"),
  list(label = A17Label("A17priv"),     data = d,       var = "A17Priv_corrected", value = "Yes"),
  list(label = A17Label("A17both"),     data = dAccess, var = "A17both",           value = "Yes"),
  list(label = A17Label("A17justPub"),  data = dAccess, var = "A17justPub",        value = "Yes"),
  list(label = A17Label("A17justPriv"), data = dAccess, var = "A17justPriv",       value = "Yes")
)))
```

`r sect_landscape()`

## Favorite Waterbody Distance

The median one-way distance to the favorite water body is roughly `r D3(ch3.t$a7med, "Overall")` miles, computed on band midpoints. Walleye / Sauger anglers' median is `r D3(ch3.t$a7med, "Walleye / Sauger")` miles, and the Wiper and Northern pike medians fall in the 101-to-250-mile band: the favorite waters of these three groups are a substantial drive. No group's median separates below the overall.

`r paste(trimws(GetQuestion(q, A7, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3A7}
CreateFlex(Ch3SelectOneTable(d, "A7"))
```

`r sect_landscape()`

`r paste("Distance in miles to the favorite water body, using the midpoint of the band each respondent selected.", "  ", caption.ch3medians, "  ", caption.raked, sep="")`

```{r ch3A7miles}
CreateFlex(Ch3MediansTable(d, "A7_miles", "Median one-way miles", digits = 0))
```

```{r ch3A7milesPlot, fig.width=6.5, fig.height=5}
Ch3MedianPlot(
  d, "A7_miles", "Median one-way miles",
  titleText = "Distance to the favorite water body",
  subtitleText = "Band midpoints; bars are the bootstrap 95 percent interval"
)
```

`r run_pagebreak()`

`r sect_portrait()`

## Most-Visited Waterbody Distance

The water fished most often is closer (median `r D3(ch3.t$a8med, "Overall")` miles overall), and the split is sharp: the Bass, Panfish / Sunfish and Catfish family medians fall to `r D3(ch3.t$a8med, "Bass")` miles, while the Wiper median stays in the 101-to-250-mile band and Northern pike anglers' is `r D3(ch3.t$a8med, "Northern pike")` miles. The banner separates local-water constituencies from travelling ones, which bears on where a regulation change would actually be felt by each group.

`r paste(trimws(GetQuestion(q, A8, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3A8}
CreateFlex(Ch3SelectOneTable(d, "A8"))
```

`r sect_landscape()`

`r paste("Distance in miles to the most-visited water body, using the midpoint of the band each respondent selected.", "  ", caption.ch3medians, "  ", caption.raked, sep="")`

```{r ch3A8miles}
CreateFlex(Ch3MediansTable(d, "A8_miles", "Median one-way miles", digits = 0))
```

```{r ch3A8milesPlot, fig.width=6.5, fig.height=5}
Ch3MedianPlot(
  d, "A8_miles", "Median one-way miles",
  titleText = "Distance to the most-visited water body",
  subtitleText = "Band midpoints; bars are the bootstrap 95 percent interval"
)
```

`r run_pagebreak()`

## Satisfaction

Mean satisfaction here is scored from 1 (Very satisfied) to 5 (Very dissatisfied), so lower is better. Walleye / Sauger anglers are the only group less satisfied than the overall (`r M3(ch3.t$a9, "Walleye / Sauger")` against `r M3(ch3.t$a9, "Overall")`), while Wiper (`r M3(ch3.t$a9, "Wiper")`), Bluegill / Sunfish (`r M3(ch3.t$a9, "Bluegill / Sunfish")`) and Trout (`r M3(ch3.t$a9, "Trout")`) anglers are more satisfied. The same ordering appears in the preferred-fish satisfaction item in Chapter 2, and Chapter 4 examines the satisfaction items as a set.

`r paste(trimws(GetQuestion(q, A9, 2025)), "  ", caption.ch3selectone, "  Mean scores the five responses from 1 (Very satisfied) to 5 (Very dissatisfied).", "  ", caption.raked, sep="")`

```{r ch3A9}
CreateFlex(Ch3SelectOneTable(d, "A9", includeMean = TRUE))
```

```{r ch3A9Plot, fig.width=6.5, fig.height=6}
Ch3StackPlot(
  d %>% filter(!is.na(A9)), "A9",
  titleText = trimws(GetQuestion(q, A9, 2025))
)
```

```{r ch3A9MeanPlot, fig.width=6.5, fig.height=5}
Ch3MeanPlot(
  d, "A9", "Mean response",
  titleText = trimws(GetQuestion(q, A9, 2025)),
  subtitleText = "1 = Very satisfied to 5 = Very dissatisfied, so a lower score is more satisfied",
  xExpand = c(1, 5), xBreaks = 1:5
)
```

`r run_pagebreak()`

## Live-imaging Sonar Use

`r P3(ch3.t$q16, "Overall")` of anglers used live-imaging sonar in 2025. Wiper (`r P3(ch3.t$q16, "Wiper")`) and Walleye / Sauger (`r P3(ch3.t$q16, "Walleye / Sauger")`) anglers sit well above the overall; Catfish (`r P3(ch3.t$q16, "Catfish")`) and No preference (`r P3(ch3.t$q16, "No preference")`) anglers sit below it. Uptake concentrates in the boat-borne, open-water groups, so any future rule on the technology would land unevenly across the banner.

`r paste(trimws(GetQuestion(q, Q16, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3Q16}
CreateFlex(Ch3SelectOneTable(d %>% filter(!is.na(Q16)), "Q16"))
```

```{r ch3Q16Plot, fig.width=6.5, fig.height=5}
Ch3RatePlot(
  d %>% filter(!is.na(Q16)), "Q16", "Yes", "Percent answering Yes",
  titleText = trimws(GetQuestion(q, Q16, 2025))
)
```

`r run_pagebreak()`

## Conservation Officer

`r P3(ch3.t$e7, "Overall")` of anglers encountered a conservation officer while fishing. Walleye / Sauger anglers are the only group above the overall (`r P3(ch3.t$e7, "Walleye / Sauger")`) and No preference anglers the only group below it (`r P3(ch3.t$e7, "No preference")`), consistent with the two groups' effort and boat use elsewhere in this chapter.

`r paste(trimws(GetQuestion(q, E7, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3E7}
CreateFlex(Ch3SelectOneTable(d, "E7"))
```

`r sect_portrait()`

## Guided Trips

Hiring a guide is uncommon (`r P3(ch3.t$guide, "Overall")` of anglers), and Walleye / Sauger anglers (`r P3(ch3.t$guide, "Walleye / Sauger")`) are the only group above the overall rate. The trip-count means in the second table rest on few respondents per column and should be read with their intervals in view.

`r paste(trimws(GetQuestion(q, Q18, 2025)), "  ", caption.ch3indicator, "  ", caption.raked, sep="")`

```{r ch3Q18pct}
# dHiredGuide is built in ch3TextHelpers, above, so the section narrative can
# quote it before this table renders.
CreateFlex(Ch3IndicatorTable(list(
  list(label = "Hired a guide",                 data = dHiredGuide, var = "hiredAny",     value = TRUE),
  list(label = "Hired in Nebraska",             data = dHiredGuide, var = "hiredNE",      value = TRUE),
  list(label = "Only hired in Nebraska",        data = dHiredGuide, var = "hiredNEonly",  value = TRUE),
  list(label = "Hired outside Nebraska",        data = dHiredGuide, var = "hiredOutside", value = TRUE),
  list(label = "Only hired outside Nebraska",   data = dHiredGuide, var = "hiredOutOnly", value = TRUE),
  list(label = "Hired both in and outside",     data = dHiredGuide, var = "hiredBoth",    value = TRUE)
)))
```

`r paste("Number of guided trips taken, among anglers who hired a guide in the universe named by each column.", "  ", caption.ch3means, "  ", caption.raked, sep="")`

```{r ch3Q18means}
# Column universes copied from 2025CrossTabReport.rmd L620.
dQ18means <- d %>%
  mutate(
    hiredNE = !is.na(Q18a) & Q18a > 0,
    hiredOutside = !is.na(Q18b) & Q18b > 0,
    Q18total = coalesce(Q18a, 0) + coalesce(Q18b, 0)
  )

CreateFlex(Ch3MeansSpecTable(list(
  list(label = "Hired a guide",               data = dQ18means %>% filter(hiredNE | hiredOutside),  var = "Q18total"),
  list(label = "Hired in Nebraska",           data = dQ18means %>% filter(hiredNE),                 var = "Q18a"),
  list(label = "Only hired in Nebraska",      data = dQ18means %>% filter(hiredNE & !hiredOutside), var = "Q18a"),
  list(label = "Hired outside Nebraska",      data = dQ18means %>% filter(hiredOutside),            var = "Q18b"),
  list(label = "Only hired outside Nebraska", data = dQ18means %>% filter(hiredOutside & !hiredNE), var = "Q18b"),
  list(label = "Hired both in and outside",   data = dQ18means %>% filter(hiredNE & hiredOutside),  var = "Q18total")
)))
```

`r sect_landscape()`

## Days Fished

Anglers fished a mean of `r D3(ch3.t$daysmean, "Overall")` days in 2025, with a median of `r D3(ch3.t$daysmed, "Overall")`. Bass anglers are above the overall on both (mean `r D3(ch3.t$daysmean, "Bass")`, median `r D3(ch3.t$daysmed, "Bass")`) and Catfish anglers on the median (`r D3(ch3.t$daysmed, "Catfish")`); Northern pike anglers (mean `r D3(ch3.t$daysmean, "Northern pike")`) and No preference anglers (mean `r D3(ch3.t$daysmean, "No preference")`, median `r D3(ch3.t$daysmed, "No preference")`) fished the least. Effort concentrates in the bass and catfish constituencies, and the No preference group's low effort marks it as the most casual segment of the licence base.

`r paste(trimws(GetQuestion(q, C1, 2025)), "  Total days fished across all months.", "  ", caption.ch3means, "  ", caption.ch3medians, "  ", caption.raked, sep="")`

```{r ch3Days}
# dDays is built in ch3TextHelpers, above, so the section narrative can quote
# it before this table renders.
left_join(
  Ch3MeansTable(dDays, "C1Total_days", "Mean days fished"),
  Ch3MediansTable(dDays, "C1Total_days", "Median days fished"),
  by = "Preferred species"
) %>%
  CreateFlex()
```

```{r ch3DaysPlot, fig.width=6.5, fig.height=5}
Ch3MeanPlot(
  dDays, "C1Total_days", "Mean days fished",
  titleText = "Total days fished in 2025"
)
```

`r run_pagebreak()`

## Ice Fishing

`r P3(ch3.t$q26, "Overall")` of anglers ice fish. Northern pike (`r P3(ch3.t$q26, "Northern pike")`), Crappie (`r P3(ch3.t$q26, "Crappie")`), Panfish / Sunfish (`r P3(ch3.t$q26, "Panfish / Sunfish")`) and Walleye / Sauger (`r P3(ch3.t$q26, "Walleye / Sauger")`) anglers do so above the overall rate; White bass (`r P3(ch3.t$q26, "White bass")`), Trout (`r P3(ch3.t$q26, "Trout")`), No preference (`r P3(ch3.t$q26, "No preference")`) and Largemouth bass (`r P3(ch3.t$q26, "Largemouth bass")`) anglers fall below it. The ordering repeats the ice-fishing method in the Methods section and maps onto the species reachable through the ice.

`r paste(trimws(GetQuestion(q, Q26, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3Q26}
CreateFlex(Ch3SelectOneTable(
  d %>% filter(!is.na(Q26)) %>% mutate(Q26 = factor(Q26, levels = c("Yes", "No"))),
  "Q26"
))
```

```{r ch3Q26Plot, fig.width=6.5, fig.height=5}
Ch3RatePlot(
  d %>% filter(!is.na(Q26)), "Q26", "Yes", "Percent answering Yes",
  titleText = trimws(GetQuestion(q, Q26, 2025))
)
```

`r run_pagebreak()`

## Angler Motivations

Across the four motivation sub-scales, the natural-environment (`r M3(ch3.t$mn, "Overall")` overall) and social (`r M3(ch3.t$ms, "Overall")`) scales rate highest and the fishery-resource scale lowest (`r M3(ch3.t$mr, "Overall")`). The group separations concentrate in the resource scale: Wiper (`r M3(ch3.t$mr, "Wiper")`), Walleye / Sauger (`r M3(ch3.t$mr, "Walleye / Sauger")`) and Catfish (`r M3(ch3.t$mr, "Catfish")`) anglers sit above the overall and No preference anglers below it (`r M3(ch3.t$mr, "No preference")`). Wiper anglers are also above on the natural-environment scale (`r M3(ch3.t$mn, "Wiper")`), and No preference anglers below the overall on the natural-environment and psychological scales. No group separates on the social scale in either direction: the companionship motive is shared across species preferences.

`r paste(trimws(GetQuestion(q, C2, 2025)), "  Items are grouped by the motivation sub-scale they belong to in Scales.csv; the grouping organizes the tables and does not change any value.", "  ", caption.ch3means, "  ", caption.raked, sep="")`

### Natural Environment

```{r ch3C2natural}
f <- SubScaleFields(s, "Motivations", "Natural Environment")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Motivations")))
```

### Psychological and Physiological

```{r ch3C2pp}
f <- SubScaleFields(s, "Motivations", "Psychological and Physiological")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Motivations")))
```

### Social

```{r ch3C2social}
f <- SubScaleFields(s, "Motivations", "Social")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Motivations")))
```

### Fishery Resource

```{r ch3C2resource}
f <- SubScaleFields(s, "Motivations", "Fishery Resource")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Motivations")))
```

### Motivation scale scores

`r paste("Each scale score is the mean of its items, computed only for respondents who answered every item in that scale.", "  ", caption.ch3means, "  ", caption.raked, sep="")`

```{r ch3C2scales}
v <- c("motivation_pp", "motivation_natural", "motivation_social", "motivation_resource")
CreateFlex(Ch3MeansTable(d, v, ScaleLabel(v, l), gates = paste0(v, "_AnsweredAll")))
```

```{r ch3C2scalesPlot, fig.width=6.5, fig.height=7.5}
Ch3ScaleFacetPlot(
  d, v, ScaleLabel(v, l), gates = paste0(v, "_AnsweredAll"),
  titleText = "Motivation scale scores",
  subtitleText = "1 = Not At All Important ... 5 = Extremely Important",
  xExpand = c(1, 5), xBreaks = 1:5
)
```

`r paste("The same items also form a two-part split between catch-oriented and non-catch-oriented motivations, reported below on the same basis.", "  ", caption.ch3means, "  ", caption.raked, sep="")`

```{r ch3C2catchScales}
v <- c("motivation_noncatch", "motivation_catch")
CreateFlex(Ch3MeansTable(d, v, ScaleLabel(v, l), gates = paste0(v, "_AnsweredAll")))
```

`r run_pagebreak()`

## Regulations

The regulation scales separate few groups. On comprehension and confidence (`r M3(ch3.t$rc, "Overall")` overall), Bass (`r M3(ch3.t$rc, "Bass")`) and especially Smallmouth bass (`r M3(ch3.t$rc, "Smallmouth bass")`) anglers sit above the overall, and Smallmouth bass anglers are the one group above it on site-specific support (`r M3(ch3.t$rs, "Smallmouth bass")` against `r M3(ch3.t$rs, "Overall")`). On preference for uniform statewide regulations (`r M3(ch3.t$ru, "Overall")` overall), Northern pike anglers are the only group below the overall (`r M3(ch3.t$ru, "Northern pike")`), consistent with a group fishing a small set of specialized waters.

`r paste(trimws(GetQuestion(q, Q31, 2025)), "  Items are grouped by the regulation sub-scale they belong to in Scales.csv. Item means are computed on the responses as recorded and are not reverse-adjusted, matching the 2025 Crosstabs report. None of the three sub-scales reported here contains a reverse-coded item; the reversals the codebook records for this battery belong to a separate bipolar orientation scale that this report does not use.", "  ", caption.ch3means, "  ", caption.raked, sep="")`

### Comprehension and Confidence

```{r ch3Q31comp}
f <- SubScaleFields(s, "Regulations", "Comprehension and Confidence")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Regulations")))
```

### Site-Specific Support

```{r ch3Q31site}
f <- SubScaleFields(s, "Regulations", "Site-Specific Support")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Regulations")))
```

`r sect_portrait()`

### Uniform Preference

```{r ch3Q31uniform}
f <- SubScaleFields(s, "Regulations", "Uniform Preference")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Regulations")))
```

`r sect_landscape()`

### Items outside the three regulation sub-scales

`r paste("These items are part of the battery but belong to no sub-scale of the Regulations scale.", "  ", caption.ch3means, sep="")`

```{r ch3Q31other}
f <- UnassignedFields(s, "Regulations", q31.fields)
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Regulations")))
```

### Regulation scale scores

`r paste("Each scale score is the mean of its items, computed only for respondents who answered every item in that scale.", "  ", caption.ch3means, "  ", caption.raked, sep="")`

```{r ch3Q31scales}
v <- c("reg_comprehension", "reg_sitesupport", "reg_uniform")
CreateFlex(Ch3MeansTable(d, v, ScaleLabel(v, l), gates = paste0(v, "_AnsweredAll")))
```

```{r ch3Q31scalesPlot, fig.width=6.5, fig.height=5}
Ch3ScaleFacetPlot(
  d, v, ScaleLabel(v, l), gates = paste0(v, "_AnsweredAll"),
  titleText = "Regulation scale scores",
  subtitleText = "1 = Strongly disagree ... 5 = Strongly agree",
  xExpand = c(1, 5), xBreaks = 1:5, ncol = 3
)
```

`r run_pagebreak()`

## Angler Attitudes

The four attitude scales reprise the evidence behind Chapter 1's groupings. Walleye / Sauger anglers are the only group above the overall on catching something (`r M3(ch3.t$ac, "Walleye / Sauger")` against `r M3(ch3.t$ac, "Overall")`) and on numbers of fish (`r M3(ch3.t$an, "Walleye / Sauger")` against `r M3(ch3.t$an, "Overall")`); No preference anglers fall below on both, and Trout anglers on numbers. On size of fish, Wiper (`r M3(ch3.t$asz, "Wiper")`) and Northern pike (`r M3(ch3.t$asz, "Northern pike")`) anglers sit highest and Bass anglers also above the overall (`r M3(ch3.t$asz, "Bass")`), with Panfish / Sunfish and particularly Bluegill / Sunfish anglers (`r M3(ch3.t$asz, "Bluegill / Sunfish")`) below. On harvesting, White bass (`r M3(ch3.t$ah, "White bass")`), Walleye / Sauger (`r M3(ch3.t$ah, "Walleye / Sauger")`) and Channel catfish (`r M3(ch3.t$ah, "Channel catfish")`) anglers are above the overall and Bass anglers well below it (`r M3(ch3.t$ah, "Bass")`): bass anglers are the most release-oriented constituency in the survey, and walleye and white bass anglers the most harvest-oriented.

`r paste(trimws(GetQuestion(q, E1, 2025)), "  Items are grouped by the attitude sub-scale they belong to in Scales.csv. Item means are computed on the responses as recorded and are not reverse-adjusted; a dagger marks an item the codebook flags as reverse-coded.", "  ", caption.ch3means, "  ", ReversedItemsNote("Attitudes"), "  ", caption.raked, sep="")`

### Catch something

```{r ch3E1catch}
f <- SubScaleFields(s, "Attitudes", "Catch something")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Attitudes")))
```

### Numbers of fish

```{r ch3E1numbers}
f <- SubScaleFields(s, "Attitudes", "Numbers of fish")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Attitudes")))
```

### Size of fish

```{r ch3E1size}
f <- SubScaleFields(s, "Attitudes", "Size of fish")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Attitudes")))
```

### Harvesting fish

```{r ch3E1harvest}
f <- SubScaleFields(s, "Attitudes", "Harvesting fish")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Attitudes")))
```

### Attitude scale scores

`r paste("Each scale score is the mean of its items, computed only for respondents who answered every item in that scale. Reverse-coded items are reversed before the scale score is formed.", "  ", caption.ch3means, "  ", ReversedItemsNote("Attitudes"), "  ", caption.raked, sep="")`

```{r ch3E1scales}
v <- c("attitude_catch", "attitude_numbers", "attitude_size", "attitude_harvest")
CreateFlex(Ch3MeansTable(d, v, ScaleLabel(v, l), gates = paste0(v, "_AnsweredAll")))
```

```{r ch3E1scalesPlot, fig.width=6.5, fig.height=7.5}
Ch3ScaleFacetPlot(
  d, v, ScaleLabel(v, l), gates = paste0(v, "_AnsweredAll"),
  titleText = "Attitude scale scores",
  subtitleText = "1 = Strongly Disagree ... 5 = Strongly Agree; reverse-coded items are reversed before the score is formed",
  xExpand = c(1, 5), xBreaks = 1:5
)
```

`r run_pagebreak()`

## Gender

`r P3(ch3.t$e2f, "Overall")` of anglers who answered are female. The share is above the overall among No preference anglers (`r P3(ch3.t$e2f, "No preference")`) and below it among Wiper anglers (`r P3(ch3.t$e2f, "Wiper")`); no other group separates. Group differences elsewhere in this report are therefore partly demographic as well as behavioural.

`r paste(trimws(GetQuestion(q, E2, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, "  Percentages are weighted, as they are throughout this report.", sep="")`

```{r ch3E2}
CreateFlex(Ch3SelectOneTable(d %>% filter(!is.na(E2)), "E2"))
```

`r run_pagebreak()`

## Age

The weighted mean age is `r D3(ch3.t$age, "Overall")` years. Walleye / Sauger and Panfish / Sunfish anglers are older than the overall (both about `r D3(ch3.t$age, "Walleye / Sauger")`), while Bass (`r D3(ch3.t$age, "Bass")`), Smallmouth bass (`r D3(ch3.t$age, "Smallmouth bass")`) and Wiper (`r D3(ch3.t$age, "Wiper")`) anglers are younger. The age gradient is worth holding alongside the effort and attitude differences above when deciding whether a group contrast reflects the species or the cohort that pursues it.

`r paste("Respondent age group.", "  ", caption.ch3selectone, "  The final column is the weighted mean age in years, taken from the reported age rather than from the bands, and computed on the same respondents as the percentages.", "  ", caption.raked, "  Percentages and the mean are weighted, as they are throughout this report.", sep="")`

```{r ch3E3}
# The single N column is only correct while the band and the reported age are
# missing on exactly the same respondents (they are: E3 is derived from Age).
# If that ever stops holding, the denominator claim in the caption is wrong and
# the render should stop rather than print it.
stopifnot(identical(is.na(d$Age), is.na(d$E3)))

CreateFlex(Ch3SelectOneTable(
  d %>% filter(!is.na(E3)), "E3",
  includeMean = TRUE, meanVar = "Age", meanLabel = "Mean age \u00b1 CI"
))
```

`r run_pagebreak()`

# Chapter 4: Satisfaction

```{r ch4Setup}
# A9 reversed, plus the two paired differences. Additive only: no row is added,
# dropped, or reweighted, so nothing in Chapters 1-3 changes.
nBeforeCh4 <- nrow(d)
d <- Ch4AddSatVars(d)

ch4.nSix <- Ch4CorrComplete(d)
ch4.groupMeans <- Ch4GroupMeans(d)
ch4.gapCatch <- Ch4GapNumbers(d, "D4i", "D4k")
ch4.gapHarvest <- Ch4GapNumbers(d, "D4j", "D4l")

stopifnot(
  nrow(d) == nBeforeCh4,
  # The reversal has to be exact, or the reconciliation stated in the caption
  # is false and every column in this chapter points a different way.
  all(d$A9rev + as.numeric(d$A9) == 6, na.rm = TRUE),
  identical(is.na(d$A9rev), is.na(d$A9)),
  # Overall plus one row per preferred group
  nrow(ch4.groupMeans) == nrow(banner.definition) + 1,
  nrow(ch4.gapCatch) == nrow(banner.definition) + 1,
  nrow(ch4.gapHarvest) == nrow(banner.definition) + 1
)
```

```{r ch4TextHelpers, echo=FALSE}
# Long tables behind the Chapter 4 narrative, built by the same function as the
# matrix table. The text claims a group differs from Overall only when its
# interval lies entirely outside the Overall interval (SepHi / SepLo), and claims
# a within-angler gap only when its own interval excludes zero (GapSet). Every
# claim is asserted, by rule, so the render stops if the data stop supporting it.
tt4 <- setNames(
  lapply(ch4.sat.items$Field, function(f) Ch3MeanLong(d, f)),
  ch4.sat.items$Field
)
ch4.gapSize <- Ch4GapNumbers(d, "D4i", "D4j")
ch4.gapNum <- Ch4GapNumbers(d, "D4k", "D4l")

GLo <- function(t, g) sprintf("%.2f", round(t$Gap[t$RawLabel == g] - t$CI[t$RawLabel == g], 2) + 0)
G4 <- function(t, g) sprintf("%.2f", round(t$Gap[t$RawLabel == g], 2) + 0)
G4ci <- function(t, g) sprintf("%.2f", t$CI[t$RawLabel == g])
G4n <- function(t, g) t$N[t$RawLabel == g]
GapSet <- function(t, dir = c("pos", "neg")) {
  dir <- match.arg(dir)
  s <- t[t$Type != "Overall" & abs(t$Gap) > t$CI, ]
  s$RawLabel[if (dir == "pos") s$Gap > 0 else s$Gap < 0]
}
OvB <- function(f) {
  b <- Ch3Bounds(tt4[[f]])
  b[b$RawLabel == "Overall", ]
}

ch4.ov <- vapply(tt4, function(t) V3(t, "Overall"), numeric(1))
stopifnot(
  # Harvestable items above their caught counterparts, intervals apart
  OvB("D4j")$lo > OvB("D4i")$hi,
  OvB("D4l")$lo > OvB("D4k")$hi,
  # Season rating above every preferred-fish item; success and number caught lowest
  ch4.ov["A9rev"] > max(ch4.ov[c("D4a", "D4i", "D4j", "D4k", "D4l")]),
  setequal(names(sort(ch4.ov[c("D4a", "D4i", "D4j", "D4k", "D4l")]))[1:2], c("D4a", "D4k")),
  OvB("D4a")$hi > OvB("D4k")$lo
)

ch3.claim(tt4$A9rev, hi = c("Bluegill / Sunfish", "Wiper", "Trout"), lo = "Walleye / Sauger",
          hi_only = TRUE, lo_only = TRUE)
ch3.claim(tt4$D4a, hi = c("Channel catfish", "White bass", "Trout"), lo = "Walleye / Sauger",
          hi_only = TRUE, lo_only = TRUE)
ch3.claim(tt4$D4i, hi = "Wiper", lo = c("Bass", "Largemouth bass"), hi_only = TRUE, lo_only = TRUE)
ch3.claim(tt4$D4j, hi = "Bluegill / Sunfish", lo = c("Northern pike", "No preference"),
          hi_only = TRUE, lo_only = TRUE)
ch3.claim(tt4$D4k, hi = "Channel catfish", hi_only = TRUE)
stopifnot(length(SepLo(tt4$D4k)) == 0, length(SepLo(tt4$D4l)) == 0)
ch3.claim(tt4$D4l, hi = c("Panfish / Sunfish", "Bluegill / Sunfish"), hi_only = TRUE)
stopifnot(!("Walleye / Sauger" %in% unlist(lapply(tt4[c("D4i", "D4j", "D4k", "D4l")],
                                                 function(t) c(SepHi(t), SepLo(t))))))

stopifnot(
  ch4.gapCatch$Gap[1] > ch4.gapCatch$CI[1],
  setequal(GapSet(ch4.gapCatch, "pos"), c("Walleye / Sauger", "Catfish", "Flathead catfish", "Wiper")),
  setequal(GapSet(ch4.gapCatch, "neg"), c("Bass", "Largemouth bass")),
  !("Channel catfish" %in% c(GapSet(ch4.gapCatch, "pos"), GapSet(ch4.gapCatch, "neg"))),
  abs(ch4.gapHarvest$Gap[1]) <= ch4.gapHarvest$CI[1],
  length(GapSet(ch4.gapHarvest, "pos")) == 0,
  setequal(GapSet(ch4.gapHarvest, "neg"), "No preference"),
  # Size caught minus size allowed: negative overall, Wiper the only positive
  ch4.gapSize$Gap[1] < -ch4.gapSize$CI[1],
  setequal(GapSet(ch4.gapSize, "pos"), "Wiper")
)

# Caught versus allowed, every group, size and number (D4i-D4j, D4k-D4l).
# Negative means the allowed side is rated above the caught side.
stopifnot(
  ch4.gapNum$Gap[1] < -ch4.gapNum$CI[1],
  setequal(GapSet(ch4.gapSize, "neg"),
           c("Walleye / Sauger", "Bass", "Largemouth bass", "Panfish / Sunfish", "Crappie", "Bluegill / Sunfish")),
  length(GapSet(ch4.gapNum, "pos")) == 0,
  length(GapSet(ch4.gapNum, "neg")) == 11,
  !any(c("Wiper", "Bluegill / Sunfish", "Trout", "Northern pike") %in% GapSet(ch4.gapNum, "neg")),
  # Walleye / Sauger: larger on number than on size. Bass: larger on size than on number.
  ch4.gapNum$Gap[ch4.gapNum$RawLabel == "Walleye / Sauger"] < ch4.gapSize$Gap[ch4.gapSize$RawLabel == "Walleye / Sauger"],
  ch4.gapSize$Gap[ch4.gapSize$RawLabel == "Bass"] < ch4.gapNum$Gap[ch4.gapNum$RawLabel == "Bass"],
  # Catfish: a number gap only
  !("Catfish" %in% GapSet(ch4.gapSize, "neg")), "Catfish" %in% GapSet(ch4.gapNum, "neg"),
  # Wiper: positive on size with the interval above zero, not flagged on number
  ch4.gapSize$Gap[ch4.gapSize$RawLabel == "Wiper"] - ch4.gapSize$CI[ch4.gapSize$RawLabel == "Wiper"] > 0,
  !("Wiper" %in% c(GapSet(ch4.gapNum, "pos"), GapSet(ch4.gapNum, "neg"))),
  D4Top("D4i") == "Wiper", D4Top("D4c") == "Wiper", D4Top("D4e") == "Wiper"
)
```

Managers usually want to know how satisfied anglers are, but one satisfaction score does not say what is behind it. The survey therefore asks about satisfaction in several ways, and this chapter is organised around what each way can tell apart. One item (A9) asks about the season as a whole. Another (D4a) asks about success at catching the angler's preferred fish. Four more (D4i to D4l) form a two-by-two: satisfaction with the size or the number of the preferred fish, for the fish the angler catches or the fish the angler is allowed to harvest. The pairs are there to answer two questions. Is an unhappy group short of large fish or of many fish? And is the complaint about what the water produces or about what the rules let anglers keep? The chapter reports the six items together by preferred group, then compares size with numbers within each angler, first for the catch and then for the harvest, and finally compares what each angler catches with what the same angler is allowed to keep. As in Chapter 3, a group is described as different from the overall only when its interval lies entirely outside the Overall interval. A within-angler difference is described only when the interval around that difference excludes zero.

`r paste0("The survey measures satisfaction in two places that this report has so far kept apart. A9 asks how satisfied the angler was with fishing in Nebraska during 2025 and is reported in Chapter 3. Five items in the D4 battery ask about the one type of fish the angler prefers to fish for and are reported one at a time in Chapter 2. This chapter puts all six in one place, pointing the same direction, across the same preferred groups. No cell is computed differently here: the same summary functions, the same universe, and the same row set are used, so a value in this chapter and its counterpart in Chapter 2 or 3 are the same number.")`

`r caption.ch4a9`

`r caption.ch3rows`

`r run_pagebreak()`

## The satisfaction items

The six items are listed below with the short names used in the rest of the chapter. Each is scored so that a higher mean means a more satisfied angler.

`r paste0("The six items, with the question text as it appears in the instrument, the short name used in the tables that follow, and the chapter that reports the item in full. N is the raw unweighted number of respondents in the analysis sample who answered the item; the mean is weighted, with a 95 percent confidence interval. ", caption.raked)`

```{r ch4items}
CreateFlex(Ch4ItemTable(d, q))
```

Anglers rate the season as a whole highest (`r M3(tt4$A9rev, "Overall")`) and their preferred fish lower. Success (`r M3(tt4$D4a, "Overall")`) and the number caught (`r M3(tt4$D4k, "Overall")`) are the lowest of the five preferred-fish items, and their intervals overlap. The season item is worded differently from the D4 items, so the distance between it and the rest is only a rough guide. The four size and number items share their wording, and among those the comparison is cleaner. Anglers rate what the rules allow them to keep above what they catch, for size (`r M3(tt4$D4j, "Overall")` harvestable against `r M3(tt4$D4i, "Overall")` caught) and for number (`r M3(tt4$D4l, "Overall")` against `r M3(tt4$D4k, "Overall")`), and the intervals do not overlap in either pair. On average, then, the harvest side draws less complaint than the catch side.

`r run_pagebreak()`

`r sect_portrait()`

## Satisfaction by preferred group

The table sets the six items side by side for every preferred group. Higher is more satisfied on every item.

`r paste0("All six items across the preferred groups. ", caption.ch3means, " ", caption.ch3rows, " ", caption.raked)`

```{r ch4matrix}
CreateFlex(Ch3MeansTable(d, ch4.sat.items$Field, ch4.sat.items$Short))
```

Walleye / Sauger anglers are the only group below the overall on the season (`r M3(tt4$A9rev, "Walleye / Sauger")` against `r M3(tt4$A9rev, "Overall")`) and on success (`r M3(tt4$D4a, "Walleye / Sauger")` against `r M3(tt4$D4a, "Overall")`). They do not separate from the overall on any of the four size and number items, so this screen cannot place the shortfall in one of them. The next section looks at it directly. On the positive side, Wiper (`r M3(tt4$A9rev, "Wiper")`), Bluegill / Sunfish (`r M3(tt4$A9rev, "Bluegill / Sunfish")`) and Trout (`r M3(tt4$A9rev, "Trout")`) anglers rate the season above the overall. Trout (`r M3(tt4$D4a, "Trout")`), Channel catfish (`r M3(tt4$D4a, "Channel catfish")`) and White bass (`r M3(tt4$D4a, "White bass")`) anglers are above it on success, and Channel catfish anglers are also above on the number caught (`r M3(tt4$D4k, "Channel catfish")`). Wiper anglers alone are above on the size caught (`r M3(tt4$D4i, "Wiper")`).

The remaining separations are specific to one item. Bass anglers, and Largemouth bass anglers in particular, are below the overall on the size caught (`r M3(tt4$D4i, "Bass")` and `r M3(tt4$D4i, "Largemouth bass")` against `r M3(tt4$D4i, "Overall")`). Chapter 3 shows the same anglers above the overall on the size-of-fish attitude scale, so this is a group that cares about size and is less satisfied with the size it catches. On the size allowed to harvest, Northern pike (`r M3(tt4$D4j, "Northern pike")`) and No preference anglers (`r M3(tt4$D4j, "No preference")`) are below the overall (`r M3(tt4$D4j, "Overall")`), and Bluegill / Sunfish anglers are above it (`r M3(tt4$D4j, "Bluegill / Sunfish")`). Panfish / Sunfish (`r M3(tt4$D4l, "Panfish / Sunfish")`) and Bluegill / Sunfish (`r M3(tt4$D4l, "Bluegill / Sunfish")`) anglers are above the overall on the number allowed. Most cells have no flag at all. That does not show those groups are typical, because the smaller groups have wide intervals and a real difference could sit inside one.

<!--

`r sect_landscape()`

 ## Consistency between the items

`r paste0("Two different questions are asked here. The first table asks whether individual anglers answer the six items alike: an angler satisfied with one thing is, or is not, satisfied with the others. The second asks whether the preferred groups rank alike across items: the groups that rate the season highly are, or are not, the groups satisfied with size or with numbers. A set of items can behave one way at the respondent level and the other way at the group level, so both are shown.")`

### Agreement between individual anglers' answers

`r paste0("Weighted correlations between the six items, computed on the ", format(ch4.nSix, big.mark=","), " respondents who answered all six. ", caption.ch4corr)`

```{r ch4corr}
CreateFlex(Ch4CorrTable(d))
```

`r run_pagebreak()`

### Agreement between the group averages

`r paste0("Rank correlations between the preferred-group means shown in the previous section, one observation per group. ", caption.ch4groupcorr)`

```{r ch4groupcorr}
CreateFlex(Ch4GroupCorrTable(ch4.groupMeans))
```

`r run_pagebreak()` -->

## Size and numbers: the fish anglers catch

Each angler answered one item on the size of the preferred fish caught and one on the number caught, so the two answers can be compared within the angler. A positive difference means the angler is happier with size than with numbers.

`r paste0("D4i and D4k ask the same question about the same fish, one about the size caught and one about the number caught, so the two can be compared within an angler rather than across anglers. ", caption.ch4gap, " ", caption.ch3rows)`

```{r ch4gapCatch}
CreateFlex(Ch4GapTable(d, "D4i", "D4k", "Size caught", "Number caught"))
```

```{r ch4gapCatchPlot, fig.width=6.5, fig.height=5}
Ch4DumbbellPlot(
  d, "D4i", "D4k", "Size of fish caught", "Number of fish caught",
  titleText = "Satisfaction with the size, and with the number, of the preferred fish caught",
  subtitleText = "1 = Strongly Disagree to 5 = Strongly Agree. Rows are sorted by the size-minus-numbers difference"
)
```

`r paste0("Reading the difference column against its own interval, and without any adjustment for the number of groups compared: the interval lies above zero, with size rated higher than numbers, for ", Ch4GapNames(ch4.gapCatch, "positive"), "; it lies below zero, with numbers rated higher than size, for ", Ch4GapNames(ch4.gapCatch, "negative"), ". For the remaining ", sum(ch4.gapCatch$Type != "Overall" & abs(ch4.gapCatch$Gap) <= ch4.gapCatch$CI), " groups the interval includes zero. Overall the difference is ", FmtMeanGap(ch4.gapCatch$Gap[1], ch4.gapCatch$CI[1]), ".")`

Across all anglers the difference is small (`r G4(ch4.gapCatch, "Overall")` ± `r G4ci(ch4.gapCatch, "Overall")`). The interval only just clears zero, so the average angler is about equally content with size and numbers. The groups are where the separation shows up.

Four groups rate size above numbers: Wiper (`r G4(ch4.gapCatch, "Wiper")`), Flathead catfish (`r G4(ch4.gapCatch, "Flathead catfish")`), Catfish as a family (`r G4(ch4.gapCatch, "Catfish")`) and Walleye / Sauger (`r G4(ch4.gapCatch, "Walleye / Sauger")`). For these anglers the weaker side of the catch is how many fish they get, not how large they are. That agrees with Chapter 2, where Flathead catfish anglers had the lowest satisfaction with the number caught of any group, and with Chapter 3, where Walleye / Sauger anglers score above the overall on the numbers attitude. It also gives the walleye result in the previous section somewhere to land: the season and success ratings are low, and among the catch items it is the number of fish that trails. Two groups go the other way, Bass (`r G4(ch4.gapCatch, "Bass")`) and Largemouth bass (`r G4(ch4.gapCatch, "Largemouth bass")`). Bass anglers are comparatively content with how many fish they catch and less so with how large, which matches their size-focused attitudes.

The Wiper and Flathead catfish differences are the largest, but they rest on `r G4n(ch4.gapCatch, "Wiper")` and `r G4n(ch4.gapCatch, "Flathead catfish")` respondents and their intervals are about ± `r G4ci(ch4.gapCatch, "Wiper")` and ± `r G4ci(ch4.gapCatch, "Flathead catfish")`. The direction is more dependable than the size. Channel catfish anglers, the larger part of the catfish family, are not flagged (`r G4(ch4.gapCatch, "Channel catfish")` ± `r G4ci(ch4.gapCatch, "Channel catfish")`), so the family result leans on Flathead catfish. None of these intervals is adjusted for the number of groups compared.

`r run_pagebreak()`

## Size and numbers: the fish anglers may harvest

The same comparison follows for the fish an angler is allowed to keep. These items describe the rules rather than the catch, so a difference here says something about regulation and not about the fishery.

`r paste0("D4j and D4l repeat the comparison for the fish an angler is allowed to keep rather than the fish caught. ", caption.ch4gap, " ", caption.ch3rows)`

```{r ch4gapHarvest}
CreateFlex(Ch4GapTable(d, "D4j", "D4l", "Size harvestable", "Number harvestable"))
```

```{r ch4gapHarvestPlot, fig.width=6.5, fig.height=5}
Ch4DumbbellPlot(
  d, "D4j", "D4l", "Size allowed to harvest", "Number allowed to harvest",
  titleText = "Satisfaction with the size, and with the number, of the preferred fish that may be harvested",
  subtitleText = "1 = Strongly Disagree to 5 = Strongly Agree. Rows are sorted by the size-minus-numbers difference"
)
```

`r paste0("On the same reading: the interval lies above zero for ", Ch4GapNames(ch4.gapHarvest, "positive"), ", and below zero for ", Ch4GapNames(ch4.gapHarvest, "negative"), ". For the remaining ", sum(ch4.gapHarvest$Type != "Overall" & abs(ch4.gapHarvest$Gap) <= ch4.gapHarvest$CI), " groups the interval includes zero. Overall the difference is ", FmtMeanGap(ch4.gapHarvest$Gap[1], ch4.gapHarvest$CI[1]), ".")`

The overall difference is `r G4(ch4.gapHarvest, "Overall")` ± `r G4ci(ch4.gapHarvest, "Overall")`, so the average angler is as satisfied with the size allowed as with the number allowed. One group is flagged, No preference (`r G4(ch4.gapHarvest, "No preference")` ± `r G4ci(ch4.gapHarvest, "No preference")`, `r G4n(ch4.gapHarvest, "No preference")` respondents), who are happier with the number allowed. With `r nrow(ch4.gapHarvest) - 1` groups compared and no adjustment, one flagged group is about what chance alone would produce, so this result should carry little weight.

The contrast with the previous section is the useful part. The groups that leaned toward size or toward numbers on the catch (walleye, catfish, Wiper and bass anglers) show no lean on the harvest items. Their differences are about what the fishery delivers, not about how the rules balance size against number. For management that separates the two readings: the catch differences look like a signal about fishery performance, while satisfaction with the harvest rules is fairly even across groups on this comparison.

Even fairness between size and number does not mean every group is equally content with the rules. The next section sets what anglers catch against what they may keep, and there one group, Wiper, stands apart from the rest.

`r run_pagebreak()`

## Caught versus allowed

This section compares each angler's rating of the fish caught with the same angler's rating of the fish that may be harvested, once for size and once for number. A negative difference means the angler is happier with what the rules allow than with what the water gives.

### Size

`r paste0("D4i and D4j ask about the size of the preferred fish, one for the fish caught and one for the fish that may be harvested. The difference is size caught minus size harvestable. ", caption.ch4gap, " ", caption.ch3rows)`

```{r ch4gapSizeCvA}
CreateFlex(Ch4GapTable(d, "D4i", "D4j", "Size caught", "Size harvestable"))
```

```{r ch4gapSizeCvAPlot, fig.width=6.5, fig.height=5}
Ch4DumbbellPlot(
  d, "D4i", "D4j", "Size of fish caught", "Size allowed to harvest",
  titleText = "Satisfaction with the size of the preferred fish caught, and with the size that may be harvested",
  subtitleText = "1 = Strongly Disagree to 5 = Strongly Agree. Rows are sorted by the caught-minus-allowed difference"
)
```

`r run_pagebreak()`

### Number

`r paste0("D4k and D4l repeat the comparison for the number of fish. The difference is number caught minus number harvestable. ", caption.ch4gap, " ", caption.ch3rows)`

```{r ch4gapNumCvA}
CreateFlex(Ch4GapTable(d, "D4k", "D4l", "Number caught", "Number harvestable"))
```

```{r ch4gapNumCvAPlot, fig.width=6.5, fig.height=5}
Ch4DumbbellPlot(
  d, "D4k", "D4l", "Number of fish caught", "Number allowed to harvest",
  titleText = "Satisfaction with the number of the preferred fish caught, and with the number that may be harvested",
  subtitleText = "1 = Strongly Disagree to 5 = Strongly Agree. Rows are sorted by the caught-minus-allowed difference"
)
```

Across all anglers the allowed side is rated above the catch side, for size (`r G4(ch4.gapSize, "Overall")` ± `r G4ci(ch4.gapSize, "Overall")`) and for number (`r G4(ch4.gapNum, "Overall")` ± `r G4ci(ch4.gapNum, "Overall")`). The pattern is broad rather than driven by a few groups. On size, `r length(GapSet(ch4.gapSize, "neg"))` groups are flagged (Walleye / Sauger, Bass, Largemouth bass, Panfish / Sunfish, Crappie and Bluegill / Sunfish) and every one goes the same way. On number, `r length(GapSet(ch4.gapNum, "neg"))` of the `r nrow(ch4.gapNum) - 1` groups are flagged, and again none goes the other way. For most of the survey the harvest rules draw less complaint than the catch does, which is the reading that has run through this chapter: where anglers are dissatisfied, the place to look first is the fishery.

The size of the gap depends on the group in a way that matches the catch results above. Walleye / Sauger anglers have a larger gap on number (`r G4(ch4.gapNum, "Walleye / Sauger")`) than on size (`r G4(ch4.gapSize, "Walleye / Sauger")`), which fits their shortfall in numbers caught. Bass anglers show the reverse, a larger gap on size (`r G4(ch4.gapSize, "Bass")`) than on number (`r G4(ch4.gapNum, "Bass")`), which fits their lower satisfaction with the size they catch. Catfish anglers are not flagged on size (`r G4(ch4.gapSize, "Catfish")` ± `r G4ci(ch4.gapSize, "Catfish")`) but are on number (`r G4(ch4.gapNum, "Catfish")` ± `r G4ci(ch4.gapNum, "Catfish")`), so their gap is a numbers gap only.

Wiper anglers are the exception, and only on size. They rate the size they catch above the size they may keep (`r G4(ch4.gapSize, "Wiper")` ± `r G4ci(ch4.gapSize, "Wiper")`, `r G4n(ch4.gapSize, "Wiper")` respondents), and they are the only group with a positive size difference. On number they are not separated from zero (`r G4(ch4.gapNum, "Wiper")` ± `r G4ci(ch4.gapNum, "Wiper")`). The result sits comfortably with the rest of the Wiper profile. They are the group most satisfied with the size of fish they catch (`r M3(tt4$D4i, "Wiper")`), the most supportive of regulations to increase size and the most willing to harvest fewer fish for larger ones (both in Chapter 2). Their rating of the size they may keep is lower, at `r M3(tt4$D4j, "Wiper")`. What falls short for this group is the size that can be taken home, which is a question about length limits more than about the fishery, and worth having in view when wiper length limits are reviewed.

Two cautions apply. The Wiper estimate rests on `r G4n(ch4.gapSize, "Wiper")` respondents, and although its interval stays above zero (the lower end is `r GLo(ch4.gapSize, "Wiper")`), the direction is more dependable than the size. And these are `r 2 * (nrow(ch4.gapSize) - 1)` comparisons (`r nrow(ch4.gapSize) - 1` groups, two items) with no adjustment, so a handful of flagged groups could appear by chance alone. The number flagged here is far larger than that, which is why the overall pattern can be trusted, and Wiper stands out because every other flagged group points the other way.

`r run_pagebreak()`

# Chapter 5: Angler Type Profiles

```{r ch5Setup}
# Additive only: columns are added to d, but no row is added, dropped, or
# reweighted, so nothing in Chapters 1-4 changes. The model is never fitted
# here; Ch5LPALoadResults() reads the saved results (D152) and errors if they
# were fitted to different data.
nBeforeCh5 <- nrow(d)
d <- Ch5LPAGate(d)
ch5.frame <- Ch5LPAFrame(d)
ch5.models <- Ch5LPALoadResults(ch5.frame)
ch5.diag <- Ch5LPADiagnostics(ch5.models)
ch5.selected <- Ch5LPASelect(ch5.diag)
ch5.sel <- ch5.diag %>% filter(Model == ch5.selected)
ch5.k <- ch5.sel$Classes
d <- Ch5LPAAssign(d, ch5.models[[ch5.selected]])

ch5.nFitted <- sum(d$lpa_fitted)
ch5.nUnassigned <- sum(d$lpa_class == ch5.lpa.unassigned)
ch5.long <- Ch5ClassBySpeciesLong(d)
ch5.prof <- Ch5LPAProfileLong(d, l)

ch5.floorFail <- ch5.diag %>%
  filter(StatusCode %in% c(0, 1), !PassSize) %>%
  arrange(Classes)
ch5.spikes <- purrr::map_dfr(
  ch5.diag$Model[!ch5.diag$StatusCode %in% c(0, 1)],
  function(m) Ch5LPASpike(ch5.models[[m]], ch5.frame)
) %>%
  left_join(ch5.diag %>% select(Model, Profiles = Classes), by = "Model") %>%
  arrange(Profiles)
ch5.equalBIC <- ch5.diag %>% filter(Variances == "equal") %>% arrange(Classes) %>% pull(BIC)

caption.ch5diag <- "BIC is minus twice the log-likelihood plus the number of estimated parameters times the natural log of the number of fitted respondents; lower values indicate better fit. Relative entropy runs from 0 to 1, with 1 meaning every respondent is assigned with certainty. The lowest mean assigned probability is the average membership probability among the respondents assigned to a profile, for the profile where that average is smallest. OpenMx status 0 or 1 indicates the estimation converged. All values in this table are unweighted model quantities."

stopifnot(
  nrow(d) == nBeforeCh5,
  # D156: the final selection. A different result means the data or the rule changed.
  ch5.selected == "equal_6",
  length(ch5.models) == length(Ch5LPAModelNames()),
  ch5.nFitted == nrow(ch5.frame),
  ch5.nUnassigned == sum(!d$lpa_fitted),
  !anyNA(d$lpa_class),
  all(as.vector(table(d$lpa_class))[seq_len(ch5.k)] ==
    tabulate(ch5.models[[ch5.selected]]$modal, ch5.k)),
  # Unassigned is a level, so every row's shares sum to 100
  all(abs(tapply(ch5.long$Value, ch5.long$Column, sum) - 100) < 1e-6),
  nrow(ch5.prof) == (ch5.k + 1) * length(ch5.lpa.vars),
  !anyNA(ch5.prof$Value),
  # The exclusion text describes exactly these cases (F76, F77)
  nrow(ch5.floorFail) == 2,
  nrow(ch5.spikes) == 2,
  all(ch5.spikes$AtMax == ch5.spikes$Answered),
  length(unique(ch5.spikes$Variable)) == 1,
  all(diff(ch5.equalBIC) < 0)
)
```

`r paste0("This chapter groups anglers into profiles using a latent profile analysis of eleven scale scores reported in Chapter 3: the four angler-attitude scales, the four motivation scales, and the three regulation scales. One model is fitted to the whole report universe, so the profiles are defined once and are the same in every preferred-species row; the tables below report how each row's respondents are distributed across them. The model is fitted without the survey weights. Every percentage and mean reported from it is weighted, with intervals built on the Kish effective N and raw unweighted counts displayed, as in Chapters 1 to 4.")`

`r paste0(FmtCount(ch5.nFitted), " of the ", FmtCount(nrow(d)), " respondents in this report's universe (", formatC(100 * ch5.nFitted / nrow(d), format = "f", digits = 1), "%) answered at least ", ch5.lpa.min.scales, " of the eleven scales and were included in the fit. Scales that a fitted respondent left blank are handled within the model rather than imputed. The other ", FmtCount(ch5.nUnassigned), " respondents are reported as Unassigned rather than dropped. Profiles are numbered 1 to ", ch5.k, " in the order the estimation produced them; the numbers are labels and carry no order.")`

`r sect_portrait()`

## Choosing the number of profiles

`r paste0("Models with 1 to ", max(ch5.lpa.classes), " profiles were fitted under two within-profile variance structures: equal, in which every profile shares one variance per scale, and varying, in which each profile has its own. The equal structure was extended to ", max(ch5.lpa.extend.equal), " profiles. The model used in the rest of this chapter is the one with the lowest BIC among models that converged, whose smallest profile holds at least ", 100 * ch5.lpa.min.class.prop, " percent of fitted respondents, and whose relative entropy is at least ", formatC(ch5.lpa.min.entropy, format = "f", digits = 2), ". That is the ", ch5.k, "-profile ", ch5.sel$Variances, "-variance model.  ", caption.ch5diag)`

```{r ch5Diagnostics}
CreateFlex(Ch5LPADiagnosticsTable(ch5.diag, ch5.selected))
```

`r paste0("Four models with a lower BIC than the selected model are not eligible. The ", paste(ch5.floorFail$Classes, collapse = "- and "), "-profile equal-variance models converged, but their smallest profiles hold ", paste(formatC(100 * ch5.floorFail$SmallestClassProp, format = "f", digits = 1), collapse = " and "), " percent of fitted respondents. BIC is lower at every larger equal-variance model fitted, so the selected model is the largest eligible equal-variance model rather than the point at which BIC stops decreasing. The ", paste(ch5.spikes$Profiles, collapse = "- and "), "-profile varying-variance models did not converge (OpenMx status ", paste(unique(ch5.diag$StatusCode[ch5.diag$Model %in% ch5.spikes$Model]), collapse = ", "), "). In each, one profile (", paste(FmtCount(ch5.spikes$ClassN), collapse = " and "), " respondents) contains only respondents at the scale maximum of ", ch5.spikes$Max[1], " on the ", ScaleLabel(ch5.spikes$Variable[1], l), " regulation scale among those who answered it (", paste0(ch5.spikes$AtMax, " of ", ch5.spikes$Answered, collapse = " and "), "), and that profile's estimated variance on the scale is effectively zero (", paste(formatC(ch5.spikes$Variance, format = "e", digits = 1), collapse = " and "), ").")`

## Assignment certainty

`r paste0("Each fitted respondent is assigned to the profile with the highest estimated membership probability. The table below shows how certain those assignments are, by the number of scales the respondent answered. The values are unweighted model quantities for the ", FmtCount(ch5.nFitted), " fitted respondents.")`

```{r ch5Certainty}
CreateFlex(Ch5LPACertaintyTable(d))
```

`r sect_landscape()`

## Profile means

`r paste0("The two figures below show the weighted mean of each scale for the respondents assigned to each profile, with 95 percent confidence intervals. These are weighted means of the assigned respondents, not the unweighted means the model estimated for each profile. The first figure places the profiles side by side across the eleven scales.")`

```{r ch5ProfileLines, fig.width=6.5, fig.height=5.5}
Ch5LPAProfileLinePlot(ch5.prof, "Scale means by profile")
```

`r paste0("The second figure shows one panel per scale, with the profiles along the horizontal axis and the Overall weighted mean for every respondent who answered that scale as a dashed line.")`

```{r ch5ProfileFacets, fig.width=6.5, fig.height=7}
Ch5LPAProfileFacetPlot(ch5.prof, "Scale means by profile, one panel per scale")
```

`r sect_portrait()`

`r paste0("The values behind both figures are below. The Overall column is computed on every respondent in the universe who answered the scale, including Unassigned respondents, and equals the Overall row of the Chapter 3 scale tables.  ", caption.ch3means, "  ", caption.raked)`

```{r ch5ProfileTable}
stopifnot(Ch5ImagesPresent())
CreateFlex(Ch5LPAProfileTable(ch5.prof), mergeOnFirst = TRUE) %>% Ch5IconHeader()
```

## Profiles on other survey questions

```{r ch5CompareSetup}
# D163: questions chosen by the user (prompt 123) before any results were seen.
ch5.dcmp <- Ch5LPACompareData(d)
ch5.cmp <- Ch5LPACompareLong(ch5.dcmp)
ch5.mix <- Ch5LPAClassMix(d)

# For every row, Overall N minus the six profile Ns must equal the Unassigned
# respondents who have that measure: nobody lost, nobody double-counted.
ch5.cmpN <- ch5.cmp %>%
  group_by(var, Kind) %>%
  summarise(
    gap = N[Class == "Overall"] - sum(N[Class != "Overall"]),
    .groups = "drop"
  ) %>%
  mutate(unassigned = purrr::map_int(var, function(v) {
    sum(!is.na(ch5.dcmp[[v]]) & ch5.dcmp$lpa_class == ch5.lpa.unassigned)
  }))
stopifnot(
  nrow(ch5.cmp) == nrow(ch5.compare.spec) * (ch5.k + 1),
  !anyNA(ch5.cmp$Value),
  all(ch5.cmpN$gap == ch5.cmpN$unassigned),
  all(abs(tapply(ch5.mix$Value, ch5.mix$Class, sum) - 100) < 1e-6)
)
```

`r paste0("The table below compares the profiles on other survey questions. Each question keeps the universe it has in Chapter 3, so N differs by row, and the Overall column equals the Overall row of the corresponding Chapter 3 table. Unassigned respondents are counted in Overall only and have no column of their own. The river and stream row counts a respondent who fished the Missouri River, the Platte River, or other streams, rivers, and canals; it combines three Chapter 3 waterbody types and has no single Chapter 3 counterpart. Percentage and mean cells show the weighted value with a 95 percent confidence interval, followed by N. Median cells show the lower limit, the weighted median and the upper limit, followed by N, as in Chapter 3. Satisfaction is scored from 1, Very satisfied, to 5, Very dissatisfied, as in Chapter 3.  ", caption.raked)`

```{r ch5Compare}
CreateFlex(Ch5LPACompareTable(ch5.cmp)) %>% Ch5IconHeader()
```

`r sect_landscape()`

## The six profiles

```{r ch5Describe}
# D161: interpretive descriptions, added at the user's request (prompt 122).
# Every comparative claim in the paragraphs below is asserted here, so a change
# in the data or model stops the render instead of leaving the prose wrong.
ch5.std <- Ch5LPAStd(ch5.prof, d)
ch5.classN <- table(d$lpa_class)
z <- function(cls, v) Ch5Cell(ch5.std, cls, v)$Z
top <- function(v) Ch5Extreme(ch5.std, v, which.max)
bottom <- function(v) Ch5Extreme(ch5.std, v, which.min)
reg.vars <- c("reg_comprehension", "reg_sitesupport", "reg_uniform")

stopifnot(
  nrow(ch5.std) == ch5.k * length(ch5.lpa.vars),
  # Class 1
  top("attitude_harvest") == 1, bottom("reg_comprehension") == 1,
  bottom("reg_sitesupport") == 1, top("reg_uniform") == 1,
  z(1, "attitude_catch") > 0, z(1, "attitude_numbers") > 0,
  abs(z(1, "attitude_size")) < 0.2, all(abs(sapply(motivation.vars, z, cls = 1)) < 0.3),
  # Class 2
  all(sapply(attitude.vars, z, cls = 2) < 0),
  names(which.min(sapply(motivation.vars, z, cls = 2))) == "motivation_resource",
  z(2, "motivation_natural") > 0, z(2, "motivation_social") > 0,
  z(2, "reg_uniform") > 0, all(abs(sapply(reg.vars, z, cls = 2)) < 0.5),
  # Class 3
  z(3, "attitude_size") > 0, z(3, "attitude_catch") > 0, z(3, "attitude_harvest") < 0,
  all(sapply(motivation.vars, z, cls = 3) < 0.05),
  z(3, "reg_comprehension") > 0.5, z(3, "reg_sitesupport") > 0.5, z(3, "reg_uniform") < -0.5,
  # Class 4
  all(sapply(motivation.vars, top) == 4), top("attitude_size") == 4,
  z(4, "attitude_numbers") > 0, abs(z(4, "attitude_catch")) < 0.2,
  abs(z(4, "attitude_harvest")) < 0.2, z(4, "reg_sitesupport") > 0,
  # Class 5
  all(sapply(motivation.vars, bottom) == 5),
  abs(z(5, "attitude_catch")) < 0.2, abs(z(5, "attitude_harvest")) < 0.2,
  z(5, "attitude_numbers") < 0, z(5, "attitude_size") < 0,
  all(abs(sapply(reg.vars, z, cls = 5)) < 0.35),
  # Class 6
  all(sapply(attitude.vars, bottom) == 6), top("reg_comprehension") == 6,
  top("reg_sitesupport") == 6, bottom("reg_uniform") == 6,
  z(6, "motivation_natural") > 0, z(6, "motivation_social") > 0, z(6, "motivation_resource") < 0,
  # Species shares quoted below
  # Walleye / Sauger has the smallest Class 6 share of any displayed family group
  with(
    ch5.long[ch5.long$Class == "Class 6" & !ch5.long$Suppressed & ch5.long$Type == "Family", ],
    Column[which.min(Value)] == "Walleye / Sauger"
  ),
  with(
    ch5.long[ch5.long$Class == "Class 6" & !ch5.long$Suppressed & ch5.long$Type != "Overall", ],
    Column[which.max(Value)] == "Bluegill / Sunfish"
  )
)
# Comparison claims in the second paragraphs (D163)
cv <- function(cls, v, kind) Ch5CmpRow(ch5.cmp, cls, v, kind)$Value
hi <- function(v, kind) Ch5CmpRank(ch5.cmp, v, kind, which.max)
lo <- function(v, kind) Ch5CmpRank(ch5.cmp, v, kind, which.min)
activity <- list(
  c("cmpTourney", "pct"), c("cmpKayak", "pct"), c("cmpIce", "pct"),
  c("cmpStream", "pct"), c("cmpPark", "pct"), c("cmpOutState", "pct"),
  c("cmpLiveScope", "pct")
)
femaleTop2 <- ch5.cmp %>%
  filter(var == "cmpFemale", Class != "Overall") %>%
  slice_max(Value, n = 2) %>%
  pull(Class) %>%
  as.character()
stopifnot(
  # Class 1
  abs(cv(1, "cmpDays", "mean") - cv("Overall", "cmpDays", "mean")) < 3,
  cv(1, "cmpGuide", "pct") > cv("Overall", "cmpGuide", "pct"),
  cv(1, "cmpIce", "pct") > cv("Overall", "cmpIce", "pct"),
  cv(1, "cmpBoat", "pct") > cv("Overall", "cmpBoat", "pct"),
  hi("cmpSatisfaction", "mean") == 1,
  # Class 2
  cv(2, "cmpDays", "median") < cv("Overall", "cmpDays", "median"),
  cv(2, "cmpTourney", "pct") < cv("Overall", "cmpTourney", "pct"),
  cv(2, "cmpIce", "pct") < cv("Overall", "cmpIce", "pct"),
  cv(2, "cmpSatisfaction", "mean") < cv("Overall", "cmpSatisfaction", "mean"),
  setequal(femaleTop2, c("Class 2", "Class 6")),
  # Class 3
  cv(3, "cmpDays", "mean") > cv("Overall", "cmpDays", "mean"),
  cv(3, "cmpDays", "median") > cv("Overall", "cmpDays", "median"),
  hi("cmpGuide", "pct") == 3, hi("cmpPrivate", "pct") == 3,
  abs(cv(3, "cmpTourney", "pct") - cv("Overall", "cmpTourney", "pct")) < 2,
  # Class 4 is the profile most associated with tournaments (prompt 124)
  hi("cmpTourney", "pct") == 4, top("motivation_resource") == 4,
  cv(3, "cmpMiles", "median") < cv("Overall", "cmpMiles", "median"),
  lo("cmpFemale", "pct") == 3,
  # Class 4
  hi("cmpDays", "mean") == 4, hi("cmpDays", "median") == 4,
  all(vapply(activity, function(a) hi(a[1], a[2]), integer(1)) == 4),
  lo("cmpAge", "mean") == 4,
  # Class 5
  lo("cmpDays", "mean") == 5, lo("cmpDays", "median") == 5,
  all(vapply(activity[-1], function(a) lo(a[1], a[2]), integer(1)) == 5),
  hi("cmpAge", "mean") == 5,
  # Class 6
  cv(6, "cmpDays", "median") < cv("Overall", "cmpDays", "median"),
  lo("cmpGuide", "pct") == 6, lo("cmpBoat", "pct") == 6, lo("cmpTourney", "pct") == 6,
  cv(6, "cmpMiles", "median") < cv("Overall", "cmpMiles", "median"),
  lo("cmpSatisfaction", "mean") == 6
)
A <- function(cls, v, kind) {
  paste0(Ch5CmpFmt(ch5.cmp, cls, v, kind), ", against ", Ch5CmpFmt(ch5.cmp, "Overall", v, kind), " overall")
}
V <- function(cls, v, kind) Ch5CmpFmt(ch5.cmp, cls, v, kind)
MIX <- function(cls) Ch5MixCaveat(ch5.mix, cls, hidden = unique(ch5.long$Column[ch5.long$Suppressed]))

M <- function(cls, v) Ch5M(ch5.std, cls, v)
MZ <- function(cls, v) Ch5MZ(ch5.std, cls, v)
S <- function(cls, col) Ch5Share(ch5.long, cls, col)
Sov <- function(cls) Ch5Share(ch5.long, cls, "Overall", ci = FALSE)
```

`r paste0("The six profiles are listed below with the icon that marks each profile's column in the tables of this chapter. Shares are weighted percentages of respondents; N is the number of respondents assigned to the profile.")`

```{r ch5IconKey}
# D169: key table for the profile icons (prompt 126).
Ch5IconKeyTable(
  shares = vapply(seq_len(ch5.k), Sov, character(1)),
  ns = as.integer(ch5.classN[paste("Class", seq_len(ch5.k))])
)
```

`r paste0("The paragraphs below describe each profile by the scales on which it differs most from the Overall mean. Means are the weighted means in the profile means table; the figure after each mean is its distance from the Overall mean in standard deviations of the Overall weighted distribution (SD). Two scale names need a note: the Fishery resource motivation scale is made up of catch outcomes (competing for prizes, obtaining fish to eat, catching a trophy, the fun of catching), and the Simplification regulation scale measures agreement with uniform statewide regulations. Species shares are the row percentages from the profiles-by-preferred-species table at the end of this chapter, with their confidence intervals. The label and the closing picture in each paragraph are an interpretive summary of the eleven scale scores. They are not measured directly, and traits beyond those scales, such as how often or how an angler fishes, are not established by these data.")`

`r paste0("The second paragraph for each profile compares it with the Overall column on the other survey questions in the table above; the values quoted are from that table, and its confidence intervals show that several of the differences described are small relative to their precision. Where a family group makes up at least ", ch5.mix.gap, " percentage points more of a profile than of all assigned respondents, the paragraph names it, unless its row is below the effective-N floor and therefore not shown, because questions that vary by species may partly reflect that mix rather than the profile itself.")`

### Class 1: `r ch5.class.labels[1]`

```{r ch5Photo1, fig.width=6.5, fig.height=3.55, dev="jpeg", dpi=250}
Ch5PhotoWithIcon(1)
```

*`r paste0("Class 1: ", ch5.class.labels[1])`*

`r paste0("Class 1 holds ", Sov(1), " of respondents (n = ", FmtCount(ch5.classN[['Class 1']]), "). It has the highest harvest score of any profile (", MZ(1, 'attitude_harvest'), ") and is above average on needing to catch something (", M(1, 'attitude_catch'), ") and on catching many fish (", M(1, 'attitude_numbers'), "). Size matters no more than average (", M(1, 'attitude_size'), "), and its motivations sit near the Overall means. What sets it apart is regulations: it reports the least comprehension of the rules (", MZ(1, 'reg_comprehension'), "), the least support for site-specific rules (", M(1, 'reg_sitesupport'), "), and the strongest preference for uniform statewide rules (", MZ(1, 'reg_uniform'), "). Picture someone who fishes for a meal, measures a trip by what goes in the cooler, and finds a patchwork of lake-specific rules confusing. Class 1 makes up ", S(1, 'Walleye / Sauger'), " of Walleye / Sauger, ", S(1, 'Crappie'), " of Crappie and ", S(1, 'Panfish / Sunfish'), " of Panfish / Sunfish anglers, against ", Sov(1), " overall.")`

`r paste0("On the other survey questions, Class 1 fishes about as often as anglers overall (mean days ", A(1, 'cmpDays', 'mean'), "). It is more likely than average to have hired a guide (", A(1, 'cmpGuide', 'pct'), "), to have ice fished (", A(1, 'cmpIce', 'pct'), ") and to have fished from a motorized boat (", A(1, 'cmpBoat', 'pct'), "). It reports the lowest overall satisfaction of any profile (mean ", A(1, 'cmpSatisfaction', 'mean'), ", where higher means less satisfied). ", MIX(1))`

### Class 2: `r ch5.class.labels[2]`

```{r ch5Photo2, fig.width=6.5, fig.height=3.55, dev="jpeg", dpi=250}
Ch5PhotoWithIcon(2)
```

*`r paste0("Class 2: ", ch5.class.labels[2])`*

`r paste0("Class 2 holds ", Sov(2), " of respondents (n = ", FmtCount(ch5.classN[['Class 2']]), "). It is below average on all four catch attitudes: catch something ", M(2, 'attitude_catch'), ", numbers ", M(2, 'attitude_numbers'), ", size ", M(2, 'attitude_size'), ", harvest ", M(2, 'attitude_harvest'), ". Its lowest motivation is catch outcomes (", MZ(2, 'motivation_resource'), "), while the outdoors (", M(2, 'motivation_natural'), ") and social (", M(2, 'motivation_social'), ") motivations run slightly above average. Its regulation scores are middling, with a slight lean toward uniform rules (", M(2, 'reg_uniform'), "). Picture someone who goes for the day out, the company and the water, and for whom a fishless trip is not a failed trip. Class 2 makes up ", S(2, 'No preference'), " of No preference and ", S(2, 'Trout'), " of Trout anglers, against ", Sov(2), " overall.")`

`r paste0("On the other survey questions, Class 2 fishes less often than average (median days ", A(2, 'cmpDays', 'median'), ") and seldom fishes tournaments (", A(2, 'cmpTourney', 'pct'), "). It ice fishes less often than average (", A(2, 'cmpIce', 'pct'), ") and is more satisfied than average (mean ", A(2, 'cmpSatisfaction', 'mean'), "). Together with Class 6 it has the highest share of women of any profile (", V(2, 'cmpFemale', 'pct'), ", and ", V(6, 'cmpFemale', 'pct'), " in Class 6, against ", V('Overall', 'cmpFemale', 'pct'), " overall). ", MIX(2))`

### Class 3: `r ch5.class.labels[3]`

```{r ch5Photo3, fig.width=6.5, fig.height=3.55, dev="jpeg", dpi=250}
Ch5PhotoWithIcon(3)
```

*`r paste0("Class 3: ", ch5.class.labels[3])`*

`r paste0("Class 3 holds ", Sov(3), " of respondents (n = ", FmtCount(ch5.classN[['Class 3']]), "). It is above average on size (", MZ(3, 'attitude_size'), ") and on needing a catch (", M(3, 'attitude_catch'), "), but below average on harvest (", M(3, 'attitude_harvest'), "): it wants a fish on the line, preferably a good one, and then lets it go. Its motivations are at or slightly below average (social ", MZ(3, 'motivation_social'), "). It is strongly engaged with regulations, with high comprehension (", MZ(3, 'reg_comprehension'), "), high support for site-specific rules (", MZ(3, 'reg_sitesupport'), "), and a low preference for uniform rules (", MZ(3, 'reg_uniform'), "). Picture an angler, often a bass angler, who reads the regulations and values rules tailored to each lake. Class 3 makes up ", S(3, 'Bass'), " of Bass, ", S(3, 'Largemouth bass'), " of Largemouth bass and ", S(3, 'Flathead catfish'), " of Flathead catfish anglers, against ", Sov(3), " overall.")`

`r paste0("On the other survey questions, Class 3 fishes more often than average (mean days ", A(3, 'cmpDays', 'mean'), "; median ", A(3, 'cmpDays', 'median'), "). It has the highest rate of hiring a guide of any profile (", A(3, 'cmpGuide', 'pct'), ") and the highest use of private areas (", A(3, 'cmpPrivate', 'pct'), "); its tournament participation is close to the overall rate (", A(3, 'cmpTourney', 'pct'), "). Its median distance to its most visited water is ", V(3, 'cmpMiles', 'median'), " miles, against ", V('Overall', 'cmpMiles', 'median'), " overall, and it has the lowest share of women of any profile (", A(3, 'cmpFemale', 'pct'), "). ", MIX(3))`

### Class 4: `r ch5.class.labels[4]`

```{r ch5Photo4, fig.width=6.5, fig.height=3.55, dev="jpeg", dpi=250}
Ch5PhotoWithIcon(4)
```

*`r paste0("Class 4: ", ch5.class.labels[4])`*

`r paste0("Class 4 holds ", Sov(4), " of respondents (n = ", FmtCount(ch5.classN[['Class 4']]), "). It has the highest score of any profile on all four motivations: challenge and relaxation (", MZ(4, 'motivation_pp'), "), outdoors (", MZ(4, 'motivation_natural'), "), social (", MZ(4, 'motivation_social'), "), and catch outcomes (", MZ(4, 'motivation_resource'), "). It is also the most size-oriented profile (", MZ(4, 'attitude_size'), ") and is above average on numbers (", M(4, 'attitude_numbers'), "), with average scores on needing a catch (", M(4, 'attitude_catch'), ") and on harvest (", M(4, 'attitude_harvest'), "). Its support for site-specific rules is above average (", M(4, 'reg_sitesupport'), "). The catch-outcomes scale, on which no other profile scores as high, includes competing for prizes or money. Picture the angler for whom fishing is a central hobby: every reason to go matters, trophies and tournament competition included. Class 4 makes up ", S(4, 'Smallmouth bass'), " of Smallmouth bass anglers, against ", Sov(4), " overall.")`

`r paste0("On the other survey questions, Class 4 is the most active profile and the one most likely to fish tournaments (", A(4, 'cmpTourney', 'pct'), "), although tournament anglers remain a small share of it. It has the highest mean days fished (", A(4, 'cmpDays', 'mean'), ") and median days fished (", A(4, 'cmpDays', 'median'), "), and the highest rates of any profile for using a kayak or canoe (", A(4, 'cmpKayak', 'pct'), "), ice fishing (", A(4, 'cmpIce', 'pct'), "), fishing rivers and streams (", A(4, 'cmpStream', 'pct'), "), fishing waters that require a Park Entry Permit (", A(4, 'cmpPark', 'pct'), "), fishing outside Nebraska (", A(4, 'cmpOutState', 'pct'), ") and using live-imaging sonar (", A(4, 'cmpLiveScope', 'pct'), "). It is also the youngest profile (mean age ", A(4, 'cmpAge', 'mean'), "). ", MIX(4))`

### Class 5: `r ch5.class.labels[5]`

```{r ch5Photo5, fig.width=6.5, fig.height=3.55, dev="jpeg", dpi=250}
Ch5PhotoWithIcon(5)
```

*`r paste0("Class 5: ", ch5.class.labels[5])`*

`r paste0("Class 5 holds ", Sov(5), " of respondents (n = ", FmtCount(ch5.classN[['Class 5']]), "). It has the lowest score of any profile on all four motivations: challenge and relaxation (", MZ(5, 'motivation_pp'), "), outdoors (", MZ(5, 'motivation_natural'), "), social (", MZ(5, 'motivation_social'), "), and catch outcomes (", MZ(5, 'motivation_resource'), "). It is near average on needing a catch (", M(5, 'attitude_catch'), ") and on harvest (", M(5, 'attitude_harvest'), "), below average on numbers (", MZ(5, 'attitude_numbers'), ") and size (", MZ(5, 'attitude_size'), "), and close to average on the three regulation scales. Picture a licence holder for whom fishing is incidental rather than a pursuit in its own right. Uniformly low importance ratings can also reflect how a respondent uses the rating scale. Class 5 makes up ", S(5, 'No preference'), " of No preference anglers, against ", Sov(5), " overall.")`

`r paste0("On the other survey questions, Class 5 is the least active profile. It has the lowest mean days fished (", A(5, 'cmpDays', 'mean'), ") and median days fished (", A(5, 'cmpDays', 'median'), "), and the lowest rates of any profile for using a kayak or canoe (", A(5, 'cmpKayak', 'pct'), "), ice fishing (", A(5, 'cmpIce', 'pct'), "), fishing rivers and streams (", A(5, 'cmpStream', 'pct'), "), fishing waters that require a Park Entry Permit (", A(5, 'cmpPark', 'pct'), "), fishing outside Nebraska (", A(5, 'cmpOutState', 'pct'), ") and using live-imaging sonar (", A(5, 'cmpLiveScope', 'pct'), "). It is the oldest profile (mean age ", A(5, 'cmpAge', 'mean'), "). ", MIX(5))`

### Class 6: `r ch5.class.labels[6]`

```{r ch5Photo6, fig.width=6.5, fig.height=3.55, dev="jpeg", dpi=250}
Ch5PhotoWithIcon(6)
```

*`r paste0("Class 6: ", ch5.class.labels[6])`*

`r paste0("Class 6 holds ", Sov(6), " of respondents (n = ", FmtCount(ch5.classN[['Class 6']]), "), the smallest profile. It has the lowest score of any profile on all four catch attitudes: catch something ", M(6, 'attitude_catch'), ", numbers ", M(6, 'attitude_numbers'), " (", sprintf("%+.2f", z(6, 'attitude_numbers')), " SD), size ", M(6, 'attitude_size'), ", harvest ", M(6, 'attitude_harvest'), "; catching and keeping fish are close to irrelevant to it. It is motivated by the outdoors (", M(6, 'motivation_natural'), ") and by social reasons (", M(6, 'motivation_social'), ") but not by catch outcomes (", M(6, 'motivation_resource'), "). It has the highest comprehension of the rules (", M(6, 'reg_comprehension'), ") and support for site-specific rules (", M(6, 'reg_sitesupport'), ") of any profile, and the lowest preference for uniform rules (", M(6, 'reg_uniform'), "). Picture someone who values the experience and well-managed waters over the catch. Class 6 makes up ", S(6, 'Walleye / Sauger'), " of Walleye / Sauger anglers, its smallest share of any displayed family group; its largest share of any displayed row is ", S(6, 'Bluegill / Sunfish'), " of Bluegill / Sunfish anglers.")`

`r paste0("On the other survey questions, Class 6 fishes less often than average (median days ", A(6, 'cmpDays', 'median'), ") and has the lowest rates of any profile for fishing tournaments (", A(6, 'cmpTourney', 'pct'), "), hiring a guide (", A(6, 'cmpGuide', 'pct'), ") and fishing from a motorized boat (", A(6, 'cmpBoat', 'pct'), "). Its median distance to its most visited water is ", V(6, 'cmpMiles', 'median'), " miles, against ", V('Overall', 'cmpMiles', 'median'), " overall. It reports the highest overall satisfaction of any profile (mean ", A(6, 'cmpSatisfaction', 'mean'), ", where lower means more satisfied), and, with Class 2, the highest share of women (", A(6, 'cmpFemale', 'pct'), "). With ", FmtCount(ch5.classN[['Class 6']]), " respondents it is the smallest profile, and most of its intervals in the table are correspondingly wide. ", MIX(6))`

`r sect_portrait()`

## Profiles by preferred species

`r paste0("The table below gives, for each preferred-species row, the weighted percentage of its respondents assigned to each profile, with Unassigned as a column so that each row sums to 100. The rows overlap, as elsewhere in this report, and must not be totalled. Where a row has no respondents in a profile, the percentage is 0.0 and the interval has zero width. ", Ch5SuppressedNote(ch5.long), " This is the only chapter of the report that withholds rows; the effective-N floor was set before the model was fitted.  ", caption.ch3selectone, "  ", caption.raked)`

```{r ch5ClassBySpecies}
CreateFlex(Ch5ClassBySpeciesTable(d, ch5.long)) %>% Ch5IconHeader()
```

```{r ch5FamilyMixSetup}
# D171 (prompt 129), cards D173 (prompt 131): interpretive text on family-group
# makeup, including management implications, at the user's request. Claims are asserted here.
ch5.fam <- ch5.long %>%
  filter(Type %in% c("Overall", "Family"), !Suppressed, Class != ch5.lpa.unassigned)
fv <- function(col, cls) ch5.fam$Value[ch5.fam$Column == col & ch5.fam$Class == paste("Class", cls)]
gap <- function(col, cls) fv(col, cls) - fv("Overall", cls)
top.cls <- function(col) {
  x <- ch5.fam %>% filter(Column == col)
  as.integer(sub("Class ", "", x$Class[which.max(x$Value)]))
}
fam.cols <- setdiff(unique(ch5.fam$Column), "Overall")
fam.n <- ch5.long %>% filter(Type == "Family") %>% distinct(Column, ColumnN)
fam.unassigned <- ch5.long %>% filter(Type == "Family", Class == ch5.lpa.unassigned)
# Trout is the smallest family group, so it has the widest intervals
small.ci <- ch5.fam %>% filter(Column == "Trout") %>% pull(CI) %>% max()
ch5.splitSpecies <- banner.definition$Column[banner.definition$Type == "Split"]
FN <- function(col) FmtCount(fam.n$ColumnN[fam.n$Column == col])
SA <- function(cls, col) paste0(S(cls, col), " against ", Sov(cls), " overall")

# Family-group means on the 11 profile scales, standardized against Overall
# exactly as the profiles are (Ch5FamilyScales). Card text cites these.
ch5.fs <- Ch5FamilyScales(d)
FS <- function(col, v) {
  r <- ch5.fs[ch5.fs$Column == col & ch5.fs$var == v, ]
  stopifnot(nrow(r) == 1)
  r
}
zf <- function(col, v) FS(col, v)$Z
FZ <- function(col, v) {
  r <- FS(col, v)
  paste0(formatC(r$Value, format = "f", digits = 1), ", ", sprintf("%+.2f", r$Z), " SD")
}
fam.top <- function(v) fam.cols[which.max(vapply(fam.cols, zf, numeric(1), v = v))]
fam.bot <- function(v) fam.cols[which.min(vapply(fam.cols, zf, numeric(1), v = v))]
mot.vars <- c("motivation_pp", "motivation_natural", "motivation_social", "motivation_resource")
att.vars <- c("attitude_catch", "attitude_numbers", "attitude_size", "attitude_harvest")
zs <- function(col, vars) vapply(vars, function(v) zf(col, v), numeric(1))
Wl <- "Walleye / Sauger"; Pf <- "Panfish / Sunfish"; Np <- "No preference"

stopifnot(
  nrow(ch5.fs) == length(fam.cols) * length(ch5.lpa.vars),
  setequal(unique(ch5.fs$Column), fam.cols),
  # Walleye / Sauger
  fam.top("attitude_harvest") == Wl, zf(Wl, "attitude_harvest") >= 0.4, zf(Wl, "attitude_catch") >= 0.2,
  setequal(fam.cols[order(-vapply(fam.cols, zf, numeric(1), v = "motivation_resource"))][1:2], c(Wl, "Catfish")),
  zf(Wl, "motivation_natural") < 0, zf(Wl, "reg_comprehension") < 0, zf(Wl, "reg_sitesupport") < 0,
  # Bass
  fam.bot("attitude_harvest") == "Bass", zf("Bass", "attitude_harvest") <= -0.5, zf("Bass", "attitude_size") >= 0.2,
  all(zs("Bass", c("motivation_pp", "motivation_natural")) > 0),
  all(zs("Bass", c("reg_comprehension", "reg_sitesupport")) >= 0.1),
  # Panfish / Sunfish
  zf(Pf, "attitude_size") <= -0.3, all(zs(Pf, c("attitude_catch", "attitude_harvest")) > 0),
  all(abs(zs(Pf, mot.vars)) < 0.1),
  # Catfish
  zf("Catfish", "motivation_resource") >= 0.2,
  all(abs(zs("Catfish", setdiff(ch5.lpa.vars, "motivation_resource"))) < 0.15),
  # Trout
  all(zs("Trout", c("attitude_catch", "attitude_numbers", "motivation_resource")) <= -0.2),
  zf("Trout", "motivation_natural") > 0, zf("Trout", "reg_uniform") > 0,
  # No preference
  all(zs(Np, mot.vars) < 0), fam.bot("motivation_resource") == Np, zf(Np, "motivation_resource") <= -0.5,
  all(zs(Np, att.vars) <= -0.15)
)

stopifnot(
  length(fam.cols) == sum(banner.definition$Type == "Family"),
  # every family group has every profile
  all(ch5.fam$Value > 0),
  # the largest share of any profile in any family group
  with(ch5.fam %>% filter(Type == "Family"), Column[which.max(Value)] == "Walleye / Sauger" && Class[which.max(Value)] == "Class 1"),
  all(abs(sapply(1:6, gap, col = "Catfish")) < ch5.mix.gap),
  fam.n$Column[which.max(fam.n$ColumnN)] == "Walleye / Sauger",
  top.cls("Walleye / Sauger") == 1, gap("Walleye / Sauger", 1) >= ch5.mix.gap, gap("Walleye / Sauger", 6) < 0,
  top.cls("Bass") == 3, gap("Bass", 3) >= ch5.mix.gap, gap("Bass", 1) <= -ch5.mix.gap,
  gap("Panfish / Sunfish", 1) > 0, gap("Panfish / Sunfish", 6) > 0, gap("Panfish / Sunfish", 2) <= -ch5.mix.gap,
  gap("Trout", 2) >= ch5.mix.gap, gap("Trout", 3) <= -ch5.mix.gap,
  top.cls("No preference") == 2, gap("No preference", 2) >= ch5.mix.gap,
  gap("No preference", 5) >= ch5.mix.gap, gap("No preference", 1) <= -ch5.mix.gap
)
fam.order <- ch5.long %>% filter(Type == "Family", !Suppressed) %>% distinct(Order, Column) %>% arrange(Order) %>% pull(Column)
stopifnot(setequal(fam.order, fam.cols))

# D173: one card per family group, text keyed by family name.
fam.text <- list(
  `Walleye / Sauger` = paste0("Walleye / Sauger anglers, the largest family group (n = ", FN(Wl), "), lean toward Class 1, the harvest-minded, keep-it-simple angler (", SA(1, Wl), "), and include very few Class 6 purists (", SA(6, Wl), "). Their attitude scores agree: keeping fish matters more to them than to any other family group (", FZ(Wl, "attitude_harvest"), "), and needing a catch is above average (", FZ(Wl, "attitude_catch"), "). Together with Catfish anglers they score highest on catch outcomes as a motivation (", FZ(Wl, "motivation_resource"), "), while the outdoors is slightly below average (", FZ(Wl, "motivation_natural"), "). Harvest opportunity and catch results are the levers most likely to matter to this group. Their comprehension of the rules (", FZ(Wl, "reg_comprehension"), ") is slightly below average, so plain-language communication of lake-specific length and bag limits also has a role."),
  Bass = paste0("Bass anglers (n = ", FN("Bass"), ") sit at the opposite end from Walleye / Sauger anglers on harvest. Class 3, the regulation-savvy catch-and-release angler, is their largest profile (", SA(3, "Bass"), "), and Class 1 is less common among them (", SA(1, "Bass"), "). Keeping fish matters least to them of any family group (", FZ("Bass", "attitude_harvest"), "), and the size of the fish matters more than average (", FZ("Bass", "attitude_size"), "). Their motivations are close to average, with the physical and psychological rewards (", FZ("Bass", "motivation_pp"), ") and the outdoors (", FZ("Bass", "motivation_natural"), ") slightly above. They also report above-average comprehension of the rules (", FZ("Bass", "reg_comprehension"), ") and support for site-specific rules (", FZ("Bass", "reg_sitesupport"), "). Bass anglers look like a receptive audience for size-focused management, including special length limits and catch-and-release rules for individual waters."),
  `Panfish / Sunfish` = paste0("Panfish / Sunfish anglers (n = ", FN(Pf), ") combine two contrasting profiles: Class 1 harvest-minded anglers (", SA(1, Pf), ") and Class 6 conservation-minded purists (", SA(6, Pf), ") are both more common than overall, while Class 2 is less common (", SA(2, Pf), "). Their attitudes lean toward keeping fish (", FZ(Pf, "attitude_harvest"), ") and needing a catch (", FZ(Pf, "attitude_catch"), "), while the size of the fish matters less than average (", FZ(Pf, "attitude_size"), "). All four motivations are within 0.1 SD of the Overall means, so this group differs in what it wants from the catch rather than in why it fishes. Panfish management may need to balance harvest opportunity for the larger group with the experience-focused values of the smaller one."),
  Catfish = paste0("Catfish anglers (n = ", FN("Catfish"), ") are the closest to the angler population as a whole: no profile's share among them differs from its Overall share by ", ch5.mix.gap, " percentage points or more. Of the ", length(ch5.lpa.vars), " scales, only motivation by catch outcomes is 0.15 SD or more from the Overall mean (", FZ("Catfish", "motivation_resource"), "), and the rest are all within 0.15 SD. Catfish anglers are therefore much like Nebraska anglers generally, with a somewhat stronger interest in what they catch, so catfish management is in effect management for the general angler."),
  Trout = paste0("Trout anglers lean toward Class 2, the relaxed, catch-optional angler (", SA(2, "Trout"), "), with fewer Class 3 anglers (", SA(3, "Trout"), "); with ", FN("Trout"), " respondents these intervals, and the scale means below, are imprecise. They score below average on needing a catch (", FZ("Trout", "attitude_catch"), "), on catching numbers of fish (", FZ("Trout", "attitude_numbers"), ") and on catch outcomes as a motivation (", FZ("Trout", "motivation_resource"), "), and slightly above average on the outdoors (", FZ("Trout", "motivation_natural"), "). The pattern fits a stocked fishery valued for the outing, where access, the timing of stockings and a pleasant setting may matter more than catch rates or trophy potential."),
  `No preference` = paste0("Anglers with no preferred species (n = ", FN(Np), ") are the group most weighted toward the less committed profiles: Class 2 (", SA(2, Np), ") and Class 5, the low-involvement angler (", SA(5, Np), "), are both more common than overall, and Class 1 is less common (", SA(1, Np), "). They score below the Overall mean on every attitude and every motivation. Catch outcomes as a motivation is lowest of any family group (", FZ(Np, "motivation_resource"), "), and the physical and psychological rewards (", FZ(Np, "motivation_pp"), ") and the importance of size (", FZ(Np, "attitude_size"), ") are also low. These anglers are a natural focus for recruitment, retention and reactivation efforts, where convenience, easy access and general information are more likely to reach them than species-specific management.")
)
stopifnot(setequal(names(fam.text), fam.order))
Card <- function(i) {
  f <- fam.order[i]
  Ch5FamilyCard(f, Ch5FamilyCardPlot(ch5.long, f), fam.text[[f]], plotLeft = i %% 2 == 1)
}
```

`r paste0("The figure below shows the profile makeup of each family group against the Overall share of each profile. Unassigned respondents, between ", formatC(min(fam.unassigned$Value), format = 'f', digits = 1), " and ", formatC(max(fam.unassigned$Value), format = 'f', digits = 1), " percent of each family group, are not shown, so the bars in a panel sum to less than 100. ", knitr::combine_words(ch5.splitSpecies), " are reported as individual species because their families were not combined, and are not in the figure.")`

```{r ch5FamilyMix, fig.width=9, fig.height=5.5}
Ch5FamilyMixPlot(ch5.long, "Profile makeup of each family group")
```

## Profile makeup of family-group anglers

`r paste0("Every family group contains anglers of all six profiles. No family group is dominated by a single profile; the largest share of any profile in any family group is Class 1 among Walleye / Sauger anglers (", S(1, 'Walleye / Sauger'), "). Managing for any one species therefore means serving a mix of angler types, and the differences described in the cards below are differences of emphasis rather than of kind. Each card shows one family group's weighted percentage in each profile, with 95 percent confidence intervals, on a common scale; the icons along the bottom mark the profiles, and the dashed mark is the Overall share of that profile. The text beside each card also gives the group's mean on the attitude, motivation and regulation scales used to fit the profiles (1 to 5 scales), with the difference from the Overall mean in standard deviations (SD); the largest such difference for any family group is ", formatC(max(abs(ch5.fs$Z)), format = 'f', digits = 2), " SD.")`

```{r ch5Card1}
Card(1)
```

```{r ch5Card2}
Card(2)
```

```{r ch5Card3}
Card(3)
```

```{r ch5Card4}
Card(4)
```

```{r ch5Card5}
Card(5)
```

```{r ch5Card6}
Card(6)
```

`r paste0("These implications are interpretive. The profiles are built from attitude, motivation and regulation scales, not from behaviour, and the shares are associations: preferring a species does not place an angler in a profile, nor the reverse. Differences of less than about ", ch5.mix.gap, " percentage points are within the precision of these estimates for most family groups, and the Trout group, the smallest family group, has intervals that reach \u00b1", formatC(small.ci, format = 'f', digits = 1), " points.")`

`r sect_landscape()`

<!--
D36: Appendix A is a deliberately blank placeholder. The paper questionnaire is
pasted in by hand, matching 2025CrossTabReport.rmd L1545-1547, which does the
same thing. Do not pour the instrument in programmatically.
-->

# Appendix A - 2025 Nebraska Licensed Angler Survey (Paper Version)

`r run_pagebreak()`

# Appendix B - Statistical Methodology

## Analysis sample

`r paste0("This report is restricted to respondents who answered the preferred-species question. Of the ", format(nAll2025, big.mark=","), " anglers who responded to the 2025 survey, ", format(nNoB1, big.mark=","), " left that question blank and are excluded from the report entirely rather than merely from the species columns. The analysis sample is therefore ", format(nrow(d), big.mark=","), " respondents.")`

`r paste0("A second, narrower exclusion applies only to the preferred groups. ", nBannerExcluded, " respondents in the analysis sample prefer a species that has no preferred-group column, either because it is in no candidate family or because it and its family did not meet the selection rules in Chapter 1. They remain in the Overall column of every table but receive no preferred-group column of their own. The two exclusions are distinct and are reported separately in Chapter 1.")`

`r paste0("Because of the first restriction, the Overall column of this report estimates a different population than the Overall column of the 2025 Crosstabs report: anglers who stated a species preference, rather than all licensed anglers. The two reports will therefore not agree in that column, and no attempt has been made to reconcile them. The one exception is the preferred-species distribution itself, which is computed on respondents to that question in both reports and does match exactly.")`

## Weighting and raking by survey year

Every respondent record carries a pre-calculated weight that is computed during data aggregation and stored with the survey data. All percentages and means in this report are weighted using that stored value; sample sizes (N) shown in parentheses are always
**raw, unweighted respondent counts** and not weighted Ns.  Calculated weights for the 2025 sum to population size values and not sample size values and displaying the weighted N's would be difficult for readers to interpret. Full detail on
how the 2025 raking weights themselves were constructed can be found in Hurley (2026).

## Percentage confidence intervals

Percentage tables (`base.summary.percent.selectOne` /
`base.summary.percent.selectAll` in `BaseFunctions_2025_UPDATED.R`) use a
normal-approximation (Wald) interval:

$$CI = 1.96 \times \sqrt{\frac{p(1-p)}{effN}} \times 100$$

where $p$ is the weighted proportion and $effN$ is the **Kish effective
sample size**, not the raw respondent count or the raw sum of weights:

$$effN = \frac{(\sum w)^2}{\sum w^2}$$

This matters because the 2025 weights sum to the angler population (roughly
234,000 across all 2025 respondents, a mean weight around 83), not to the
number of respondents. A formula that treated the sum of weights as the sample
size would inherit that population scale and give intervals roughly 9 times
too narrow. The Kish effective sample size avoids this in two ways: it is
unchanged if every weight is multiplied by a constant, so the population scale
drops out; and it is smaller than the respondent count, reflecting the design
effect of unequal weighting.

## Mean confidence intervals

Mean tables (`base.summary.means`) compute a weighted mean and a weighted
standard deviation, then a standard error using the same **Kish effective
sample size** ($effN$) used by the percentage formula above, rather than the
raw respondent count:

$$SE = \frac{SD_w}{\sqrt{effN}}, \qquad CI = 1.96 \times SE$$

This mirrors the percentage CI fix for the same underlying reason: using $effN$ keeps mean
CIs on the same design-effect-corrected basis as percentage CIs. The sample size (N) displayed alongside each mean is still the raw, unweighted respondent count; only the internal SE calculation changed.

## Median confidence intervals

Median tables report a weighted median together with
a genuine 95% confidence interval for that median, computed by weighted
bootstrap: respondents are resampled with replacement, with selection probability
proportional to the precalculated weight values, 1,000 times; the (unweighted) median is
computed for each resample; and the 2.5th and 97.5th percentiles of those
1,000 bootstrap medians form the reported CI bounds. A fixed random seed
(7361) is set before each grouped computation so results are reproducible
from one render to the next. This method was chosen because there is no
simple closed-form confidence interval for a weighted median under
arbitrary, non-integer survey weights.

## Reverse-coded item markers (dagger, &dagger;)

Some questions in this report mark individual items with a dagger and a
caption explaining that dagger-marked items "are reverse coded... before
computing scale means." That marking is only meaningful when a table
actually being shown reflects a reversed value. That is
true for the Angler Attitudes (E1) tables -- `attitude_catch` and
`attitude_harvest`, both shown in this report, genuinely reverse items E1a,
E1k, E1f, and E1l when computing those subscale and item means.

## Scale scores and the completeness gate

`r paste0("The motivation and attitude scale scores are rebuilt from the raw item responses at render time, applying the reversals flagged in Scales.csv. Each scale table is restricted to respondents who answered every item in that sub-scale, matching the 2025 Crosstabs report. The gate is applied per scale, so each scale carries its own sample size; across the eight scales used here the analysis sample ranges from 1,653 to 1,715 respondents. This is an inherited listwise requirement rather than a discretionary exclusion, and the resulting sample size is printed beside every estimate.")`

## Population expansions

`r paste0("The species table in Chapter 1 reports a population expansion, obtained by applying each weighted percentage to the full weighted 2025 angler population of ", format(round(popTotalAll), big.mark=","), ". That column therefore sums to the full angler population. The weights carried by the ", format(nrow(d), big.mark=","), " respondents in the analysis sample themselves total only ", format(round(popTotalAnalysis), big.mark=","), ", or about ", round(popTotalAnalysis / popTotalAll * 100), " percent of the population, because the respondents who skipped the preferred-species question carry weight too.")`

`r paste0("Expanding to the full population rather than to the ", format(round(popTotalAnalysis), big.mark=","), " represented by the analysis sample assumes that skipping the preferred-species question is unrelated to which species an angler prefers. That assumption cannot be tested with these data, since no preference was recorded for the respondents who skipped the question. Readers who prefer not to make it should scale the expansion column by ", round(popTotalAnalysis / popTotalAll, 3), ".")`

## The preferred groups, and why columns do not sum

`r paste0("The preferred groups are not a partition. A family that Chapter 1 combined appears both as a family column and as one column per constituent species that met the minimum size, so a respondent who prefers largemouth bass is counted in both the Bass column and the Largemouth bass column. A family that was not combined has no family column, and only its species that met the minimum size appear, each as a column of its own.")`

`r paste0("The columns are chosen by rule, not by hand. A candidate family is combined only if none of its within-family tests has a family-adjusted p-value below ", family.alpha, ". A column, whether for a family or a species, requires at least ", min.group.n, " raw respondents; the size rule is applied after testing, so every species in a candidate family is tested even if it later falls below the minimum. The hand-typed column list is checked against these rules at every render and the render stops if they disagree.")`

`r paste0("Two consequences follow. Preferred-group column counts sum to ", format(nBannerCellSum, big.mark=","), " against ", format(nBanner, big.mark=","), " distinct respondents, so they must never be totalled. And because each column is computed on its own respondents and uses its own denominator, the percentages within any single column remain correct; only addition across columns is invalid.")`

## Comparisons between species

Chapter 1 compares species within a family using design-based two-sample
comparisons (`svyttest` from the **survey** package) on a design object built
with the survey weights rescaled to sum to the number of respondents in the
pair being compared:

$$w_{norm} = w \times \frac{n}{\sum w}$$

The rescaling is presentational. Like the Kish effective sample size, the
linearized standard errors that **survey** computes do not change when every
weight is multiplied by a constant, so raw and rescaled weights give identical
standard errors and degrees of freedom. The sum-of-weights problem described
under percentage confidence intervals does not arise here.

**No omnibus test is reported.** Each row of a comparison table is a single
two-species contrast. An overall F-test across the species in a family was
considered and dropped, and with it any model $R^2$ or $\eta^2$, because the
split-or-combine decisions were made from the species estimates directly.

## Multiplicity

`r paste0("The Bonferroni adjustment is applied across every test in a family: the number of species pairs multiplied by the nine outcomes. A two-species family therefore carries ", 9, " tests and a three-species family ", 27, ". The unadjusted p-value for each test is multiplied by the family's test count and capped at 1, and both the unadjusted p and the family-adjusted p are printed.")`

Bonferroni was chosen over Holm for simplicity of exposition. The two rest on
identical assumptions and Bonferroni is uniformly the more conservative of the
two, so any comparison Bonferroni separates, Holm would separate as well.
Tukey's HSD was not used: it is not valid here given the unequal group sizes and
the weighted design. Benjamini-Hochberg was not used because false-discovery
control is suited to screening rather than to the go/no-go grouping decisions
this chapter supports.

`r paste0("The family-adjusted p-values are used for one decision: a family is combined only if none of its adjusted p-values is below ", family.alpha, ". The comparisons for the smaller species are underpowered, and overlapping confidence intervals are weak evidence that two species are similar, so failing to separate two species is not evidence that they are alike. Comparisons in which one species has fewer than ", min.group.n, " respondents are marked with a dagger in the contrast tables.")`

## Effect sizes

`r paste0("Every comparison reports the weighted difference in means with a 95% confidence interval, and Hedges' g, a standardized difference computed by pooling the two weighted standard deviations on the effective sample sizes and applying the usual small-sample correction. Both are shown because several species in this survey are represented by very few respondents, where a comparison that separates nothing is not evidence that the species behave alike -- the interval is simply too wide to distinguish the two possibilities. The difference, its interval, and g together let the reader tell those cases apart.")`

## How differences are described in the text

The narrative in Chapters 3 and 4 describes a preferred group as different from the Overall estimate only when the group's 95 percent confidence interval lies entirely outside the Overall 95 percent interval: the lower limit of the group is above the upper limit of Overall, or the upper limit of the group is below the lower limit of Overall. The intervals are those printed in the tables, the Kish effective-N interval for percentages and means and the bootstrap percentile interval for medians. A group whose interval overlaps the Overall interval is not described as different, and a group that goes unmentioned is not thereby shown to be typical. Within-angler differences in Chapter 4 (size against numbers, and caught against allowed) are described as different from zero only when the 95 percent interval around the paired difference excludes zero.

`r paste0("This screen is not a hypothesis test and carries no p-value. For a single comparison it is more conservative than a two-sided test at the 5 percent level, because it requires the two intervals not to touch rather than the difference to exceed its own standard error; how much more conservative depends on how wide the group interval is relative to the Overall interval. It is not adjusted for the number of comparisons. Each table screens ", nrow(banner.definition), " groups, and Chapter 3 screens many outcomes, so some flagged comparisons could arise by chance. The comparisons are also not independent: every group is part of the Overall it is compared with, and a family row contains the respondents in its own species rows.")`

A percentage of 0 or 100 has a Wald interval of zero width, so the screen carries no information for such a cell. The text reports those cells descriptively, as groups in which no respondent gave the response, and not as screened differences.

`r paste0("The rule is not applied everywhere. The Chapter 1 narrative reports the Bonferroni-adjusted family tests described above. The Chapter 2 per-item paragraphs describe group means and their ordering as printed in the item tables and apply no interval screen; the interval for any group is in the table. The closing section of Chapter 2, Reading Across the Items, applies the interval screen above. Chapter 5 is described in its own section below. In Chapters 1 to 4 every value quoted in the narrative is computed from the same objects as the tables, and each claim is checked against its rule when the report is built, so the build stops if the data no longer support a statement.")`

## Satisfaction comparisons in Chapter 4

`r paste0("Chapter 4 reports no new estimator. Its group means are the weighted means described above, with the same Kish effective-N confidence intervals, and its rows are the same preferred groups used in Chapters 2 and 3.")`

`r paste0("One variable is transformed. A9 is recorded from 1, Very satisfied, to 5, Very dissatisfied, while every D4 item runs from 1, Strongly Disagree, to 5, Strongly Agree. Chapter 4 reports A9 as 6 minus the recorded response so that all six items point the same way. Subtraction from a constant shifts and reflects the scale without changing its spread, so the confidence interval is unchanged: the overall A9 mean of 2.3 plus or minus 0.06 in Chapter 3 appears as 3.7 plus or minus 0.06 in Chapter 4.")`

`r paste0("The size-and-numbers comparisons are paired. For each respondent who answered both items of a pair, the difference between the two responses is computed first, and the group figure is the weighted mean of those differences with the usual interval. Restricting to respondents who answered both items means the two means printed beside the difference describe the same people, so the difference column equals the difference of the columns. Pairing removes between-angler variation in how the scale is used, which is why a difference of a few hundredths of a scale point can carry a narrower interval than either mean.")`

`r paste0("Chapter 4 also compares what each angler catches with what the same angler is allowed to harvest, for size (D4i and D4j) and for number (D4k and D4l). The method is the paired method above. The difference is the caught item minus the harvestable item, so a negative value means the harvestable item is rated higher. It is computed for every row of the table, Overall and the ", nrow(banner.definition), " preferred groups, for both pairs: ", 2 * nrow(banner.definition), " group comparisons, none adjusted for multiplicity. The size comparison was added after the Chapter 2 item paragraphs suggested a difference for one group, Wiper. It is reported for every group so that the group is read against the others and not alone.")`

`r paste0("No significance test is reported in Chapter 4, and no adjustment for multiple comparisons is applied. Each interval is a 95 percent interval for its own group taken alone. ", nrow(banner.definition), " groups are shown for each pair, and the groups overlap, since a family row contains the respondents in its own species rows; reading every interval at once is therefore a weaker exercise than reading any one of them, and a group whose interval just excludes zero should be read with that in mind.")`

## Angler type profiles in Chapter 5

```{r ch5AppendixB}
# Every figure quoted below is computed here or in ch5Setup, so this section
# cannot drift from the chapter.
ch5.appb.n0 <- sum(d$lpa_n_scales == 0)
ch5.appb.n16 <- sum(d$lpa_n_scales >= 1 & !d$lpa_fitted)
ch5.appb.cert <- Ch5LPACertainty(d) %>% arrange(desc(Band))
ch5.appb.spec <- D4RowSpec(includeOverall = TRUE)
ch5.appb.supp <- ch5.long %>%
  filter(Suppressed) %>%
  distinct(Order, Column, ColumnN, ColumnEffN, Type) %>%
  arrange(Order)
# A Species row's family is the nearest Family row above it in the row order.
ch5.appb.family <- vapply(
  ch5.appb.supp$Order[ch5.appb.supp$Type == "Species"],
  function(o) {
    fam <- ch5.appb.spec %>% filter(Type == "Family", Order < o)
    fam$RawLabel[which.max(fam$Order)]
  },
  character(1)
)
ch5.appb.inFamily <- ch5.appb.supp$Column[ch5.appb.supp$Type == "Species"]
ch5.appb.split <- ch5.appb.supp$Column[ch5.appb.supp$Type == "Split"]

stopifnot(
  ch5.appb.n0 + ch5.appb.n16 == ch5.nUnassigned,
  nrow(ch5.appb.cert) == 3,
  all(ch5.appb.supp$Type %in% c("Species", "Split")),
  length(ch5.appb.inFamily) + length(ch5.appb.split) == nrow(ch5.appb.supp),
  nrow(ch5.appb.supp) > 0
)
```

### The model

`r paste0("Chapter 5 groups anglers using a latent profile analysis, a finite mixture model in which each respondent is assumed to belong to one of a number of unobserved profiles and, within a profile, each indicator is normally distributed. The indicators are the eleven scale scores reported in Chapter 3: the four angler-attitude scales, the four motivation scales, and the three regulation scales. Within each profile the eleven indicators are treated as uncorrelated, so each profile is described by eleven means and a set of variances.")`

`r paste0("Models were fitted with the tidySEM package (version ", packageVersion("tidySEM"), "), function mx_profiles(), which estimates by maximum likelihood in OpenMx (version ", packageVersion("OpenMx"), "). tidySEM obtains starting values from a k-means partition, refines them by simulated annealing, and then runs gradient-based optimization. A fixed random seed (", ch5.lpa.seed, ") is set before each model so the fits are reproducible. Starting values come from a single k-means run, and the sensitivity of the solution to other starting values has not been examined.")`

### Who was fitted

`r paste0("Of the ", FmtCount(nrow(d)), " respondents in the analysis sample, ", FmtCount(ch5.nFitted), " (", formatC(100 * ch5.nFitted / nrow(d), format = "f", digits = 1), " percent) answered at least ", ch5.lpa.min.scales, " of the eleven scales and were included in the fit. The threshold was set before fitting. Where a fitted respondent is missing some scales, the model uses the scales that were answered (full-information maximum likelihood); no values are imputed. The remaining ", FmtCount(ch5.nUnassigned), " respondents (", FmtCount(ch5.appb.n16), " who answered between 1 and ", ch5.lpa.min.scales - 1, " scales and ", FmtCount(ch5.appb.n0), " who answered none) are reported as Unassigned. They are not dropped: they remain in every Chapter 5 row, and Unassigned appears as its own column, so each row's percentages are of all respondents in that row.")`

`r paste0("Each scale score carries the completeness gate described under Scale scores and the completeness gate above, so the scores entering the model are the same values summarized in the Chapter 5 profile figures and profile means table.")`

### Choosing the number of profiles

`r paste0("Two within-profile variance structures were fitted: one in which every profile shares the same variance for a given indicator (equal), and one in which each profile has its own variances (varying). Under both structures, models with 1 to ", max(ch5.lpa.classes), " profiles were fitted. The equal structure was then extended to ", paste(ch5.lpa.extend.equal, collapse = " and "), " profiles because the Bayesian information criterion (BIC) was still decreasing at ", max(ch5.lpa.classes), ".")`

`r paste0("The number of profiles was chosen by a stated convention rather than a statistical test: among all fitted models, the one with the lowest BIC, restricted to models in which the smallest profile holds at least ", 100 * ch5.lpa.min.class.prop, " percent of fitted respondents and the relative entropy is at least ", formatC(ch5.lpa.min.entropy, format = "f", digits = 2), ". Only fits that OpenMx reports as converged (status code 0 or 1) are eligible. BIC is computed as")`

$$BIC = -2\log L + p \ln(n)$$

`r paste0("with p the number of estimated parameters and n = ", FmtCount(ch5.nFitted), ". OpenMx's default summary reports a different, degrees-of-freedom-adjusted BIC; it was not used. Relative entropy summarizes how distinctly respondents are assigned:")`

$$E = 1 - \frac{\sum_i \sum_j -\hat{p}_{ij} \ln \hat{p}_{ij}}{n \ln k}$$

`r paste0("where p-hat(ij) is respondent i's estimated probability of belonging to profile j and k is the number of profiles. It runs from 0 to 1, with 1 indicating that every respondent is assigned with certainty.")`

`r paste0("The selected model has ", ch5.k, " profiles with ", ch5.sel$Variances, " variances: BIC ", formatC(ch5.sel$BIC, format = "f", digits = 1, big.mark = ","), ", relative entropy ", formatC(ch5.sel$Entropy, format = "f", digits = 3), ", smallest profile ", FmtCount(ch5.sel$SmallestClassN), " respondents (", formatC(100 * ch5.sel$SmallestClassProp, format = "f", digits = 1), " percent of those fitted). The full table of fitted models is given in Chapter 5.")`

### Models that were fitted but not eligible

`r paste0("Four fits had a lower BIC than the selected model and were excluded under the convention above. The ", paste(ch5.floorFail$Classes, collapse = "- and "), "-profile equal-variance models (BIC ", paste(formatC(ch5.floorFail$BIC, format = "f", digits = 1, big.mark = ","), collapse = " and "), ") converged, but their smallest profiles hold ", paste(formatC(100 * ch5.floorFail$SmallestClassProp, format = "f", digits = 1), collapse = " and "), " percent of fitted respondents, below the ", 100 * ch5.lpa.min.class.prop, " percent floor. Because BIC continued to decrease through ", max(ch5.floorFail$Classes), " profiles, the selected model is the largest equal-variance model that satisfies the floor rather than the point at which BIC stops improving.")`

`r paste0("The ", paste(ch5.spikes$Profiles, collapse = "- and "), "-profile varying-variance models (BIC ", paste(formatC(ch5.diag$BIC[match(ch5.spikes$Model, ch5.diag$Model)], format = "f", digits = 1, big.mark = ","), collapse = " and "), ") did not converge (OpenMx status code ", paste(unique(ch5.diag$StatusCode[ch5.diag$Model %in% ch5.spikes$Model]), collapse = ", "), ": first-order optimality conditions not met). Inspection showed the cause. In each, one profile (", paste(FmtCount(ch5.spikes$ClassN), collapse = " and "), " respondents) contains only respondents whose ", ScaleLabel(ch5.spikes$Variable[1], l), " regulation score is exactly ", ch5.spikes$Max[1], ", the top of the scale, among those who answered it (", paste0(ch5.spikes$AtMax, " of ", ch5.spikes$Answered, collapse = " and "), "). That profile's variance on the indicator shrinks toward zero (estimates of ", paste(formatC(ch5.spikes$Variance, format = "e", digits = 1), collapse = " and "), "). Because the normal likelihood increases without limit as a variance approaches zero, the lower BIC of these two models reflects that collapse rather than a better description of the data. A further optimization attempt was not made, since it would search the same unbounded region. Placing a lower bound on the variances was considered and not adopted, because it would change the model specification. Both fits are excluded.")`

### Assigning respondents to profiles

`r paste0("Each fitted respondent is assigned to the profile with the highest estimated membership probability. Assignment is not certain: the average probability of the assigned profile among its members is at least ", formatC(ch5.sel$MinMeanPosterior, format = "f", digits = 3), " for every profile. Certainty also depends on how many scales a respondent answered. Mean assigned-profile probability is ", paste0(formatC(ch5.appb.cert$MeanMaxPosterior, format = "f", digits = 3), " for respondents who answered ", c("all eleven scales", "ten", "seven to nine"), " (", FmtCount(ch5.appb.cert$N), " respondents)", collapse = ", "), "; the share assigned with probability below 0.70 is ", paste(formatC(100 * ch5.appb.cert$ShareBelow70, format = "f", digits = 1), collapse = ", "), " percent respectively. The profile numbers are arbitrary labels produced by the estimation and carry no order.")`

### Weights

`r paste0("The model is fitted without the survey weights: each fitted respondent contributes equally to the estimated profiles. Everything reported from the model is then weighted in the same way as the rest of this report. The share of each profile in each row is a weighted percentage with the Kish effective-N confidence interval, and the profile means in the Chapter 5 figures and profile means table are weighted means with the Kish effective-N confidence interval, computed from the assigned respondents. These weighted means are therefore not the same quantities as the unweighted means the model estimated for each profile. Whether the fitting software can carry survey weights into the estimation was not verified. The model diagnostics and the assignment-certainty table are unweighted model quantities.")`

### Reporting floor for species rows

`r paste0("Chapter 5 is the only chapter of this report that withholds rows. Before the model was fitted, a floor of ", ch5.effn.floor, " on the Kish effective sample size was set for species rows, adopting the effective-sample-size element of the National Center for Health Statistics data presentation standards for proportions (Parker JD, Talih M, Malec DJ, et al. National Center for Health Statistics Data Presentation Standards for Proportions. Vital and Health Statistics, Series 2, No. 175. 2017). Only that element is adopted: the NCHS standard also calls for a raw sample size of at least 30 and for Korn-Graubard confidence intervals with width criteria, while this report's intervals are Wald intervals on the Kish effective N, as described above, and no width criterion is applied.")`

`r paste0(c("No", "One", "Two", "Three", "Four", "Five", "Six")[nrow(ch5.appb.supp) + 1], " rows fall below the floor and are not shown in the Chapter 5 tables: ", paste0(ch5.appb.supp$Column, " (", FmtCount(ch5.appb.supp$ColumnN), " respondents, effective N ", formatC(ch5.appb.supp$ColumnEffN, format = "f", digits = 1), ")", collapse = "; "), ". The floor applies to reporting only; these respondents are included in the model fit and in the Overall row. ", if (length(ch5.appb.inFamily) > 0) paste0(paste(ch5.appb.inFamily, collapse = " and "), " respondents are also contained in the ", paste(ch5.appb.family, collapse = " and "), " family rows", if (length(ch5.appb.family) > 1) ", respectively" else "", ". ") else "", if (length(ch5.appb.split) > 0) paste0(knitr::combine_words(ch5.appb.split), " are species whose family was not combined and have no family row, so their respondents appear in no displayed Chapter 5 species row. ") else "", "Where a profile has no respondents in a displayed row, the percentage is 0 and the Wald interval has zero width; this is a property of the interval formula, not a measurement of certainty.")`

### Comparisons on other survey questions

`r paste0("The Chapter 5 table of profiles on other survey questions uses the same estimators as Chapter 3: weighted percentages and means with Kish effective-N intervals, and weighted medians with the bootstrap interval described above. Each question keeps its Chapter 3 universe, and the Overall column reproduces the Overall row of the corresponding Chapter 3 table. Unassigned respondents are counted in Overall only. One row is constructed for this chapter: a respondent counts as fishing rivers and streams if they reported the Missouri River, the Platte River, or other streams, rivers, and canals, among respondents who answered the waterbody question.")`

`r paste0("These comparisons treat each respondent's assigned profile as known. Because assignment is uncertain, some respondents are counted in a profile they may not belong to, which tends to make the profiles look more alike on these questions than they are; the differences shown are therefore more likely understated than overstated. The profile paragraphs name a family group when it makes up at least ", ch5.mix.gap, " percentage points more of a profile than of all assigned respondents, as a reminder that species preference and profile membership are related; a group whose row is below the reporting floor is not named. No adjustment for species mix is made.")`

### What is not reported

`r paste0("No significance test is reported in Chapter 5, and the profile shares in different rows are not formally compared. As in other chapters, the species rows overlap and must not be totalled.")`

## Display precision

`r paste0("Scale means and their confidence intervals are printed to three decimal places in Chapter 1, rather than the one decimal place used in the 2025 Crosstabs report. At one decimal place a scale-mean interval of roughly plus or minus 0.04 rounds to zero, which would make the species comparisons unreadable. This is a rounding change in presentation only; the underlying values are identical to those the inherited functions produce.")`

`r paste0("For the same reason, the paired difference columns in Chapter 4 carry two decimal places rather than the one used for the means beside them. The overall difference between satisfaction with size and satisfaction with numbers is 0.07, which one decimal place would print as 0.1 next to an interval of 0.06.")`

```{r timing}
toc()
```
