---
#title: "2025 Licensed Angler Survey — Preferred Species"
#date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  officedown::rdocx_document:
    toc: false
always_allow_html: yes
---

```{r setup, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, fig.width=7.5, fig.height=7}
knitr::opts_chunk$set(echo=FALSE, include=TRUE, warning=FALSE, error=FALSE, message=FALSE, ft.align="left")
library(tictoc)
tic("Report Took ")
options(stringsAsFactors = FALSE)
library(officedown)
library(officer)
library(rmarkdown)
library(tidyverse)
library(knitr)
library(flextable)
library(stringr)
library(survey)

setwd("F:/Survey/Analysis/PreferredSpecies/")

source("..\\BaseFunctions_2025_UPDATED.R") #load file of common functions
# Sourced read-only to inherit the crosstab report's caption text and table
# wrappers verbatim rather than duplicating them. Nothing in CrossTabTables/ is
# modified. PreferredSpeciesFunctions.R is sourced last so it wins any conflict.
source("..\\CrossTabTables\\CrossTabTableFunctions.R")
source("PreferredSpeciesFunctions.R") #load file of preferred species report functions
# Chapter 5 is the latent profile analysis (D140-D156). Ch5LPA.R replaced
# Ch5Functions.R (k-means, D120), which was deleted and is in git history.
source("Ch5LPA.R")
```

```{r getData, echo=FALSE}
load(file="../../Data/DataAggregation1/aggregateData_20260624.rData")

# D76: 2018 snapshot for the Chapter 2 D4 slope figures, taken before d is
# filtered to 2025. Same !is.na(B1) rule as the 2025 universe (D23); "No
# preference" stays in d2018 here and is excluded later, item-by-item, only
# from the slope comparison itself (D4SlopeData), not from this snapshot.
d2018 <- d %>% filter(surveyYear == 2018, !is.na(B1))

d <- d %>% filter(surveyYear==2025)

# Population total over ALL 2025 respondents, captured before the B1 filter
# because the expansion column is reported on the full-population basis (D29).
popTotalAll <- sum(d$postWeight)
nAll2025 <- nrow(d)
nNoB1 <- sum(is.na(d$B1))

# Captured before the B1 filter so Chapter 2 can report how many respondents
# answered the D4 battery but are outside this report's universe (F12).
nD4AnyAll2025 <- sum(rowSums(!is.na(d[, d4.items])) > 0)
nD4AnyNoB1 <- sum(rowSums(!is.na(d[, d4.items])) > 0 & is.na(d$B1))

# D23: the B1 filter is the first analytic filter. Respondents who left B1
# blank are out of the report entirely, not merely out of the banner.
d <- d %>% filter(!is.na(B1))

# Rebuild scale/subscale scores from raw item factors, applying reversals
# flagged in Scales.csv (single source of truth) at report time.
d <- add_scale_scores(d)

d$B1banner <- AssignBannerGroup(d$B1)

q <- read.csv(file="../../Data/DataAggregation1/FactorLevels_aggregated.csv") %>% filter(Year==2025)
l <- read.csv(file="../../Data/DataAggregation1/Labels.csv")
```

```{r dataChecks, echo=FALSE}
# Checks after the universe is fixed. These stop the render rather than letting
# a silent miscount propagate into every table.
stopifnot(
  nrow(d) == nAll2025 - nNoB1,
  sum(is.na(d$B1)) == 0,
  sum(!is.na(d$B1banner)) + sum(is.na(d$B1banner)) == nrow(d)
)

# D76: the 2018 snapshot must carry every species name the banner uses and
# the same five D4 response levels, or D4SlopeData's cross-year join would
# silently miss species rather than erroring.
stopifnot(
  all(unique(d2018$surveyYear) == 2018),
  sum(is.na(d2018$B1)) == 0,
  length(setdiff(unlist(banner.definition$Members), as.character(d2018$B1))) == 0,
  identical(levels(d2018$D4a), levels(d$D4a))
)

sizeTbl <- SpeciesSizeTable(d, popTotalAll)

stopifnot(
  abs(sum(sizeTbl$Percent) - 100) < 1e-8,
  sum(sizeTbl$Respondents) == nrow(d),
  abs(sum(sizeTbl$TotalAnglers) - popTotalAll) < 1e-6
)

nBanner <- sum(!is.na(d$B1banner))
nBannerExcluded <- sum(is.na(d$B1banner))

# Sum of the banner column counts. Exceeds nBanner because family columns
# contain their own species columns; quoted in Appendix B so the overlap is
# documented with a live figure rather than a hardcoded one.
nBannerCellSum <- sum(vapply(
  banner.definition$Members,
  function(m) sum(as.character(d$B1) %in% m),
  integer(1)
))

popTotalAnalysis <- sum(d$postWeight)
```

<!--
D33: page 1 is intentionally left blank for a hand-built title page, and the
table of contents is placed explicitly rather than via the YAML `toc` option so
that it follows the title page instead of preceding it.
-->

&nbsp;

`r run_pagebreak()`

```{r toc}
block_toc()
```

`r run_pagebreak()`

# Chapter 1: Determining Species Groupings

`r paste0("This report covers only anglers who answered the preferred-species question. Of the ", format(nAll2025, big.mark=","), " anglers who responded to the 2025 survey, ", format(nNoB1, big.mark=","), " left that question blank, leaving an analysis sample of ", format(nrow(d), big.mark=","), ".")`

`r paste0("Because of that restriction, the Overall column of this report describes anglers who stated a species preference rather than all licensed anglers, and it will therefore not match the Overall column of the 2025 Crosstabs report. The preferred-species distribution in the next table is the one quantity unaffected by the restriction, and it does match the Crosstabs report exactly.")`

## Question Text

`r paste0("*", trimws(GetQuestion(q, B1, 2025)), "*")`

## Sample Sizes and Population Estimates by Species

`r paste(caption.sizes, "  ", caption.raked, sep="")`

```{r speciesSizes}
CreateFlex(ArrangeSpeciesSizeTable(sizeTbl))
```

`r paste0("Total anglers applies each species percentage to the full weighted 2025 angler population of ", format(round(popTotalAll), big.mark=","), ", so the column sums to that population. This assumes that leaving the preferred-species question blank is unrelated to which species an angler prefers. The weights carried by the ", format(nrow(d), big.mark=","), " respondents in the analysis sample themselves total ", format(round(sum(d$postWeight)), big.mark=","), ".")`

## Preferred Groups

`r paste0("There are ", nrow(banner.definition), " preferred groups. Seven are family groups; eight are individual species reported alongside the family group that contains them; and two, northern pike and muskellunge, replace the Esocids family group outright. Species that fall outside every family group keep their place in the Overall column of every table but receive no preferred-group column of their own.")`

`r paste(caption.banner, sep="")`

```{r bannerSizes}
CreateFlex(BannerSizeTable(d))
```

`r paste0("Preferred species that fall outside every family group. These ", nBannerExcluded, " respondents remain in the Overall column of every table but receive no preferred-group column.")`

```{r bannerExclusions}
CreateFlex(BannerExclusionTable(d))
```

`r paste0("The preferred groups cover ", format(nBanner, big.mark=","), " distinct respondents of the ", format(nrow(d), big.mark=","), " in the analysis sample; ", nBannerExcluded, " do not appear in any preferred-group column. Because family columns contain their own species columns, the respondent counts in the table above add to more than ", format(nBanner, big.mark=","), " and should not be totalled.")`

## Comparisons Within Family Groups

`r paste0("The four family groups below contain more than one species, so each is shown broken out by species alongside the family group as a whole. These are the comparisons used to decide whether any individual species is reported separately in later chapters.")`

### Bass

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, "  ", caption.comparison, sep="")`

```{r bassMotivation}
CreateFlex(GenusMeansTable(d, "Bass", motivation.vars, l))
```

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.raked, "  ", caption.reversed, sep="")`

```{r bassAttitude}
CreateFlex(GenusMeansTable(d, "Bass", attitude.vars, l))
```

`r paste("Total days fished in Nebraska during 2025.", "  ", caption.means, "  ", caption.medians, "  ", caption.raked, sep="")`

```{r bassEffort}
CreateFlex(GenusEffortTable(d, "Bass"))
```

`r paste(caption.contrasts, sep="")`

```{r bassContrasts}
CreateFlex(ContrastTable(d, "Bass", c(motivation.vars, attitude.vars), l))
```

`r paste("Days fished, same species comparisons.", "  ", caption.contrasts, sep="")`

```{r bassEffortContrasts}
CreateFlex(EffortContrastTable(d, "Bass"))
```

### Panfish / Sunfish

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, "  ", caption.comparison, sep="")`

```{r panfishMotivation}
CreateFlex(GenusMeansTable(d, "Panfish / Sunfish", motivation.vars, l))
```

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.raked, "  ", caption.reversed, sep="")`

```{r panfishAttitude}
CreateFlex(GenusMeansTable(d, "Panfish / Sunfish", attitude.vars, l))
```

`r paste("Total days fished in Nebraska during 2025.", "  ", caption.means, "  ", caption.medians, "  ", caption.raked, sep="")`

```{r panfishEffort}
CreateFlex(GenusEffortTable(d, "Panfish / Sunfish"))
```

`r paste(caption.contrasts, sep="")`

```{r panfishContrasts}
CreateFlex(ContrastTable(d, "Panfish / Sunfish", c(motivation.vars, attitude.vars), l))
```

`r paste("Days fished, same species comparisons.", "  ", caption.contrasts, sep="")`

```{r panfishEffortContrasts}
CreateFlex(EffortContrastTable(d, "Panfish / Sunfish"))
```

### Esocids

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, "  ", caption.comparison, sep="")`

```{r esocidMotivation}
CreateFlex(GenusMeansTable(d, "Esocids", motivation.vars, l))
```

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.raked, "  ", caption.reversed, sep="")`

```{r esocidAttitude}
CreateFlex(GenusMeansTable(d, "Esocids", attitude.vars, l))
```

`r paste("Total days fished in Nebraska during 2025.", "  ", caption.means, "  ", caption.medians, "  ", caption.raked, sep="")`

```{r esocidEffort}
CreateFlex(GenusEffortTable(d, "Esocids"))
```

`r paste(caption.contrasts, sep="")`

```{r esocidContrasts}
CreateFlex(ContrastTable(d, "Esocids", c(motivation.vars, attitude.vars), l))
```

`r paste("Days fished, same species comparisons.", "  ", caption.contrasts, sep="")`

```{r esocidEffortContrasts}
CreateFlex(EffortContrastTable(d, "Esocids"))
```

### Catfish

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, "  ", caption.comparison, sep="")`

```{r catfishMotivation}
CreateFlex(GenusMeansTable(d, "Catfish", motivation.vars, l))
```

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.raked, "  ", caption.reversed, sep="")`

```{r catfishAttitude}
CreateFlex(GenusMeansTable(d, "Catfish", attitude.vars, l))
```

`r paste("Total days fished in Nebraska during 2025.", "  ", caption.means, "  ", caption.medians, "  ", caption.raked, sep="")`

```{r catfishEffort}
CreateFlex(GenusEffortTable(d, "Catfish"))
```

`r paste(caption.contrasts, sep="")`

```{r catfishContrasts}
CreateFlex(ContrastTable(d, "Catfish", c(motivation.vars, attitude.vars), l))
```

`r paste("Days fished, same species comparisons.", "  ", caption.contrasts, sep="")`

```{r catfishEffortContrasts}
CreateFlex(EffortContrastTable(d, "Catfish"))
```

<!--
Chapter 1 is complete apart from the 3.6 disposition table, which is not needed
now that the split decisions have been made (D31).
-->

`r run_pagebreak()`

# Chapter 2: Species-Linked Scale Questions

```{r d4Setup}
# Universe for the battery: the report universe, with each item keeping its own
# non-missing filter as the crosstab report does (2025CrossTabReport.rmd L768).
nD4Any <- sum(rowSums(!is.na(d[, d4.items])) > 0)
d4.categories <- levels(d[[d4.items[1]]])

stopifnot(
  length(d4.items) == 13,
  all(d4.items %in% names(d)),
  length(d4.categories) == 5
)
```

`r paste0("*", trimws(GetQuestion(q, D4, 2025)), "*")`

`r paste0("Each item is reported in its own table. Rows are the preferred groups from Chapter 1, with individual species indented beneath the family group that contains them; family rows include the respondents in their species rows, so rows overlap and must not be totalled. Of the analysis sample of ", format(nrow(d), big.mark=","), " anglers, ", format(nD4Any, big.mark=","), " answered at least one item in this battery.")`

`r paste0("This battery diverges from the 2025 Crosstabs report by more than the rest of the report does. The preferred-species question was not a strict gate on the battery in the delivered data: across all ", format(nAll2025, big.mark=","), " respondents to the 2025 survey, ", format(nD4AnyAll2025, big.mark=","), " answered at least one item in this battery, of whom ", format(nD4AnyNoB1, big.mark=","), " left the preferred-species question blank. Those respondents are outside this report's universe, so the Overall row here rests on fewer respondents than the corresponding Crosstabs report table.")`

`r paste(caption.d4gate, sep="")`

## `r ItemQuestionText("D4a", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4a}
CreateFlex(D4ItemTable(d, "D4a", d4.categories))
```

```{r d4aPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4a", d4.categories, titleText = ItemQuestionText("D4a", q))
```

```{r d4aMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4a", titleText = ItemQuestionText("D4a", q))
```

```{r d4aSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4a", titleText = ItemQuestionText("D4a", q))
```

`r paste0("For this item, Trout and Channel catfish anglers report the highest satisfaction, each averaging roughly 3.6 on the five-point scale, with more than half of each group agreeing or strongly agreeing and well under a fifth disagreeing. Walleye/Sauger anglers -- the largest single preferred group in the survey -- report the lowest satisfaction of any well-represented group, averaging 2.8, and are the only large group where more anglers disagree (40%) than agree (28%). The roughly three-quarter-point gap between Walleye/Sauger and Trout/Channel catfish anglers is the largest contrast among the larger preferred groups for this item, and may point to a difference in how reliably each species can be caught rather than a difference in how much anglers enjoy the pursuit itself. A similar pattern shows up within single families: Channel catfish anglers are considerably more satisfied (3.6) than Blue catfish (2.8) or Flathead catfish (3.0) anglers, and Yellow perch anglers report much lower satisfaction (2.4) than Bluegill/Sunfish (3.3) or Crappie (3.2) anglers within the panfish group.")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. Within 2025, one further pattern stands out: anglers with no single preferred species report above-average satisfaction (3.4, against 3.2 overall) and the largest neutral share of any group (45%), and neutral responses are common across the board -- roughly three in ten anglers in most groups take neither side -- so the group differences described above rest on the balance between agreement and disagreement rather than on lopsided views within any group.")`

## `r ItemQuestionText("D4b", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4b}
CreateFlex(D4ItemTable(d, "D4b", d4.categories))
```

```{r d4bPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4b", d4.categories, titleText = ItemQuestionText("D4b", q))
```

```{r d4bMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4b", titleText = ItemQuestionText("D4b", q))
```

```{r d4bSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4b", titleText = ItemQuestionText("D4b", q))
```

`r paste0("Overall, disagreement (38%) outweighs agreement (24%) with this trade-off. Northern pike and Muskellunge anglers reject it most strongly of any preferred group, both averaging about 2.4 on the five-point scale, and Flathead catfish and Yellow perch anglers post the next-highest disagreement rates, at about half of each group. Pike and muskellunge anglers pursue larger, trophy-oriented fish, which may explain their reluctance to trade size for numbers. Blue catfish anglers stand apart at the opposite end as the only group where agreement (48%) outweighs disagreement (17%) by a wide margin, suggesting Blue catfish anglers place comparatively more value on numbers over size than anglers preferring any other species.")`

`r paste0("Blue catfish anglers' agreement rose sharply between 2018 and 2025, from 2.3 to 3.4 -- the largest year-over-year movement seen on this item, carrying them from the most reluctant group in 2018 to the most willing in 2025. No other group's change was large enough to appear in the figure above.")`

## `r ItemQuestionText("D4c", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4c}
CreateFlex(D4ItemTable(d, "D4c", d4.categories))
```

```{r d4cPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4c", d4.categories, titleText = ItemQuestionText("D4c", q))
```

```{r d4cMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4c", titleText = ItemQuestionText("D4c", q))
```

```{r d4cSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4c", titleText = ItemQuestionText("D4c", q))
```

`r paste0("Support for size-increasing regulations is broad across every preferred group, but Muskellunge (4.5), Moronides (4.2), and Northern pike (4.0) anglers support it most strongly, while Yellow perch anglers support it least (3.3) and also disagree more than any other group (27%) -- a pattern that may reflect perch anglers' comparative indifference to trophy size on a species rarely pursued for its size in the first place. Largemouth and Smallmouth bass anglers are closely aligned with each other on this item (3.9 each), unlike several other items in this battery where the two bass species diverge.")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. What distinguishes the groups in 2025 is instead the firmness of the support: in every group but Yellow perch, supporters outnumber opponents by at least three to one, and not a single Muskellunge respondent chose neutral -- every angler in that group took a side.")`

## `r ItemQuestionText("D4d", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4d}
CreateFlex(D4ItemTable(d, "D4d", d4.categories))
```

```{r d4dPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4d", d4.categories, titleText = ItemQuestionText("D4d", q))
```

```{r d4dMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4d", titleText = ItemQuestionText("D4d", q))
```

```{r d4dSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4d", titleText = ItemQuestionText("D4d", q))
```

`r paste0("Support for regulations aimed at increasing numbers is stronger and more uniform across preferred groups than support for size-increasing regulations was on the previous item -- disagreement stays in the single digits for most groups, and every Muskellunge respondent agreed. Muskellunge and Blue catfish anglers support numbers-focused regulation most strongly; Yellow perch and Crappie anglers support it comparatively least, though a clear majority of both still agree.")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. Set against the previous item, most groups support numbers-focused regulation more strongly than size-focused regulation; Northern pike anglers are the main exception, backing size rules somewhat more strongly, with Moronides and Crappie anglers rating the two about equally. That tilt toward numbers over size may indicate that, for most anglers, catching fish at all matters more than catching bigger ones.")`

## `r ItemQuestionText("D4e", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4e}
CreateFlex(D4ItemTable(d, "D4e", d4.categories))
```

```{r d4ePercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4e", d4.categories, titleText = ItemQuestionText("D4e", q))
```

```{r d4eMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4e", titleText = ItemQuestionText("D4e", q))
```

```{r d4eSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4e", titleText = ItemQuestionText("D4e", q))
```

`r paste0("This item asks about the opposite trade-off from the harvest-satisfaction item above -- willingness to accept fewer fish in exchange for larger ones -- and the pattern largely mirrors it. Muskellunge (3.9) and Smallmouth bass (3.9) anglers are most willing to make that trade; Bluegill/Sunfish (3.2) and Walleye/Sauger anglers are least willing among the larger groups. Yellow perch anglers land in the middle on average but are unusually divided, with about a third disagreeing, one of the higher disagreement rates on this item.")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. The 2025 pattern is internally consistent with the harvest-versus-size question two items later: the groups most willing to sacrifice numbers for size here -- Muskellunge and both bass groups -- are the same ones that lean toward size over harvest opportunity there, while Walleye/Sauger anglers, among the least willing here, lean furthest toward harvest opportunity. No group falls below neutral on average, so the differences are in degree of willingness, not direction.")`

## `r ItemQuestionText("D4f", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4f}
CreateFlex(D4ItemTable(d, "D4f", d4.categories))
```

```{r d4fPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4f", d4.categories, titleText = ItemQuestionText("D4f", q))
```

```{r d4fMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4f", titleText = ItemQuestionText("D4f", q))
```

```{r d4fSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4f", titleText = ItemQuestionText("D4f", q))
```

`r paste0("Yellow perch and Blue catfish anglers feel most strongly that their preferred fish has become harder to catch, and Walleye/Sauger anglers -- the largest preferred group -- also lean toward agreement, with 56% agreeing. Bluegill/Sunfish and Channel catfish anglers feel this least. The two catfish species diverge sharply from each other here -- Channel catfish anglers see little change in difficulty while Blue catfish anglers see a great deal -- and the same divergence appears within panfish, where Yellow perch anglers report much more difficulty than Bluegill/Sunfish anglers despite both belonging to the same combined preferred group.")`

`r paste0("Agreement that the preferred fish has become harder to catch rose modestly across all anglers between 2018 and 2025, from 3.2 to 3.3 -- one of only two items in this battery, along with the water-availability item at the end, where the change across all anglers is what stands out between years. No individual preferred group's change was large enough to appear in the figure above, which suggests a broad, shallow drift toward agreement rather than a sharp movement concentrated in any one group.")`

## `r ItemQuestionText("D4g", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4g}
CreateFlex(D4ItemTable(d, "D4g", d4.categories))
```

```{r d4gPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4g", d4.categories, titleText = ItemQuestionText("D4g", q))
```

```{r d4gMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4g", titleText = ItemQuestionText("D4g", q))
```

```{r d4gSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4g", titleText = ItemQuestionText("D4g", q))
```

`r paste0("Trout (3.3) and Walleye/Sauger (3.2) anglers lean furthest toward valuing the opportunity to harvest their preferred fish over its size, though neither sits far above the scale midpoint. Smallmouth bass anglers are the clear outlier at the other end, disagreeing by more than four to one -- consistent with smallmouth bass fisheries' typical size- and release-oriented management. Both bass species in fact lean toward size over harvest, but Smallmouth bass anglers (2.4) do so far more sharply than Largemouth bass anglers (2.7), and Moronides (2.6) and Muskellunge (2.7) anglers land near them at the size-oriented end of the scale.")`

`r paste0("Moronides anglers are the only group whose change between 2018 and 2025 appears in the figure above, moving from leaning toward harvest opportunity (3.2) to leaning toward size (2.6) -- one of the larger single-group shifts in this battery, and one that carries Moronides anglers from the harvest-oriented end of this item across to the size-oriented end, alongside the bass groups.")`

## `r ItemQuestionText("D4h", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4h}
CreateFlex(D4ItemTable(d, "D4h", d4.categories))
```

```{r d4hPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4h", d4.categories, titleText = ItemQuestionText("D4h", q))
```

```{r d4hMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4h", titleText = ItemQuestionText("D4h", q))
```

```{r d4hSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4h", titleText = ItemQuestionText("D4h", q))
```

`r paste0("Bluegill/Sunfish anglers register the strongest disagreement seen anywhere in this battery -- roughly three in four disagree that they travel too far -- consistent with panfish being widely available close to home, and Largemouth bass and catfish anglers broadly share that view. Yellow perch (3.8) and Muskellunge (3.6) anglers sit at the opposite extreme -- not a single Yellow perch respondent disagreed -- suggesting perch and muskellunge anglers travel farther for their preferred fish than most other anglers do. Walleye/Sauger, Moronides, and Trout anglers also lean further toward agreement than the overall average, which may reflect how concentrated the waters holding those species are.")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. The travel pattern does line up with the water-availability item at the end of this battery: Yellow perch, Muskellunge, and Northern pike anglers sit at or near the top of both, while Bluegill/Sunfish and Channel catfish anglers sit at or near the bottom of both, suggesting that travel distance and the perceived shortage of places to fish are two readings of the same underlying access picture for these species.")`

## `r ItemQuestionText("D4i", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4i}
CreateFlex(D4ItemTable(d, "D4i", d4.categories))
```

```{r d4iPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4i", d4.categories, titleText = ItemQuestionText("D4i", q))
```

```{r d4iMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4i", titleText = ItemQuestionText("D4i", q))
```

```{r d4iSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4i", titleText = ItemQuestionText("D4i", q))
```

`r paste0("Moronides (3.8) and Muskellunge (3.8) anglers report the highest satisfaction with the size of fish they catch; Yellow perch (2.8) and Northern pike (3.0) anglers report the lowest. The gap between Muskellunge and Northern pike anglers is notable given both prefer esocids -- muskellunge, which grow considerably larger than pike, appear to deliver more size satisfaction to the anglers who pursue them. Within the bass and panfish families, Smallmouth bass and Bluegill/Sunfish anglers (both 3.5) are clearly more size-satisfied than Largemouth bass (3.0) and Yellow perch anglers respectively.")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. Within 2025, how the groups arrive at their averages differs as much as the averages themselves: Northern pike anglers split into opposing camps (43% agree, 37% disagree, only a fifth neutral), while nearly half of Blue catfish anglers (47%) and four in ten Trout anglers take no side at all.")`

## `r ItemQuestionText("D4j", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4j}
CreateFlex(D4ItemTable(d, "D4j", d4.categories))
```

```{r d4jPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4j", d4.categories, titleText = ItemQuestionText("D4j", q))
```

```{r d4jMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4j", titleText = ItemQuestionText("D4j", q))
```

```{r d4jSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4j", titleText = ItemQuestionText("D4j", q))
```

`r paste0("Bluegill/Sunfish anglers (3.9) and Muskellunge anglers are most satisfied with the size limits that govern harvest of their preferred fish, and agreement outweighs disagreement in every group but one: Northern pike anglers, where disagreement (40%) edges out agreement (38%). That echoes the pike/muskellunge gap seen on the size-satisfaction item above -- pike anglers appear comparatively dissatisfied with both the size of fish they catch and the size they are allowed to keep.")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. Compared with the previous item, nearly every group rates the size they are allowed to harvest at least as favorably as the size they actually catch; Moronides anglers are the one clear exception, rating the size they catch (3.8) above the size they are allowed to keep (3.5), which may hint that where Moronides anglers have a complaint, it is with the rules rather than the fish.")`

## `r ItemQuestionText("D4k", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4k}
CreateFlex(D4ItemTable(d, "D4k", d4.categories))
```

```{r d4kPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4k", d4.categories, titleText = ItemQuestionText("D4k", q))
```

```{r d4kMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4k", titleText = ItemQuestionText("D4k", q))
```

```{r d4kSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4k", titleText = ItemQuestionText("D4k", q))
```

`r paste0("Bluegill/Sunfish (3.6) and Channel catfish (3.4) anglers are most satisfied with the number of fish they catch; Yellow perch (2.7) and Flathead catfish (2.8) anglers are least. The catfish family splits sharply on this item: half of Flathead catfish anglers disagree -- the highest disagreement rate of any group on this item -- and Blue catfish anglers also lean toward dissatisfaction, while Channel catfish anglers are among the most satisfied groups, which may point to differences in how consistently each catfish species can be caught rather than anything about catfish angling as a whole.")`

`r paste0("No group's change between 2018 and 2025 was large enough to appear in the figure above. The 2025 ranking largely mirrors the overall fishing-success item at the top of this battery -- Channel catfish and Trout anglers near the top of both, Yellow perch and Walleye/Sauger anglers near the bottom of both -- which may indicate that when anglers judge their overall success, the number of fish caught weighs at least as heavily as their size.")`

## `r ItemQuestionText("D4l", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4l}
CreateFlex(D4ItemTable(d, "D4l", d4.categories))
```

```{r d4lPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4l", d4.categories, titleText = ItemQuestionText("D4l", q))
```

```{r d4lMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4l", titleText = ItemQuestionText("D4l", q))
```

```{r d4lSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4l", titleText = ItemQuestionText("D4l", q))
```

`r paste0("Bluegill/Sunfish anglers (3.9) are again the most satisfied group, this time with harvest-number limits, and a majority of most groups agree. Both esocid species land at the bottom together on average, but they arrive there differently: Northern pike anglers (3.1) show real dissatisfaction, with about three in ten disagreeing, while Muskellunge anglers (3.2) are overwhelmingly neutral rather than dissatisfied -- not one disagreed. Yellow perch anglers (3.3) sit just above the esocids, continuing the comparatively low perch satisfaction that runs through most of the satisfaction items in this battery.")`

`r paste0("Moronides anglers are the only group whose change between 2018 and 2025 appears in the figure above, declining by nearly half a point -- from the most satisfied group on this item in 2018 to the lower third in 2025, a reversal worth noting given their generally high standing on the other satisfaction items in this battery.")`

## `r ItemQuestionText("D4m", q)`

`r paste(caption.d4item, "  ", caption.raked, sep="")`

```{r d4m}
CreateFlex(D4ItemTable(d, "D4m", d4.categories))
```

```{r d4mPercentPlot, fig.width=6.5, fig.height=6}
D4PercentStackPlot(d, "D4m", d4.categories, titleText = ItemQuestionText("D4m", q))
```

```{r d4mMeansPlot, fig.width=6.5, fig.height=5}
D4MeansOrderedPlot(d, "D4m", titleText = ItemQuestionText("D4m", q))
```

```{r d4mSlopePlot, fig.width=6.5, fig.height=4}
D4SlopePlot(d, d2018, "D4m", titleText = ItemQuestionText("D4m", q))
```

`r paste0("Muskellunge anglers agree more strongly than any other preferred group (4.3) that there are not enough places to fish for their preferred fish, and Northern pike (3.5) and Yellow perch (3.5) anglers also lean toward agreement -- consistent with muskellunge, pike, and perch all being managed in a comparatively limited number of Nebraska waters. Bluegill/Sunfish and Channel catfish anglers feel the opposite, disagreeing by roughly two to one, consistent with how widely those species are stocked and available.")`

`r paste0("Flathead catfish anglers' agreement rose sharply between 2018 and 2025, from 2.5 to 3.3 -- the largest movement of any group on this item, and second in this battery only to Blue catfish anglers' shift on the smaller-fish trade-off item. Agreement across all anglers also crept upward between the two years, from 2.9 to 3.1, another instance, like the difficulty-of-catching item earlier, where the shift shows up broadly rather than only within individual preferred groups.")`

# Chapter 3: Crosstabs by Preferred Species

```{r ch3Setup}
# Layout helpers. In officedown a block_section describes the section that ENDS
# at that point, so a wide table is bracketed by a portrait break before it and
# a landscape break after it (D43).
sect_portrait <- function() {
  block_section(prop_section(
    page_size = page_size(orient = "portrait"),
    type = "nextPage"
  ))
}
sect_landscape <- function() {
  block_section(prop_section(
    page_size = page_size(orient = "landscape"),
    type = "nextPage"
  ))
}

# Select-all field sets, selected exactly as 2025CrossTabReport.rmd L247 does.
# Several A4 fields carry no 2025 data; they contribute nothing and drop out of
# the percentage calculation on their own, as they do in the crosstab report.
a4.fields <- d %>% dplyr::select(contains("A4")) %>% select(-contains("Answered")) %>% names()
a5.fields <- d %>% dplyr::select(contains("A5")) %>% select(-contains("Answered")) %>% names()
a6.fields <- d %>% dplyr::select(contains("A6")) %>% select(-contains("Answered")) %>% names()

# Sub-scale membership drives the battery tables (D88). Read here rather than
# in getData so Chapter 3's inputs stay in one place.
s <- read.csv(file = "../../Data/DataAggregation1/Scales.csv")

# The tournament count is relabeled exactly as 2025CrossTabReport.rmd L205 does.
dTourney <- d %>%
  mutate(fishedTourney = factor(
    if_else(fishedTourney, "Fished Tournaments", "No Tournaments"),
    levels = c("No Tournaments", "Fished Tournaments")
  ))

# Daggers mark items reversed within the named scale, read from Scales.csv.
Ch3ItemLabels <- function(fields, scaleName = NULL) {
  rev <- if (is.null(scaleName)) {
    character(0)
  } else {
    unique(s$Field[s$ScaleName == scaleName & s$Reversed])
  }
  vapply(
    fields, Ch3ItemLabel, character(1),
    codebook = q, reversedFields = rev, USE.NAMES = FALSE
  )
}

c2.fields <- d %>% dplyr::select(contains("C2")) %>% select(-contains("Answered")) %>% names()
q31.fields <- d %>% dplyr::select(contains("Q31")) %>% select(-contains("Answered")) %>% names()
e1.fields <- d %>% dplyr::select(contains("E1")) %>% select(-contains("Answered")) %>% names()

stopifnot(
  all(c(a4.fields, a5.fields, a6.fields) %in% names(d)),
  nrow(s) > 0,
  sum(!is.na(dTourney$fishedTourney)) == sum(!is.na(d$fishedTourney)),
  # Every battery item must land in exactly one table: a sub-scale table or
  # the unassigned-items table that follows it.
  length(c2.fields) == 17,
  length(q31.fields) == 12,
  length(e1.fields) == 16
)
```

`r paste0("This chapter crosstabs the remaining survey questions by preferred group. Questions appear in the order they are reported in the 2025 Crosstabs report, and each question keeps the universe and the derived variables that report uses; only the columns of the original crosstabs -- residency, gender, and age -- are replaced by the preferred groups. ", caption.ch3rows)`

`r paste0("Two conventions for the sample size are used. Where every response column of a table shares one denominator, a single N column reports it. Where each column carries its own universe -- a battery item with its own missingness, a scale score with its completeness gate, or an indicator computed on its own subset -- the count appears inside each cell after the confidence interval. N is the raw unweighted respondent count in both cases.")`

<!--
There is no visualizations chapter. Step 4 of the plan produces figures that are
interspersed within Chapters 1-3 next to the questions they illustrate (D34).
Chapter 3 figures are held until the tables have been reviewed (D91).
-->

`r run_pagebreak()`

## Fish Out-Of-State

`r paste(trimws(GetQuestion(q, A11, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3A11}
CreateFlex(Ch3SelectOneTable(d, "A11"))
```

```{r ch3A11Plot, fig.width=6.5, fig.height=5}
Ch3RatePlot(
  d, "A11", "Yes", "Percent answering Yes",
  titleText = trimws(GetQuestion(q, A11, 2025))
)
```

`r run_pagebreak()`

## Boat Out-Of-State

`r paste(trimws(GetQuestion(q, A12, 2025)), "  ", caption.ch3selectone, "  Only respondents who fished out of state are included in this calculation.", "  ", caption.raked, sep="")`

```{r ch3A12}
CreateFlex(Ch3SelectOneTable(d %>% filter(A11 == "Yes"), "A12"))
```

```{r ch3A12Plot, fig.width=6.5, fig.height=5}
Ch3RatePlot(
  d %>% filter(A11 == "Yes"), "A12", "Yes", "Percent answering Yes",
  titleText = trimws(GetQuestion(q, A12, 2025))
)
```

`r run_pagebreak()`

## Park Entry Permit

`r paste(trimws(GetQuestion(q, A10, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3A10}
CreateFlex(Ch3SelectOneTable(d, "A10"))
```

`r run_pagebreak()`

## Fishing Tournaments

`r paste("Percent of respondents who participated in at least one fishing tournament (derived from ", trimws(GetQuestion(q, A13, 2025)), ").", "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3Tourney}
CreateFlex(Ch3SelectOneTable(dTourney, "fishedTourney"))
```

```{r ch3TourneyPlot, fig.width=6.5, fig.height=5}
Ch3RatePlot(
  dTourney, "fishedTourney", "Fished Tournaments",
  "Percent fishing at least one tournament",
  titleText = "Fishing tournament participation"
)
```

`r paste(trimws(GetQuestion(q, A13, 2025)), "  ", caption.ch3means, "  Only respondents who participated in at least one tournament are included in this calculation.", "  ", caption.raked, sep="")`

```{r ch3TourneyMean}
CreateFlex(Ch3MeansTable(
  d %>% filter(A13_corrected > 0),
  "A13_corrected",
  "Mean tournaments fished"
))
```

`r run_pagebreak()`

`r sect_portrait()`

## Waterbody Types

`r paste(trimws(GetQuestion(q, A4, 2025)), "  ", caption.ch3selectall, "  ", caption.raked, sep="")`

```{r ch3A4}
CreateFlex(Ch3SelectAllTable(d, a4.fields, "A4_Answered"))
```

`r run_pagebreak()`

## Methods

`r paste(trimws(GetQuestion(q, A5, 2025)), "  ", caption.ch3selectall, "  ", caption.raked, sep="")`

```{r ch3A5}
CreateFlex(Ch3SelectAllTable(d, a5.fields, "A5_Answered"))
```

`r sect_landscape()`

## Techniques

`r paste(trimws(GetQuestion(q, A6, 2025)), "  ", caption.ch3selectall, "  ", caption.raked, sep="")`

```{r ch3A6}
CreateFlex(Ch3SelectAllTable(d, a6.fields, "A6_Answered"))
```

`r sect_landscape()`

## Crowding

`r paste(trimws(GetQuestion(q, Q11, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3Q11}
CreateFlex(Ch3SelectOneTable(d %>% filter(!is.na(Q11)), "Q11"))
```

```{r ch3Q11Plot, fig.width=6.5, fig.height=6}
Ch3StackPlot(
  d %>% filter(!is.na(Q11)), "Q11",
  titleText = trimws(GetQuestion(q, Q11, 2025))
)
```

`r sect_portrait()`

## Access

`r paste(trimws(GetQuestion(q, A17, 2025)), "  ", caption.ch3indicator, "  The first two columns are computed on everyone who answered the question; the last three are computed on respondents who used at least one of the two area types, matching the 2025 Crosstabs report.", "  ", caption.raked, sep="")`

```{r ch3A17}
# Universe for the combination columns copied from 2025CrossTabReport.rmd L317:
# respondents who answered both parts and used at least one area type.
dAccess <- d %>%
  filter(!is.na(A17Pub_corrected) & !is.na(A17Priv_corrected)) %>%
  filter(!(A17Pub_corrected == "No" & A17Priv_corrected == "No"))

A17Label <- function(key) l$Label[l$Response == key]

CreateFlex(Ch3IndicatorTable(list(
  list(label = A17Label("A17pub"),      data = d,       var = "A17Pub_corrected",  value = "Yes"),
  list(label = A17Label("A17priv"),     data = d,       var = "A17Priv_corrected", value = "Yes"),
  list(label = A17Label("A17both"),     data = dAccess, var = "A17both",           value = "Yes"),
  list(label = A17Label("A17justPub"),  data = dAccess, var = "A17justPub",        value = "Yes"),
  list(label = A17Label("A17justPriv"), data = dAccess, var = "A17justPriv",       value = "Yes")
)))
```

`r sect_landscape()`

## Favorite Waterbody Distance

`r paste(trimws(GetQuestion(q, A7, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3A7}
CreateFlex(Ch3SelectOneTable(d, "A7"))
```

`r sect_landscape()`

`r paste("Distance in miles to the favorite water body, using the midpoint of the band each respondent selected.", "  ", caption.ch3medians, "  ", caption.raked, sep="")`

```{r ch3A7miles}
CreateFlex(Ch3MediansTable(d, "A7_miles", "Median one-way miles", digits = 0))
```

```{r ch3A7milesPlot, fig.width=6.5, fig.height=5}
Ch3MedianPlot(
  d, "A7_miles", "Median one-way miles",
  titleText = "Distance to the favorite water body",
  subtitleText = "Band midpoints; bars are the bootstrap 95 percent interval"
)
```

`r run_pagebreak()`

`r sect_portrait()`

## Most-Visited Waterbody Distance

`r paste(trimws(GetQuestion(q, A8, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3A8}
CreateFlex(Ch3SelectOneTable(d, "A8"))
```

`r sect_landscape()`

`r paste("Distance in miles to the most-visited water body, using the midpoint of the band each respondent selected.", "  ", caption.ch3medians, "  ", caption.raked, sep="")`

```{r ch3A8miles}
CreateFlex(Ch3MediansTable(d, "A8_miles", "Median one-way miles", digits = 0))
```

```{r ch3A8milesPlot, fig.width=6.5, fig.height=5}
Ch3MedianPlot(
  d, "A8_miles", "Median one-way miles",
  titleText = "Distance to the most-visited water body",
  subtitleText = "Band midpoints; bars are the bootstrap 95 percent interval"
)
```

`r run_pagebreak()`

## Satisfaction

`r paste(trimws(GetQuestion(q, A9, 2025)), "  ", caption.ch3selectone, "  Mean scores the five responses from 1 (Very satisfied) to 5 (Very dissatisfied).", "  ", caption.raked, sep="")`

```{r ch3A9}
CreateFlex(Ch3SelectOneTable(d, "A9", includeMean = TRUE))
```

```{r ch3A9Plot, fig.width=6.5, fig.height=6}
Ch3StackPlot(
  d %>% filter(!is.na(A9)), "A9",
  titleText = trimws(GetQuestion(q, A9, 2025))
)
```

```{r ch3A9MeanPlot, fig.width=6.5, fig.height=5}
Ch3MeanPlot(
  d, "A9", "Mean response",
  titleText = trimws(GetQuestion(q, A9, 2025)),
  subtitleText = "1 = Very satisfied to 5 = Very dissatisfied, so a lower score is more satisfied",
  xExpand = c(1, 5), xBreaks = 1:5
)
```

`r run_pagebreak()`

## Live-imaging Sonar Use

`r paste(trimws(GetQuestion(q, Q16, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3Q16}
CreateFlex(Ch3SelectOneTable(d %>% filter(!is.na(Q16)), "Q16"))
```

```{r ch3Q16Plot, fig.width=6.5, fig.height=5}
Ch3RatePlot(
  d %>% filter(!is.na(Q16)), "Q16", "Yes", "Percent answering Yes",
  titleText = trimws(GetQuestion(q, Q16, 2025))
)
```

`r run_pagebreak()`

## Conservation Officer

`r paste(trimws(GetQuestion(q, E7, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3E7}
CreateFlex(Ch3SelectOneTable(d, "E7"))
```

`r sect_portrait()`

## Guided Trips

`r paste(trimws(GetQuestion(q, Q18, 2025)), "  ", caption.ch3indicator, "  ", caption.raked, sep="")`

```{r ch3Q18pct}
# Indicator construction copied from 2025CrossTabReport.rmd L563.
dHiredGuide <- d %>%
  mutate(
    hiredNE      = if_else(is.na(hiredGuide), NA, !is.na(Q18a) & Q18a > 0),
    hiredOutside = if_else(is.na(hiredGuide), NA, !is.na(Q18b) & Q18b > 0),
    hiredNEonly  = if_else(is.na(hiredGuide), NA, hiredNE & !hiredOutside),
    hiredOutOnly = if_else(is.na(hiredGuide), NA, hiredOutside & !hiredNE),
    hiredBoth    = if_else(is.na(hiredGuide), NA, hiredNE & hiredOutside),
    hiredAny     = if_else(is.na(hiredGuide), NA, hiredNE | hiredOutside)
  )

CreateFlex(Ch3IndicatorTable(list(
  list(label = "Hired a guide",                 data = dHiredGuide, var = "hiredAny",     value = TRUE),
  list(label = "Hired in Nebraska",             data = dHiredGuide, var = "hiredNE",      value = TRUE),
  list(label = "Only hired in Nebraska",        data = dHiredGuide, var = "hiredNEonly",  value = TRUE),
  list(label = "Hired outside Nebraska",        data = dHiredGuide, var = "hiredOutside", value = TRUE),
  list(label = "Only hired outside Nebraska",   data = dHiredGuide, var = "hiredOutOnly", value = TRUE),
  list(label = "Hired both in and outside",     data = dHiredGuide, var = "hiredBoth",    value = TRUE)
)))
```

`r paste("Number of guided trips taken, among anglers who hired a guide in the universe named by each column.", "  ", caption.ch3means, "  ", caption.raked, sep="")`

```{r ch3Q18means}
# Column universes copied from 2025CrossTabReport.rmd L620.
dQ18means <- d %>%
  mutate(
    hiredNE = !is.na(Q18a) & Q18a > 0,
    hiredOutside = !is.na(Q18b) & Q18b > 0,
    Q18total = coalesce(Q18a, 0) + coalesce(Q18b, 0)
  )

CreateFlex(Ch3MeansSpecTable(list(
  list(label = "Hired a guide",               data = dQ18means %>% filter(hiredNE | hiredOutside),  var = "Q18total"),
  list(label = "Hired in Nebraska",           data = dQ18means %>% filter(hiredNE),                 var = "Q18a"),
  list(label = "Only hired in Nebraska",      data = dQ18means %>% filter(hiredNE & !hiredOutside), var = "Q18a"),
  list(label = "Hired outside Nebraska",      data = dQ18means %>% filter(hiredOutside),            var = "Q18b"),
  list(label = "Only hired outside Nebraska", data = dQ18means %>% filter(hiredOutside & !hiredNE), var = "Q18b"),
  list(label = "Hired both in and outside",   data = dQ18means %>% filter(hiredNE & hiredOutside),  var = "Q18total")
)))
```

`r sect_landscape()`

## Days Fished

`r paste(trimws(GetQuestion(q, C1, 2025)), "  Total days fished across all months.", "  ", caption.ch3means, "  ", caption.ch3medians, "  ", caption.raked, sep="")`

```{r ch3Days}
# Universe copied from 2025CrossTabReport.rmd L976: a total is only used when
# every month was answered.
dDays <- d %>% filter(!is.na(C1Total_days) & C1_AnsweredAll == TRUE)

left_join(
  Ch3MeansTable(dDays, "C1Total_days", "Mean days fished"),
  Ch3MediansTable(dDays, "C1Total_days", "Median days fished"),
  by = "Preferred species"
) %>%
  CreateFlex()
```

```{r ch3DaysPlot, fig.width=6.5, fig.height=5}
Ch3MeanPlot(
  dDays, "C1Total_days", "Mean days fished",
  titleText = "Total days fished in 2025"
)
```

`r run_pagebreak()`

## Ice Fishing

`r paste(trimws(GetQuestion(q, Q26, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, sep="")`

```{r ch3Q26}
CreateFlex(Ch3SelectOneTable(
  d %>% filter(!is.na(Q26)) %>% mutate(Q26 = factor(Q26, levels = c("Yes", "No"))),
  "Q26"
))
```

```{r ch3Q26Plot, fig.width=6.5, fig.height=5}
Ch3RatePlot(
  d %>% filter(!is.na(Q26)), "Q26", "Yes", "Percent answering Yes",
  titleText = trimws(GetQuestion(q, Q26, 2025))
)
```

`r run_pagebreak()`

## Angler Motivations

`r paste(trimws(GetQuestion(q, C2, 2025)), "  Items are grouped by the motivation sub-scale they belong to in Scales.csv; the grouping organizes the tables and does not change any value.", "  ", caption.ch3means, "  ", caption.raked, sep="")`

### Natural Environment

```{r ch3C2natural}
f <- SubScaleFields(s, "Motivations", "Natural Environment")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Motivations")))
```

### Psychological and Physiological

```{r ch3C2pp}
f <- SubScaleFields(s, "Motivations", "Psychological and Physiological")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Motivations")))
```

### Social

```{r ch3C2social}
f <- SubScaleFields(s, "Motivations", "Social")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Motivations")))
```

### Fishery Resource

```{r ch3C2resource}
f <- SubScaleFields(s, "Motivations", "Fishery Resource")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Motivations")))
```

### Motivation scale scores

`r paste("Each scale score is the mean of its items, computed only for respondents who answered every item in that scale.", "  ", caption.ch3means, "  ", caption.raked, sep="")`

```{r ch3C2scales}
v <- c("motivation_pp", "motivation_natural", "motivation_social", "motivation_resource")
CreateFlex(Ch3MeansTable(d, v, ScaleLabel(v, l), gates = paste0(v, "_AnsweredAll")))
```

```{r ch3C2scalesPlot, fig.width=6.5, fig.height=7.5}
Ch3ScaleFacetPlot(
  d, v, ScaleLabel(v, l), gates = paste0(v, "_AnsweredAll"),
  titleText = "Motivation scale scores",
  subtitleText = "1 = Not At All Important ... 5 = Extremely Important",
  xExpand = c(1, 5), xBreaks = 1:5
)
```

`r paste("The same items also form a two-part split between catch-oriented and non-catch-oriented motivations, reported below on the same basis.", "  ", caption.ch3means, "  ", caption.raked, sep="")`

```{r ch3C2catchScales}
v <- c("motivation_noncatch", "motivation_catch")
CreateFlex(Ch3MeansTable(d, v, ScaleLabel(v, l), gates = paste0(v, "_AnsweredAll")))
```

`r run_pagebreak()`

## Regulations

`r paste(trimws(GetQuestion(q, Q31, 2025)), "  Items are grouped by the regulation sub-scale they belong to in Scales.csv. Item means are computed on the responses as recorded and are not reverse-adjusted, matching the 2025 Crosstabs report. None of the three sub-scales reported here contains a reverse-coded item; the reversals the codebook records for this battery belong to a separate bipolar orientation scale that this report does not use.", "  ", caption.ch3means, "  ", caption.raked, sep="")`

### Comprehension and Confidence

```{r ch3Q31comp}
f <- SubScaleFields(s, "Regulations", "Comprehension and Confidence")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Regulations")))
```

### Site-Specific Support

```{r ch3Q31site}
f <- SubScaleFields(s, "Regulations", "Site-Specific Support")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Regulations")))
```

`r sect_portrait()`

### Uniform Preference

```{r ch3Q31uniform}
f <- SubScaleFields(s, "Regulations", "Uniform Preference")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Regulations")))
```

`r sect_landscape()`

### Items outside the three regulation sub-scales

`r paste("These items are part of the battery but belong to no sub-scale of the Regulations scale.", "  ", caption.ch3means, sep="")`

```{r ch3Q31other}
f <- UnassignedFields(s, "Regulations", q31.fields)
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Regulations")))
```

### Regulation scale scores

`r paste("Each scale score is the mean of its items, computed only for respondents who answered every item in that scale.", "  ", caption.ch3means, "  ", caption.raked, sep="")`

```{r ch3Q31scales}
v <- c("reg_comprehension", "reg_sitesupport", "reg_uniform")
CreateFlex(Ch3MeansTable(d, v, ScaleLabel(v, l), gates = paste0(v, "_AnsweredAll")))
```

```{r ch3Q31scalesPlot, fig.width=6.5, fig.height=5}
Ch3ScaleFacetPlot(
  d, v, ScaleLabel(v, l), gates = paste0(v, "_AnsweredAll"),
  titleText = "Regulation scale scores",
  subtitleText = "1 = Strongly disagree ... 5 = Strongly agree",
  xExpand = c(1, 5), xBreaks = 1:5, ncol = 3
)
```

`r run_pagebreak()`

## Angler Attitudes

`r paste(trimws(GetQuestion(q, E1, 2025)), "  Items are grouped by the attitude sub-scale they belong to in Scales.csv. Item means are computed on the responses as recorded and are not reverse-adjusted; a dagger marks an item the codebook flags as reverse-coded.", "  ", caption.ch3means, "  ", ReversedItemsNote("Attitudes"), "  ", caption.raked, sep="")`

### Catch something

```{r ch3E1catch}
f <- SubScaleFields(s, "Attitudes", "Catch something")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Attitudes")))
```

### Numbers of fish

```{r ch3E1numbers}
f <- SubScaleFields(s, "Attitudes", "Numbers of fish")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Attitudes")))
```

### Size of fish

```{r ch3E1size}
f <- SubScaleFields(s, "Attitudes", "Size of fish")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Attitudes")))
```

### Harvesting fish

```{r ch3E1harvest}
f <- SubScaleFields(s, "Attitudes", "Harvesting fish")
CreateFlex(Ch3MeansTable(d, f, Ch3ItemLabels(f, "Attitudes")))
```

### Attitude scale scores

`r paste("Each scale score is the mean of its items, computed only for respondents who answered every item in that scale. Reverse-coded items are reversed before the scale score is formed.", "  ", caption.ch3means, "  ", ReversedItemsNote("Attitudes"), "  ", caption.raked, sep="")`

```{r ch3E1scales}
v <- c("attitude_catch", "attitude_numbers", "attitude_size", "attitude_harvest")
CreateFlex(Ch3MeansTable(d, v, ScaleLabel(v, l), gates = paste0(v, "_AnsweredAll")))
```

```{r ch3E1scalesPlot, fig.width=6.5, fig.height=7.5}
Ch3ScaleFacetPlot(
  d, v, ScaleLabel(v, l), gates = paste0(v, "_AnsweredAll"),
  titleText = "Attitude scale scores",
  subtitleText = "1 = Strongly Disagree ... 5 = Strongly Agree; reverse-coded items are reversed before the score is formed",
  xExpand = c(1, 5), xBreaks = 1:5
)
```

`r run_pagebreak()`

## Gender

`r paste(trimws(GetQuestion(q, E2, 2025)), "  ", caption.ch3selectone, "  ", caption.raked, "  Percentages are weighted, as they are throughout this report.", sep="")`

```{r ch3E2}
CreateFlex(Ch3SelectOneTable(d %>% filter(!is.na(E2)), "E2"))
```

`r run_pagebreak()`

## Age

`r paste("Respondent age group.", "  ", caption.ch3selectone, "  The final column is the weighted mean age in years, taken from the reported age rather than from the bands, and computed on the same respondents as the percentages.", "  ", caption.raked, "  Percentages and the mean are weighted, as they are throughout this report.", sep="")`

```{r ch3E3}
# The single N column is only correct while the band and the reported age are
# missing on exactly the same respondents (they are: E3 is derived from Age).
# If that ever stops holding, the denominator claim in the caption is wrong and
# the render should stop rather than print it.
stopifnot(identical(is.na(d$Age), is.na(d$E3)))

CreateFlex(Ch3SelectOneTable(
  d %>% filter(!is.na(E3)), "E3",
  includeMean = TRUE, meanVar = "Age", meanLabel = "Mean age \u00b1 CI"
))
```

`r run_pagebreak()`

# Chapter 4: Satisfaction

```{r ch4Setup}
# A9 reversed, plus the two paired differences. Additive only: no row is added,
# dropped, or reweighted, so nothing in Chapters 1-3 changes.
nBeforeCh4 <- nrow(d)
d <- Ch4AddSatVars(d)

ch4.nSix <- Ch4CorrComplete(d)
ch4.alphaSat <- Ch4Alpha(d, c("D4i", "D4j", "D4k", "D4l"))
ch4.groupMeans <- Ch4GroupMeans(d)
ch4.gapCatch <- Ch4GapNumbers(d, "D4i", "D4k")
ch4.gapHarvest <- Ch4GapNumbers(d, "D4j", "D4l")

stopifnot(
  nrow(d) == nBeforeCh4,
  # The reversal has to be exact, or the reconciliation stated in the caption
  # is false and every column in this chapter points a different way.
  all(d$A9rev + as.numeric(d$A9) == 6, na.rm = TRUE),
  identical(is.na(d$A9rev), is.na(d$A9)),
  nrow(ch4.groupMeans) == 18,
  nrow(ch4.gapCatch) == 18,
  nrow(ch4.gapHarvest) == 18
)
```

`r paste0("The survey measures satisfaction in two places that this report has so far kept apart. A9 asks how satisfied the angler was with fishing in Nebraska during 2025 and is reported in Chapter 3. Five items in the D4 battery ask about the one type of fish the angler prefers to fish for and are reported one at a time in Chapter 2. This chapter puts all six in one place, pointing the same direction, across the same preferred groups. No cell is computed differently here: the same summary functions, the same universe, and the same row set are used, so a value in this chapter and its counterpart in Chapter 2 or 3 are the same number.")`

`r caption.ch4a9`

`r caption.ch3rows`

`r run_pagebreak()`

## The satisfaction items

`r paste0("The six items, with the question text as it appears in the instrument, the short name used in the tables that follow, and the chapter that reports the item in full. N is the raw unweighted number of respondents in the analysis sample who answered the item; the mean is weighted, with a 95 percent confidence interval. ", caption.raked)`

```{r ch4items}
CreateFlex(Ch4ItemTable(d, q))
```

`r run_pagebreak()`

`r sect_portrait()`

## Satisfaction by preferred group

`r paste0("All six items across the preferred groups. ", caption.ch3means, " ", caption.ch3rows, " ", caption.raked)`

```{r ch4matrix}
CreateFlex(Ch3MeansTable(d, ch4.sat.items$Field, ch4.sat.items$Short))
```

<!--

`r sect_landscape()`

 ## Consistency between the items

`r paste0("Two different questions are asked here. The first table asks whether individual anglers answer the six items alike: an angler satisfied with one thing is, or is not, satisfied with the others. The second asks whether the preferred groups rank alike across items: the groups that rate the season highly are, or are not, the groups satisfied with size or with numbers. A set of items can behave one way at the respondent level and the other way at the group level, so both are shown.")`

### Agreement between individual anglers' answers

`r paste0("Weighted correlations between the six items, computed on the ", format(ch4.nSix, big.mark=","), " respondents who answered all six. ", caption.ch4corr)`

```{r ch4corr}
CreateFlex(Ch4CorrTable(d))
```

`r paste0("For reference, the four D4 satisfaction items form the Satisfaction sub-scale identified by the separate analysis of the D4 battery; their weighted alpha on this report's sample is ", formatC(ch4.alphaSat$alpha, format="f", digits=3), " on ", format(ch4.alphaSat$n, big.mark=","), " respondents. No composite score is built here and none is used anywhere in this report, which stays item-level. A9 asks about the season rather than about the preferred fish, and the D4 analysis places D4a with the constraint items rather than the satisfaction items, so neither is included in that coefficient. A single coefficient across all six would also conceal the structure visible in the table above.")`

`r run_pagebreak()`

### Agreement between the group averages

`r paste0("Rank correlations between the preferred-group means shown in the previous section, one observation per group. ", caption.ch4groupcorr)`

```{r ch4groupcorr}
CreateFlex(Ch4GroupCorrTable(ch4.groupMeans))
```

`r run_pagebreak()` -->

## Size and numbers: the fish anglers catch

`r paste0("D4i and D4k ask the same question about the same fish, one about the size caught and one about the number caught, so the two can be compared within an angler rather than across anglers. ", caption.ch4gap, " ", caption.ch3rows)`

```{r ch4gapCatch}
CreateFlex(Ch4GapTable(d, "D4i", "D4k", "Size caught", "Number caught"))
```

```{r ch4gapCatchPlot, fig.width=6.5, fig.height=5}
Ch4DumbbellPlot(
  d, "D4i", "D4k", "Size of fish caught", "Number of fish caught",
  titleText = "Satisfaction with the size, and with the number, of the preferred fish caught",
  subtitleText = "1 = Strongly Disagree to 5 = Strongly Agree. Rows are sorted by the size-minus-numbers difference"
)
```

`r paste0("Reading the difference column against its own interval, and without any adjustment for the number of groups compared: the interval lies above zero, with size rated higher than numbers, for ", Ch4GapNames(ch4.gapCatch, "positive"), "; it lies below zero, with numbers rated higher than size, for ", Ch4GapNames(ch4.gapCatch, "negative"), ". For the remaining ", sum(ch4.gapCatch$Type != "Overall" & abs(ch4.gapCatch$Gap) <= ch4.gapCatch$CI), " groups the interval includes zero. Overall the difference is ", FmtMeanGap(ch4.gapCatch$Gap[1], ch4.gapCatch$CI[1]), ".")`

`r run_pagebreak()`

## Size and numbers: the fish anglers may harvest

`r paste0("D4j and D4l repeat the comparison for the fish an angler is allowed to keep rather than the fish caught. ", caption.ch4gap, " ", caption.ch3rows)`

```{r ch4gapHarvest}
CreateFlex(Ch4GapTable(d, "D4j", "D4l", "Size harvestable", "Number harvestable"))
```

```{r ch4gapHarvestPlot, fig.width=6.5, fig.height=5}
Ch4DumbbellPlot(
  d, "D4j", "D4l", "Size allowed to harvest", "Number allowed to harvest",
  titleText = "Satisfaction with the size, and with the number, of the preferred fish that may be harvested",
  subtitleText = "1 = Strongly Disagree to 5 = Strongly Agree. Rows are sorted by the size-minus-numbers difference"
)
```

`r paste0("On the same reading: the interval lies above zero for ", Ch4GapNames(ch4.gapHarvest, "positive"), ", and below zero for ", Ch4GapNames(ch4.gapHarvest, "negative"), ". For the remaining ", sum(ch4.gapHarvest$Type != "Overall" & abs(ch4.gapHarvest$Gap) <= ch4.gapHarvest$CI), " groups the interval includes zero. Overall the difference is ", FmtMeanGap(ch4.gapHarvest$Gap[1], ch4.gapHarvest$CI[1]), ".")`

`r run_pagebreak()`

# Chapter 5: Angler Type Profiles

```{r ch5Setup}
# Additive only: columns are added to d, but no row is added, dropped, or
# reweighted, so nothing in Chapters 1-4 changes. The model is never fitted
# here; Ch5LPALoadResults() reads the saved results (D152) and errors if they
# were fitted to different data.
nBeforeCh5 <- nrow(d)
d <- Ch5LPAGate(d)
ch5.frame <- Ch5LPAFrame(d)
ch5.models <- Ch5LPALoadResults(ch5.frame)
ch5.diag <- Ch5LPADiagnostics(ch5.models)
ch5.selected <- Ch5LPASelect(ch5.diag)
ch5.sel <- ch5.diag %>% filter(Model == ch5.selected)
ch5.k <- ch5.sel$Classes
d <- Ch5LPAAssign(d, ch5.models[[ch5.selected]])

ch5.nFitted <- sum(d$lpa_fitted)
ch5.nUnassigned <- sum(d$lpa_class == ch5.lpa.unassigned)
ch5.long <- Ch5ClassBySpeciesLong(d)
ch5.prof <- Ch5LPAProfileLong(d, l)

ch5.floorFail <- ch5.diag %>%
  filter(StatusCode %in% c(0, 1), !PassSize) %>%
  arrange(Classes)
ch5.spikes <- purrr::map_dfr(
  ch5.diag$Model[!ch5.diag$StatusCode %in% c(0, 1)],
  function(m) Ch5LPASpike(ch5.models[[m]], ch5.frame)
) %>%
  left_join(ch5.diag %>% select(Model, Profiles = Classes), by = "Model") %>%
  arrange(Profiles)
ch5.equalBIC <- ch5.diag %>% filter(Variances == "equal") %>% arrange(Classes) %>% pull(BIC)

caption.ch5diag <- "BIC is minus twice the log-likelihood plus the number of estimated parameters times the natural log of the number of fitted respondents; lower values indicate better fit. Relative entropy runs from 0 to 1, with 1 meaning every respondent is assigned with certainty. The lowest mean assigned probability is the average membership probability among the respondents assigned to a profile, for the profile where that average is smallest. OpenMx status 0 or 1 indicates the estimation converged. All values in this table are unweighted model quantities."

stopifnot(
  nrow(d) == nBeforeCh5,
  # D156: the final selection. A different result means the data or the rule changed.
  ch5.selected == "equal_6",
  length(ch5.models) == length(Ch5LPAModelNames()),
  ch5.nFitted == nrow(ch5.frame),
  ch5.nUnassigned == sum(!d$lpa_fitted),
  !anyNA(d$lpa_class),
  all(as.vector(table(d$lpa_class))[seq_len(ch5.k)] ==
    tabulate(ch5.models[[ch5.selected]]$modal, ch5.k)),
  # Unassigned is a level, so every row's shares sum to 100
  all(abs(tapply(ch5.long$Value, ch5.long$Column, sum) - 100) < 1e-6),
  nrow(ch5.prof) == (ch5.k + 1) * length(ch5.lpa.vars),
  !anyNA(ch5.prof$Value),
  # The exclusion text describes exactly these cases (F76, F77)
  nrow(ch5.floorFail) == 2,
  nrow(ch5.spikes) == 2,
  all(ch5.spikes$AtMax == ch5.spikes$Answered),
  length(unique(ch5.spikes$Variable)) == 1,
  all(diff(ch5.equalBIC) < 0)
)
```

`r paste0("This chapter groups anglers into profiles using a latent profile analysis of eleven scale scores reported in Chapter 3: the four angler-attitude scales, the four motivation scales, and the three regulation scales. One model is fitted to the whole report universe, so the profiles are defined once and are the same in every preferred-species row; the tables below report how each row's respondents are distributed across them. The model is fitted without the survey weights. Every percentage and mean reported from it is weighted, with intervals built on the Kish effective N and raw unweighted counts displayed, as in Chapters 1 to 4.")`

`r paste0(FmtCount(ch5.nFitted), " of the ", FmtCount(nrow(d)), " respondents in this report's universe (", formatC(100 * ch5.nFitted / nrow(d), format = "f", digits = 1), "%) answered at least ", ch5.lpa.min.scales, " of the eleven scales and were included in the fit. Scales that a fitted respondent left blank are handled within the model rather than imputed. The other ", FmtCount(ch5.nUnassigned), " respondents are reported as Unassigned rather than dropped. Profiles are numbered 1 to ", ch5.k, " in the order the estimation produced them; the numbers are labels and carry no order.")`

`r sect_portrait()`

## Choosing the number of profiles

`r paste0("Models with 1 to ", max(ch5.lpa.classes), " profiles were fitted under two within-profile variance structures: equal, in which every profile shares one variance per scale, and varying, in which each profile has its own. The equal structure was extended to ", max(ch5.lpa.extend.equal), " profiles. The model used in the rest of this chapter is the one with the lowest BIC among models that converged, whose smallest profile holds at least ", 100 * ch5.lpa.min.class.prop, " percent of fitted respondents, and whose relative entropy is at least ", formatC(ch5.lpa.min.entropy, format = "f", digits = 2), ". That is the ", ch5.k, "-profile ", ch5.sel$Variances, "-variance model.  ", caption.ch5diag)`

```{r ch5Diagnostics}
CreateFlex(Ch5LPADiagnosticsTable(ch5.diag, ch5.selected))
```

`r paste0("Four models with a lower BIC than the selected model are not eligible. The ", paste(ch5.floorFail$Classes, collapse = "- and "), "-profile equal-variance models converged, but their smallest profiles hold ", paste(formatC(100 * ch5.floorFail$SmallestClassProp, format = "f", digits = 1), collapse = " and "), " percent of fitted respondents. BIC is lower at every larger equal-variance model fitted, so the selected model is the largest eligible equal-variance model rather than the point at which BIC stops decreasing. The ", paste(ch5.spikes$Profiles, collapse = "- and "), "-profile varying-variance models did not converge (OpenMx status ", paste(unique(ch5.diag$StatusCode[ch5.diag$Model %in% ch5.spikes$Model]), collapse = ", "), "). In each, one profile (", paste(FmtCount(ch5.spikes$ClassN), collapse = " and "), " respondents) contains only respondents at the scale maximum of ", ch5.spikes$Max[1], " on the ", ScaleLabel(ch5.spikes$Variable[1], l), " regulation scale among those who answered it (", paste0(ch5.spikes$AtMax, " of ", ch5.spikes$Answered, collapse = " and "), "), and that profile's estimated variance on the scale is effectively zero (", paste(formatC(ch5.spikes$Variance, format = "e", digits = 1), collapse = " and "), ").")`

## Assignment certainty

`r paste0("Each fitted respondent is assigned to the profile with the highest estimated membership probability. The table below shows how certain those assignments are, by the number of scales the respondent answered. The values are unweighted model quantities for the ", FmtCount(ch5.nFitted), " fitted respondents.")`

```{r ch5Certainty}
CreateFlex(Ch5LPACertaintyTable(d))
```

`r sect_landscape()`

## Profile means

`r paste0("The two figures below show the weighted mean of each scale for the respondents assigned to each profile, with 95 percent confidence intervals. These are weighted means of the assigned respondents, not the unweighted means the model estimated for each profile. The first figure places the profiles side by side across the eleven scales.")`

```{r ch5ProfileLines, fig.width=6.5, fig.height=5.5}
Ch5LPAProfileLinePlot(ch5.prof, "Scale means by profile")
```

`r paste0("The second figure shows one panel per scale, with the profiles along the horizontal axis and the Overall weighted mean for every respondent who answered that scale as a dashed line.")`

```{r ch5ProfileFacets, fig.width=6.5, fig.height=7}
Ch5LPAProfileFacetPlot(ch5.prof, "Scale means by profile, one panel per scale")
```

`r sect_portrait()`

`r paste0("The values behind both figures are below. The Overall column is computed on every respondent in the universe who answered the scale, including Unassigned respondents, and equals the Overall row of the Chapter 3 scale tables.  ", caption.ch3means, "  ", caption.raked)`

```{r ch5ProfileTable}
CreateFlex(Ch5LPAProfileTable(ch5.prof), mergeOnFirst = TRUE)
```

## Profiles by preferred species

`r paste0("The table below gives, for each preferred-species row, the weighted percentage of its respondents assigned to each profile, with Unassigned as a column so that each row sums to 100. The rows overlap, as elsewhere in this report, and must not be totalled. Where a row has no respondents in a profile, the percentage is 0.0 and the interval has zero width. ", Ch5SuppressedNote(ch5.long), " This is the only chapter of the report that withholds rows; the effective-N floor was set before the model was fitted.  ", caption.ch3selectone, "  ", caption.raked)`

```{r ch5ClassBySpecies}
CreateFlex(Ch5ClassBySpeciesTable(d, ch5.long))
```

## Profiles on other survey questions

```{r ch5CompareSetup}
# D163: questions chosen by the user (prompt 123) before any results were seen.
ch5.dcmp <- Ch5LPACompareData(d)
ch5.cmp <- Ch5LPACompareLong(ch5.dcmp)
ch5.mix <- Ch5LPAClassMix(d)

# For every row, Overall N minus the six profile Ns must equal the Unassigned
# respondents who have that measure: nobody lost, nobody double-counted.
ch5.cmpN <- ch5.cmp %>%
  group_by(var, Kind) %>%
  summarise(
    gap = N[Class == "Overall"] - sum(N[Class != "Overall"]),
    .groups = "drop"
  ) %>%
  mutate(unassigned = purrr::map_int(var, function(v) {
    sum(!is.na(ch5.dcmp[[v]]) & ch5.dcmp$lpa_class == ch5.lpa.unassigned)
  }))
stopifnot(
  nrow(ch5.cmp) == nrow(ch5.compare.spec) * (ch5.k + 1),
  !anyNA(ch5.cmp$Value),
  all(ch5.cmpN$gap == ch5.cmpN$unassigned),
  all(abs(tapply(ch5.mix$Value, ch5.mix$Class, sum) - 100) < 1e-6)
)
```

`r paste0("The table below compares the profiles on other survey questions. Each question keeps the universe it has in Chapter 3, so N differs by row, and the Overall column equals the Overall row of the corresponding Chapter 3 table. Unassigned respondents are counted in Overall only and have no column of their own. The river and stream row counts a respondent who fished the Missouri River, the Platte River, or other streams, rivers, and canals; it combines three Chapter 3 waterbody types and has no single Chapter 3 counterpart. Percentage and mean cells show the weighted value with a 95 percent confidence interval, followed by N. Median cells show the lower limit, the weighted median and the upper limit, followed by N, as in Chapter 3. Satisfaction is scored from 1, Very satisfied, to 5, Very dissatisfied, as in Chapter 3.  ", caption.raked)`

```{r ch5Compare}
CreateFlex(Ch5LPACompareTable(ch5.cmp))
```

`r sect_landscape()`

## The six profiles

```{r ch5Describe}
# D161: interpretive descriptions, added at the user's request (prompt 122).
# Every comparative claim in the paragraphs below is asserted here, so a change
# in the data or model stops the render instead of leaving the prose wrong.
ch5.std <- Ch5LPAStd(ch5.prof, d)
ch5.classN <- table(d$lpa_class)
z <- function(cls, v) Ch5Cell(ch5.std, cls, v)$Z
top <- function(v) Ch5Extreme(ch5.std, v, which.max)
bottom <- function(v) Ch5Extreme(ch5.std, v, which.min)
reg.vars <- c("reg_comprehension", "reg_sitesupport", "reg_uniform")

stopifnot(
  nrow(ch5.std) == ch5.k * length(ch5.lpa.vars),
  # Class 1
  top("attitude_harvest") == 1, bottom("reg_comprehension") == 1,
  bottom("reg_sitesupport") == 1, top("reg_uniform") == 1,
  z(1, "attitude_catch") > 0, z(1, "attitude_numbers") > 0,
  abs(z(1, "attitude_size")) < 0.2, all(abs(sapply(motivation.vars, z, cls = 1)) < 0.3),
  # Class 2
  all(sapply(attitude.vars, z, cls = 2) < 0),
  names(which.min(sapply(motivation.vars, z, cls = 2))) == "motivation_resource",
  z(2, "motivation_natural") > 0, z(2, "motivation_social") > 0,
  z(2, "reg_uniform") > 0, all(abs(sapply(reg.vars, z, cls = 2)) < 0.5),
  # Class 3
  z(3, "attitude_size") > 0, z(3, "attitude_catch") > 0, z(3, "attitude_harvest") < 0,
  all(sapply(motivation.vars, z, cls = 3) < 0.05),
  z(3, "reg_comprehension") > 0.5, z(3, "reg_sitesupport") > 0.5, z(3, "reg_uniform") < -0.5,
  # Class 4
  all(sapply(motivation.vars, top) == 4), top("attitude_size") == 4,
  z(4, "attitude_numbers") > 0, abs(z(4, "attitude_catch")) < 0.2,
  abs(z(4, "attitude_harvest")) < 0.2, z(4, "reg_sitesupport") > 0,
  # Class 5
  all(sapply(motivation.vars, bottom) == 5),
  abs(z(5, "attitude_catch")) < 0.2, abs(z(5, "attitude_harvest")) < 0.2,
  z(5, "attitude_numbers") < 0, z(5, "attitude_size") < 0,
  all(abs(sapply(reg.vars, z, cls = 5)) < 0.35),
  # Class 6
  all(sapply(attitude.vars, bottom) == 6), top("reg_comprehension") == 6,
  top("reg_sitesupport") == 6, bottom("reg_uniform") == 6,
  z(6, "motivation_natural") > 0, z(6, "motivation_social") > 0, z(6, "motivation_resource") < 0,
  # Species shares quoted below
  ch5.long$Number[ch5.long$Class == "Class 6" & ch5.long$Column == "Moronides"] == 0,
  with(
    ch5.long[ch5.long$Class == "Class 6" & !ch5.long$Suppressed & ch5.long$Type != "Overall", ],
    Column[which.max(Value)] == "Bluegill / Sunfish"
  )
)
# Comparison claims in the second paragraphs (D163)
cv <- function(cls, v, kind) Ch5CmpRow(ch5.cmp, cls, v, kind)$Value
hi <- function(v, kind) Ch5CmpRank(ch5.cmp, v, kind, which.max)
lo <- function(v, kind) Ch5CmpRank(ch5.cmp, v, kind, which.min)
activity <- list(
  c("cmpTourney", "pct"), c("cmpKayak", "pct"), c("cmpIce", "pct"),
  c("cmpStream", "pct"), c("cmpPark", "pct"), c("cmpOutState", "pct"),
  c("cmpLiveScope", "pct")
)
femaleTop2 <- ch5.cmp %>%
  filter(var == "cmpFemale", Class != "Overall") %>%
  slice_max(Value, n = 2) %>%
  pull(Class) %>%
  as.character()
stopifnot(
  # Class 1
  abs(cv(1, "cmpDays", "mean") - cv("Overall", "cmpDays", "mean")) < 3,
  cv(1, "cmpGuide", "pct") > cv("Overall", "cmpGuide", "pct"),
  cv(1, "cmpIce", "pct") > cv("Overall", "cmpIce", "pct"),
  cv(1, "cmpBoat", "pct") > cv("Overall", "cmpBoat", "pct"),
  hi("cmpSatisfaction", "mean") == 1,
  # Class 2
  cv(2, "cmpDays", "median") < cv("Overall", "cmpDays", "median"),
  cv(2, "cmpTourney", "pct") < cv("Overall", "cmpTourney", "pct"),
  cv(2, "cmpIce", "pct") < cv("Overall", "cmpIce", "pct"),
  cv(2, "cmpSatisfaction", "mean") < cv("Overall", "cmpSatisfaction", "mean"),
  setequal(femaleTop2, c("Class 2", "Class 6")),
  # Class 3
  cv(3, "cmpDays", "mean") > cv("Overall", "cmpDays", "mean"),
  cv(3, "cmpDays", "median") > cv("Overall", "cmpDays", "median"),
  hi("cmpGuide", "pct") == 3, hi("cmpPrivate", "pct") == 3,
  abs(cv(3, "cmpTourney", "pct") - cv("Overall", "cmpTourney", "pct")) < 2,
  # Class 4 is the profile most associated with tournaments (prompt 124)
  hi("cmpTourney", "pct") == 4, top("motivation_resource") == 4,
  cv(3, "cmpMiles", "median") < cv("Overall", "cmpMiles", "median"),
  lo("cmpFemale", "pct") == 3,
  # Class 4
  hi("cmpDays", "mean") == 4, hi("cmpDays", "median") == 4,
  all(vapply(activity, function(a) hi(a[1], a[2]), integer(1)) == 4),
  lo("cmpAge", "mean") == 4,
  # Class 5
  lo("cmpDays", "mean") == 5, lo("cmpDays", "median") == 5,
  all(vapply(activity[-1], function(a) lo(a[1], a[2]), integer(1)) == 5),
  hi("cmpAge", "mean") == 5,
  # Class 6
  cv(6, "cmpDays", "median") < cv("Overall", "cmpDays", "median"),
  lo("cmpGuide", "pct") == 6, lo("cmpBoat", "pct") == 6, lo("cmpTourney", "pct") == 6,
  cv(6, "cmpMiles", "median") < cv("Overall", "cmpMiles", "median"),
  lo("cmpSatisfaction", "mean") == 6
)
A <- function(cls, v, kind) {
  paste0(Ch5CmpFmt(ch5.cmp, cls, v, kind), ", against ", Ch5CmpFmt(ch5.cmp, "Overall", v, kind), " overall")
}
V <- function(cls, v, kind) Ch5CmpFmt(ch5.cmp, cls, v, kind)
MIX <- function(cls) Ch5MixCaveat(ch5.mix, cls)

M <- function(cls, v) Ch5M(ch5.std, cls, v)
MZ <- function(cls, v) Ch5MZ(ch5.std, cls, v)
S <- function(cls, col) Ch5Share(ch5.long, cls, col)
Sov <- function(cls) Ch5Share(ch5.long, cls, "Overall", ci = FALSE)
```

`r paste0("The paragraphs below describe each profile by the scales on which it differs most from the Overall mean. Means are the weighted means in the profile means table; the figure after each mean is its distance from the Overall mean in standard deviations of the Overall weighted distribution (SD). Two scale names need a note: the Fishery resource motivation scale is made up of catch outcomes (competing for prizes, obtaining fish to eat, catching a trophy, the fun of catching), and the Simplification regulation scale measures agreement with uniform statewide regulations. Species shares are the row percentages from the table above, with their confidence intervals. The label and the closing picture in each paragraph are an interpretive summary of the eleven scale scores. They are not measured directly, and traits beyond those scales, such as how often or how an angler fishes, are not established by these data.")`

`r paste0("The second paragraph for each profile compares it with the Overall column on the other survey questions in the table above; the values quoted are from that table, and its confidence intervals show that several of the differences described are small relative to their precision. Where a family group makes up at least ", ch5.mix.gap, " percentage points more of a profile than of all assigned respondents, the paragraph names it, because questions that vary by species may partly reflect that mix rather than the profile itself.")`

### Class 1: The harvest-minded, keep-it-simple angler

`r paste0("Class 1 holds ", Sov(1), " of respondents (n = ", FmtCount(ch5.classN[['Class 1']]), "). It has the highest harvest score of any profile (", MZ(1, 'attitude_harvest'), ") and is above average on needing to catch something (", M(1, 'attitude_catch'), ") and on catching many fish (", M(1, 'attitude_numbers'), "). Size matters no more than average (", M(1, 'attitude_size'), "), and its motivations sit near the Overall means. What sets it apart is regulations: it reports the least comprehension of the rules (", MZ(1, 'reg_comprehension'), "), the least support for site-specific rules (", M(1, 'reg_sitesupport'), "), and the strongest preference for uniform statewide rules (", MZ(1, 'reg_uniform'), "). Picture someone who fishes for a meal, measures a trip by what goes in the cooler, and finds a patchwork of lake-specific rules confusing. Class 1 makes up ", S(1, 'Walleye / Sauger'), " of Walleye / Sauger, ", S(1, 'Crappie'), " of Crappie and ", S(1, 'Panfish / Sunfish'), " of Panfish / Sunfish anglers, against ", Sov(1), " overall.")`

`r paste0("On the other survey questions, Class 1 fishes about as often as anglers overall (mean days ", A(1, 'cmpDays', 'mean'), "). It is more likely than average to have hired a guide (", A(1, 'cmpGuide', 'pct'), "), to have ice fished (", A(1, 'cmpIce', 'pct'), ") and to have fished from a motorized boat (", A(1, 'cmpBoat', 'pct'), "). It reports the lowest overall satisfaction of any profile (mean ", A(1, 'cmpSatisfaction', 'mean'), ", where higher means less satisfied). ", MIX(1))`

### Class 2: The relaxed, catch-optional angler

`r paste0("Class 2 holds ", Sov(2), " of respondents (n = ", FmtCount(ch5.classN[['Class 2']]), "). It is below average on all four catch attitudes: catch something ", M(2, 'attitude_catch'), ", numbers ", M(2, 'attitude_numbers'), ", size ", M(2, 'attitude_size'), ", harvest ", M(2, 'attitude_harvest'), ". Its lowest motivation is catch outcomes (", MZ(2, 'motivation_resource'), "), while the outdoors (", M(2, 'motivation_natural'), ") and social (", M(2, 'motivation_social'), ") motivations run slightly above average. Its regulation scores are middling, with a slight lean toward uniform rules (", M(2, 'reg_uniform'), "). Picture someone who goes for the day out, the company and the water, and for whom a fishless trip is not a failed trip. Class 2 makes up ", S(2, 'No preference'), " of No preference and ", S(2, 'Trout'), " of Trout anglers, against ", Sov(2), " overall.")`

`r paste0("On the other survey questions, Class 2 fishes less often than average (median days ", A(2, 'cmpDays', 'median'), ") and seldom fishes tournaments (", A(2, 'cmpTourney', 'pct'), "). It ice fishes less often than average (", A(2, 'cmpIce', 'pct'), ") and is more satisfied than average (mean ", A(2, 'cmpSatisfaction', 'mean'), "). Together with Class 6 it has the highest share of women of any profile (", V(2, 'cmpFemale', 'pct'), ", and ", V(6, 'cmpFemale', 'pct'), " in Class 6, against ", V('Overall', 'cmpFemale', 'pct'), " overall). ", MIX(2))`

### Class 3: The regulation-savvy catch-and-release sport angler

`r paste0("Class 3 holds ", Sov(3), " of respondents (n = ", FmtCount(ch5.classN[['Class 3']]), "). It is above average on size (", MZ(3, 'attitude_size'), ") and on needing a catch (", M(3, 'attitude_catch'), "), but below average on harvest (", M(3, 'attitude_harvest'), "): it wants a fish on the line, preferably a good one, and then lets it go. Its motivations are at or slightly below average (social ", MZ(3, 'motivation_social'), "). It is strongly engaged with regulations, with high comprehension (", MZ(3, 'reg_comprehension'), "), high support for site-specific rules (", MZ(3, 'reg_sitesupport'), "), and a low preference for uniform rules (", MZ(3, 'reg_uniform'), "). Picture an angler, often a bass angler, who reads the regulations and values rules tailored to each lake. Class 3 makes up ", S(3, 'Bass'), " of Bass, ", S(3, 'Largemouth bass'), " of Largemouth bass and ", S(3, 'Flathead catfish'), " of Flathead catfish anglers, against ", Sov(3), " overall.")`

`r paste0("On the other survey questions, Class 3 fishes more often than average (mean days ", A(3, 'cmpDays', 'mean'), "; median ", A(3, 'cmpDays', 'median'), "). It has the highest rate of hiring a guide of any profile (", A(3, 'cmpGuide', 'pct'), ") and the highest use of private areas (", A(3, 'cmpPrivate', 'pct'), "); its tournament participation is close to the overall rate (", A(3, 'cmpTourney', 'pct'), "). Its median distance to its most visited water is ", V(3, 'cmpMiles', 'median'), " miles, against ", V('Overall', 'cmpMiles', 'median'), " overall, and it has the lowest share of women of any profile (", A(3, 'cmpFemale', 'pct'), "). ", MIX(3))`

### Class 4: The all-in enthusiast

`r paste0("Class 4 holds ", Sov(4), " of respondents (n = ", FmtCount(ch5.classN[['Class 4']]), "). It has the highest score of any profile on all four motivations: challenge and relaxation (", MZ(4, 'motivation_pp'), "), outdoors (", MZ(4, 'motivation_natural'), "), social (", MZ(4, 'motivation_social'), "), and catch outcomes (", MZ(4, 'motivation_resource'), "). It is also the most size-oriented profile (", MZ(4, 'attitude_size'), ") and is above average on numbers (", M(4, 'attitude_numbers'), "), with average scores on needing a catch (", M(4, 'attitude_catch'), ") and on harvest (", M(4, 'attitude_harvest'), "). Its support for site-specific rules is above average (", M(4, 'reg_sitesupport'), "). The catch-outcomes scale, on which no other profile scores as high, includes competing for prizes or money. Picture the angler for whom fishing is a central hobby: every reason to go matters, trophies and tournament competition included. Class 4 makes up ", S(4, 'Moronides'), " of Moronides and ", S(4, 'Smallmouth bass'), " of Smallmouth bass anglers, against ", Sov(4), " overall.")`

`r paste0("On the other survey questions, Class 4 is the most active profile and the one most likely to fish tournaments (", A(4, 'cmpTourney', 'pct'), "), although tournament anglers remain a small share of it. It has the highest mean days fished (", A(4, 'cmpDays', 'mean'), ") and median days fished (", A(4, 'cmpDays', 'median'), "), and the highest rates of any profile for using a kayak or canoe (", A(4, 'cmpKayak', 'pct'), "), ice fishing (", A(4, 'cmpIce', 'pct'), "), fishing rivers and streams (", A(4, 'cmpStream', 'pct'), "), fishing waters that require a Park Entry Permit (", A(4, 'cmpPark', 'pct'), "), fishing outside Nebraska (", A(4, 'cmpOutState', 'pct'), ") and using live-imaging sonar (", A(4, 'cmpLiveScope', 'pct'), "). It is also the youngest profile (mean age ", A(4, 'cmpAge', 'mean'), "). ", MIX(4))`

### Class 5: The low-involvement angler

`r paste0("Class 5 holds ", Sov(5), " of respondents (n = ", FmtCount(ch5.classN[['Class 5']]), "). It has the lowest score of any profile on all four motivations: challenge and relaxation (", MZ(5, 'motivation_pp'), "), outdoors (", MZ(5, 'motivation_natural'), "), social (", MZ(5, 'motivation_social'), "), and catch outcomes (", MZ(5, 'motivation_resource'), "). It is near average on needing a catch (", M(5, 'attitude_catch'), ") and on harvest (", M(5, 'attitude_harvest'), "), below average on numbers (", MZ(5, 'attitude_numbers'), ") and size (", MZ(5, 'attitude_size'), "), and close to average on the three regulation scales. Picture a licence holder for whom fishing is incidental rather than a pursuit in its own right. Uniformly low importance ratings can also reflect how a respondent uses the rating scale. Class 5 makes up ", S(5, 'No preference'), " of No preference anglers, against ", Sov(5), " overall.")`

`r paste0("On the other survey questions, Class 5 is the least active profile. It has the lowest mean days fished (", A(5, 'cmpDays', 'mean'), ") and median days fished (", A(5, 'cmpDays', 'median'), "), and the lowest rates of any profile for using a kayak or canoe (", A(5, 'cmpKayak', 'pct'), "), ice fishing (", A(5, 'cmpIce', 'pct'), "), fishing rivers and streams (", A(5, 'cmpStream', 'pct'), "), fishing waters that require a Park Entry Permit (", A(5, 'cmpPark', 'pct'), "), fishing outside Nebraska (", A(5, 'cmpOutState', 'pct'), ") and using live-imaging sonar (", A(5, 'cmpLiveScope', 'pct'), "). It is the oldest profile (mean age ", A(5, 'cmpAge', 'mean'), "). ", MIX(5))`

### Class 6: The conservation-minded purist

`r paste0("Class 6 holds ", Sov(6), " of respondents (n = ", FmtCount(ch5.classN[['Class 6']]), "), the smallest profile. It has the lowest score of any profile on all four catch attitudes: catch something ", M(6, 'attitude_catch'), ", numbers ", M(6, 'attitude_numbers'), " (", sprintf("%+.2f", z(6, 'attitude_numbers')), " SD), size ", M(6, 'attitude_size'), ", harvest ", M(6, 'attitude_harvest'), "; catching and keeping fish are close to irrelevant to it. It is motivated by the outdoors (", M(6, 'motivation_natural'), ") and by social reasons (", M(6, 'motivation_social'), ") but not by catch outcomes (", M(6, 'motivation_resource'), "). It has the highest comprehension of the rules (", M(6, 'reg_comprehension'), ") and support for site-specific rules (", M(6, 'reg_sitesupport'), ") of any profile, and the lowest preference for uniform rules (", M(6, 'reg_uniform'), "). Picture someone who values the experience and well-managed waters over the catch. Class 6 makes up ", S(6, 'Walleye / Sauger'), " of Walleye / Sauger anglers and none of the ", FmtCount(ch5.long$ColumnN[ch5.long$Column == 'Moronides'][1]), " Moronides respondents; its largest share of any displayed row is ", S(6, 'Bluegill / Sunfish'), " of Bluegill / Sunfish anglers.")`

`r paste0("On the other survey questions, Class 6 fishes less often than average (median days ", A(6, 'cmpDays', 'median'), ") and has the lowest rates of any profile for fishing tournaments (", A(6, 'cmpTourney', 'pct'), "), hiring a guide (", A(6, 'cmpGuide', 'pct'), ") and fishing from a motorized boat (", A(6, 'cmpBoat', 'pct'), "). Its median distance to its most visited water is ", V(6, 'cmpMiles', 'median'), " miles, against ", V('Overall', 'cmpMiles', 'median'), " overall. It reports the highest overall satisfaction of any profile (mean ", A(6, 'cmpSatisfaction', 'mean'), ", where lower means more satisfied), and, with Class 2, the highest share of women (", A(6, 'cmpFemale', 'pct'), "). With ", FmtCount(ch5.classN[['Class 6']]), " respondents it is the smallest profile, and most of its intervals in the table are correspondingly wide. ", MIX(6))`

`r run_pagebreak()`

<!--
D36: Appendix A is a deliberately blank placeholder. The paper questionnaire is
pasted in by hand, matching 2025CrossTabReport.rmd L1545-1547, which does the
same thing. Do not pour the instrument in programmatically.
-->

# Appendix A - Nebraska Licensed Angler Survey (Paper Version)

`r run_pagebreak()`

# Appendix B - Statistical Methodology

## Analysis sample

`r paste0("This report is restricted to respondents who answered the preferred-species question. Of the ", format(nAll2025, big.mark=","), " anglers who responded to the 2025 survey, ", format(nNoB1, big.mark=","), " left that question blank and are excluded from the report entirely rather than merely from the species columns. The analysis sample is therefore ", format(nrow(d), big.mark=","), " respondents.")`

`r paste0("A second, narrower exclusion applies only to the preferred groups. ", nBannerExcluded, " respondents in the analysis sample prefer a species that falls outside every family group -- bullhead, drum, sturgeon, common carp, invasive carp, paddlefish, and the literal \"Other\" response. They remain in the Overall column of every table but receive no preferred-group column of their own. The two exclusions are distinct and are reported separately in Chapter 1.")`

`r paste0("Because of the first restriction, the Overall column of this report estimates a different population than the Overall column of the 2025 Crosstabs report: anglers who stated a species preference, rather than all licensed anglers. The two reports will therefore not agree in that column, and no attempt has been made to reconcile them. The one exception is the preferred-species distribution itself, which is computed on respondents to that question in both reports and does match exactly.")`

## Weighting and raking by survey year

Every respondent record carries a pre-calculated weight that is computed during data aggregation and stored with the survey data. All percentages and means in this report are weighted using that stored value; sample sizes (N) shown in parentheses are always
**raw, unweighted respondent counts** and not weighted Ns.  Calculated weights for the 2025 sum to population size values and not sample size values and displaying the weighted N's would be difficult for readers to interpret. Full detail on
how the 2025 raking weights themselves were constructed can be found in Hurley (2026).

## Percentage confidence intervals

Percentage tables (`base.summary.percent.selectOne` /
`base.summary.percent.selectAll` in `BaseFunctions_2025_UPDATED.R`) use a
normal-approximation (Wald) interval:

$$CI = 1.96 \times \sqrt{\frac{p(1-p)}{effN}} \times 100$$

where $p$ is the weighted proportion and $effN$ is the **Kish effective
sample size**, not the raw respondent count or the raw sum of weights:

$$effN = \frac{(\sum w)^2}{\sum w^2}$$

This matters because of the population-scaling difference noted above: 2025
weights sum to roughly 234,000 with a mean weight around 83. Using the
raw sum of weights as the CI denominator would make intervals roughly 9x too
tight. The Kish effective sample size
corrects for this by accounting for the variance introduced by unequal
weighting (the "design effect").

## Mean confidence intervals

Mean tables (`base.summary.means`) compute a weighted mean and a weighted
standard deviation, then a standard error using the same **Kish effective
sample size** ($effN$) used by the percentage formula above, rather than the
raw respondent count:

$$SE = \frac{SD_w}{\sqrt{effN}}, \qquad CI = 1.96 \times SE$$

This mirrors the percentage CI fix for the same underlying reason: using $effN$ keeps mean
CIs on the same design-effect-corrected basis as percentage CIs. The sample size (N) displayed alongside each mean is still the raw, unweighted respondent count; only the internal SE calculation changed.

## Median confidence intervals

Median tables report a weighted median together with
a genuine 95% confidence interval for that median, computed by weighted
bootstrap: respondents are resampled with replacement, with selection probability
proportional to the precalculated weight values, 1,000 times; the (unweighted) median is
computed for each resample; and the 2.5th and 97.5th percentiles of those
1,000 bootstrap medians form the reported CI bounds. A fixed random seed
(7361) is set before each grouped computation so results are reproducible
from one render to the next. This method was chosen because there is no
simple closed-form confidence interval for a weighted median under
arbitrary, non-integer survey weights.

## Reverse-coded item markers (dagger, &dagger;)

Some questions in this report mark individual items with a dagger and a
caption explaining that dagger-marked items "are reverse coded... before
computing scale means." That marking is only meaningful when a table
actually being shown reflects a reversed value. That is
true for the Angler Attitudes (E1) tables -- `attitude_catch` and
`attitude_harvest`, both shown in this report, genuinely reverse items E1a,
E1k, E1f, and E1l when computing those subscale and item means.

## Scale scores and the completeness gate

`r paste0("The motivation and attitude scale scores are rebuilt from the raw item responses at render time, applying the reversals flagged in Scales.csv. Each scale table is restricted to respondents who answered every item in that sub-scale, matching the 2025 Crosstabs report. The gate is applied per scale, so each scale carries its own sample size; across the eight scales used here the analysis sample ranges from 1,653 to 1,715 respondents. This is an inherited listwise requirement rather than a discretionary exclusion, and the resulting sample size is printed beside every estimate.")`

## Population expansions

`r paste0("The species table in Chapter 1 reports a population expansion, obtained by applying each weighted percentage to the full weighted 2025 angler population of ", format(round(popTotalAll), big.mark=","), ". That column therefore sums to the full angler population. The weights carried by the ", format(nrow(d), big.mark=","), " respondents in the analysis sample themselves total only ", format(round(popTotalAnalysis), big.mark=","), ", or about ", round(popTotalAnalysis / popTotalAll * 100), " percent of the population, because the respondents who skipped the preferred-species question carry weight too.")`

`r paste0("Expanding to the full population rather than to the ", format(round(popTotalAnalysis), big.mark=","), " represented by the analysis sample assumes that skipping the preferred-species question is unrelated to which species an angler prefers. That assumption cannot be tested with these data, since no preference was recorded for the respondents who skipped the question. Readers who prefer not to make it should scale the expansion column by ", round(popTotalAnalysis / popTotalAll, 3), ".")`

## The preferred groups, and why columns do not sum

`r paste0("The preferred groups are not a partition. Bass, Panfish / Sunfish, and Catfish each appear both as a combined family column and as one column per constituent species, so a respondent who prefers largemouth bass is counted in both the Bass column and the Largemouth bass column. The Esocids family was replaced outright by separate northern pike and muskellunge columns and has no combined column.")`

`r paste0("Two consequences follow. Preferred-group column counts sum to ", format(nBannerCellSum, big.mark=","), " against ", format(nBanner, big.mark=","), " distinct respondents, so they must never be totalled. And because each column is computed on its own respondents and uses its own denominator, the percentages within any single column remain correct; only addition across columns is invalid.")`

## Comparisons between species

Chapter 1 compares species within a family using design-based two-sample
comparisons (`svyttest` from the **survey** package) on a design object built
with the survey weights rescaled to sum to the number of respondents in the
pair being compared:

$$w_{norm} = w \times \frac{n}{\sum w}$$

The rescaling is presentational rather than a variance correction. With
independent sampling units, the linearized standard errors that **survey**
computes are scale-invariant in the weights: the raw weights and the rescaled
weights give identical standard errors and identical degrees of freedom. The
"roughly 9x too tight" problem described under percentage confidence intervals
above belongs specifically to the manual sum-of-weights calculation that the
Kish effective sample size corrects, and it does **not** carry over to the
design objects used here.

**No omnibus test is reported.** Each row of a comparison table is a single
two-species contrast. An overall F-test across the species in a family was
considered and dropped, and with it any model $R^2$ or $\eta^2$, because the
split-or-combine decisions were made from the species estimates directly.

## Multiplicity

`r paste0("Where a family contains three species there are three possible pairwise comparisons, and the unadjusted p-value for each is multiplied by three (Bonferroni). Where a family contains two species there is a single comparison and no adjustment is applied. Both the unadjusted and the Bonferroni-adjusted p-value are printed, rather than a single verdict against a fixed threshold.")`

Bonferroni was chosen over Holm for simplicity of exposition. The two rest on
identical assumptions and Bonferroni is uniformly the more conservative of the
two, so any comparison Bonferroni separates, Holm would separate as well.
Tukey's HSD was not used: it is not valid here given the unequal group sizes and
the weighted design. Benjamini-Hochberg was not used because false-discovery
control is suited to screening rather than to the go/no-go grouping decisions
this chapter supports.

**The adjustment covers one dimension only.** It accounts for the number of
species comparisons made within a single outcome, not for the number of
outcomes examined. Each family is compared on eight scale scores plus days
fished, so a three-species family carries 27 comparisons in total with no
adjustment across the outcome dimension. Readers should treat a single
adjusted p-value near the conventional threshold accordingly.

## Effect sizes

`r paste0("Every comparison reports the weighted difference in means with a 95% confidence interval, and Hedges' g, a standardized difference computed by pooling the two weighted standard deviations on the effective sample sizes and applying the usual small-sample correction. Both are shown because several species in this survey are represented by very few respondents, where a comparison that separates nothing is not evidence that the species behave alike -- the interval is simply too wide to distinguish the two possibilities. The difference, its interval, and g together let the reader tell those cases apart.")`

## Satisfaction comparisons in Chapter 4

`r paste0("Chapter 4 reports no new estimator. Its group means are the weighted means described above, with the same Kish effective-N confidence intervals, and its rows are the same preferred groups used in Chapters 2 and 3.")`

`r paste0("One variable is transformed. A9 is recorded from 1, Very satisfied, to 5, Very dissatisfied, while every D4 item runs from 1, Strongly Disagree, to 5, Strongly Agree. Chapter 4 reports A9 as 6 minus the recorded response so that all six items point the same way. Subtraction from a constant shifts and reflects the scale without changing its spread, so the confidence interval is unchanged: the overall A9 mean of 2.3 plus or minus 0.06 in Chapter 3 appears as 3.7 plus or minus 0.06 in Chapter 4.")`

`r paste0("The size-and-numbers comparisons are paired. For each respondent who answered both items of a pair, the difference between the two responses is computed first, and the group figure is the weighted mean of those differences with the usual interval. Restricting to respondents who answered both items means the two means printed beside the difference describe the same people, so the difference column equals the difference of the columns. Pairing removes between-angler variation in how the scale is used, which is why a difference of a few hundredths of a scale point can carry a narrower interval than either mean.")`

`r paste0("No significance test is reported in Chapter 4, and no adjustment for multiple comparisons is applied. Each interval is a 95 percent interval for its own group taken alone. Seventeen groups are shown for each pair, and the groups overlap, since a family row contains the respondents in its own species rows; reading every interval at once is therefore a weaker exercise than reading any one of them, and a group whose interval just excludes zero should be read with that in mind. The correlation tables are likewise descriptive summaries with no test attached, and the group-level correlations are computed across 17 overlapping groups rather than across independent observations.")`

`r paste0("The reliability coefficient quoted in Chapter 4 is a weighted raw alpha for the four D4 satisfaction items. It is reported for reference only; no composite score is constructed anywhere in this report, which is item-level throughout.")`

## Angler type profiles in Chapter 5

```{r ch5AppendixB}
# Every figure quoted below is computed here or in ch5Setup, so this section
# cannot drift from the chapter.
ch5.appb.n0 <- sum(d$lpa_n_scales == 0)
ch5.appb.n16 <- sum(d$lpa_n_scales >= 1 & !d$lpa_fitted)
ch5.appb.cert <- Ch5LPACertainty(d) %>% arrange(desc(Band))
ch5.appb.spec <- D4RowSpec(includeOverall = TRUE)
ch5.appb.supp <- ch5.long %>%
  filter(Suppressed) %>%
  distinct(Order, Column, ColumnN, ColumnEffN, Type) %>%
  arrange(Order)
# A Species row's family is the nearest Family row above it in the row order.
ch5.appb.family <- vapply(
  ch5.appb.supp$Order[ch5.appb.supp$Type == "Species"],
  function(o) {
    fam <- ch5.appb.spec %>% filter(Type == "Family", Order < o)
    fam$RawLabel[which.max(fam$Order)]
  },
  character(1)
)
ch5.appb.inFamily <- ch5.appb.supp$Column[ch5.appb.supp$Type == "Species"]
ch5.appb.split <- ch5.appb.supp$Column[ch5.appb.supp$Type == "Split"]

stopifnot(
  ch5.appb.n0 + ch5.appb.n16 == ch5.nUnassigned,
  nrow(ch5.appb.cert) == 3,
  all(ch5.appb.supp$Type %in% c("Species", "Split")),
  length(ch5.appb.inFamily) > 0,
  length(ch5.appb.split) > 0
)
```

### The model

`r paste0("Chapter 5 groups anglers using a latent profile analysis, a finite mixture model in which each respondent is assumed to belong to one of a number of unobserved profiles and, within a profile, each indicator is normally distributed. The indicators are the eleven scale scores reported in Chapter 3: the four angler-attitude scales, the four motivation scales, and the three regulation scales. Within each profile the eleven indicators are treated as uncorrelated, so each profile is described by eleven means and a set of variances.")`

`r paste0("Models were fitted with the tidySEM package (version ", packageVersion("tidySEM"), "), function mx_profiles(), which estimates by maximum likelihood in OpenMx (version ", packageVersion("OpenMx"), "). tidySEM obtains starting values from a k-means partition, refines them by simulated annealing, and then runs gradient-based optimization. A fixed random seed (", ch5.lpa.seed, ") is set before each model so the fits are reproducible. Starting values come from a single k-means run, and the sensitivity of the solution to other starting values has not been examined.")`

### Who was fitted

`r paste0("Of the ", FmtCount(nrow(d)), " respondents in the analysis sample, ", FmtCount(ch5.nFitted), " (", formatC(100 * ch5.nFitted / nrow(d), format = "f", digits = 1), " percent) answered at least ", ch5.lpa.min.scales, " of the eleven scales and were included in the fit. The threshold was set before fitting. Where a fitted respondent is missing some scales, the model uses the scales that were answered (full-information maximum likelihood); no values are imputed. The remaining ", FmtCount(ch5.nUnassigned), " respondents (", FmtCount(ch5.appb.n16), " who answered between 1 and ", ch5.lpa.min.scales - 1, " scales and ", FmtCount(ch5.appb.n0), " who answered none) are reported as Unassigned. They are not dropped: they remain in every Chapter 5 row, and Unassigned appears as its own column, so each row's percentages are of all respondents in that row.")`

`r paste0("Each scale score carries the completeness gate described under Scale scores and the completeness gate above, so the scores entering the model are the same values summarized in the Chapter 5 profile figures and profile means table.")`

### Choosing the number of profiles

`r paste0("Two within-profile variance structures were fitted: one in which every profile shares the same variance for a given indicator (equal), and one in which each profile has its own variances (varying). Under both structures, models with 1 to ", max(ch5.lpa.classes), " profiles were fitted. The equal structure was then extended to ", paste(ch5.lpa.extend.equal, collapse = " and "), " profiles because the Bayesian information criterion (BIC) was still decreasing at ", max(ch5.lpa.classes), ".")`

`r paste0("The number of profiles was chosen by a stated convention rather than a statistical test: among all fitted models, the one with the lowest BIC, restricted to models in which the smallest profile holds at least ", 100 * ch5.lpa.min.class.prop, " percent of fitted respondents and the relative entropy is at least ", formatC(ch5.lpa.min.entropy, format = "f", digits = 2), ". Only fits that OpenMx reports as converged (status code 0 or 1) are eligible. BIC is computed as")`

$$BIC = -2\log L + p \ln(n)$$

`r paste0("with p the number of estimated parameters and n = ", FmtCount(ch5.nFitted), ". OpenMx's default summary reports a different, degrees-of-freedom-adjusted BIC; it was not used. Relative entropy summarizes how distinctly respondents are assigned:")`

$$E = 1 - \frac{\sum_i \sum_j -\hat{p}_{ij} \ln \hat{p}_{ij}}{n \ln k}$$

`r paste0("where p-hat(ij) is respondent i's estimated probability of belonging to profile j and k is the number of profiles. It runs from 0 to 1, with 1 indicating that every respondent is assigned with certainty.")`

`r paste0("The selected model has ", ch5.k, " profiles with ", ch5.sel$Variances, " variances: BIC ", formatC(ch5.sel$BIC, format = "f", digits = 1, big.mark = ","), ", relative entropy ", formatC(ch5.sel$Entropy, format = "f", digits = 3), ", smallest profile ", FmtCount(ch5.sel$SmallestClassN), " respondents (", formatC(100 * ch5.sel$SmallestClassProp, format = "f", digits = 1), " percent of those fitted). The full table of fitted models is given in Chapter 5.")`

### Models that were fitted but not eligible

`r paste0("Four fits had a lower BIC than the selected model and were excluded under the convention above. The ", paste(ch5.floorFail$Classes, collapse = "- and "), "-profile equal-variance models (BIC ", paste(formatC(ch5.floorFail$BIC, format = "f", digits = 1, big.mark = ","), collapse = " and "), ") converged, but their smallest profiles hold ", paste(formatC(100 * ch5.floorFail$SmallestClassProp, format = "f", digits = 1), collapse = " and "), " percent of fitted respondents, below the ", 100 * ch5.lpa.min.class.prop, " percent floor. Because BIC continued to decrease through ", max(ch5.floorFail$Classes), " profiles, the selected model is the largest equal-variance model that satisfies the floor rather than the point at which BIC stops improving.")`

`r paste0("The ", paste(ch5.spikes$Profiles, collapse = "- and "), "-profile varying-variance models (BIC ", paste(formatC(ch5.diag$BIC[match(ch5.spikes$Model, ch5.diag$Model)], format = "f", digits = 1, big.mark = ","), collapse = " and "), ") did not converge (OpenMx status code ", paste(unique(ch5.diag$StatusCode[ch5.diag$Model %in% ch5.spikes$Model]), collapse = ", "), ": first-order optimality conditions not met). Inspection showed the cause. In each, one profile (", paste(FmtCount(ch5.spikes$ClassN), collapse = " and "), " respondents) contains only respondents whose ", ScaleLabel(ch5.spikes$Variable[1], l), " regulation score is exactly ", ch5.spikes$Max[1], ", the top of the scale, among those who answered it (", paste0(ch5.spikes$AtMax, " of ", ch5.spikes$Answered, collapse = " and "), "). That profile's variance on the indicator shrinks toward zero (estimates of ", paste(formatC(ch5.spikes$Variance, format = "e", digits = 1), collapse = " and "), "). Because the normal likelihood increases without limit as a variance approaches zero, the lower BIC of these two models reflects that collapse rather than a better description of the data. A further optimization attempt was not made, since it would search the same unbounded region. Placing a lower bound on the variances was considered and not adopted, because it would change the model specification. Both fits are excluded.")`

### Assigning respondents to profiles

`r paste0("Each fitted respondent is assigned to the profile with the highest estimated membership probability. Assignment is not certain: the average probability of the assigned profile among its members is at least ", formatC(ch5.sel$MinMeanPosterior, format = "f", digits = 3), " for every profile. Certainty also depends on how many scales a respondent answered. Mean assigned-profile probability is ", paste0(formatC(ch5.appb.cert$MeanMaxPosterior, format = "f", digits = 3), " for respondents who answered ", c("all eleven scales", "ten", "seven to nine"), " (", FmtCount(ch5.appb.cert$N), " respondents)", collapse = ", "), "; the share assigned with probability below 0.70 is ", paste(formatC(100 * ch5.appb.cert$ShareBelow70, format = "f", digits = 1), collapse = ", "), " percent respectively. The profile numbers are arbitrary labels produced by the estimation and carry no order.")`

### Weights

`r paste0("The model is fitted without the survey weights: each fitted respondent contributes equally to the estimated profiles. Everything reported from the model is then weighted in the same way as the rest of this report. The share of each profile in each row is a weighted percentage with the Kish effective-N confidence interval, and the profile means in the Chapter 5 figures and profile means table are weighted means with the Kish effective-N confidence interval, computed from the assigned respondents. These weighted means are therefore not the same quantities as the unweighted means the model estimated for each profile. Whether the fitting software can carry survey weights into the estimation was not verified. The model diagnostics and the assignment-certainty table are unweighted model quantities.")`

### Reporting floor for species rows

`r paste0("Chapter 5 is the only chapter of this report that withholds rows. Before the model was fitted, a floor of ", ch5.effn.floor, " on the Kish effective sample size was set for species rows, adopting the effective-sample-size element of the National Center for Health Statistics data presentation standards for proportions (Parker JD, Talih M, Malec DJ, et al. National Center for Health Statistics Data Presentation Standards for Proportions. Vital and Health Statistics, Series 2, No. 175. 2017). Only that element is adopted: the NCHS standard also calls for a raw sample size of at least 30 and for Korn-Graubard confidence intervals with width criteria, while this report's intervals are Wald intervals on the Kish effective N, as described above, and no width criterion is applied.")`

`r paste0("Four rows fall below the floor and are not shown in the Chapter 5 tables: ", paste0(ch5.appb.supp$Column, " (", FmtCount(ch5.appb.supp$ColumnN), " respondents, effective N ", formatC(ch5.appb.supp$ColumnEffN, format = "f", digits = 1), ")", collapse = "; "), ". The floor applies to reporting only; these respondents are included in the model fit and in the Overall row. ", paste(ch5.appb.inFamily, collapse = " and "), " respondents are also contained in the ", paste(ch5.appb.family, collapse = " and "), " family rows", if (length(ch5.appb.family) > 1) ", respectively" else "", ". ", paste(ch5.appb.split, collapse = " and "), " have no family row, so their respondents appear in no displayed Chapter 5 species row. Where a profile has no respondents in a displayed row, the percentage is 0 and the Wald interval has zero width; this is a property of the interval formula, not a measurement of certainty.")`

### Comparisons on other survey questions

`r paste0("The Chapter 5 table of profiles on other survey questions uses the same estimators as Chapter 3: weighted percentages and means with Kish effective-N intervals, and weighted medians with the bootstrap interval described above. Each question keeps its Chapter 3 universe, and the Overall column reproduces the Overall row of the corresponding Chapter 3 table. Unassigned respondents are counted in Overall only. One row is constructed for this chapter: a respondent counts as fishing rivers and streams if they reported the Missouri River, the Platte River, or other streams, rivers, and canals, among respondents who answered the waterbody question.")`

`r paste0("These comparisons treat each respondent's assigned profile as known. Because assignment is uncertain, some respondents are counted in a profile they may not belong to, which tends to make the profiles look more alike on these questions than they are; the differences shown are therefore more likely understated than overstated. The profile paragraphs name a family group when it makes up at least ", ch5.mix.gap, " percentage points more of a profile than of all assigned respondents, as a reminder that species preference and profile membership are related. No adjustment for species mix is made.")`

### What is not reported

`r paste0("No significance test is reported in Chapter 5, and the profile shares in different rows are not formally compared. As in other chapters, the species rows overlap and must not be totalled.")`

## Display precision

`r paste0("Scale means and their confidence intervals are printed to three decimal places in Chapter 1, rather than the one decimal place used in the 2025 Crosstabs report. At one decimal place a scale-mean interval of roughly plus or minus 0.04 rounds to zero, which would make the species comparisons unreadable. This is a rounding change in presentation only; the underlying values are identical to those the inherited functions produce.")`

`r paste0("For the same reason, the paired difference columns in Chapter 4 carry two decimal places rather than the one used for the means beside them. The overall difference between satisfaction with size and satisfaction with numbers is 0.07, which one decimal place would print as 0.1 next to an interval of 0.06.")`

```{r timing}
toc()
```
