---
title: "2025 Licensed Angler Survey Trends"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  # word_document: default
  officedown::rdocx_document:
    toc: true
    toc_depth: 2
always_allow_html: yes
---

```{r setup, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, fig.width=6.5, fig.height=6.5}
knitr::opts_chunk$set(echo=FALSE, include=TRUE, warning=FALSE, error=FALSE, message=FALSE,  ft.align="left", fig.width = 6.5)
options(stringsAsFactors = FALSE)
#devtools::install_github("davidgohel/officer")
#devtools::install_github("davidgohel/officedown")
library(officedown)
library(rmarkdown)
library(likert)
library(knitr)
library(flextable)
library(stringr)
library(foreach)
library(tidyverse)
library(patchwork)

source("..\\BaseFunctions_2025_UPDATED.R") #load file of common functions
source("TrendTableFunctions.R") #load file of cross tab report functions
```

```{r getData, echo=FALSE}
# Load combined data (2002, 2012, 2018, 2025). postWeight is pre-calculated.
load(file="../../Data/DataAggregation1/aggregateData_20260624.rData")

# Rebuild motivation/attitude subscale composites (and _AnsweredAll flags) from
# raw item factors for all years, applying reversals flagged in Scales.csv.
d <- add_scale_scores(d)

#load questions (all years; 2025 used for question wording)
q <- read.csv(file="../../Data/DataAggregation1/FactorLevels_aggregated.csv")

#load labels
l <- read.csv(file="../../Data/DataAggregation1/Labels.csv")

#load scales
s <- read.csv(file="../../Data/DataAggregation1/Scales.csv")
```

`r officer::run_pagebreak()`

# Summary

Nebraska has surveyed licensed anglers four times over two decades. This report tracks the questions asked across those surveys so we can see how angler behavior, preferences, and attitudes have or have not shifted.  A few percentage-point movements between any two surveys are normal.  Major shifts or changes in ranking across surveys may indicate societal changes or shifts important for consideration in fisheries management.

The share of license holders who did **not** fish in Nebraska fell from about 17% (2002) to under 10% (2025).  Including this questions is more for context than indicative of angler behavior.  During the 2002 and 2012 survey distribution, recepients were chosen from the previous years' licensed angler list due to the capabilities of the permit system in place.  Answers of no during those years are a mix of anglers who were licensed but chose not to fish and truely lapsed anglers (did not by a license in the survey year).  Beginning in the 2018 survey, the year covered by the survey was presented to current license holders.  However, a decrease in fishing participation among licensed anglers was seen indicating more people bought licenses that they did not use.  In the 2025 survey we also have a confounding effect of multi-year permits which presents anglers that are licensed due to a purchase during a previous year that may or may not fish.  Those that did not are not truly "lapsed" from an license standpoint but do represent decreased participation.  Among those who fished during each survey, the typical angler reported about 18–19 days on the water per year, stable across all four surveys (with a temporary rise to ~23 days in 2018).

```{r chart_participation, fig.width=6.5, fig.height=3.2}
p_fished <- base.summary.percent.selectOne(d, A2) %>%
  filter(Response == "No") %>%
  mutate(Fished = 100 - Value) %>%
  ggplot(aes(Year, Fished)) +
  geom_line(linewidth = 1.5) + geom_point(size = 4) +
  scale_x_continuous(breaks = c(2002, 2012, 2018, 2025)) +
  ylim(80, 95) +
  labs(title = "Percent who fished", x = NULL, y = "Percent") +
  theme_minimal()

# Median total days per year (anglers who fished) with a bootstrap 95% CI of the
# weighted median.
set.seed(4127)
boot_median_ci <- function(df, B = 2000) {
  wm <- as.numeric(weighted.quantile(df$days, df$w, probs = 0.5))
  bs <- replicate(B, {
    idx <- sample.int(nrow(df), replace = TRUE)
    as.numeric(weighted.quantile(df$days[idx], df$w[idx], probs = 0.5))
  })
  tibble(Value = wm, lo = quantile(bs, 0.025), hi = quantile(bs, 0.975))
}

p_days <- d %>%
  filter(C1_AnsweredAll == TRUE & C1Total_days > 0) %>%
  transmute(Year = surveyYear, days = C1Total_days, w = postWeight) %>%
  group_by(Year) %>%
  group_modify(~ boot_median_ci(.x)) %>%
  ungroup() %>%
  ggplot(aes(factor(Year), Value)) +
  geom_col() +
  geom_errorbar(aes(ymin = lo, ymax = hi), width = 0.4) +
  labs(title = "Median days fished per year",
       x = NULL, y = "Median days (anglers who fished)") +
  theme_minimal()

p_fished | p_days
```

Bank fishing and wading remain the backbone of Nebraska angling (roughly three-quarters of anglers) with little change. Use of a motorized boat, however, has declined steadily — from about 67% (2002) to 52% (2025) — while kayaks and canoes have emerged as a distinct and growing mode (~15–17% in the two most recent surveys). 

```{r chart_methods, fig.width=6.5, fig.height=3}
mf5 <- d %>% dplyr::select(contains("A5")) %>% dplyr::select(-contains("Answered")) %>% names()
base.summary.percent.selectAll(d, mf5, A5_Answered) %>%
  filter(Response %in% c("Bank/wading", "Motorized boat", "Kayak/Canoe")) %>%
  ggplot(aes(Year, Value, color = Response)) +
  geom_line(linewidth = 1.5) + geom_point(size = 4) +
  scale_color_viridis_d(end = 0.9) +
  scale_x_continuous(breaks = c(2002, 2012, 2018, 2025)) +
  labs(title = "Fishing method", x = NULL, y = "Percent of anglers", color = NULL) +
  theme_minimal()
```

Most anglers fish close to home with their most-visited waterbody about 30 miles or less from home. While the last two surveys have shown a slight increase in the percentage of anglers fishing closer to home, the 2025 respondants showed similar travel distances to the 2002 survey with a slightly larger percentage of anglers traveling 100 or more miles to their most-visited waters.  This could also indicate some anglers fished fewer but farther trips at the expense of more numerous local trips.

```{r chart_distance, fig.width=6.5, fig.height=3.2}
dist_levels <- c("10 or fewer miles", "11 to 20 miles", "21 to 40 miles",
                  "41 to 60 miles", "61 to 100 miles", "101 to 250 miles",
                  "251 to 500 miles", "Over 500 miles")

base.summary.percent.selectOne(d, A8) %>%
  mutate(Response = factor(as.character(Response), levels = dist_levels)) %>%
  ggplot(aes(factor(Year), Value, fill = Response)) +
  geom_col(position = position_stack(reverse = TRUE)) +
  scale_fill_viridis_d(end = 0.95, direction = -1) +
  labs(title = "Distance traveled to most-visited waterbody",
       x = NULL, y = "Percent of anglers", fill = NULL) +
  theme_minimal()
```

Walleye remains the single most-preferred species but its share has slipped from about 31% (2002) to 24% (2025). Largemouth bass remains second while channel catfish preference has declined. The largest change is the rise of anglers who do not prefer any particular species, up from 10% to 18%, and is now one of the most common responses. Angler preference is becoming less concentrated on a few flagship species.

```{r chart_species, fig.width=6.5, fig.height=3}
base.summary.percent.selectOne(d, B1) %>%
  mutate(Response = as.character(Response)) %>%
  filter(Response %in% c("Walleye / Sauger", "Largemouth bass", "Channel catfish",
                         "I do not prefer any particular type of fish")) %>%
  mutate(Response = ifelse(Response == "I do not prefer any particular type of fish",
                           "No particular species", Response)) %>%
  OrderLegendByFinalYear() %>%
  ggplot(aes(Year, Value, color = Response)) +
  geom_line(linewidth = 1.5) + geom_point(size = 4) +
  scale_color_viridis_d(end = 0.9) +
  scale_x_continuous(breaks = c(2002, 2012, 2018, 2025)) +
  labs(title = "Most-preferred fish", x = NULL, y = "Percent naming as favorite", color = NULL) +
  theme_minimal()
```

Satisfaction improved between 2002 and 2012 and has held since. The share who are "very satisfied" has climbed every survey (16% to 28%) while dissatisfaction has fallen from about a quarter of anglers to roughly 15%.

```{r chart_satisfaction, fig.width=6.5, fig.height=3.5}
sat_levels <- c("Very satisfied", "Somewhat satisfied", "Neutral",
                "Somewhat dissatisfied", "Very dissatisfied")
sat <- base.summary.percent.selectOne(d, A9) %>%
  mutate(Response = factor(as.character(Response), levels = sat_levels))
sat_line <- sat %>%
  filter(Response %in% c("Very satisfied", "Somewhat satisfied")) %>%
  group_by(Year) %>% summarise(pct = sum(Value), .groups = "drop")

ggplot() +
  geom_col(data = sat, aes(factor(Year), Value, fill = Response),
           position = position_stack(reverse = TRUE)) +
  geom_line(data = sat_line, aes(factor(Year), pct, group = 1,
                                 color = "Satisfied (very + somewhat)"), linewidth = 1.5) +
  geom_point(data = sat_line, aes(factor(Year), pct,
                                  color = "Satisfied (very + somewhat)"), size = 4) +
  scale_fill_viridis_d(end = 0.9) +
  scale_color_manual(values = c("Satisfied (very + somewhat)" = "black"), name = NULL) +
  guides(fill = guide_legend(reverse = TRUE)) +
  labs(title = "Angler satisfaction with Nebraska fishing",
       x = NULL, y = "Percent of anglers", fill = NULL) +
  theme_minimal()
```

When examining the components to Nebraska anglers' attitudes of a successful trip, rank order of the four attitudes has not changed over the four surveys.  Anglers' orientation towards size of fish and catching something have remained relatively constant.  The importance of numbers of fish caught has increased in the last two surveys yet remains lower than the importance of size of fish. The clearest movement is a modest, steady decline in harvest-oriented attitudes of Nebraska anglers.

```{r chart_attitudes, fig.width=6.5, fig.height=3}
foreach(i = c("attitude_catch","attitude_numbers","attitude_size","attitude_harvest"),
        .combine = "rbind") %do%
  base.summary.means(d %>% filter(get(paste0(i, "_AnsweredAll")) == TRUE), !!rlang::sym(i)) %>%
  LabelResponses(l) %>%
  OrderLegendByFinalYear() %>%
  ggplot(aes(Year, Value, color = Response)) +
  geom_line(linewidth = 1.5) + geom_point(size = 4) +
  scale_color_viridis_d(end = 0.9) +
  scale_x_continuous(breaks = c(2002, 2012, 2018, 2025)) +
  labs(title = "Angler attitudes",
       x = NULL, y = "Mean rating", color = NULL) +
  theme_minimal()
```

Younger anglers place more importance on the size and number of fish caught, while older anglers place relatively more importance on harvest; orientation toward simply catching something is fairly stable across age groups. Age groups are only available for the 2025 survey.

```{r chart_attitudes_age, fig.width=6.5, fig.height=3.5}
foreach(i = c("attitude_catch","attitude_numbers","attitude_size","attitude_harvest"),
        .combine = "rbind") %do%
  base.summary.means(
    d %>% filter(surveyYear == 2025, get(paste0(i, "_AnsweredAll")) == TRUE, !is.na(E3)),
    !!rlang::sym(i),
    E3
  ) %>%
  LabelResponses(l) %>%
  OrderLegendByFinalX(xField = "Group") %>%
  ggplot(aes(Group, Value, color = Response, group = Response)) +
  geom_errorbar(aes(ymin = Value - CI, ymax = Value + CI), width = 0.2, linewidth = 0.6) +
  geom_line(linewidth = 1.5) + geom_point(size = 4) +
  scale_color_viridis_d(end = 0.9) +
  labs(title = "Angler attitudes by age group (2025)",
       x = NULL, y = "Mean rating", color = NULL) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

The declining harvest orientation is reflected in what anglers actually do with their catch. When anglers who sought a species were asked how much of their catch they kept, harvest has declined steadily for almost every species across the four surveys. Anglers of traditional harvest species such as crappie, channel catfish, bluegill, and walleye have shifted from keeping roughly half of their catch toward keeping only a few with trout anglers showing the largest decline.  Harvest among the release-oriented largemouth bass anglers continues to fall. Voluntary release is rising broadly outside of the traditional trophy fisheries, which affects assumptions about exploitation rates and how harvest-oriented regulations will function.

```{r chart_harvest_species, fig.width=6.5, fig.height=3.5}
harvestFields <- d %>% dplyr::select(contains("B3")) %>%
  dplyr::select(-contains("Answered")) %>%
  dplyr::select(-contains("oth")) %>% dplyr::select(-contains("any")) %>% names()

harvest_b3 <- foreach(i = harvestFields, .combine = "rbind") %do% {
  base.summary.means(
    d %>% filter(!is.na(get(i))) %>% filter(as.numeric(get(gsub("3", "2", i))) == 2),
    !!rlang::sym(i))
} %>% LabelResponses(l)

harvest_b3 %>%
  filter(Response %in% c("Walleye/Sauger", "Crappie", "Channel catfish",
                         "Bluegill/Sunfish", "Trout", "Largemouth bass")) %>%
  # Invert (6 - response) so declining lines = declining harvest, matching the
  # attitude chart above.
  mutate(Value = 6 - Value) %>%
  ggplot(aes(Year, Value, color = Response)) +
  geom_errorbar(aes(ymin = Value - CI, ymax = Value + CI), width = 1.2, linewidth = 0.6) +
  geom_line(linewidth = 1.5) + geom_point(size = 4) +
  scale_color_viridis_d(end = 0.9) +
  scale_x_continuous(breaks = c(2002, 2012, 2018, 2025)) +
  scale_y_continuous(limits = c(1, 5), breaks = 1:5, labels = c("Kept None", "Kept Few", "Kept Half", "Kept Many", "Kept all")) +
  labs(title = "Harvest rates by species",
       x = NULL, y = "Mean harvest",
       caption = "",
       color = NULL) +
  theme_minimal()
```

When asked about four different motivations for fishing, anglers rate social motivations and natural environment motivations as most important. During the 2018 survey natural environment motivations overtook social motivations for the top ranking and the that rank order remained during the 2025 survey.  Motivations tied strictly to the fishery resource itself (the importance of the catch and keeping fish) rank last among motivational factors and fall significantly lower on the scale.  For a large share of anglers, the quality of the overall outdoor experience and social motivations are as important as the catch. All scale scores were higher for all scales than in previous survey and likely represents a survey artifect and attention should remain on rank order and relative differences within years and not examined for relative differences in scale scores between years.

```{r chart_motivations, fig.width=6.5, fig.height=3}
foreach(i = c("motivation_pp","motivation_natural","motivation_social","motivation_resource"),
        .combine = "rbind") %do%
  base.summary.means(d %>% filter(get(paste0(i, "_AnsweredAll")) == TRUE), !!rlang::sym(i)) %>%
  LabelResponses(l) %>%
  OrderLegendByFinalYear() %>%
  ggplot(aes(Year, Value, color = Response)) +
  geom_line(linewidth = 1.5) + geom_point(size = 4) +
  scale_color_viridis_d(end = 0.9) +
  scale_x_continuous(breaks = c(2002, 2012, 2018, 2025)) +
  labs(title = "Angler motivations",
       x = NULL, y = "Mean importance", color = NULL) +
  theme_minimal()
```

Over the past two decades, Nebraska's licensed anglers have become more active,
consistently satisfied, less reliant on motorized boats, broader in the species
they pursue, and less focused on harvest. The implications for management
is that anglers value access and a quality overall experience across diverse species and settings.  Management should continue to provide access to a diversity of waters and opportunites alongside the traditional draw of premier species.  Continued attention to shore and small-craft access, dependable fishing close to home, and the broader experience will serve the largest segments of the angling public.

`r officer::run_pagebreak()`

# Longitudinal Results

## Fished in Nebraska

`r paste(trimws(GetQuestion(q, A2, 2025)),"  ", caption.percents, sep="")`

```{r A2_NoFish}
CreateFt(
  ArrangeTable(
    base.summary.percent.selectOne(d, A2) %>% filter(Response=="No"),
    roundDigits=1
  )
)
```

```{r A2}
CreatePercPlot(base.summary.percent.selectOne(d, A2), freeScale = FALSE)

```

`r officer::run_pagebreak()`

## Reasons for Not Fishing

`r paste(trimws(GetQuestion(q, A3, 2025)),"  ", caption.percents, sep="")`

```{r A3_whyNoFish}
CreateFt(
  ArrangeTable(
    base.summary.percent.selectOne(d, A3),
    roundDigits=1
  )
)
```

```{r A3}
CreatePercPlot(base.summary.percent.selectOne(d, A3))
```

`r officer::run_pagebreak()`

## Waterbody Types

`r paste(trimws(GetQuestion(q, A4, 2025)),"  ", caption.percents, sep="")`

```{r A4_WaterbodyTypes}
myFields<-d %>% dplyr::select(contains("A4")) %>% select(-contains("Answered")) %>% names()
CreateFt(ArrangeTable(
  base.summary.percent.selectAll(d, myFields, myAnsweredVar = A4_Answered),
  roundDigits = 1))
```

```{r A4}
CreatePercPlot(base.summary.percent.selectAll(d , myFields, myAnsweredVar = A4_Answered))
```

`r officer::run_pagebreak()`

## Fishing Methods

`r paste(trimws(GetQuestion(q, A5, 2025)),"  ", caption.percents, sep="")`

```{r A5_Methods}
myFields<-d %>% dplyr::select(contains("A5")) %>% select(-contains("Answered")) %>% names()
CreateFt(ArrangeTable(
  base.summary.percent.selectAll(d, myFields, myAnsweredVar = A5_Answered),
  roundDigits = 1))
```

```{r A5}
CreatePercPlot(base.summary.percent.selectAll(d, myFields, myAnsweredVar = A5_Answered))
```

`r officer::run_pagebreak()`

## Fishing Techniques

`r paste(trimws(GetQuestion(q, A6, 2025)),"  ", caption.percents, sep="")`

```{r A6_techniques}
myFields<-d %>% dplyr::select(contains("A6")) %>% select(-contains("Answered")) %>% names()
CreateFt(ArrangeTable(
  base.summary.percent.selectAll(d, myFields, myAnsweredVar = A6_Answered),
  roundDigits = 1))
```

```{r A6}
CreatePercPlot(base.summary.percent.selectAll(d, myFields, myAnsweredVar = A6_Answered))
```

`r officer::run_pagebreak()`

## Distance to Waterbody

`r paste(trimws(GetQuestion(q, A7, 2025)),"  ", caption.medians, "  ", labels.distance, sep="")`

```{r A7_favoriteMiles}
CreateFt(ArrangeTableMedians(
  base.summary.medians(d, A7_miles)%>% mutate(CI=paste(CIupper, "/", CIlower, sep="")),
  roundDigits = 1) %>% select(-Response))
```

`r paste(trimws(GetQuestion(q, A8, 2025)),"  ", caption.percents, "  ", labels.distance, sep="")`

```{r A8_mostVisitiedMiles}
CreateFt(ArrangeTableMedians(
  base.summary.medians(d, A8_miles)%>% mutate(CI=paste(CIupper, "/", CIlower, sep="")),
  roundDigits = 1) %>% select(-Response))
```

`r officer::run_pagebreak()`

## Satisfaction

`r paste(trimws(GetQuestion(q, A9, 2025)),"  ", caption.percents, "  ", labels.satisfaction, sep="")`

```{r A9_satisfactionPerc}
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(d, A9),
  roundDigits = 1))
```

```{r A9}
CreatePercPlot(base.summary.percent.selectOne(d, A9), freeScale = FALSE)
```

`r paste(trimws(GetQuestion(q, A9, 2025)),"  ", caption.means, "  ", labels.satisfaction, sep="")`

```{r A9_satisfactionMean}
CreateFt(ArrangeTable(
  base.summary.means(d, A9),
  roundDigits = 1) %>% select(-Response))
```

`r officer::run_pagebreak()`

## State Park Entry Permits

`r paste(trimws(GetQuestion(q, A10, 2025)),"  ", caption.means, sep="")`

```{r A10_parkPermits}
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(d, A10),
  roundDigits = 1))
```

```{r A10}
CreatePercPlot(base.summary.percent.selectOne(d, A10), freeScale = FALSE)
```

`r officer::run_pagebreak()`

## Conservation Officer Contact

`r paste(trimws(GetQuestion(q, E7, 2025)),"  ", caption.percents, sep="")`

```{r E7_CO}
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(d, E7),
  roundDigits = 1))
```

```{r E7}
CreatePercPlot(base.summary.percent.selectOne(d, E7), freeScale = FALSE)
```

`r officer::run_pagebreak()`

## Most-Preferred Species

`r paste(trimws(GetQuestion(q, B1, 2025)),"  ", caption.percents, sep="")`

```{r }
CreateFt(
  ArrangeTable(
    base.summary.percent.selectOne(d,B1),
    roundDigits = 1)
)
```

<!---CHUNK_PAGEBREAK--->

```{r fig.height=7}
CreatePercPlot(base.summary.percent.selectOne(d,B1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B1, 2025)),"  ", caption.ranks, sep="")`

```{r B1_rank}
op<-base.summary.percent.selectOne(d,B1) %>%
  group_by(Year) %>%
  arrange(-Value) %>%
  mutate(Rank=seq(1,length(Value))) %>%
  ungroup() %>%
  select(Year, Response, Value, Rank)

CreateFtRanks(ArrangeTableRanks(op))

```

`r officer::run_pagebreak()`

## Most Sought Species

`r paste(trimws(GetQuestion(q, B2, 2025)),"  ", caption.percents, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B2")) %>% select(-contains("_")) %>% select(-contains("Answered")) %>% names()
op<-base.summary.percent.selectAll(d, myFields, B2_Answered)
CreateFt(ArrangeTable(op,
    roundDigits = 1)
         )
```

<!---CHUNK_PAGEBREAK--->

```{r fig.height=7}
CreatePercPlot(base.summary.percent.selectOne(d,B1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B2, 2025)),"  ", caption.ranks, sep="")`

```{r B2_rank}
myFields<-d %>% dplyr::select(contains("B2")) %>% select(-contains("_")) %>% select(-contains("Answered")) %>% names()

op<-base.summary.percent.selectAll(d, myFields, B2_Answered) %>%
  group_by(Year) %>%
  arrange(-Value) %>%
  mutate(Rank=seq(1,length(Value))) %>%
  ungroup() %>%
  select(Year, Response, Value, Rank)

CreateFtRanks(ArrangeTableRanks(op))
```

`r officer::run_pagebreak()`

## Fish Harvest and Release

`r paste(trimws(GetQuestion(q, B3, 2025)),"  ", caption.percents, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B3")) %>% select(-contains("Answered")) %>% select(-contains("oth")) %>% select(-contains("any")) %>% names()
op<-foreach(i=myFields, .combine="bind_rows") %do% {
  data.frame(Species=i,
             ArrangeTable(
                base.summary.percent.selectOne(d %>% filter(!is.na(get(i))) %>% filter(as.numeric(get(gsub("3", "2", i)))==2),
                                            !!rlang::sym(i))),
             check.names = FALSE)
}

CreateFt(LabelResponses(op,l, responseField="Species"), headerColumn=Species, mergeOnFirst = TRUE)

```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B3, 2025)),"  ", caption.means, "  ", labels.release, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B3")) %>% select(-contains("Answered")) %>% select(-contains("oth")) %>% select(-contains("any")) %>% names()
op<-foreach(i=myFields, .combine="rbind") %do% {
  base.summary.means(d %>% filter(!is.na(get(i))) %>% filter(as.numeric(get(gsub("3", "2", i)))==2), !!rlang::sym(i))
}

CreateFt(ArrangeTable(LabelResponses(op, l)))
```


`r officer::run_pagebreak()`

## Days Fished

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

January

```{r}
mydata<-d %>% filter(!is.na("C1Jan_days"))  %>% filter(C1Jan_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Jan_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

February

```{r}
mydata<-d %>% filter(!is.na("C1Feb_days"))  %>% filter(C1Feb_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Feb_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

March

```{r}
mydata<-d %>% filter(!is.na("C1Mar_days")) %>% filter(C1Mar_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Mar_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

April

```{r}
mydata<-d %>% filter(!is.na("C1Apr_days")) %>% filter(C1Apr_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Apr_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

May

```{r}
mydata<-d %>% filter(!is.na("C1May_days")) %>% filter(C1May_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1May_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

June

```{r}
mydata<-d %>% filter(!is.na("C1June_days"))  %>% filter(C1June_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1June_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

July

```{r}
mydata<-d %>% filter(!is.na("C1July_days"))  %>% filter(C1July_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1July_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

August

```{r}
mydata<-d %>% filter(!is.na("C1Aug_days"))  %>% filter(C1Aug_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Aug_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

September

```{r SeptDays}
mydata<-d %>% filter(!is.na("C1Sept_days"))  %>% filter(C1Sept_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Sept_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

October

```{r}
mydata<-d %>% filter(!is.na("C1Oct_days"))  %>% filter(C1Oct_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Oct_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", "This table represents all respondants to this question including those who did not fish during the given time period.  ", caption.medians, "  ", labels.freq, sep="")`

```{r TotalDays}
mydata<-d %>% filter(!is.na("C1Total_days") & C1_AnsweredAll==TRUE) 
myFields<-mydata %>% select(contains("_days"))  %>% select(-contains("Total")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  ArrangeTableMedians(base.summary.medians(mydata, myFields[i]) %>% mutate(Response=myFields[i]),
  roundDigits = 1)
}

CreateFt(LabelResponses(op,l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", "Only respondants that fished at least once during the time period were included in this breakdown.  ", caption.medians, "  ", labels.freq, sep="")`

```{r C1_medianDays}
mydata<-d %>% filter(!is.na("C1Total_days") & C1_AnsweredAll==TRUE)
myFields<-mydata %>% select(contains("_days")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  ArrangeTableMedians(base.summary.medians(mydata %>% filter(get(myFields[i])>0), myFields[i]) %>% mutate(Response=myFields[i]),
  roundDigits = 1)
}

CreateFt(LabelResponses(op,l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", "Only respondants that fished at least once during the time period were included in this breakdown.  ", caption.medians, "  ", labels.freq, sep="")`

```{r C1_medianDaysJoyplot}
library(ggridges)
mydata %>%
  mutate(surveyYear=factor(surveyYear)) %>%
  filter(!is.na(C1Total_days)) %>%
  ggplot() +
  geom_density_ridges(aes(x=C1Total_days, y=surveyYear, fill=surveyYear),scale=5, rel_min_height=0.013 ) +
  scale_fill_viridis_d(begin=0.3, end=0.8) +
  labs(x="Total Days", y="") +
  theme_minimal() +
  theme(legend.position = "none")
```

`r officer::run_pagebreak()`

## Angler Motivations

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, sep="")`

```{r C2_motivations}
myFields<-d %>% dplyr::select(contains("C2")) %>% select(-contains("Answered")) %>% names()
op<-foreach(i=1:length(myFields), .combine = "rbind") %do% {
  base.summary.means(d, !!rlang::sym(myFields[i]))
}

CreateFt(ArrangeTable(SubstitueQuesForResponse(op, q, C2, 2025)))
```

```{r C2_likert, fig.width=6.5, fig.height=8}
op<-CreateSubScaleLikertGraphs(d, "Motivations", q)
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=6.5, fig.height=8}
print(op[[1]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=6.5, fig.height=8}
print(op[[2]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=6.5, fig.height=8}
print(op[[3]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=6.5, fig.height=8}
print(op[[4]])
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, sep="")`

```{r C2_table}
myFields<-c("motivation_pp","motivation_natural", "motivation_social","motivation_resource")
op<-foreach(i=myFields, .combine="rbind") %do% {
  base.summary.means(d%>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), !!rlang::sym(i))
}

CreateFt(ArrangeTable(LabelResponses(op, l)))
```

```{r C2_means}
CreateMeanPlot(LabelResponses(op, l), freeScale = FALSE, numCols=4) + theme(panel.background = element_rect(fill="gray80"))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, sep="")`

```{r}
myFields<-c("motivation_noncatch","motivation_catch")
op<-foreach(i=myFields, .combine="rbind") %do% {
  base.summary.means(d%>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), !!rlang::sym(i))
}

CreateFt(ArrangeTable(LabelResponses(op, l)))
```

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, sep="")`

```{r C2_means_catch}
CreateMeanPlot(LabelResponses(op, l), freeScale = FALSE, numCols=4) + theme(panel.background = element_rect(fill="gray80"))
```

`r officer::run_pagebreak()`

## Angler Attitudes

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, sep="")`

```{r E1, fig.height=8}
myFields<-d %>% dplyr::select(contains("E1")) %>% select(-contains("Answered")) %>% names()
op<-foreach(i=1:length(myFields), .combine = "rbind") %do% {
  base.summary.means(d, !!rlang::sym(myFields[i]))
}

CreateFt(ArrangeTable(SubstitueQuesForResponse(op, q, E1, 2025)))
```

<!---CHUNK_PAGEBREAK--->

```{r E1_likert, fig.width=6.5, fig.height=8}
op<-CreateSubScaleLikertGraphs(d, "Attitudes", q)
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=6.5, fig.height=8}
print(op[[1]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=6.5, fig.height=8}
print(op[[2]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=6.5, fig.height=8}
print(op[[3]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=6.5, fig.height=8}
print(op[[4]])
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, sep="")`

```{r E1_means_subscales}
myFields<-c("attitude_catch", "attitude_numbers", "attitude_size", "attitude_harvest")

op<-foreach(i=myFields, .combine="rbind") %do% {
  base.summary.means(d%>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), !!rlang::sym(i))
}

CreateFt(ArrangeTable(LabelResponses(op, l)))
```

```{r E1_means_catch_noncatch}
CreateMeanPlot(LabelResponses(op, l), freeScale = FALSE, numCols=4) + theme(panel.background = element_rect(fill="gray80"))
```
