---
title: "2025 Licensed Angler Survey Trends"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  # word_document: default
  officedown::rdocx_document:
    toc: true
    toc_depth: 2
always_allow_html: yes
---

```{r setup, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, fig.width=6.5, fig.height=6.5}
knitr::opts_chunk$set(echo=FALSE, include=TRUE, warning=FALSE, error=FALSE, message=FALSE,  ft.align="left", fig.width = 6.5)
options(stringsAsFactors = FALSE)
#devtools::install_github("davidgohel/officer")
#devtools::install_github("davidgohel/officedown")
library(officedown)
library(rmarkdown)
library(likert)
library(knitr)
library(flextable)
library(stringr)
library(foreach)
library(tidyverse)
library(patchwork)

source("..\\BaseFunctions_2025_UPDATED.R") #load file of common functions
source("TrendTableFunctions.R") #load file of cross tab report functions
```

```{r getData, echo=FALSE}
# Load combined data (2002, 2012, 2018, 2025). postWeight is pre-calculated.
load(file="../../Data/DataAggregation1/aggregateData_20260624.rData")

# Rebuild motivation/attitude subscale composites (and _AnsweredAll flags) from
# raw item factors for all years, applying reversals flagged in Scales.csv.
d <- add_scale_scores(d)

#load questions (all years; 2025 used for question wording)
q <- read.csv(file="../../Data/DataAggregation1/FactorLevels_aggregated.csv")

#load labels
l <- read.csv(file="../../Data/DataAggregation1/Labels.csv")

#load scales
s <- read.csv(file="../../Data/DataAggregation1/Scales.csv")
```

`r officer::run_pagebreak()`

# Summary

Nebraska has surveyed licensed anglers four times over two decades. This report tracks the questions asked across those surveys so we can see how angler behavior, preferences, and attitudes have or have not shifted.  A few percentage-point movements between any two surveys are normal.  Major shifts or changes in ranking across surveys may indicate societal changes or shifts important for consideration in fisheries management.

The share of license holders who did **not** fish in Nebraska fell from about 17% (2002) to under 10% (2025).  Including this questions is more for context than indicative of angler behavior.  During the 2002 and 2012 survey distribution, recepients were chosen from the previous years' licensed angler list due to the capabilities of the permit system in place.  Answers of no during those years are a mix of anglers who were licensed but chose not to fish and truely lapsed anglers (did not by a license in the survey year).  Beginning in the 2018 survey, the year covered by the survey was presented to current license holders.  However, a decrease in fishing participation among licensed anglers was seen indicating more people bought licenses that they did not use.  In the 2025 survey we also have a confounding effect of multi-year permits which presents anglers that are licensed due to a purchase during a previous year that may or may not fish.  Those that did not are not truly "lapsed" from an license standpoint but do represent decreased participation.  Among those who fished during each survey, the typical angler reported about 18–19 days on the water per year, stable across all four surveys (with a temporary rise to ~23 days in 2018).

```{r chart_participation, fig.width=6.5, fig.height=3.2}
p_fished <- base.summary.percent.selectOne(d, A2) %>%
  filter(Response == "No") %>%
  mutate(Fished = 100 - Value) %>%
  ggplot(aes(Year, Fished)) +
  geom_line(linewidth = 1.5) + geom_point(size = 4) +
  scale_x_continuous(breaks = c(2002, 2012, 2018, 2025)) +
  ylim(80, 95) +
  labs(title = "Percent who fished", x = NULL, y = "Percent") +
  theme_minimal()

# Median total days per year (anglers who fished) with a bootstrap 95% CI of the
# weighted median.
set.seed(4127)
boot_median_ci <- function(df, B = 2000) {
  wm <- as.numeric(weighted.quantile(df$days, df$w, probs = 0.5))
  bs <- replicate(B, {
    idx <- sample.int(nrow(df), replace = TRUE)
    as.numeric(weighted.quantile(df$days[idx], df$w[idx], probs = 0.5))
  })
  tibble(Value = wm, lo = quantile(bs, 0.025), hi = quantile(bs, 0.975))
}

p_days <- d %>%
  filter(C1_AnsweredAll == TRUE & C1Total_days > 0) %>%
  transmute(Year = surveyYear, days = C1Total_days, w = postWeight) %>%
  group_by(Year) %>%
  group_modify(~ boot_median_ci(.x)) %>%
  ungroup() %>%
  ggplot(aes(factor(Year), Value)) +
  geom_col() +
  geom_errorbar(aes(ymin = lo, ymax = hi), width = 0.4) +
  labs(title = "Median days fished per year",
       x = NULL, y = "Median days (anglers who fished)") +
  theme_minimal()

p_fished | p_days
```

Bank fishing and wading remain the backbone of Nebraska angling (roughly three-quarters of anglers) with little change. Use of a motorized boat, however, has declined steadily — from about 67% (2002) to 52% (2025) — while kayaks and canoes have emerged as a distinct and growing mode (~15–17% in the two most recent surveys). 

```{r chart_methods, fig.width=6.5, fig.height=3}
mf5 <- d %>% dplyr::select(contains("A5")) %>% dplyr::select(-contains("Answered")) %>% names()
base.summary.percent.selectAll(d, mf5, A5_Answered) %>%
  filter(Response %in% c("Bank/wading", "Motorized boat", "Kayak/Canoe")) %>%
  ggplot(aes(Year, Value, color = Response)) +
  geom_line(linewidth = 1.5) + geom_point(size = 4) +
  scale_color_viridis_d(end = 0.9) +
  scale_x_continuous(breaks = c(2002, 2012, 2018, 2025)) +
  labs(title = "Fishing method", x = NULL, y = "Percent of anglers", color = NULL) +
  theme_minimal()
```

Most anglers fish close to home with their most-visited waterbody about 30 miles or less from home. While the last two surveys have shown a slight increase in the percentage of anglers fishing closer to home, the 2025 respondants showed similar travel distances to the 2002 survey with a slightly larger percentage of anglers traveling 100 or more miles to their most-visited waters.  This could also indicate some anglers fished fewer but farther trips at the expense of more numerous local trips.

```{r chart_distance, fig.width=6.5, fig.height=3.2}
dist_levels <- c("10 or fewer miles", "11 to 20 miles", "21 to 40 miles",
                  "41 to 60 miles", "61 to 100 miles", "101 to 250 miles",
                  "251 to 500 miles", "Over 500 miles")

base.summary.percent.selectOne(d, A8) %>%
  mutate(Response = factor(as.character(Response), levels = dist_levels)) %>%
  ggplot(aes(factor(Year), Value, fill = Response)) +
  geom_col(position = position_stack(reverse = TRUE)) +
  scale_fill_viridis_d(end = 0.95, direction = -1) +
  labs(title = "Distance traveled to most-visited waterbody",
       x = NULL, y = "Percent of anglers", fill = NULL) +
  theme_minimal()
```

Walleye remains the single most-preferred species but its share has slipped from about 31% (2002) to 24% (2025). Largemouth bass remains second while channel catfish preference has declined. The largest change is the rise of anglers who do not prefer any particular species, up from 10% to 18%, and is now one of the most common responses. Angler preference is becoming less concentrated on a few flagship species.

```{r chart_species, fig.width=6.5, fig.height=3}
base.summary.percent.selectOne(d, B1) %>%
  mutate(Response = as.character(Response)) %>%
  filter(Response %in% c("Walleye / Sauger", "Largemouth bass", "Channel catfish",
                         "I do not prefer any particular type of fish")) %>%
  mutate(Response = ifelse(Response == "I do not prefer any particular type of fish",
                           "No particular species", Response)) %>%
  OrderLegendByFinalYear() %>%
  ggplot(aes(Year, Value, color = Response)) +
  geom_line(linewidth = 1.5) + geom_point(size = 4) +
  scale_color_viridis_d(end = 0.9) +
  scale_x_continuous(breaks = c(2002, 2012, 2018, 2025)) +
  labs(title = "Most-preferred fish", x = NULL, y = "Percent naming as favorite", color = NULL) +
  theme_minimal()
```

Satisfaction improved between 2002 and 2012 and has held since. The share who are "very satisfied" has climbed every survey (16% to 28%) while dissatisfaction has fallen from about a quarter of anglers to roughly 15%.

```{r chart_satisfaction, fig.width=6.5, fig.height=3.5}
sat_levels <- c("Very satisfied", "Somewhat satisfied", "Neutral",
                "Somewhat dissatisfied", "Very dissatisfied")
sat <- base.summary.percent.selectOne(d, A9) %>%
  mutate(Response = factor(as.character(Response), levels = sat_levels))
sat_line <- sat %>%
  filter(Response %in% c("Very satisfied", "Somewhat satisfied")) %>%
  group_by(Year) %>% summarise(pct = sum(Value), .groups = "drop")

ggplot() +
  geom_col(data = sat, aes(factor(Year), Value, fill = Response),
           position = position_stack(reverse = TRUE)) +
  geom_line(data = sat_line, aes(factor(Year), pct, group = 1,
                                 color = "Satisfied (very + somewhat)"), linewidth = 1.5) +
  geom_point(data = sat_line, aes(factor(Year), pct,
                                  color = "Satisfied (very + somewhat)"), size = 4) +
  scale_fill_viridis_d(end = 0.9) +
  scale_color_manual(values = c("Satisfied (very + somewhat)" = "black"), name = NULL) +
  guides(fill = guide_legend(reverse = TRUE)) +
  labs(title = "Angler satisfaction with Nebraska fishing",
       x = NULL, y = "Percent of anglers", fill = NULL) +
  theme_minimal()
```

When examining the components to Nebraska anglers' attitudes of a successful trip, rank order of the four attitudes has not changed over the four surveys.  Anglers' orientation towards size of fish and catching something have remained relatively constant.  The importance of numbers of fish caught has increased in the last two surveys yet remains lower than the importance of size of fish. The clearest movement is a modest, steady decline in harvest-oriented attitudes of Nebraska anglers.

```{r chart_attitudes, fig.width=6.5, fig.height=3}
foreach(i = c("attitude_catch","attitude_numbers","attitude_size","attitude_harvest"),
        .combine = "rbind") %do%
  base.summary.means(d %>% filter(get(paste0(i, "_AnsweredAll")) == TRUE), !!rlang::sym(i)) %>%
  LabelResponses(l) %>%
  OrderLegendByFinalYear() %>%
  ggplot(aes(Year, Value, color = Response)) +
  geom_line(linewidth = 1.5) + geom_point(size = 4) +
  scale_color_viridis_d(end = 0.9) +
  scale_x_continuous(breaks = c(2002, 2012, 2018, 2025)) +
  labs(title = "Angler attitudes",
       x = NULL, y = "Mean rating", color = NULL) +
  theme_minimal()
```

Younger anglers place more importance on the size and number of fish caught, while older anglers place relatively more importance on harvest; orientation toward simply catching something is fairly stable across age groups. Age groups are only available for the 2025 survey.

```{r chart_attitudes_age, fig.width=6.5, fig.height=3.5}
foreach(i = c("attitude_catch","attitude_numbers","attitude_size","attitude_harvest"),
        .combine = "rbind") %do%
  base.summary.means(
    d %>% filter(surveyYear == 2025, get(paste0(i, "_AnsweredAll")) == TRUE, !is.na(E3)),
    !!rlang::sym(i),
    E3
  ) %>%
  LabelResponses(l) %>%
  OrderLegendByFinalX(xField = "Group") %>%
  ggplot(aes(Group, Value, color = Response, group = Response)) +
  geom_errorbar(aes(ymin = Value - CI, ymax = Value + CI), width = 0.2, linewidth = 0.6) +
  geom_line(linewidth = 1.5) + geom_point(size = 4) +
  scale_color_viridis_d(end = 0.9) +
  labs(title = "Angler attitudes by age group (2025)",
       x = NULL, y = "Mean rating", color = NULL) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

The declining harvest orientation is reflected in what anglers actually do with their catch. When anglers who sought a species were asked how much of their catch they kept, harvest has declined steadily for almost every species across the four surveys. Anglers of traditional harvest species such as crappie, channel catfish, bluegill, and walleye have shifted from keeping roughly half of their catch toward keeping only a few with trout anglers showing the largest decline.  Harvest among the release-oriented largemouth bass anglers continues to fall. Voluntary release is rising broadly outside of the traditional trophy fisheries, which affects assumptions about exploitation rates and how harvest-oriented regulations will function.

```{r chart_harvest_species, fig.width=6.5, fig.height=3.5}
harvestFields <- d %>% dplyr::select(contains("B3")) %>%
  dplyr::select(-contains("Answered")) %>%
  dplyr::select(-contains("oth")) %>% dplyr::select(-contains("any")) %>% names()

harvest_b3 <- foreach(i = harvestFields, .combine = "rbind") %do% {
  base.summary.means(
    d %>% filter(!is.na(get(i))) %>% filter(as.numeric(get(gsub("3", "2", i))) == 2),
    !!rlang::sym(i))
} %>% LabelResponses(l)

harvest_b3 %>%
  filter(Response %in% c("Walleye/Sauger", "Crappie", "Channel catfish",
                         "Bluegill/Sunfish", "Trout", "Largemouth bass")) %>%
  # Invert (6 - response) so declining lines = declining harvest, matching the
  # attitude chart above.
  mutate(Value = 6 - Value) %>%
  ggplot(aes(Year, Value, color = Response)) +
  geom_errorbar(aes(ymin = Value - CI, ymax = Value + CI), width = 1.2, linewidth = 0.6) +
  geom_line(linewidth = 1.5) + geom_point(size = 4) +
  scale_color_viridis_d(end = 0.9) +
  scale_x_continuous(breaks = c(2002, 2012, 2018, 2025)) +
  scale_y_continuous(limits = c(1, 5), breaks = 1:5, labels = c("Kept None", "Kept Few", "Kept Half", "Kept Many", "Kept all")) +
  labs(title = "Harvest rates by species",
       x = NULL, y = "Mean harvest",
       caption = "",
       color = NULL) +
  theme_minimal()
```

When asked about four different motivations for fishing, anglers rate social motivations and natural environment motivations as most important. During the 2018 survey natural environment motivations overtook social motivations for the top ranking and the that rank order remained during the 2025 survey.  Motivations tied strictly to the fishery resource itself (the importance of the catch and keeping fish) rank last among motivational factors and fall significantly lower on the scale.  For a large share of anglers, the quality of the overall outdoor experience and social motivations are as important as the catch. All scale scores were higher for all scales than in previous survey and likely represents a survey artifect and attention should remain on rank order and relative differences within years and not examined for relative differences in scale scores between years.

```{r chart_motivations, fig.width=6.5, fig.height=3}
foreach(i = c("motivation_pp","motivation_natural","motivation_social","motivation_resource"),
        .combine = "rbind") %do%
  base.summary.means(d %>% filter(get(paste0(i, "_AnsweredAll")) == TRUE), !!rlang::sym(i)) %>%
  LabelResponses(l) %>%
  OrderLegendByFinalYear() %>%
  ggplot(aes(Year, Value, color = Response)) +
  geom_line(linewidth = 1.5) + geom_point(size = 4) +
  scale_color_viridis_d(end = 0.9) +
  scale_x_continuous(breaks = c(2002, 2012, 2018, 2025)) +
  labs(title = "Angler motivations",
       x = NULL, y = "Mean importance", color = NULL) +
  theme_minimal()
```

Over the past two decades, Nebraska's licensed anglers have become more active,
consistently satisfied, less reliant on motorized boats, broader in the species
they pursue, and less focused on harvest. The implications for management
is that anglers value access and a quality overall experience across diverse species and settings.  Management should continue to provide access to a diversity of waters and opportunites alongside the traditional draw of premier species.  Continued attention to shore and small-craft access, dependable fishing close to home, and the broader experience will serve the largest segments of the angling public.

`r officer::run_pagebreak()`

# Longitudinal Results

## Fished in Nebraska

`r paste(trimws(GetQuestion(q, A2, 2025)),"  ", caption.percents, sep="")`

```{r A2_NoFish}
CreateFt(
  ArrangeTable(
    base.summary.percent.selectOne(d, A2) %>% filter(Response=="No"),
    roundDigits=1
  )
)
```

```{r A2}
CreatePercPlot(base.summary.percent.selectOne(d, A2), freeScale = FALSE)

```

`r officer::run_pagebreak()`

## Reasons for Not Fishing

`r paste(trimws(GetQuestion(q, A3, 2025)),"  ", caption.percents, sep="")`

```{r A3_whyNoFish}
CreateFt(
  ArrangeTable(
    base.summary.percent.selectOne(d, A3),
    roundDigits=1
  )
)
```

```{r A3}
CreatePercPlot(base.summary.percent.selectOne(d, A3))
```

`r officer::run_pagebreak()`

## Waterbody Types

`r paste(trimws(GetQuestion(q, A4, 2025)),"  ", caption.percents, sep="")`

```{r A4_WaterbodyTypes}
myFields<-d %>% dplyr::select(contains("A4")) %>% select(-contains("Answered")) %>% names()
CreateFt(ArrangeTable(
  base.summary.percent.selectAll(d, myFields, myAnsweredVar = A4_Answered),
  roundDigits = 1))
```

```{r A4}
CreatePercPlot(base.summary.percent.selectAll(d , myFields, myAnsweredVar = A4_Answered))
```

`r officer::run_pagebreak()`

## Fishing Methods

`r paste(trimws(GetQuestion(q, A5, 2025)),"  ", caption.percents, sep="")`

```{r A5_Methods}
myFields<-d %>% dplyr::select(contains("A5")) %>% select(-contains("Answered")) %>% names()
CreateFt(ArrangeTable(
  base.summary.percent.selectAll(d, myFields, myAnsweredVar = A5_Answered),
  roundDigits = 1))
```

```{r A5}
CreatePercPlot(base.summary.percent.selectAll(d, myFields, myAnsweredVar = A5_Answered))
```

`r officer::run_pagebreak()`

## Fishing Techniques

`r paste(trimws(GetQuestion(q, A6, 2025)),"  ", caption.percents, sep="")`

```{r A6_techniques}
myFields<-d %>% dplyr::select(contains("A6")) %>% select(-contains("Answered")) %>% names()
CreateFt(ArrangeTable(
  base.summary.percent.selectAll(d, myFields, myAnsweredVar = A6_Answered),
  roundDigits = 1))
```

```{r A6}
CreatePercPlot(base.summary.percent.selectAll(d, myFields, myAnsweredVar = A6_Answered))
```

`r officer::run_pagebreak()`

## Distance to Waterbody

`r paste(trimws(GetQuestion(q, A7, 2025)),"  ", caption.medians, "  ", labels.distance, sep="")`

```{r A7_favoriteMiles}
CreateFt(ArrangeTableMedians(
  base.summary.medians(d, A7_miles)%>% mutate(CI=paste(CIupper, "/", CIlower, sep="")),
  roundDigits = 1) %>% select(-Response))
```

`r paste(trimws(GetQuestion(q, A8, 2025)),"  ", caption.percents, "  ", labels.distance, sep="")`

```{r A8_mostVisitiedMiles}
CreateFt(ArrangeTableMedians(
  base.summary.medians(d, A8_miles)%>% mutate(CI=paste(CIupper, "/", CIlower, sep="")),
  roundDigits = 1) %>% select(-Response))
```

`r officer::run_pagebreak()`

## Satisfaction

`r paste(trimws(GetQuestion(q, A9, 2025)),"  ", caption.percents, "  ", labels.satisfaction, sep="")`

```{r A9_satisfactionPerc}
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(d, A9),
  roundDigits = 1))
```

```{r A9}
CreatePercPlot(base.summary.percent.selectOne(d, A9), freeScale = FALSE)
```

`r paste(trimws(GetQuestion(q, A9, 2025)),"  ", caption.means, "  ", labels.satisfaction, sep="")`

```{r A9_satisfactionMean}
CreateFt(ArrangeTable(
  base.summary.means(d, A9),
  roundDigits = 1) %>% select(-Response))
```

`r officer::run_pagebreak()`

## State Park Entry Permits

`r paste(trimws(GetQuestion(q, A10, 2025)),"  ", caption.means, sep="")`

```{r A10_parkPermits}
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(d, A10),
  roundDigits = 1))
```

```{r A10}
CreatePercPlot(base.summary.percent.selectOne(d, A10), freeScale = FALSE)
```

`r officer::run_pagebreak()`

## Conservation Officer Contact

`r paste(trimws(GetQuestion(q, E7, 2025)),"  ", caption.percents, sep="")`

```{r E7_CO}
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(d, E7),
  roundDigits = 1))
```

```{r E7}
CreatePercPlot(base.summary.percent.selectOne(d, E7), freeScale = FALSE)
```

`r officer::run_pagebreak()`

## Most-Preferred Species

`r paste(trimws(GetQuestion(q, B1, 2025)),"  ", caption.percents, sep="")`

```{r }
CreateFt(
  ArrangeTable(
    base.summary.percent.selectOne(d,B1),
    roundDigits = 1)
)
```

<!---CHUNK_PAGEBREAK--->

```{r fig.height=7}
CreatePercPlot(base.summary.percent.selectOne(d,B1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B1, 2025)),"  ", caption.ranks, sep="")`

```{r B1_rank}
op<-base.summary.percent.selectOne(d,B1) %>%
  group_by(Year) %>%
  arrange(-Value) %>%
  mutate(Rank=seq(1,length(Value))) %>%
  ungroup() %>%
  select(Year, Response, Value, Rank)

CreateFtRanks(ArrangeTableRanks(op))

```

`r officer::run_pagebreak()`

## Most Sought Species

`r paste(trimws(GetQuestion(q, B2, 2025)),"  ", caption.percents, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B2")) %>% select(-contains("_")) %>% select(-contains("Answered")) %>% names()
op<-base.summary.percent.selectAll(d, myFields, B2_Answered)
CreateFt(ArrangeTable(op,
    roundDigits = 1)
         )
```

<!---CHUNK_PAGEBREAK--->

```{r fig.height=7}
CreatePercPlot(base.summary.percent.selectOne(d,B1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B2, 2025)),"  ", caption.ranks, sep="")`

```{r B2_rank}
myFields<-d %>% dplyr::select(contains("B2")) %>% select(-contains("_")) %>% select(-contains("Answered")) %>% names()

op<-base.summary.percent.selectAll(d, myFields, B2_Answered) %>%
  group_by(Year) %>%
  arrange(-Value) %>%
  mutate(Rank=seq(1,length(Value))) %>%
  ungroup() %>%
  select(Year, Response, Value, Rank)

CreateFtRanks(ArrangeTableRanks(op))
```

`r officer::run_pagebreak()`

## Fish Harvest and Release

`r paste(trimws(GetQuestion(q, B3, 2025)),"  ", caption.percents, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B3")) %>% select(-contains("Answered")) %>% select(-contains("oth")) %>% select(-contains("any")) %>% names()
op<-foreach(i=myFields, .combine="bind_rows") %do% {
  data.frame(Species=i,
             ArrangeTable(
                base.summary.percent.selectOne(d %>% filter(!is.na(get(i))) %>% filter(as.numeric(get(gsub("3", "2", i)))==2),
                                            !!rlang::sym(i))),
             check.names = FALSE)
}

CreateFt(LabelResponses(op,l, responseField="Species"), headerColumn=Species, mergeOnFirst = TRUE)

```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B3, 2025)),"  ", caption.means, "  ", labels.release, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B3")) %>% select(-contains("Answered")) %>% select(-contains("oth")) %>% select(-contains("any")) %>% names()
op<-foreach(i=myFields, .combine="rbind") %do% {
  base.summary.means(d %>% filter(!is.na(get(i))) %>% filter(as.numeric(get(gsub("3", "2", i)))==2), !!rlang::sym(i))
}

CreateFt(ArrangeTable(LabelResponses(op, l)))
```


`r officer::run_pagebreak()`

## Days Fished

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

January

```{r}
mydata<-d %>% filter(!is.na("C1Jan_days"))  %>% filter(C1Jan_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Jan_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

February

```{r}
mydata<-d %>% filter(!is.na("C1Feb_days"))  %>% filter(C1Feb_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Feb_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

March

```{r}
mydata<-d %>% filter(!is.na("C1Mar_days")) %>% filter(C1Mar_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Mar_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

April

```{r}
mydata<-d %>% filter(!is.na("C1Apr_days")) %>% filter(C1Apr_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Apr_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

May

```{r}
mydata<-d %>% filter(!is.na("C1May_days")) %>% filter(C1May_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1May_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

June

```{r}
mydata<-d %>% filter(!is.na("C1June_days"))  %>% filter(C1June_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1June_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

July

```{r}
mydata<-d %>% filter(!is.na("C1July_days"))  %>% filter(C1July_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1July_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

August

```{r}
mydata<-d %>% filter(!is.na("C1Aug_days"))  %>% filter(C1Aug_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Aug_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

September

```{r SeptDays}
mydata<-d %>% filter(!is.na("C1Sept_days"))  %>% filter(C1Sept_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Sept_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, sep="")`

October

```{r}
mydata<-d %>% filter(!is.na("C1Oct_days"))  %>% filter(C1Oct_days<22)
CreateFt(ArrangeTable(
  base.summary.percent.selectOne(mydata, C1Oct_days),
  roundDigits = 1))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", "This table represents all respondants to this question including those who did not fish during the given time period.  ", caption.medians, "  ", labels.freq, sep="")`

```{r TotalDays}
mydata<-d %>% filter(!is.na("C1Total_days") & C1_AnsweredAll==TRUE) 
myFields<-mydata %>% select(contains("_days"))  %>% select(-contains("Total")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  ArrangeTableMedians(base.summary.medians(mydata, myFields[i]) %>% mutate(Response=myFields[i]),
  roundDigits = 1)
}

CreateFt(LabelResponses(op,l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", "Only respondants that fished at least once during the time period were included in this breakdown.  ", caption.medians, "  ", labels.freq, sep="")`

```{r C1_medianDays}
mydata<-d %>% filter(!is.na("C1Total_days") & C1_AnsweredAll==TRUE)
myFields<-mydata %>% select(contains("_days")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  ArrangeTableMedians(base.summary.medians(mydata %>% filter(get(myFields[i])>0), myFields[i]) %>% mutate(Response=myFields[i]),
  roundDigits = 1)
}

CreateFt(LabelResponses(op,l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", "Only respondants that fished at least once during the time period were included in this breakdown.  ", caption.medians, "  ", labels.freq, sep="")`

```{r C1_medianDaysJoyplot}
library(ggridges)
mydata %>%
  mutate(surveyYear=factor(surveyYear)) %>%
  filter(!is.na(C1Total_days)) %>%
  ggplot() +
  geom_density_ridges(aes(x=C1Total_days, y=surveyYear, fill=surveyYear),scale=5, rel_min_height=0.013 ) +
  scale_fill_viridis_d(begin=0.3, end=0.8) +
  labs(x="Total Days", y="") +
  theme_minimal() +
  theme(legend.position = "none")
```

`r officer::run_pagebreak()`

## Angler Motivations

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, sep="")`

```{r C2_motivations}
myFields<-d %>% dplyr::select(contains("C2")) %>% select(-contains("Answered")) %>% names()
op<-foreach(i=1:length(myFields), .combine = "rbind") %do% {
  base.summary.means(d, !!rlang::sym(myFields[i]))
}

CreateFt(ArrangeTable(SubstitueQuesForResponse(op, q, C2, 2025)))
```

```{r C2_likert, fig.width=6.5, fig.height=8}
op<-CreateSubScaleLikertGraphs(d, "Motivations", q)
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=6.5, fig.height=8}
print(op[[1]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=6.5, fig.height=8}
print(op[[2]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=6.5, fig.height=8}
print(op[[3]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=6.5, fig.height=8}
print(op[[4]])
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, sep="")`

```{r C2_table}
myFields<-c("motivation_pp","motivation_natural", "motivation_social","motivation_resource")
op<-foreach(i=myFields, .combine="rbind") %do% {
  base.summary.means(d%>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), !!rlang::sym(i))
}

CreateFt(ArrangeTable(LabelResponses(op, l)))
```

```{r C2_means}
CreateMeanPlot(LabelResponses(op, l), freeScale = FALSE, numCols=4) + theme(panel.background = element_rect(fill="gray80"))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, sep="")`

```{r}
myFields<-c("motivation_noncatch","motivation_catch")
op<-foreach(i=myFields, .combine="rbind") %do% {
  base.summary.means(d%>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), !!rlang::sym(i))
}

CreateFt(ArrangeTable(LabelResponses(op, l)))
```

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, sep="")`

```{r C2_means_catch}
CreateMeanPlot(LabelResponses(op, l), freeScale = FALSE, numCols=4) + theme(panel.background = element_rect(fill="gray80"))
```

`r officer::run_pagebreak()`

## Angler Attitudes

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, sep="")`

```{r E1, fig.height=8}
myFields<-d %>% dplyr::select(contains("E1")) %>% select(-contains("Answered")) %>% names()
op<-foreach(i=1:length(myFields), .combine = "rbind") %do% {
  base.summary.means(d, !!rlang::sym(myFields[i]))
}

CreateFt(ArrangeTable(SubstitueQuesForResponse(op, q, E1, 2025)))
```

<!---CHUNK_PAGEBREAK--->

```{r E1_likert, fig.width=6.5, fig.height=8}
op<-CreateSubScaleLikertGraphs(d, "Attitudes", q)
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=6.5, fig.height=8}
print(op[[1]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=6.5, fig.height=8}
print(op[[2]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=6.5, fig.height=8}
print(op[[3]])
```

<!---CHUNK_PAGEBREAK--->

```{r, fig.width=6.5, fig.height=8}
print(op[[4]])
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, sep="")`

```{r E1_means_subscales}
myFields<-c("attitude_catch", "attitude_numbers", "attitude_size", "attitude_harvest")

op<-foreach(i=myFields, .combine="rbind") %do% {
  base.summary.means(d%>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), !!rlang::sym(i))
}

CreateFt(ArrangeTable(LabelResponses(op, l)))
```

```{r E1_means_catch_noncatch}
CreateMeanPlot(LabelResponses(op, l), freeScale = FALSE, numCols=4) + theme(panel.background = element_rect(fill="gray80"))
```


`r officer::run_pagebreak()`

# Appendix B - Statistical Methodology

This appendix documents how weighting and confidence intervals are calculated
in this report, and how those calculations differ across the four survey
years (2002, 2012, 2018, 2025) that appear in the combined LAS dataset. It is
intended so that future analyses building on this report understand what each
number represents and why cross-year comparisons behave the way they do.

## Weighting and raking by survey year

Every respondent record carries a pre-calculated `postWeight` column, computed
during data aggregation (`Data/DataAggregation1/AggregateData.R`) rather than
on the fly in this report. All percentages and means in this report are
weighted using `postWeight`; sample sizes (N) shown in parentheses are always
**raw, unweighted respondent counts**, by project convention, not weighted Ns.

```{r appendixB_weighting_table, echo=FALSE}
weightingTable <- data.frame(
  Year = c("2002", "2012", "2018", "2025"),
  Weighting = c(
    "None (postWeight = 1 for all respondents).",
    "None (postWeight = 1 for all respondents).",
    "Age-group raking weight computed 2019-07-05 (weights_raked_ageGroup_20190705.rData), joined by license ID. Respondents without a matching weight default to 1.",
    "Per-respondent raking weight from 2025_raking_weights.csv, post-stratified on age group and residency (Hurley 2026). Scaled to the licensed-angler population rather than the sample, so weights sum to roughly the population size (~234,000) rather than to the sample size."
  ),
  check.names = FALSE
)
CreateFlex(weightingTable)
```

The practical consequence is that 2002/2012 percentages and means are
effectively unweighted (raw sample proportions), 2018 is lightly weighted on
age group only, and 2025 is weighted on age group and residency with weights
scaled to the full licensed-angler population. This last point -- that 2025
weights are population-scaled rather than sample-normalized -- is the root
cause of the confidence-interval difference described next. Full detail on
how the 2025 raking weights themselves were constructed (target margins,
convergence, etc.) is outside this codebase; see Hurley (2026) and the Bureau
of Sociological Research methodology report (2026).

## Percentage confidence intervals

Percentage tables (`base.summary.percent.selectOne` /
`base.summary.percent.selectAll` in `BaseFunctions_2025_UPDATED.R`) use a
normal-approximation (Wald) interval:

$$CI = 1.96 \times \sqrt{\frac{p(1-p)}{effN}} \times 100$$

where $p$ is the weighted proportion and $effN$ is the **Kish effective
sample size**, not the raw respondent count or the raw sum of weights:

$$effN = \frac{(\sum w)^2}{\sum w^2}$$

This matters because of the population-scaling difference noted above: 2025
weights sum to roughly 234,000 with a mean weight around 83, while 2002,
2012, and 2018 weights are sample-normalized (mean at or near 1). Using the
raw sum of weights as the CI denominator made 2025 intervals roughly 9x too
tight before this correction was made. The Kish effective sample size
corrects for this by accounting for the variance introduced by unequal
weighting (the "design effect"): for unweighted years (all weights equal to
1), $effN$ reduces exactly to the raw respondent count, so 2002/2012 and the
non-raked portions of 2018 are unaffected. Applying this correction slightly
widened 2018's confidence intervals relative to the originally published 2018
report (which effectively used raw n as the denominator) -- e.g. the A2 "No"
interval widens from &plusmn;1.37 to &plusmn;1.55 -- while percentages and
means themselves are unchanged. This tradeoff was accepted because it makes
CI methodology consistent across all four years rather than leaving 2025
intervals artificially tight.

## Mean confidence intervals

Mean tables (`base.summary.means`) compute a weighted mean and a weighted
standard deviation, then a standard error using the same **Kish effective
sample size** ($effN$) used by the percentage formula above, rather than the
raw respondent count:

$$SE = \frac{SD_w}{\sqrt{effN}}, \qquad CI = 1.96 \times SE$$

This mirrors the percentage CI fix for the same underlying reason: 2025's
population-scaled weighting inflates the variance of the weighted mean beyond
what a raw-n-based standard error would suggest, so using $effN$ keeps mean
CIs on the same design-effect-corrected basis as percentage CIs. As with
percentages, this reduces to the ordinary raw-n standard error whenever
weights are equal (2002/2012, and any unweighted subgroup), so those years'
mean CIs are unaffected. The sample size (N) displayed alongside each mean is
still the raw, unweighted respondent count, per this report's convention;
only the internal SE calculation changed.

**This is a change from earlier drafts of this report**, which used raw n for
the mean SE denominator. That was not identified as a problem until the
percentage CI fix prompted a closer look at whether the same design-effect
issue applied elsewhere in the report -- it does, so both were brought onto
a consistent basis together.

## Median confidence intervals

Median tables (`base.summary.medians`) report a weighted median together with
a genuine 95% confidence interval for that median, computed by weighted
bootstrap (`weighted_median_boot_ci` in `BaseFunctions_2025_UPDATED.R`):
respondents are resampled with replacement, with selection probability
proportional to `postWeight`, 1,000 times; the (unweighted) median is
computed for each resample; and the 2.5th and 97.5th percentiles of those
1,000 bootstrap medians form the reported CI bounds. A fixed random seed
(7361) is set before each grouped computation so results are reproducible
from one render to the next. This method was chosen because there is no
simple closed-form confidence interval for a weighted median under
arbitrary, non-integer survey weights.

**This is a change from earlier drafts of this report.** Prior to this
update, `base.summary.medians` returned the weighted 25th and 75th
percentiles (Q1 and Q3) in the two positions where the report's own caption
text ("Values represent lower 95% median confidence limit, median response,
and upper 95% median confidence limit...") claimed a confidence interval was
shown. Q1/Q3 describe the spread of individual responses around the median
and are **not** a confidence interval for the median itself, so the two did
not previously match. The caption text was accurate as written; the
underlying calculation has now been changed to match it. One consequence
worth understanding when reading these tables: because a bootstrap CI
reflects uncertainty in the estimate of the population median (which shrinks
as sample size grows) rather than the spread of individual responses, these
intervals are typically much narrower than the old Q1/Q3 display was --
including, for large or lopsided subgroups, collapsing to a very narrow range
or a single value when the weighted median is well-determined. This is
expected behavior, not an error.

Note that the separate Trend report (`Analysis/TrendTables/`) defines its own
version of `base.summary.medians` in `TrendTableFunctions.R` to preserve the
original 2018 report's median display convention (50th/95th percentile
bounds) for year-over-year continuity with that published report, and is
unaffected by the change described here.

## Consistency with the Trend report

The 4-year Trend report (`Analysis/TrendTables/TrendReport.rmd` and
`TrendTableFunctions.R`) sources the same `BaseFunctions_2025_UPDATED.R` used
by this report, and does **not** define its own version of
`base.summary.percent.selectOne`, `base.summary.percent.selectAll`, or
`base.summary.means`. It only overrides `base.summary.medians`, specifically
to preserve the original 2018 report's median display convention rather than
adopt the bootstrap CI described above. Practical consequences:

- **Percentage and mean CIs in the Trend report are automatically identical
  in methodology to this report**, since both call the exact same shared
  functions. No separate code changes were needed there for either the
  percentage effN fix or the mean effN fix described above -- they apply
  the moment the Trend report is rendered against the current
  `BaseFunctions_2025_UPDATED.R`.
- **Median CIs in the Trend report are unaffected by the bootstrap change**,
  by design, since `TrendTableFunctions.R`'s own `base.summary.medians`
  definition overwrites the shared one for that report only.
- `TrendReport.docx` has been re-rendered against the current
  `BaseFunctions_2025_UPDATED.R` and reflects both fixes -- spot-checked
  against the A2 "No" example above, which now shows the same 2018 CI
  (1.55) and a 2025 CI of 1.24. `TrendReport.html` has **not** been
  regenerated since (still dated 2026-07-09) and remains on the pre-fix
  methodology; regenerate it too if that output format is still needed.

### How this affects each survey year's values in the Trend report

Point estimates (percentages and means) are **unchanged** for every year --
these fixes only affect confidence interval width, not the values
themselves. CI width changes are also identical in kind to what's described
above for this report, since the calculation is shared:

- **2002 and 2012** (`postWeight = 1` for all respondents): $effN$ equals the
  raw respondent count exactly, so percentage and mean CIs for these two
  years are **unchanged** by either fix.
- **2018** (age-group raking only, weights close to sample-normalized):
  $effN$ is close to, but not identical to, the raw respondent count, so
  percentage and mean CIs widen **slightly** -- consistent with the
  previously-documented example (A2 "No" CI: 1.37 -> 1.55). The mean CI fix
  introduces a comparably small widening for 2018 means, confirmed directly
  below.
- **2025** (population-scaled raking weights): this is where both fixes
  matter most. Percentage CIs were previously ~9x too tight and are now
  corrected; mean CIs were similarly too tight (though not by as extreme a
  factor, since the mean formula's weighted-SD term already partially
  reflects the weight distribution) and are now corrected on the same basis.

**Mean CI validation against the published 2018 PDF.** Using the A9
(satisfaction) item -- the same item the original `BaseFunctions.R` used as
its own worked example -- against `SAS_2018_Trends_Final.pdf`
(`Analysis/TrendTables/2018/`):

```{r appendixB_mean_validation_table, echo=FALSE}
meanValidationTable <- data.frame(
  Year = c("2002", "2012", "2018"),
  `Published mean (CI)` = c("2.6 (\u00b10.07)", "2.3 (\u00b10.02)", "2.3 (\u00b10.04)"),
  `Reproduced, raw-n CI` = c("2.59 (\u00b10.067)", "2.27 (\u00b10.025)", "2.31 (\u00b10.043)"),
  `Current, effN CI` = c("2.59 (\u00b10.067)", "2.27 (\u00b10.025)", "2.31 (\u00b10.049)"),
  check.names = FALSE
)
CreateFlex(meanValidationTable)
```

This confirms three things at once: the weighted mean point estimate matches
the published value in all three years (to rounding); reproducing the
original raw-n CI formula exactly matches the published CI in all three
years, confirming the pre-fix formula was indeed what was published; and the
new effN-based CI is identical to the raw-n CI for 2002/2012 (effN equals
raw n exactly when all weights equal 1, verified: n = effN = 1,157 for 2002
and 7,244 for 2012) while widening modestly for 2018, from 0.043 to 0.049 --
the same direction and a comparable relative size to the percentage CI's
1.37 -> 1.55 widening for that year. This closes out the validation noted
as outstanding earlier: the mean CI fix behaves exactly as expected across
all three pre-2025 years, with no surprises.

## Reverse-coded item markers (dagger, &dagger;)

Some questions in this report mark individual items with a dagger and a
caption explaining that dagger-marked items "are reverse coded... before
computing scale means." That marking is only meaningful when a table
actually being shown reflects a reversed value. As of this update, that is
true for the Angler Attitudes (E1) tables -- `attitude_catch` and
`attitude_harvest`, both shown in this report, genuinely reverse items E1a,
E1k, E1f, and E1l when computing those subscale means -- so the dagger there
is accurate and was left as-is.

It was **not** true for the Regulations (Q31) tables, and the dagger there
has been removed. `Scales.csv` does flag Q31a, Q31b, Q31d, Q31f, and Q31i as
reversed, but only for the `RegulationsBipolar` composite (`reg_orientation`)
used in the separate Regs deep-dive report (`Analysis/Regs/`) -- a composite
that is never displayed anywhere in this report. Neither table shown in this
report's Regulations section used that reversal: the raw 12-item table
displays unadjusted item means (verified against the source PDF's own
Appendix A), and the three derived scales shown here (Comprehension,
Site-specific, Simplification) require no internal item reversal at all
(`Scales.csv` already marks all their items `Reversed = FALSE`, consistent
with all items loading the same direction within each scale). Since no
result actually shown in this report reflects that reversal, marking those
five items with a dagger and a "these were reverse coded" caption was
misleading, so the marking and caption text were removed from the raw
12-item Q31 table. If the `RegulationsBipolar` composite is ever added to
this report in the future, the dagger marking should be reinstated for that
specific table.

## Summary of what changed and why

```{r appendixB_summary_table, echo=FALSE}
summaryTable <- data.frame(
  Statistic = c("Percentage CI", "Mean CI", "Median CI"),
  Denominator = c(
    "Kish effective sample size (design-effect corrected)",
    "Kish effective sample size (design-effect corrected)",
    "N/A \u2013 empirical bootstrap percentiles"
  ),
  `Differs across years because` = c(
    "2025 weights are population-scaled; 2002/2012/2018 are sample-normalized (or unweighted), so the design effect differs by year.",
    "Same reason as percentage CI \u2013 shares the same effN calculation.",
    "Not affected by the weight-scaling difference; the bootstrap resamples with probability proportional to whatever postWeight values exist for that year/group."
  ),
  check.names = FALSE
)
CreateFlex(summaryTable)
```

`r officer::run_pagebreak()`