---
#title: "2025 Licensed Angler Survey Crosstabs"
#date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  officedown::rdocx_document:
    toc: true
  #word_document: default
always_allow_html: yes
---

```{r setup, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, fig.width=7.5, fig.height=7}
knitr::opts_chunk$set(echo=FALSE, include=TRUE, warning=FALSE, error=FALSE, message=FALSE,  ft.align="left")
library(tictoc)
tic("Report Took ")
options(stringsAsFactors = FALSE)
#devtools::install_github("davidgohel/officer")
#devtools::install_github("davidgohel/officedown")
library(officedown)
library(rmarkdown)
library(tidyverse)
library(knitr)
library(flextable)
library(stringr)

setwd("D:/Survey/Analysis/CrossTabTables/")

source("..\\BaseFunctions_2025_UPDATED.R") #load file of common functions
source("CrossTabTableFunctions.R") #load file of cross tab report functions
```


```{r getData, echo=FALSE}
setwd("D:/Survey/Analysis/CrossTabTables/")

#load data
load(file="../../Data/DataAggregation1/aggregateData_20260624.rData")
d<-d %>% filter(surveyYear==2025)
# Rebuild scale/subscale scores from raw item factors, applying reversals
# flagged in Scales.csv (single source of truth) at report time.
d <- add_scale_scores(d)
#q<-base.loaddata.factorlevels()
#save(q, file="q_20190802")
#load(file="../../2018 Statewide Survey/Analysis/Rscripts/CrossTabTables/q_20190802")
q<-read.csv(file="../../Data/DataAggregation1/FactorLevels_aggregated.csv") %>% filter(Year==2025)
l=read.csv(file="../../Data/DataAggregation1/Labels.csv")

```

```{r createFunctions}
CreateFlex<-function(x, mergeOnFirst=FALSE) {
  require(officer)
  require(flextable)
  
  bigborder=officer:: fp_border(color="black", width = 1.5)
  smallborder=officer:: fp_border(color="black", width=1.0)
  
  myFlex<-  flextable(x) %>%
    theme_zebra()
  
  if(mergeOnFirst==TRUE) {
    #merge first column cells  
    myFlex <-myFlex %>%
        merge_v(j=1, part="body") 
      #add border below merged cells in first column
      myFlex<-myFlex %>%
        border(border.bottom = smallborder, i=rle(cumsum(myFlex$body$spans$columns[,1] ))$values, part="body") 
  }
  
  myFlex <- myFlex %>%
    #border_outer(officer:: fp_border(color="black", width = 1.5), part="all") %>%
    #add border above and below footer
    border(border.bottom = bigborder, border.top = bigborder, part = "header") %>%
    #add border at bottom of body
    border(border.bottom = bigborder, i=nrow(myFlex$body$spans$rows), part = "body") %>%
    padding(j=1, padding.left=3) %>%
    align(align="left", part="all") %>%
    fontsize(part = "header", size = 10) %>%
    fontsize(part="body", size=8) %>%
    bold(part="header") %>%
    #autofit() %>%
    width(j = 1, width = 1.2) %>%
    set_table_properties(layout = "autofit", width = 1)

      
  myFlex
}


```

`r officer::run_pagebreak()`

This report contains the cross-tabulation results for each question in the 2025 Nebraska Licensed Angler Survey (LAS). Details on the design and administration of the LAS can be found in the companion report “Fishing Nebraska 2025-2026 Methodology Report” (BOSR 2026). Information on the responses and returns of the LAS can be found in the companion report “2026 Nebraska Licensed Angler Survey - Respondents and Responses” (Hurley 2026). When LAS returns were examined, it was determined that weighting results by age group and residency was warrented to better represent the Nebraska licensed angler population. In this report, question results that were weighted are notated in their caption.

This report is organized in the order questions were asked in the LAS.  A copy of the LAS is provided in the appendies of this report.  Breakdowns of the responses to each question are provided for:  a) all respondants, b) by residency, c) by gender, and d) by age.


`r officer::run_pagebreak()`

# Permit Type

`r paste(trimws(GetQuestion(q, A1, 2025)),"  ", caption.percents, sep="") `

```{r  }
CreateFlex(CreateTableA_selectOne_percent(d %>% mutate(postWeight = 1), A1, ordered=TRUE))
```


`r paste(trimws(GetQuestion(q, A1, 2025)),"  ", caption.percents, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d %>% mutate(postWeight = 1), A1, ordered=TRUE))
```


`r officer::run_pagebreak()`

# Did You Fish

`r paste(trimws(GetQuestion(q, A2, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, A2))
```

`r paste(trimws(GetQuestion(q, A2, 2025)),"  ", caption.percents,"  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, A2))
```


`r officer::run_pagebreak()`

# Why Didn't You Fish

`r paste(trimws(GetQuestion(q, A3, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, A3, ordered=TRUE))
```

`r paste(trimws(GetQuestion(q, A3, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, A3, ordered=TRUE))
```


`r officer::run_pagebreak()`

# Fish Out-Of-State

`r paste(trimws(GetQuestion(q, A11, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, A11))
```

`r paste(trimws(GetQuestion(q, A11, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, A11))
```

`r officer::run_pagebreak()`

# Boat Out-Of-State

`r paste(trimws(GetQuestion(q, A12, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d %>% filter(A11=="Yes"), A12))
```

`r paste(trimws(GetQuestion(q, A12, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d %>% filter(A11=="Yes"), A12))
```


`r officer::run_pagebreak()`

# Park Entry Permit

`r paste(trimws(GetQuestion(q, A10, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, A10))
```

`r paste(trimws(GetQuestion(q, A10, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, A10))
```

`r officer::run_pagebreak()`

# Fishing Tournaments

`r paste(trimws(GetQuestion(q, A13, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, fishedTourney) %>% mutate(Response=c("No Tournaments","Fished Tournaments")))
```

`r paste(trimws(GetQuestion(q, A13, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, fishedTourney) %>% mutate(Response=c("No Tournaments","Fished Tournaments")))
```


`r paste(trimws(GetQuestion(q, A13, 2025)),"  ", caption.percents, "  Only respondants who participated in AT LEAST ONE tournament are included in this calculation", "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d %>% filter(A13_corrected>0), "A13_corrected") %>% mutate(Response=as.integer(Response)))
```

`r paste(trimws(GetQuestion(q, A13, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d %>% filter(A13_corrected>0), "A13_corrected") %>% mutate(Response=as.integer(Response)))
```


`r paste(trimws(GetQuestion(q, A13, 2025)),"  ", caption.means, "  Only respondants who participated in AT LEAST ONE tournament are included in this calculation", "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_means(d %>% filter(A13_corrected>0), "A13_corrected")[,-1] )
```

`r paste(trimws(GetQuestion(q, A13, 2025)),"  ", caption.means, "  Only respondants who participated in AT LEAST ONE tournament are included in this calculation", "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_means(d %>% filter(A13_corrected>0), "A13_corrected")[,-1])
```

`r officer::run_pagebreak()`

# Waterbody Types

`r paste(trimws(GetQuestion(q, A4, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r WaterbodyTypes}
myFields<-d %>% dplyr::select(contains("A4")) %>% select(-contains("Answered")) %>% names()
CreateFlex(CreateTableA_selectAll_percent(d, myFields, myAnsweredVar = A4_Answered, ordered=TRUE))

```

`r paste(trimws(GetQuestion(q, A4, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectAll_percent(d, myFields, myAnsweredVar = A4_Answered, ordered=TRUE))
```

`r officer::run_pagebreak()`

# Methods

`r paste(trimws(GetQuestion(q, A5, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r Methods}
myFields<-d %>% dplyr::select(contains("A5")) %>% select(-contains("Answered")) %>% names()
CreateFlex(CreateTableA_selectAll_percent(d, myFields, myAnsweredVar = A5_Answered, ordered=TRUE))
```

`r paste(trimws(GetQuestion(q, A5, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectAll_percent(d, myFields, myAnsweredVar = A5_Answered, ordered=TRUE))
```


`r officer::run_pagebreak()`

# Techniques

`r paste(trimws(GetQuestion(q, A6, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("A6")) %>% select(-contains("Answered")) %>% names()
CreateFlex(CreateTableA_selectAll_percent(d, myFields, myAnsweredVar = A6_Answered, ordered=TRUE))
```

`r paste(trimws(GetQuestion(q, A6, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectAll_percent(d, myFields, myAnsweredVar = A6_Answered, ordered=TRUE))
```


`r officer::run_pagebreak()`

# Crowding

`r paste(trimws(GetQuestion(q, Q11, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d %>% filter(!is.na(Q11)), "Q11"))
```

`r paste(trimws(GetQuestion(q, Q11, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d %>% filter(!is.na(Q11)), "Q11"))
```


`r officer::run_pagebreak()`

# Access

`r paste(trimws(GetQuestion(q, A17, 2025)),"  ", caption.percents, "  The first two rows include responses from respondants that answered Yes or No to each question independant of the other question.  The last three rows only include respondants with at least one type of access (those who answered No to BOTH questions are excluded), so they sum to 100%.", "  ", caption.raked, sep="")`

```{r fig.width=7.8}
# Use the corrected A17 columns (A17Priv_corrected / A17Pub_corrected) instead
# of the originals (A17priv / A17pub), but transfer the original labels so the
# corrected versions display with the original wording.
#
# The partition rows (justPub / justPriv / both) describe HOW people with access
# are split. Respondents who answered No to BOTH public and private have no
# access and must NOT be in that denominator -- otherwise the three categories
# only sum to ~91%. dAccess restricts to respondents with at least one type of
# access so justPub + justPriv + both == 100%.
dAccess <- d %>%
  filter(!is.na(A17Pub_corrected) & !is.na(A17Priv_corrected)) %>%
  filter(!(A17Pub_corrected == "No" & A17Priv_corrected == "No"))

l_a17 <- l %>%
  bind_rows(tibble::tibble(
    Response = c("A17Priv_corrected", "A17Pub_corrected"),
    Label    = c(l$Label[l$Response == "A17priv"],
                 l$Label[l$Response == "A17pub"])
  ))
myFields <- d %>%
  dplyr::select(contains("A17")) %>%
  select(-contains("Answered")) %>%
  select(-A17priv, -A17pub) %>%
  names()
op<-foreach(i=1:length(myFields), .combine = "rbind") %do% {
  # "any access" rows (corrected pub/priv) use the full answered base;
  # partition rows (justPub/justPriv/both) use the access-only base.
  src <- if (myFields[i] %in% c("A17justPub", "A17justPriv", "A17both")) dAccess else d
  data.frame(Type=myFields[i], CreateTableA_selectOne_percent(src %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op %>% filter(Response=="Yes") %>% mutate(Response=Type) %>% select(-Type) , l_a17))
```


`r paste(trimws(GetQuestion(q, A17, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
myFields <- d %>%
  dplyr::select(contains("A17")) %>%
  select(-contains("Answered")) %>%
  select(-A17priv, -A17pub) %>%
  names()
op<-foreach(i=1:length(myFields), .combine = "rbind") %do% {
  src <- if (myFields[i] %in% c("A17justPub", "A17justPriv", "A17both")) dAccess else d
  data.frame(Type=myFields[i], CreateTableB_selectOne_percent(src %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op %>% filter(Response=="Yes")%>% mutate(Response=Type) %>% select(-Type) , l_a17))
```


`r paste(trimws(GetQuestion(q, A17, 2025)),"  ", "Values represent percent of respondants fitting each catagory and overlap. ", " ", caption.raked,sep="")`

```{r figure.width=7.6}
require(VennDiagram)

# Build the Venn from a SINGLE, consistent base: respondents who answered the
# public/private question and selected at least one option. The three
# categories A17justPub / A17justPriv / A17both are mutually exclusive and
# partition this base, so the regions add up correctly.
#
# Use the pre-calculated postWeight directly (same weighting the tables use,
# no ceiling() rounding) so the areas stay additive:
# justPub + justPriv + both == base total.
vennBase <- d %>%
  dplyr::select(A17justPub, A17justPriv, A17both, postWeight) %>%
  filter(!is.na(A17justPub) & !is.na(A17justPriv) & !is.na(A17both))

if (!"postWeight" %in% names(vennBase)) {
  vennBase$postWeight <- 1
}

justPub  <- sum(vennBase$postWeight[vennBase$A17justPub  == "Yes"], na.rm = TRUE)
justPriv <- sum(vennBase$postWeight[vennBase$A17justPriv == "Yes"], na.rm = TRUE)
both     <- sum(vennBase$postWeight[vennBase$A17both     == "Yes"], na.rm = TRUE)

vennCounts <- data.frame(
  pub  = justPub  + both,   # anyone with public access (public-only + both)
  priv = justPriv + both,   # anyone with private access (private-only + both)
  both = both
)

venn_grob <- draw.pairwise.venn(area1 = vennCounts$pub,
                                area2 = vennCounts$priv,
                                cross.area = vennCounts$both,
                                category=c("Public \nlands \nand access", "Private \nlands \nand access"),
                                fill=c("blue", "red"),
                                scaled=TRUE,
                                inverted=FALSE,
                                ext.text=FALSE,
                                cat.pos=c(225, 150),
                                cat.dist=c(0.05,0.06),
                                cat.cex=1.2,
                                print.mode="percent",
                                sigdigs=4,
                                margin = 0.075)

# Reformat percent labels to fixed 1 decimal place (sigdigs controls sig figs, not decimals)
fmt_pct_grobs <- function(g) {
  if (inherits(g, "text")) {
    g$label <- sapply(g$label, function(lbl) {
      if (grepl("^[0-9.]+%$", lbl)) {
        sprintf("%.1f%%", as.numeric(sub("%$", "", lbl)))
      } else {
        lbl
      }
    })
  }
  if (is.list(g)) g[] <- lapply(g, fmt_pct_grobs)
  g
}

grid::grid.newpage()
grid::grid.draw(fmt_pct_grobs(venn_grob))

```



`r officer::run_pagebreak()`

# Favorite Waterbody Distance

`r paste(trimws(GetQuestion(q, A7, 2025)),"  ", caption.percents, "  ", labels.distance, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, A7))
```

`r paste(trimws(GetQuestion(q, A7, 2025)),"  ", caption.percents, "  ", labels.distance, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, A7))
```


`r paste(trimws(GetQuestion(q, A7, 2025)),"  ", caption.medians, "  ", labels.distance, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_medians(d, "A7_miles")[,-1])
```

`r paste(trimws(GetQuestion(q, A7, 2025)),"  ", caption.medians, "  ", labels.distance, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_medians(d, "A7_miles")[,-1])
```


`r officer::run_pagebreak()`

# Most-Visitied Waterbody Distance

`r paste(trimws(GetQuestion(q, A8, 2025)),"  ", caption.percents, "  ", labels.distance, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, A8))
```

`r paste(trimws(GetQuestion(q, A8, 2025)),"  ", caption.percents, "  ", labels.distance, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, A8))
```


`r paste(trimws(GetQuestion(q, A8, 2025)),"  ", caption.medians, "  ", labels.distance, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_medians(d, "A8_miles")[,-1])
```

`r paste(trimws(GetQuestion(q, A8, 2025)),"  ", caption.medians, "  ", labels.distance, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_medians(d, "A8_miles")[,-1])
```


`r officer::run_pagebreak()`

# Satisfaction

`r paste(trimws(GetQuestion(q, A9, 2025)),"  ", caption.percents, "  ", labels.satisfaction, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, A9))
```

`r paste(trimws(GetQuestion(q, A9, 2025)),"  ", caption.percents, "  ", labels.satisfaction, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, A9))
```


`r paste(trimws(GetQuestion(q, A9, 2025)),"  ", caption.means, "  ", caption.raked, sep="")`

```{r }
CreateFlex(SubstitueQuesForResponse(CreateTableA_means(d, "A9"),q, A9, 2025))
```

`r paste(trimws(GetQuestion(q, A9, 2025)),"  ", caption.means, "  ", caption.raked, sep="")`

```{r }
CreateFlex(SubstitueQuesForResponse(CreateTableB_means(d, "A9"),q, A9, 2025))
```


`r officer::run_pagebreak()`

# Live-imaging Sonar Use

`r paste(trimws(GetQuestion(q, Q16, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d %>% filter(!is.na(Q16)), "Q16"))
```

`r paste(trimws(GetQuestion(q, Q16, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d %>% filter(!is.na(Q16)), "Q16"))
```


`r officer::run_pagebreak()`

# Conservation Officer

`r paste(trimws(GetQuestion(q, E7, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, E7))
```

`r paste(trimws(GetQuestion(q, E7, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, E7))
```




`r officer::run_pagebreak()`

# Guided Trips

`r paste("What percent of respondants hired a fishing guide at least once - using responses to '", trimws(GetQuestion(q, Q18c, 2025)), "'  ", caption.percents, "  ", caption.raked, sep="")`

```{r }

dHiredGuide <- d %>%
  mutate(
    hiredNE      = if_else(is.na(hiredGuide), NA, !is.na(Q18a) & Q18a > 0),
    hiredOutside = if_else(is.na(hiredGuide), NA, !is.na(Q18b) & Q18b > 0),
    hiredNEonly  = if_else(is.na(hiredGuide), NA, hiredNE & !hiredOutside),
    hiredOutOnly = if_else(is.na(hiredGuide), NA, hiredOutside & !hiredNE),
    hiredBoth    = if_else(is.na(hiredGuide), NA, hiredNE & hiredOutside),
    hiredAny     = if_else(is.na(hiredGuide), NA, hiredNE | hiredOutside)
  )

# Keep only the TRUE row from each single-select table, then stack them
guideRows <- bind_rows(
  CreateTableA_selectOne_percent(dHiredGuide, hiredAny,     ordered = FALSE) %>%
    filter(Response == TRUE) %>% mutate(Response = "Hired a guide"),
  CreateTableA_selectOne_percent(dHiredGuide, hiredNE,      ordered = FALSE) %>%
    filter(Response == TRUE) %>% mutate(Response = "Hired in Nebraska"),
  CreateTableA_selectOne_percent(dHiredGuide, hiredNEonly,  ordered = FALSE) %>%
    filter(Response == TRUE) %>% mutate(Response = "Only hired in Nebraska (not outside)"),
  CreateTableA_selectOne_percent(dHiredGuide, hiredOutside, ordered = FALSE) %>%
    filter(Response == TRUE) %>% mutate(Response = "Hired outside Nebraska"),
  CreateTableA_selectOne_percent(dHiredGuide, hiredOutOnly, ordered = FALSE) %>%
    filter(Response == TRUE) %>% mutate(Response = "Only hired outside Nebraska (not inside)"),
  CreateTableA_selectOne_percent(dHiredGuide, hiredBoth,    ordered = FALSE) %>%
    filter(Response == TRUE) %>% mutate(Response = "Hired both in and outside Nebraska")
)

CreateFlex(guideRows)

```

```{r }

# Keep only the TRUE row from each single-select table, then stack them
guideRows <- bind_rows(
  CreateTableB_selectOne_percent(dHiredGuide, hiredAny,     ordered = FALSE) %>%
    filter(Response == TRUE) %>% mutate(Response = "Hired a guide"),
  CreateTableB_selectOne_percent(dHiredGuide, hiredNE,      ordered = FALSE) %>%
    filter(Response == TRUE) %>% mutate(Response = "Hired in Nebraska"),
  CreateTableB_selectOne_percent(dHiredGuide, hiredNEonly,  ordered = FALSE) %>%
    filter(Response == TRUE) %>% mutate(Response = "Only hired in Nebraska (not outside)"),
  CreateTableB_selectOne_percent(dHiredGuide, hiredOutside, ordered = FALSE) %>%
    filter(Response == TRUE) %>% mutate(Response = "Hired outside Nebraska"),
  CreateTableB_selectOne_percent(dHiredGuide, hiredOutOnly, ordered = FALSE) %>%
    filter(Response == TRUE) %>% mutate(Response = "Only hired outside Nebraska (not inside)"),
  CreateTableB_selectOne_percent(dHiredGuide, hiredBoth,    ordered = FALSE) %>%
    filter(Response == TRUE) %>% mutate(Response = "Hired both in and outside Nebraska")
)

CreateFlex(guideRows)

```


`r paste(trimws(GetQuestion(q, Q18c, 2025)),"  Only respondants that hired at least one guide are included in this calculation.  ", caption.means, "  ", caption.raked, sep="")`

```{r }
dQ18means <- d %>%
  mutate(
    hiredNE      = !is.na(Q18a) & Q18a > 0,
    hiredOutside = !is.na(Q18b) & Q18b > 0,
    Q18total     = coalesce(Q18a, 0) + coalesce(Q18b, 0)
  )

# Mean number of guides hired per respondent. Each row includes only respondents
# who hired a guide in the scope considered, so the denominator (n) changes per row.
dQ18hired_raw <- d %>% filter(Q18_Answered & is.na(Q18c))  # still used by the Table B chunk below
specs <- list(
  list(label = "Hired a guide",                            sub = quote(hiredNE | hiredOutside),  col = "Q18total"),
  list(label = "Hired in Nebraska",                        sub = quote(hiredNE),                 col = "Q18a"),
  list(label = "Only hired in Nebraska (not outside)",     sub = quote(hiredNE & !hiredOutside), col = "Q18a"),
  list(label = "Hired outside Nebraska",                   sub = quote(hiredOutside),            col = "Q18b"),
  list(label = "Only hired outside Nebraska (not inside)", sub = quote(hiredOutside & !hiredNE), col = "Q18b"),
  list(label = "Hired both in and outside Nebraska",       sub = quote(hiredNE & hiredOutside),  col = "Q18total")
)
op <- foreach(s = specs, .combine = "rbind") %do% {
  CreateTableA_means(dQ18means %>% filter(!!s$sub), s$col) %>% mutate(Response = s$label)
}
CreateFlex(op)
```

`r paste(trimws(GetQuestion(q, Q18c, 2025)),"  Only respondants that hired at least one guide are included in this calculation.  ", caption.means, "  ", caption.raked, sep="")`

```{r }
op <- foreach(s = specs, .combine = dplyr::bind_rows) %do% {
  CreateTableB_means(dQ18means %>% filter(!!s$sub), s$col) %>% mutate(Response = s$label)
}
CreateFlex(op)
```


`r officer::run_pagebreak()`

# Trout Locations

`r paste(trimws(GetQuestion(q, D13oga, 2025)),"  ", caption.percents, "  These values only represent the respondants that selected they fished for TROUT elsewhere in the survey.", "  ", caption.raked,sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("D13")) %>% select(-contains("Answered")) %>% names()
op<-foreach(i=1:length(myFields), .combine = "rbind") %do% {
  data.frame(Location=myFields[i], CreateTableA_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))) %>% filter(B2rbt=="Trout"), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op, l, responseField="Location"), mergeOnFirst=TRUE)

```

`r paste(trimws(GetQuestion(q, D13oga, 2025)),"  ", caption.percents, "  These values only represent the respondants that selected they fished for TROUT elsewhere in the survey.", "  ", caption.raked,sep="")`

```{r }
op<-foreach(i=1:length(myFields), .combine = "rbind") %do% {
  data.frame(Type=myFields[i], CreateTableB_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))) %>% filter(B2rbt=="Trout"), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op, l, responseField="Type"), mergeOnFirst=TRUE)

```

`r paste(trimws(GetQuestion(q, D13oga, 2025)),"  ", "Values represent percent of respondants fitting each catagory and overlap.  Size of circles are not proportional to values.  These values only represent the respondants that selected they fished for TROUT elsewhere in the survey.", "  ", caption.raked,sep="")`

```{r troutVinn}
require(VennDiagram)

op<-d[d$B2rbt=="Trout",]
op<-op %>% select(D13lrp, D13rsc, D13oga, D13tr, surveyYear, age_group, postWeight)

# Code by label so this does not depend on factor level order: "Yes" -> 1, anything else (incl. NA) -> 2
op[,c("D13lrp", "D13rsc", "D13oga", "D13tr")]<-sapply(op[,c("D13lrp", "D13rsc", "D13oga", "D13tr")],function(x) ifelse(as.character(x)=="Yes", 1, 2))
op[,c("D13lrp", "D13rsc", "D13oga", "D13tr")]<-sapply(op[,c("D13lrp", "D13rsc", "D13oga", "D13tr")],function(x) ifelse(is.na(x), 2, x))

op_old<-op %>%
  filter(D13lrp==1 | D13rsc==1| D13oga==1| D13tr==1) %>%
  group_by(D13lrp, D13rsc, D13oga, D13tr) %>%
  summarise(Freq=n(), .groups = "drop")

op <- op %>%
  filter(D13lrp==1 | D13rsc==1| D13oga==1| D13tr==1) 

op<-op %>%
  group_by(D13lrp, D13rsc, D13oga, D13tr) %>%
  summarise(Freq=sum(postWeight), .groups = "drop") 

trout_venn_grob <- draw.quad.venn(area1 = sum(op$Freq[op$D13lrp==1], na.rm=TRUE),
                area2 =  sum(op$Freq[op$D13rsc==1], na.rm=TRUE),
                area3 =  sum(op$Freq[op$D13oga==1], na.rm=TRUE),
                area4 =  sum(op$Freq[op$D13tr==1], na.rm=TRUE),
                n12 =  sum(op$Freq[op$D13lrp==1 & op$D13rsc==1]),
                n13 =  sum(op$Freq[op$D13lrp==1 & op$D13oga==1]),
                n14 =  sum(op$Freq[op$D13lrp==1 & op$D13tr==1]),
                n23 =  sum(op$Freq[op$D13rsc==1 & op$D13oga==1]),
                n24 =  sum(op$Freq[op$D13rsc==1 & op$D13tr==1]),
                n34 =  sum(op$Freq[op$D13oga==1 & op$D13tr==1]),
                n123 =  sum(op$Freq[op$D13lrp==1 & op$D13rsc==1 & op$D13oga==1]),
                n124 =  sum(op$Freq[op$D13lrp==1 & op$D13rsc==1 & op$D13tr==1]),
                n134 =  sum(op$Freq[op$D13lrp==1 & op$D13oga==1 & op$D13tr==1]),
                n234 =  sum(op$Freq[op$D13rsc==1 & op$D13oga==1 & op$D13tr==1]),
                n1234 =  sum(op$Freq[op$D13lrp==1 & op$D13rsc==1 & op$D13oga==1 & op$D13tr==1]),
                category=c("Lakes, \nReservoirs, \nand Ponds",
                           "Rivers, \nStreams, \nand Canels",
                           "Lake \nOgallala \nComplex",
                           "Two Rivers"),
                fill=c("blue", "red", "orange", "brown"),
                scaled=TRUE,
                inverted=FALSE,
                ext.text=FALSE,
                #cat.pos=c(220, 145),
                #cat.dist=c(0.05,0.05),
                cat.cex=1.2,
                print.mode="percent",
                sigdigs=4,
                margin = 0.075)

grid::grid.newpage()
grid::grid.draw(fmt_pct_grobs(trout_venn_grob))

```


`r officer::run_pagebreak()`

# Preferred Fish

`r paste(trimws(GetQuestion(q, B1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, B1, ordered = TRUE))
```


`r paste(trimws(GetQuestion(q, B1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, B1, ordered=TRUE))
```


`r officer::run_pagebreak()`

# Preferred Species Questions

`r paste(trimws(GetQuestion(q, D4, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("D4")) %>% select(-contains("Answered")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  tempD<-data.frame(Item=myFields[i], CreateTableA_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
  tempD<-SubstitueQuesForResponse(tempD,q, !!rlang::sym(myFields[i]), 2025, responseField="Item")
}
CreateFlex(op, mergeOnFirst = TRUE)
```

`r paste(trimws(GetQuestion(q, D4, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  tempD<-data.frame(Item=myFields[i], CreateTableB_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
  tempD<-SubstitueQuesForResponse(tempD,q, !!rlang::sym(myFields[i]), 2025, responseField="Item")
}
CreateFlex(op, mergeOnFirst = TRUE)
```


`r paste(trimws(GetQuestion(q, D4, 2025)),"  ", caption.means, "  ", labels.agree, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("D4")) %>% select(-contains("Answered")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  tempD<-data.frame(CreateTableA_means(d %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
  tempD<-SubstitueQuesForResponse(tempD, q, !!rlang::sym(myFields[i]), 2025)
}
CreateFlex(op, mergeOnFirst = TRUE)
```


`r paste(trimws(GetQuestion(q, D4, 2025)),"  ", caption.means, "  ", labels.agree, "  ", caption.raked, sep="")`

```{r }
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  tempD<-data.frame(CreateTableB_means(d %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
  tempD<-SubstitueQuesForResponse(tempD, q, !!rlang::sym(myFields[i]), 2025)
}
CreateFlex(op, mergeOnFirst = TRUE)
```


`r officer::run_pagebreak()`

# Days Fished

`r paste(trimws(str_split(GetQuestion(q, C1, 2025), " - ")[[1]][1]),"  ", caption.percents, "  ", caption.raked, sep="")`

January

```{r}
mydata<-d %>% filter(!is.na(C1Jan_days))  %>% filter(C1Jan_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1Jan_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1Jan_days),l))
```


`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

February

```{r}
mydata<-d %>% filter(!is.na(C1Feb_days))  %>% filter(C1Feb_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1Feb_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1Feb_days),l))
```


`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

March

```{r}
mydata<-d %>% filter(!is.na(C1Mar_days)) %>% filter(C1Mar_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1Mar_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1Mar_days),l))
```


`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

April

```{r}
mydata<-d %>% filter(!is.na(C1Apr_days)) %>% filter(C1Apr_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1Apr_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1Apr_days),l))
```


`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

May

```{r}
mydata<-d %>% filter(!is.na(C1May_days)) %>% filter(C1May_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1May_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1May_days),l))
```


`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

June

```{r}
mydata<-d %>% filter(!is.na(C1June_days))  %>% filter(C1June_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1June_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1June_days),l))
```


`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

July

```{r}
mydata<-d %>% filter(!is.na(C1July_days))  %>% filter(C1July_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1July_days), l))

```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1July_days),l))
```


`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

August

```{r}
mydata<-d %>% filter(!is.na(C1Aug_days))  %>% filter(C1Aug_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1Aug_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1Aug_days),l))
```


`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

September

```{r SeptDays}
mydata<-d %>% filter(!is.na(C1Sept_days))  %>% filter(C1Sept_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1Sept_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1Sept_days),l))
```


`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

October

```{r}
mydata<-d %>% filter(!is.na(C1Oct_days))  %>% filter(C1Oct_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1Oct_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1Oct_days),l))
```



`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", "This table represents all respondants to this question including those who did not fish during the given time period.  ", caption.medians, "  ", labels.freq, "  ", caption.raked, sep="")`

```{r TotalDays}
mydata<-d %>% filter(!is.na(C1Total_days) & C1_AnsweredAll==TRUE)
myFields<-mydata %>% select(contains("_days")) %>% select(-contains("Total")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  CreateTableA_medians(mydata, myFields[i])
}
CreateFlex(LabelResponses(op,l))
```

`r "....."`

```{r}
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  CreateTableB_medians(mydata, myFields[i])
}
CreateFlex(LabelResponses(op,l))
```


`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", "Only respondants that fished at least once during the time period were included in this breakdown.  ", caption.medians, "  ", labels.freq, "  ", caption.raked, sep="")`

```{r}
mydata<-d %>% filter(!is.na(C1Total_days) & C1_AnsweredAll==TRUE)
myFields<-mydata %>% select(contains("_days")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  CreateTableA_medians(mydata %>% filter(get(myFields[i])>0), myFields[i])
}
CreateFlex(LabelResponses(op,l))
```

`r "....."`

```{r}
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  CreateTableB_medians(mydata %>% filter(get(myFields[i])>0), myFields[i])
}
CreateFlex(LabelResponses(op,l))
```



`r officer::run_pagebreak()`

# Low Water Levels

```{r Q23setup}
optoutQ23 <- "I did not experience low water levels in 2025"
q23Fields <- c("Q23_1", "Q23_2", "Q23_3")
likertQ23 <- c("Never", "Rarely", "Sometimes", "Often", "Always")


# Fallback: compute Q23_Answered if the loaded data predates the aggregation fix
if (!"Q23_Answered" %in% names(d)) {
  d <- d %>%
    mutate(Q23_Answered = rowSums(sapply(d[q23Fields], function(x) !is.na(x)), na.rm = TRUE) > 0)
}


# "Did not experience" subset: each Q23 item coded checked/unchecked
dQ23all <- d %>%
  filter(Q23_Answered) %>%
  mutate(across(all_of(q23Fields),
    ~ factor(ifelse(as.character(.) == optoutQ23, "Did not experience low water", "Unchecked"),
             levels = c("Unchecked", "Did not experience low water"))))
```


`r paste(trimws(GetQuestion(q, Q23_1, 2025)),"  Percent of all respondants at each frequency.  ", caption.percents, "  ", "  ", caption.raked, sep="")`

```{r }
ddQ23 <- d %>% filter(Q23_Answered & !is.na(Q23_1)) %>%
  mutate(Q23_1 = factor(as.character(Q23_1), levels = c(likertQ23, optoutQ23)))
CreateFlex(CreateTableA_selectOne_percent(ddQ23, "Q23_1"))
```

`r paste(trimws(GetQuestion(q, Q23_1, 2025)),"  Percent of all respondants at each frequency.  ", caption.percents, "  ", "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(ddQ23, "Q23_1"))
```


`r paste(trimws(GetQuestion(q, Q23_2, 2025)),"  Percent of all respondants at each frequency.  ", caption.percents, "  ", "  ", caption.raked, sep="")`

```{r }
ddQ23 <- d %>% filter(Q23_Answered & !is.na(Q23_2)) %>%
  mutate(Q23_2 = factor(as.character(Q23_2), levels = c(likertQ23, optoutQ23)))
CreateFlex(CreateTableA_selectOne_percent(ddQ23, "Q23_2"))
```

`r paste(trimws(GetQuestion(q, Q23_2, 2025)),"  Percent of all respondants at each frequency.  ", caption.percents, "  ", "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(ddQ23, "Q23_2"))
```


`r paste(trimws(GetQuestion(q, Q23_3, 2025)),"  Percent of all respondants at each frequency.  ", caption.percents, "  ", "  ", caption.raked, sep="")`

```{r }
ddQ23 <- d %>% filter(Q23_Answered & !is.na(Q23_3)) %>%
  mutate(Q23_3 = factor(as.character(Q23_3), levels = c(likertQ23, optoutQ23)))
CreateFlex(CreateTableA_selectOne_percent(ddQ23, "Q23_3"))
```

`r paste(trimws(GetQuestion(q, Q23_3, 2025)),"  Percent of all respondants at each frequency.  ", caption.percents, "  ", "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(ddQ23, "Q23_3"))
```


`r paste(trimws(GetQuestion(q, Q23_1, 2025)),"  Only respondants that experienced low water levels are included in this calculation.  ", caption.percents, "  ", "  ", caption.raked, sep="")`

```{r }
ddQ23 <- d %>% filter(Q23_Answered & as.character(Q23_1) != optoutQ23 & !is.na(Q23_1)) %>%
  mutate(Q23_1 = factor(as.character(Q23_1), levels = likertQ23))
CreateFlex(CreateTableA_selectOne_percent(ddQ23, "Q23_1"))
```

`r paste(trimws(GetQuestion(q, Q23_1, 2025)),"  Only respondants that experienced low water levels are included in this calculation.  ", caption.percents, "  ", "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(ddQ23, "Q23_1"))
```


`r paste(trimws(GetQuestion(q, Q23_2, 2025)),"  Only respondants that experienced low water levels are included in this calculation.  ", caption.percents, "  ", "  ", caption.raked, sep="")`

```{r }
ddQ23 <- d %>% filter(Q23_Answered & as.character(Q23_2) != optoutQ23 & !is.na(Q23_2)) %>%
  mutate(Q23_2 = factor(as.character(Q23_2), levels = likertQ23))
CreateFlex(CreateTableA_selectOne_percent(ddQ23, "Q23_2"))
```

`r paste(trimws(GetQuestion(q, Q23_2, 2025)),"  Only respondants that experienced low water levels are included in this calculation.  ", caption.percents, "  ", "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(ddQ23, "Q23_2"))
```


`r paste(trimws(GetQuestion(q, Q23_3, 2025)),"  Only respondants that experienced low water levels are included in this calculation.  ", caption.percents, "  ", "  ", caption.raked, sep="")`

```{r }
ddQ23 <- d %>% filter(Q23_Answered & as.character(Q23_3) != optoutQ23 & !is.na(Q23_3)) %>%
  mutate(Q23_3 = factor(as.character(Q23_3), levels = likertQ23))
CreateFlex(CreateTableA_selectOne_percent(ddQ23, "Q23_3"))
```

`r paste(trimws(GetQuestion(q, Q23_3, 2025)),"  Only respondants that experienced low water levels are included in this calculation.  ", caption.percents, "  ", "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(ddQ23, "Q23_3"))
```






`r officer::run_pagebreak()`

# Fish Sought

`r paste(trimws(GetQuestion(q, B2, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B2")) %>% select(-contains("_")) %>% select(-contains("Answered")) %>% names()
CreateFlex(CreateTableA_selectAll_percent(d, myFields, B2_Answered, ordered=TRUE))
```


`r paste(trimws(GetQuestion(q, B2, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectAll_percent(d, myFields, B2_Answered, ordered=TRUE))
```


`r paste(trimws(GetQuestion(q, B2, 2025)),"  Specifically, respondants indicated that they tried to catch these species in lakes, reservoirs, or ponds.", caption.percents, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B2")) %>% select(contains("_lrp")) %>% select(-contains("Answered")) %>% names()
CreateFlex(CreateTableA_selectAll_percent(d, myFields, B2_Answered, ordered=TRUE))
```


`r paste(trimws(GetQuestion(q, B2, 2025)),"  Specifically, respondants indicated that they tried to catch these species in lakes, reservoirs, or ponds.", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectAll_percent(d, myFields, B2_Answered, ordered=TRUE))
```


`r paste(trimws(GetQuestion(q, B2, 2025)),"  Specifically, respondants indicated that they tried to catch these species in rivers, streams, and canals.", caption.percents, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B2")) %>% select(contains("_rsc")) %>% select(-contains("Answered")) %>% names()
CreateFlex(CreateTableA_selectAll_percent(d, myFields, B2_Answered, ordered=TRUE))
```


`r paste(trimws(GetQuestion(q, B2, 2025)),"  Specifically, respondants indicated that they tried to catch these species in rivers, streams, and canals.", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectAll_percent(d, myFields, B2_Answered, ordered=TRUE))
```


`r officer::run_pagebreak()`

# Harvest By Species

`r paste(trimws(GetQuestion(q, B3, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B3")) %>% select(-contains("Answered")) %>% select(-contains("oth")) %>% select(-contains("any")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  data.frame(Species=myFields[i], CreateTableA_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))) %>% filter(as.numeric(get(gsub("3", "2", myFields[i])))==2), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op,l, responseField="Species"), mergeOnFirst = TRUE)
```


`r paste(trimws(GetQuestion(q, B3, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  data.frame(Species=myFields[i], CreateTableB_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))) %>% filter(as.numeric(get(gsub("3", "2", myFields[i])))==2), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op,l, responseField="Species"), mergeOnFirst = TRUE)
```


`r paste(trimws(GetQuestion(q, B3, 2025)),"  ", caption.means, "  ", labels.release, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B3")) %>% select(-contains("Answered")) %>% select(-contains("oth")) %>% select(-contains("any")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  CreateTableA_means(d %>% filter(!is.na(get(myFields[i]))) %>% filter(as.numeric(get(gsub("3", "2", myFields[i])))==2), myFields[i])
}
CreateFlex(LabelResponses(op,l))
```


`r paste(trimws(GetQuestion(q, B3, 2025)),"  ", caption.means, "  ", labels.release, "  ", caption.raked, sep="")`

```{r }
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  CreateTableB_means(d %>% filter(!is.na(get(myFields[i]))) %>% filter(as.numeric(get(gsub("3", "2", myFields[i])))==2), myFields[i])
}
CreateFlex(LabelResponses(op,l))
```


`r officer::run_pagebreak()`

# Ice Fishing

```{r iceSetup}

# Q26 is the gate for the ice fishing section.

# dQ26  = everyone who answered Q26 (base for the Q26 tables)

# iceBase = ice anglers only (Q26 == "Yes"), base for Q27-Q29
dQ26 <- d %>%
  filter(!is.na(Q26)) %>%
  mutate(Q26 = factor(Q26, levels = c("Yes", "No")))

iceBase <- d %>% filter(Q26 == "Yes")
```

`r paste(trimws(GetQuestion(q, Q26, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(dQ26, "Q26"))
```

`r paste(trimws(GetQuestion(q, Q26, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(dQ26, "Q26"))
```


`r paste(trimws(GetQuestion(q, Q27, 2025)),"  Only respondants that ice fished at least one day are included in this calculation.  ", caption.medians, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_medians(iceBase %>% filter(Q27 > 0), "Q27") %>% select(-Response))
```

`r paste(trimws(GetQuestion(q, Q27, 2025)),"  Only respondants that ice fished at least one day are included in this calculation.  ", caption.medians, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_medians(iceBase %>% filter(Q27 > 0), "Q27") %>% select(-Response))
```


`r paste(trimws(GetQuestion(q, Q28_1, 2025)),"  Proportion of harvest taken while ice fishing.  Only respondants that ice fished are included in this calculation.  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
myFields <- iceBase %>% dplyr::select(contains("Q28")) %>% select(-contains("Answered")) %>% names()
op <- foreach(i = 1:length(myFields), .combine = "rbind") %do% {
  data.frame(Species = myFields[i], CreateTableA_selectOne_percent(iceBase %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op, l, responseField = "Species"), mergeOnFirst = TRUE)
```

`r paste(trimws(GetQuestion(q, Q28_1, 2025)),"  Proportion of harvest taken while ice fishing.  Only respondants that ice fished are included in this calculation.  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
op <- foreach(i = 1:length(myFields), .combine = "rbind") %do% {
  data.frame(Species = myFields[i], CreateTableB_selectOne_percent(iceBase %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op, l, responseField = "Species"), mergeOnFirst = TRUE)
```


`r paste(trimws(GetQuestion(q, Q28_1, 2025)),"  Proportion of harvest taken while ice fishing.  Only respondants that ice fished and harvested at least one of these species are included in this calculation.  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
optoutQ28 <- "I did not harvest any of these fish in 2025"
op <- foreach(i = 1:length(myFields), .combine = "rbind") %do% {
  data.frame(Species = myFields[i], CreateTableA_selectOne_percent(iceBase %>% filter(!is.na(get(myFields[i])) & as.character(get(myFields[i])) != optoutQ28), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op, l, responseField = "Species"), mergeOnFirst = TRUE)
```

`r paste(trimws(GetQuestion(q, Q28_1, 2025)),"  Proportion of harvest taken while ice fishing.  Only respondants that ice fished and harvested at least one of these species are included in this calculation.  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
op <- foreach(i = 1:length(myFields), .combine = "rbind") %do% {
  data.frame(Species = myFields[i], CreateTableB_selectOne_percent(iceBase %>% filter(!is.na(get(myFields[i])) & as.character(get(myFields[i])) != optoutQ28), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op, l, responseField = "Species"), mergeOnFirst = TRUE)
```


`r paste(trimws(GetQuestion(q, Q29_1, 2025)),"  Of legal fish caught while ice fishing, the proportion that were harvested.  Only respondants that ice fished are included in this calculation.  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
myFields <- iceBase %>% dplyr::select(contains("Q29")) %>% select(-contains("Answered")) %>% names()
op <- foreach(i = 1:length(myFields), .combine = "rbind") %do% {
  data.frame(Species = myFields[i], CreateTableA_selectOne_percent(iceBase %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op, l, responseField = "Species"), mergeOnFirst = TRUE)
```

`r paste(trimws(GetQuestion(q, Q29_1, 2025)),"  Of legal fish caught while ice fishing, the proportion that were harvested.  Only respondants that ice fished are included in this calculation.  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
op <- foreach(i = 1:length(myFields), .combine = "rbind") %do% {
  data.frame(Species = myFields[i], CreateTableB_selectOne_percent(iceBase %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op, l, responseField = "Species"), mergeOnFirst = TRUE)
```


`r paste(trimws(GetQuestion(q, Q29_1, 2025)),"  Of legal fish caught while ice fishing, the proportion that were harvested.  Only respondants that ice fished and caught at least one of these species are included in this calculation.  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
optoutQ29 <- "I did not catch any of these fish while ice fishing in 2025"
op <- foreach(i = 1:length(myFields), .combine = "rbind") %do% {
  data.frame(Species = myFields[i], CreateTableA_selectOne_percent(iceBase %>% filter(!is.na(get(myFields[i])) & as.character(get(myFields[i])) != optoutQ29), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op, l, responseField = "Species"), mergeOnFirst = TRUE)
```

`r paste(trimws(GetQuestion(q, Q29_1, 2025)),"  Of legal fish caught while ice fishing, the proportion that were harvested.  Only respondants that ice fished and caught at least one of these species are included in this calculation.  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
op <- foreach(i = 1:length(myFields), .combine = "rbind") %do% {
  data.frame(Species = myFields[i], CreateTableB_selectOne_percent(iceBase %>% filter(!is.na(get(myFields[i])) & as.character(get(myFields[i])) != optoutQ29), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op, l, responseField = "Species"), mergeOnFirst = TRUE)
```


`r officer::run_pagebreak()`

# Angler Motivations

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("C2")) %>% select(-contains("Answered")) %>% names()
CreateFlex(SubstitueQuesForResponse(CreateTableA_means(d, myFields), q, C2, 2025))
```


`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, sep="")`

```{r}
CreateFlex(SubstitueQuesForResponse(CreateTableB_means(d, myFields), q, C2, 2025))
```


`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, sep="")`

```{r }
myFields<-c("motivation_pp","motivation_natural", "motivation_social","motivation_resource")
op<-foreach(i=myFields, .combine="rbind") %do% {
  CreateTableA_means(d %>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), i)
}
CreateFlex(LabelResponses(op,l))
```

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, sep="")`

```{r}
op<-foreach(i=myFields, .combine="rbind") %do% {
  CreateTableB_means(d %>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), i)
}
CreateFlex(LabelResponses(op,l))
```

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, sep="")`

```{r}
myFields<-c("motivation_noncatch","motivation_catch")
op<-foreach(i=myFields, .combine="rbind") %do% {
  CreateTableA_means(d %>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), i)
}
CreateFlex(LabelResponses(op,l))
```

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, sep="")`

```{r}
op<-foreach(i=myFields, .combine="rbind") %do% {
  CreateTableB_means(d %>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), i)
}
CreateFlex(LabelResponses(op,l))
```



`r officer::run_pagebreak()`

# Regulations

`r paste(trimws(GetQuestion(q, Q31, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.reversed, "  ", caption.raked, sep="")`

```{r Q31}
myFieldsQ31<-d %>% dplyr::select(contains("Q31")) %>% select(-contains("Answered")) %>% names()
CreateFlex(MarkReversedItems(SubstitueQuesForResponse(CreateTableA_means(d, myFieldsQ31), q, Q31, 2025), q, 2025))
```


`r paste(trimws(GetQuestion(q, Q31, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.reversed, "  ", caption.raked, sep="")`

```{r}
CreateFlex(MarkReversedItems(SubstitueQuesForResponse(CreateTableB_means(d, myFieldsQ31), q, Q31, 2025), q, 2025))
```


`r paste(trimws(GetQuestion(q, Q31, 2025)), "  ", caption.means, "  ", labels.agree, "  ", ReversedItemsNote("Regulations"), "  ", caption.raked, sep="")`

```{r }
myFieldsQ31sub<-c("reg_complexity", "reg_trust", "reg_objectives")

op<-foreach(i=myFieldsQ31sub, .combine="rbind") %do% {
  CreateTableA_means(d %>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), i)
}
CreateFlex(LabelResponses(op,l))

```

`r paste(trimws(GetQuestion(q, Q31, 2025)), "  ", caption.means, "  ", labels.agree, "  ", ReversedItemsNote("Regulations"), "  ", caption.raked, sep="")`

```{r}
op<-foreach(i=myFieldsQ31sub, .combine="rbind") %do% {
  CreateTableB_means(d %>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), i)
}
CreateFlex(LabelResponses(op,l))
```


`r officer::run_pagebreak()`

# Angler Attitudes

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.reversed, "  ", caption.raked, sep="")`

```{r E1}
myFields<-d %>% dplyr::select(contains("E1")) %>% select(-contains("Answered")) %>% names()
CreateFlex(MarkReversedItems(SubstitueQuesForResponse(CreateTableA_means(d, myFields), q, E1, 2025), q, 2025))
```


`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.reversed, "  ", caption.raked, sep="")`

```{r}
CreateFlex(MarkReversedItems(SubstitueQuesForResponse(CreateTableB_means(d, myFields), q, E1, 2025), q, 2025))
```


`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", ReversedItemsNote("Attitudes"), "  ", caption.raked, sep="")`

```{r }
myFields<-c("attitude_catch", "attitude_numbers", "attitude_size", "attitude_harvest")

op<-foreach(i=myFields, .combine="rbind") %do% {
  CreateTableA_means(d %>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), i)
}
CreateFlex(LabelResponses(op,l))

```

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", ReversedItemsNote("Attitudes"), "  ", caption.raked, sep="")`

```{r}
op<-foreach(i=myFields, .combine="rbind") %do% {
  CreateTableB_means(d %>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), i)
}
CreateFlex(LabelResponses(op,l))
```



`r officer::run_pagebreak()`

# Gender

`r paste(trimws(GetQuestion(q, E2, 2025)),"  ", caption.percents, "  ", sep="") `

```{r }
CreateFlex(CreateTableA_selectOne_percent(d %>% mutate(postWeight = 1), E2))
```

`r paste(trimws(GetQuestion(q, E2, 2025)),"  ", caption.percents, sep="")`

```{r}
CreateFlex(CreateTableB_selectOne_percent(d %>% mutate(postWeight = 1), E2))
```

`r officer::run_pagebreak()`

# Age

`r paste(trimws(GetQuestion(q, E3, 2025)),"  ", caption.percents, sep="") `

```{r }
CreateFlex(CreateTableA_selectOne_percent(d %>% mutate(postWeight = 1), E3))
```

`r paste(trimws(GetQuestion(q, E3, 2025)),"  ", caption.percents, sep="") `

```{r }
CreateFlex(CreateTableB_selectOne_percent(d %>% mutate(postWeight = 1), E3))
```




`r officer::run_pagebreak()`

# References

Bureau of Soci0logical Research.  2026.  Fishing Nebraska 2025-2026 Methodology Report. University of Nebraska-Lincoln.

Hurley, Keith.  2026.  2026 Nebraska Licensed Angler Survey - Respondents and Responses.  Nebraska Game and Parks Commission. (Hurley 2026). 

`r officer::run_pagebreak()`

# Appendix A - 2026 Nebraska Licensed Angler Survey (Paper Version)