dQ18all <- d %>%
  filter(Q18_Answered) %>%
  mutate(
    Q18c = factor(
      ifelse(!is.na(Q18c), "Did not hire a guide", "Unchecked"),
      levels = c("Unchecked", "Did not hire a guide")
    )
  )
CreateFlex(CreateTableA_selectAll_percent(dQ18all, "Q18c", Q18_Answered, ordered = FALSE))
```

`r paste(trimws(GetQuestion(q, Q18c, 2025)),"  Only respondants that hired at least one guide are included in this calculation.  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
dQ18hired <- d %>%
  filter(Q18_Answered & is.na(Q18c)) %>%
  mutate(
    Q18a = factor(ifelse(Q18a > 0, "Hired in Nebraska",      "Unchecked"), levels = c("Unchecked", "Hired in Nebraska")),
    Q18b = factor(ifelse(Q18b > 0, "Hired outside Nebraska", "Unchecked"), levels = c("Unchecked", "Hired outside Nebraska"))
  )
CreateFlex(CreateTableA_selectAll_percent(dQ18hired, c("Q18a", "Q18b"), Q18_Answered, ordered = FALSE))
```vey/Analysis/CrossTabTables/")

source("..\\BaseFunctions_2025_UPDATED.R") #load file of common functions
source("CrossTabTableFunctions.R") #load file of cross tab report functions
```


```{r getData, echo=FALSE}
setwd("D:/Survey/Analysis/CrossTabTables/")

#load data
load(file="../../Data/DataAggregation1/aggregateData_20260615.rData")
d<-d %>% filter(surveyYear==2025)
#q<-base.loaddata.factorlevels()
#save(q, file="q_20190802")
#load(file="../../2018 Statewide Survey/Analysis/Rscripts/CrossTabTables/q_20190802")
q<-read.csv(file="../../Data/DataAggregation1/FactorLevels_aggregated.csv") %>% filter(Year==2025)
l=read.csv(file="../../Data/DataAggregation1/Labels.csv")

```

```{r createFunctions}
CreateFlex<-function(x, mergeOnFirst=FALSE) {
  require(officer)
  require(flextable)
  
  bigborder=officer:: fp_border(color="black", width = 1.5)
  smallborder=officer:: fp_border(color="black", width=1.0)
  
  myFlex<-  flextable(x) %>%
    theme_zebra()
  
  if(mergeOnFirst==TRUE) {
    #merge first column cells  
    myFlex <-myFlex %>%
        merge_v(j=1, part="body") 
      #add border below merged cells in first column
      myFlex<-myFlex %>%
        border(border.bottom = smallborder, i=rle(cumsum(myFlex$body$spans$columns[,1] ))$values, part="body") 
  }
  
  myFlex <- myFlex %>%
    #border_outer(officer:: fp_border(color="black", width = 1.5), part="all") %>%
    #add border above and below footer
    border(border.bottom = bigborder, border.top = bigborder, part = "header") %>%
    #add border at bottom of body
    border(border.bottom = bigborder, i=nrow(myFlex$body$spans$rows), part = "body") %>%
    padding(j=1, padding.left=3) %>%
    align(align="left", part="all") %>%
    fontsize(part = "header", size = 10) %>%
    fontsize(part="body", size=8) %>%
    bold(part="header") %>%
    autofit() %>%
    width(j = 1, width = 1.2)
      
  myFlex
}


```

<!---CHUNK_PAGEBREAK--->

This report contains the cross-tabulation results for each question in the 2025 Nebraska Licensed Angler Survey (LAS).  Details on the design and administration of the LAS can be found in the companion report ???.  Information on the responses and returns of the LAS can be found in the companion report ???.  When LAS returns were examined, it was determined that weighting results by age group and residency was warrented to better represent the Nebraska licensed angler population.  In this report, question results that were weighted are notated in their caption.

This report is organized in the order questions were asked in the LAS.  A copy of the LAS is provided in the appendies of this report.  Breakdowns of the responses to each question are provided for:  a) all respondants, b) by residency, c) by gender, and d) by age.

<!---CHUNK_PAGEBREAK--->

### Permit Type

`r paste(trimws(GetQuestion(q, A1, 2025)),"  ", caption.percents, sep="") `

```{r  }
CreateFlex(CreateTableA_selectOne_percent(d %>% mutate(postWeight = 1), A1, ordered=TRUE))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, A1, 2025)),"  ", caption.percents, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d %>% mutate(postWeight = 1), A1, ordered=TRUE))
```

<!---CHUNK_PAGEBREAK--->

### Did You Fish

`r paste(trimws(GetQuestion(q, A2, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, A2))
```

`r paste(trimws(GetQuestion(q, A2, 2025)),"  ", caption.percents,"  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, A2))
```

<!---CHUNK_PAGEBREAK--->

### Why Didn't You Fish

`r paste(trimws(GetQuestion(q, A3, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, A3, ordered=TRUE))
```

`r paste(trimws(GetQuestion(q, A3, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, A3, ordered=TRUE))
```

<!---CHUNK_PAGEBREAK--->

### Fish Out-Of-State

`r paste(trimws(GetQuestion(q, A11, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, A11))
```

`r paste(trimws(GetQuestion(q, A11, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, A11))
```

### Boat Out-Of-State

`r paste(trimws(GetQuestion(q, A12, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, A12))
```

`r paste(trimws(GetQuestion(q, A12, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, A12))
```

<!---CHUNK_PAGEBREAK--->

### Park Entry Permit

`r paste(trimws(GetQuestion(q, A10, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, A10))
```

`r paste(trimws(GetQuestion(q, A10, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, A10))
```

### Fishing Tournaments

`r paste(trimws(GetQuestion(q, A13, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, fishedTourney) %>% mutate(Response=c("No Tournaments","Fished Tournaments")))
```

`r paste(trimws(GetQuestion(q, A13, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, fishedTourney) %>% mutate(Response=c("No Tournaments","Fished Tournaments")))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, A13, 2025)),"  ", caption.percents, "  Only respondants who participated in AT LEAST ONE tournament are included in this calculation", "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d %>% filter(A13_corrected>0), "A13_corrected") %>% mutate(Response=as.integer(Response)))
```

`r paste(trimws(GetQuestion(q, A13, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d %>% filter(A13_corrected>0), "A13_corrected") %>% mutate(Response=as.integer(Response)))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, A13, 2025)),"  ", caption.means, "  Only respondants who participated in AT LEAST ONE tournament are included in this calculation", "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_means(d %>% filter(A13_corrected>0), "A13_corrected")[,-1] )
```

`r paste(trimws(GetQuestion(q, A13, 2025)),"  ", caption.means, "  Only respondants who participated in AT LEAST ONE tournament are included in this calculation", "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_means(d %>% filter(A13_corrected>0), "A13_corrected")[,-1])
```

### Waterbody Types

`r paste(trimws(GetQuestion(q, A4, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r WaterbodyTypes}
myFields<-d %>% dplyr::select(contains("A4")) %>% select(-contains("Answered")) %>% names()
CreateFlex(CreateTableA_selectAll_percent(d, myFields, myAnsweredVar = A4_Answered, ordered=TRUE))

```

`r paste(trimws(GetQuestion(q, A4, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectAll_percent(d, myFields, myAnsweredVar = A4_Answered, ordered=TRUE))
```

### Methods

`r paste(trimws(GetQuestion(q, A5, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r Methods}
myFields<-d %>% dplyr::select(contains("A5")) %>% select(-contains("Answered")) %>% names()
CreateFlex(CreateTableA_selectAll_percent(d, myFields, myAnsweredVar = A5_Answered, ordered=TRUE))
```

`r paste(trimws(GetQuestion(q, A5, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectAll_percent(d, myFields, myAnsweredVar = A5_Answered, ordered=TRUE))
```

<!---CHUNK_PAGEBREAK--->

### Techniques

`r paste(trimws(GetQuestion(q, A6, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("A6")) %>% select(-contains("Answered")) %>% names()
CreateFlex(CreateTableA_selectAll_percent(d, myFields, myAnsweredVar = A6_Answered, ordered=TRUE))
```

`r paste(trimws(GetQuestion(q, A6, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectAll_percent(d, myFields, myAnsweredVar = A6_Answered, ordered=TRUE))
```

<!---CHUNK_PAGEBREAK--->

### Crowding

`r paste(trimws(GetQuestion(q, Q11, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d %>% filter(!is.na(Q11)), "Q11"))
```

`r paste(trimws(GetQuestion(q, Q11, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d %>% filter(!is.na(Q11)), "Q11"))
```

<!---CHUNK_PAGEBREAK--->

### Access

`r paste(trimws(GetQuestion(q, A17, 2025)),"  ", caption.percents, "  The first two rows include responses from respondants that answered Yes or No to each question independant of the other question.  The last three rows only include responses from respondants that answered Yes or No to BOTH questions.", "  ", caption.raked, sep="")`

```{r }
# Use the corrected A17 columns (A17Priv_corrected / A17Pub_corrected) instead
# of the originals (A17priv / A17pub), but transfer the original labels so the
# corrected versions display with the original wording.
l_a17 <- l %>%
  bind_rows(tibble::tibble(
    Response = c("A17Priv_corrected", "A17Pub_corrected"),
    Label    = c(l$Label[l$Response == "A17priv"],
                 l$Label[l$Response == "A17pub"])
  ))
myFields <- d %>%
  dplyr::select(contains("A17")) %>%
  select(-contains("Answered")) %>%
  select(-A17priv, -A17pub) %>%
  names()
op<-foreach(i=1:length(myFields), .combine = "rbind") %do% {
  data.frame(Type=myFields[i], CreateTableA_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op %>% filter(Response=="Yes") %>% mutate(Response=Type) %>% select(-Type) , l_a17))
```

```{r}
require(VennDiagram)

vennFields<-d %>% dplyr::select(contains("A17")) %>% names()
a17<-foreach(i=1:length(vennFields), .combine = "rbind") %do% {
  data.frame(Type=vennFields[i], base.summary.percent.selectOne(d %>% filter(!is.na(get(vennFields[i]))), vennFields[i]), check.names = FALSE) %>% filter(Response=="Yes") %>% select(Response=Type,Value, Number)
}

vennCounts<-data.frame(pub=round(sum(a17$Number[a17$Response=="A17justPub"],a17$Number[a17$Response=="A17both"]),1),
               priv=round(sum(a17$Number[a17$Response=="A17justPriv"],a17$Number[a17$Response=="A17both"]),1),
               both=round(a17$Number[a17$Response=="A17both"],1))

grid::grid.newpage()
grid::grid.draw(draw.pairwise.venn(area1 = vennCounts$pub,
                                   area2 = vennCounts$priv,
                                   cross.area = vennCounts$both,
                                   category=c("Public \nlands \nand access", "Private \nlands \nand access"),
                                   fill=c("blue", "red"),
                                   scaled=TRUE,
                                   inverted=FALSE,
                                   ext.text=FALSE,
                                   cat.pos=c(220, 150),
                                   cat.dist=c(0.05,0.05),
                                   cat.cex=1.2,
                                   print.mode="percent",
                                   sigdigs=3))

```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, A17, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
myFields <- d %>%
  dplyr::select(contains("A17")) %>%
  select(-contains("Answered")) %>%
  select(-A17priv, -A17pub) %>%
  names()
op<-foreach(i=1:length(myFields), .combine = "rbind") %do% {
  data.frame(Type=myFields[i], CreateTableB_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op, l_a17, responseField="Type"), mergeOnFirst=TRUE)
```

<!---CHUNK_PAGEBREAK--->

### Favorite Waterbody Distance

`r paste(trimws(GetQuestion(q, A7, 2025)),"  ", caption.percents, "  ", labels.distance, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, A7))
```

`r paste(trimws(GetQuestion(q, A7, 2025)),"  ", caption.percents, "  ", labels.distance, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, A7))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, A7, 2025)),"  ", caption.medians, "  ", labels.distance, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_medians(d, "A7_miles")[,-1])
```

`r paste(trimws(GetQuestion(q, A7, 2025)),"  ", caption.medians, "  ", labels.distance, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_medians(d, "A7_miles")[,-1])
```

<!---CHUNK_PAGEBREAK--->

### Most-Visitied Waterbody Distance

`r paste(trimws(GetQuestion(q, A8, 2025)),"  ", caption.percents, "  ", labels.distance, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, A8))
```

`r paste(trimws(GetQuestion(q, A8, 2025)),"  ", caption.percents, "  ", labels.distance, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, A8))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, A8, 2025)),"  ", caption.medians, "  ", labels.distance, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_medians(d, "A8_miles")[,-1])
```

`r paste(trimws(GetQuestion(q, A8, 2025)),"  ", caption.medians, "  ", labels.distance, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_medians(d, "A8_miles")[,-1])
```

<!---CHUNK_PAGEBREAK--->

### Satisfaction

`r paste(trimws(GetQuestion(q, A9, 2025)),"  ", caption.percents, "  ", labels.satisfaction, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, A9))
```

`r paste(trimws(GetQuestion(q, A9, 2025)),"  ", caption.percents, "  ", labels.satisfaction, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, A9))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, A9, 2025)),"  ", caption.means, "  ", caption.raked, sep="")`

```{r }
CreateFlex(SubstitueQuesForResponse(CreateTableA_means(d, "A9"),q, A9, 2025))
```

`r paste(trimws(GetQuestion(q, A9, 2025)),"  ", caption.means, "  ", caption.raked, sep="")`

```{r }
CreateFlex(SubstitueQuesForResponse(CreateTableB_means(d, "A9"),q, A9, 2025))
```

<!---CHUNK_PAGEBREAK--->

### Live-imaging Sonar Use

`r paste(trimws(GetQuestion(q, Q16, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d %>% filter(!is.na(Q16)), "Q16"))
```

`r paste(trimws(GetQuestion(q, Q16, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d %>% filter(!is.na(Q16)), "Q16"))
```


### Conservation Officer

`r paste(trimws(GetQuestion(q, E7, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, E7))
```

`r paste(trimws(GetQuestion(q, E7, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, E7))
```


<!---CHUNK_PAGEBREAK--->

### Guided Trips

`r paste(trimws(GetQuestion(q, Q18c, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
dQ18all <- d %>%
  filter(!is.na(Q18a) | !is.na(Q18b) | !is.na(Q18c)) %>%
  mutate(
    Q18c = factor(
      ifelse(!is.na(Q18c), "Did not hire a guide", "Unchecked"),
      levels = c("Unchecked", "Did not hire a guide")
    )
  )
CreateFlex(CreateTableA_selectAll_percent(dQ18all, "Q18c", Q18_Answered, ordered = FALSE))
```

`r paste(trimws(GetQuestion(q, Q18c, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectAll_percent(dQ18all, "Q18c", Q18_Answered, ordered = FALSE))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, Q18c, 2025)),"  Only respondants that hired at least one guide are included in this calculation.  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
dQ18hired <- d %>%
  filter(is.na(Q18c) & (!is.na(Q18a) | !is.na(Q18b))) %>%
  mutate(
    Q18a    = factor(ifelse(Q18a > 0, "Hired in Nebraska",      "Unchecked"), levels = c("Unchecked", "Hired in Nebraska")),
    Q18b    = factor(ifelse(Q18b > 0, "Hired outside Nebraska", "Unchecked"), levels = c("Unchecked", "Hired outside Nebraska")),
    Q18both = factor(ifelse(Q18a == "Hired in Nebraska" & Q18b == "Hired outside Nebraska", "Hired in both", "Unchecked"), levels = c("Unchecked", "Hired in both"))
  )
myFields <- c("Q18a", "Q18b", "Q18both")
CreateFlex(CreateTableA_selectAll_percent(dQ18hired, myFields, Q18_Answered, ordered = FALSE))
```

`r paste(trimws(GetQuestion(q, Q18c, 2025)),"  Only respondants that hired at least one guide are included in this calculation.  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectAll_percent(dQ18hired, myFields, Q18_Answered, ordered = FALSE))
```
<!---CHUNK_PAGEBREAK--->

### Trout Locations

`r paste(trimws(GetQuestion(q, D13oga, 2025)),"  ", caption.percents, "  These values only represent the respondants that selected they fished for TROUT elsewhere in the survey.", "  ", caption.raked,sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("D13")) %>% select(-contains("Answered")) %>% names()
op<-foreach(i=1:length(myFields), .combine = "rbind") %do% {
  data.frame(Location=myFields[i], CreateTableA_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))) %>% filter(B2rbt=="Trout"), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op, l, responseField="Location"), mergeOnFirst=TRUE)

```

...

```{r }
op<-foreach(i=1:length(myFields), .combine = "rbind") %do% {
  data.frame(Type=myFields[i], CreateTableB_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))) %>% filter(B2rbt=="Trout"), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op, l, responseField="Type"), mergeOnFirst=TRUE)

```


```{r troutVinn}
require(VennDiagram)

op<-d[d$B2rbt=="Trout",]
op<-op %>% select(D13lrp, D13rsc, D13oga, D13tr, surveyYear, age_group, postWeight)
# Code by label so this does not depend on factor level order: "Yes" -> 1, anything else (incl. NA) -> 2
op[,c("D13lrp", "D13rsc", "D13oga", "D13tr")]<-sapply(op[,c("D13lrp", "D13rsc", "D13oga", "D13tr")],function(x) ifelse(as.character(x)=="Yes", 1, 2))
op[,c("D13lrp", "D13rsc", "D13oga", "D13tr")]<-sapply(op[,c("D13lrp", "D13rsc", "D13oga", "D13tr")],function(x) ifelse(is.na(x), 2, x))

op_old<-op %>%
  filter(D13lrp==1 | D13rsc==1| D13oga==1| D13tr==1) %>%
  group_by(D13lrp, D13rsc, D13oga, D13tr) %>%
  summarise(Freq=n(), .groups = "drop")

op <- op %>%
  filter(D13lrp==1 | D13rsc==1| D13oga==1| D13tr==1) 

op<-op %>%
  group_by(D13lrp, D13rsc, D13oga, D13tr) %>%
  summarise(Freq=sum(postWeight), .groups = "drop") 

grid::grid.newpage()
grid::grid.draw(draw.quad.venn(area1 = sum(op$Freq[op$D13lrp==1], na.rm=TRUE),
                area2 =  sum(op$Freq[op$D13rsc==1], na.rm=TRUE),
                area3 =  sum(op$Freq[op$D13oga==1], na.rm=TRUE),
                area4 =  sum(op$Freq[op$D13tr==1], na.rm=TRUE),
                n12 =  sum(op$Freq[op$D13lrp==1 & op$D13rsc==1]),
                n13 =  sum(op$Freq[op$D13lrp==1 & op$D13oga==1]),
                n14 =  sum(op$Freq[op$D13lrp==1 & op$D13tr==1]),
                n23 =  sum(op$Freq[op$D13rsc==1 & op$D13oga==1]),
                n24 =  sum(op$Freq[op$D13rsc==1 & op$D13tr==1]),
                n34 =  sum(op$Freq[op$D13oga==1 & op$D13tr==1]),
                n123 =  sum(op$Freq[op$D13lrp==1 & op$D13rsc==1 & op$D13oga==1]),
                n124 =  sum(op$Freq[op$D13lrp==1 & op$D13rsc==1 & op$D13tr==1]),
                n134 =  sum(op$Freq[op$D13lrp==1 & op$D13oga==1 & op$D13tr==1]),
                n234 =  sum(op$Freq[op$D13rsc==1 & op$D13oga==1 & op$D13tr==1]),
                n1234 =  sum(op$Freq[op$D13lrp==1 & op$D13rsc==1 & op$D13oga==1 & op$D13tr==1]),
                category=c("Lakes, \nReservoirs, \nand Ponds",
                           "Rivers, \nStreams, \nand Canels",
                           "Lake \nOgallala \nComplex",
                           "Two Rivers"),
                fill=c("blue", "red", "orange", "brown"),
                scaled=TRUE,
                inverted=FALSE,
                ext.text=FALSE,
                #cat.pos=c(220, 145),
                #cat.dist=c(0.05,0.05),
                cat.cex=1.2,
                print.mode="percent"))

```

<!---CHUNK_PAGEBREAK--->

# Preferred Fish

`r paste(trimws(GetQuestion(q, B1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableA_selectOne_percent(d, B1, ordered = TRUE))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectOne_percent(d, B1, ordered=TRUE))
```

<!---CHUNK_PAGEBREAK--->

### Preferred Species Questions

`r paste(trimws(GetQuestion(q, D4, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("D4")) %>% select(-contains("Answered")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  tempD<-data.frame(Item=myFields[i], CreateTableA_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
  tempD<-SubstitueQuesForResponse(tempD,q, !!rlang::sym(myFields[i]), 2025, responseField="Item")
}
CreateFlex(op, mergeOnFirst = TRUE)
```

`r paste(trimws(GetQuestion(q, D4, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  tempD<-data.frame(Item=myFields[i], CreateTableB_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
  tempD<-SubstitueQuesForResponse(tempD,q, !!rlang::sym(myFields[i]), 2025, responseField="Item")
}
CreateFlex(op, mergeOnFirst = TRUE)
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, D4, 2025)),"  ", caption.means, "  ", labels.agree, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("D4")) %>% select(-contains("Answered")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  tempD<-data.frame(CreateTableA_means(d %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
  tempD<-SubstitueQuesForResponse(tempD, q, !!rlang::sym(myFields[i]), 2025)
}
CreateFlex(op, mergeOnFirst = TRUE)
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, D4, 2025)),"  ", caption.means, "  ", labels.agree, "  ", caption.raked, sep="")`

```{r }
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  tempD<-data.frame(CreateTableB_means(d %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
  tempD<-SubstitueQuesForResponse(tempD, q, !!rlang::sym(myFields[i]), 2025)
}
CreateFlex(op, mergeOnFirst = TRUE)
```

<!---CHUNK_PAGEBREAK--->

### Days Fished

`r paste(trimws(str_split(GetQuestion(q, C1, 2025), " - ")[[1]][1]),"  ", caption.percents, "  ", caption.raked, sep="")`

January

```{r}
mydata<-d %>% filter(!is.na("C1Jan_days"))  %>% filter(C1Jan_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1Jan_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1Jan_days),l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

February

```{r}
mydata<-d %>% filter(!is.na("C1Feb_days"))  %>% filter(C1Feb_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1Feb_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1Feb_days),l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

March

```{r}
mydata<-d %>% filter(!is.na("C1Mar_days")) %>% filter(C1Mar_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1Mar_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1Mar_days),l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

April

```{r}
mydata<-d %>% filter(!is.na("C1Apr_days")) %>% filter(C1Apr_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1Apr_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1Apr_days),l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

May

```{r}
mydata<-d %>% filter(!is.na("C1May_days")) %>% filter(C1May_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1May_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1May_days),l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

June

```{r}
mydata<-d %>% filter(!is.na("C1June_days"))  %>% filter(C1June_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1June_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1June_days),l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

July

```{r}
mydata<-d %>% filter(!is.na("C1July_days"))  %>% filter(C1July_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1July_days), l))

```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1July_days),l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

August

```{r}
mydata<-d %>% filter(!is.na("C1Aug_days"))  %>% filter(C1Aug_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1Aug_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1Aug_days),l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

September

```{r SeptDays}
mydata<-d %>% filter(!is.na("C1Sept_days"))  %>% filter(C1Sept_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1Sept_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1Sept_days),l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

October

```{r}
mydata<-d %>% filter(!is.na("C1Oct_days"))  %>% filter(C1Oct_days<22)
CreateFlex(LabelResponses(CreateTableA_selectOne_percent(mydata, C1Oct_days),l))
```

`r "....."`

```{r}
CreateFlex(LabelResponses(CreateTableB_selectOne_percent(mydata, C1Oct_days),l))
```


<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", "This table represents all respondants to this question including those who did not fish during the given time period.  ", caption.medians, "  ", labels.freq, "  ", caption.raked, sep="")`

```{r TotalDays}
mydata<-d %>% filter(!is.na("C1Total_days") & C1_AnsweredAll==TRUE)
myFields<-mydata %>% select(contains("_days")) %>% select(-contains("Total")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  CreateTableA_medians(mydata, myFields[i])
}
CreateFlex(LabelResponses(op,l))
```

`r "....."`

```{r}
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  CreateTableB_medians(mydata, myFields[i])
}
CreateFlex(LabelResponses(op,l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C1, 2025)),"  ", "Only respondants that fished at least once during the time period were included in this breakdown.  ", caption.medians, "  ", labels.freq, "  ", caption.raked, sep="")`

```{r}
mydata<-d %>% filter(!is.na("C1Total_days") & C1_AnsweredAll==TRUE)
myFields<-mydata %>% select(contains("_days")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  CreateTableA_medians(mydata %>% filter(get(myFields[i])>0), myFields[i])
}
CreateFlex(LabelResponses(op,l))
```

`r "....."`

```{r}
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  CreateTableB_medians(mydata %>% filter(get(myFields[i])>0), myFields[i])
}
CreateFlex(LabelResponses(op,l))
```


<!---CHUNK_PAGEBREAK--->

### Fish Sought

`r paste(trimws(GetQuestion(q, B2, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B2")) %>% select(-contains("_")) %>% select(-contains("Answered")) %>% names()
CreateFlex(CreateTableA_selectAll_percent(d, myFields, B2_Answered, ordered=TRUE))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B2, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectAll_percent(d, myFields, B2_Answered, ordered=TRUE))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B2, 2025)),"  Specifically, respondants indicated that they tried to catch these species in lakes, reservoirs, or ponds.", caption.percents, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B2")) %>% select(contains("_lrp")) %>% select(-contains("Answered")) %>% names()
CreateFlex(CreateTableA_selectAll_percent(d, myFields, B2_Answered, ordered=TRUE))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B2, 2025)),"  Specifically, respondants indicated that they tried to catch these species in lakes, reservoirs, or ponds.", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectAll_percent(d, myFields, B2_Answered, ordered=TRUE))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B2, 2025)),"  Specifically, respondants indicated that they tried to catch these species in rivers, streams, and canals.", caption.percents, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B2")) %>% select(contains("_rsc")) %>% select(-contains("Answered")) %>% names()
CreateFlex(CreateTableA_selectAll_percent(d, myFields, B2_Answered, ordered=TRUE))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B2, 2025)),"  Specifically, respondants indicated that they tried to catch these species in rivers, streams, and canals.", caption.percents, "  ", caption.raked, sep="")`

```{r }
CreateFlex(CreateTableB_selectAll_percent(d, myFields, B2_Answered, ordered=TRUE))
```

<!---CHUNK_PAGEBREAK--->

### Harvest By Species

`r paste(trimws(GetQuestion(q, B3, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B3")) %>% select(-contains("Answered")) %>% select(-contains("oth")) %>% select(-contains("any")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  data.frame(Species=myFields[i], CreateTableA_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))) %>% filter(as.numeric(get(gsub("3", "2", myFields[i])))==2), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op,l, responseField="Species"), mergeOnFirst = TRUE)
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B3, 2025)),"  ", caption.percents, "  ", caption.raked, sep="")`

```{r }
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  data.frame(Species=myFields[i], CreateTableB_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))) %>% filter(as.numeric(get(gsub("3", "2", myFields[i])))==2), myFields[i]), check.names = FALSE)
}
CreateFlex(LabelResponses(op,l, responseField="Species"), mergeOnFirst = TRUE)
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B3, 2025)),"  ", caption.means, "  ", labels.release, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("B3")) %>% select(-contains("Answered")) %>% select(-contains("oth")) %>% select(-contains("any")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  CreateTableA_means(d %>% filter(!is.na(get(myFields[i]))) %>% filter(as.numeric(get(gsub("3", "2", myFields[i])))==2), myFields[i])
}
CreateFlex(LabelResponses(op,l))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, B3, 2025)),"  ", caption.means, "  ", labels.release, "  ", caption.raked, sep="")`

```{r }
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  CreateTableB_means(d %>% filter(!is.na(get(myFields[i]))) %>% filter(as.numeric(get(gsub("3", "2", myFields[i])))==2), myFields[i])
}
CreateFlex(LabelResponses(op,l))
```

<!---CHUNK_PAGEBREAK--->


### Angler Motivations

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, sep="")`

```{r }
myFields<-d %>% dplyr::select(contains("C2")) %>% select(-contains("Answered")) %>% names()
CreateFlex(SubstitueQuesForResponse(CreateTableA_means(d, myFields), q, C2, 2025))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, sep="")`

```{r}
CreateFlex(SubstitueQuesForResponse(CreateTableB_means(d, myFields), q, C2, 2025))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, sep="")`

```{r }
myFields<-c("motivation_pp","motivation_natural", "motivation_social","motivation_resource")
op<-foreach(i=myFields, .combine="rbind") %do% {
  CreateTableA_means(d %>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), i)
}
CreateFlex(LabelResponses(op,l))
```

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, sep="")`

```{r}
op<-foreach(i=myFields, .combine="rbind") %do% {
  CreateTableB_means(d %>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), i)
}
CreateFlex(LabelResponses(op,l))
```

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, sep="")`

```{r}
myFields<-c("motivation_noncatch","motivation_catch")
op<-foreach(i=myFields, .combine="rbind") %do% {
  CreateTableA_means(d %>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), i)
}
CreateFlex(LabelResponses(op,l))
```

`r paste(trimws(GetQuestion(q, C2, 2025)), "  ", caption.means, "  ", labels.importance, "  ", caption.raked, sep="")`

```{r}
op<-foreach(i=myFields, .combine="rbind") %do% {
  CreateTableB_means(d %>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), i)
}
CreateFlex(LabelResponses(op,l))
```

<!---CHUNK_PAGEBREAK--->

### Angler Attitudes

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.reversed, "  ", caption.raked, sep="")`

```{r E1}
myFields<-d %>% dplyr::select(contains("E1")) %>% select(-contains("Answered")) %>% names()
CreateFlex(MarkReversedItems(SubstitueQuesForResponse(CreateTableA_means(d, myFields), q, E1, 2025), q, 2025))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.reversed, "  ", caption.raked, sep="")`

```{r}
CreateFlex(MarkReversedItems(SubstitueQuesForResponse(CreateTableB_means(d, myFields), q, E1, 2025), q, 2025))
```

<!---CHUNK_PAGEBREAK--->

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.raked, sep="")`

```{r }
myFields<-c("attitude_catch", "attitude_numbers", "attitude_size", "attitude_harvest")

op<-foreach(i=myFields, .combine="rbind") %do% {
  CreateTableA_means(d %>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), i)
}
CreateFlex(LabelResponses(op,l))

```

`r paste(trimws(GetQuestion(q, E1, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.raked, sep="")`

```{r}
op<-foreach(i=myFields, .combine="rbind") %do% {
  CreateTableB_means(d %>% filter(get(paste(i,"_AnsweredAll", sep=""))==TRUE), i)
}
CreateFlex(LabelResponses(op,l))
```

<!---CHUNK_PAGEBREAK--->


### Gender

`r paste(trimws(GetQuestion(q, E2, 2025)),"  ", caption.percents, "  ", sep="") `

```{r }
CreateFlex(CreateTableA_selectOne_percent(d %>% mutate(postWeight = 1), E2))
```

`r paste(trimws(GetQuestion(q, E2, 2025)),"  ", caption.percents, sep="")`

```{r}
CreateFlex(CreateTableB_selectOne_percent(d %>% mutate(postWeight = 1), E2))
```

### Age

`r paste(trimws(GetQuestion(q, E3, 2025)),"  ", caption.percents, sep="") `

```{r }
CreateFlex(CreateTableA_selectOne_percent(d %>% mutate(postWeight = 1), E3))
```

`r paste(trimws(GetQuestion(q, E3, 2025)),"  ", caption.percents, sep="") `

```{r }
CreateFlex(CreateTableB_selectOne_percent(d %>% mutate(postWeight = 1), E3))
```

<!---CHUNK_PAGEBREAK--->


