---
#title: "2025 Licensed Angler Survey Regulation Questions"
#date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  officedown::rdocx_document:
    toc: true
  #word_document: default
always_allow_html: yes
---

```{r setup, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, fig.width=7.5, fig.height=7}
knitr::opts_chunk$set(echo=FALSE, include=TRUE, warning=FALSE, error=FALSE, message=FALSE,  ft.align="left")
library(tictoc)
tic("Report Took ")
options(stringsAsFactors = FALSE)
#devtools::install_github("davidgohel/officer")
#devtools::install_github("davidgohel/officedown")
library(officedown)
library(rmarkdown)
library(tidyverse)
library(knitr)
library(flextable)
library(stringr)
library(likert)

setwd("D:/Survey/Analysis/CrossTabTables/")

source("..\\BaseFunctions_2025_UPDATED.R") #load file of common functions
source("CrossTabTableFunctions.R") #load file of cross tab report functions
```


```{r getData, echo=FALSE}
setwd("D:/Survey/Analysis/CrossTabTables/")

#load data
load(file="../../Data/DataAggregation1/aggregateData_20260624.rData")
d<-d %>% filter(surveyYear==2025)
# Rebuild scale/subscale scores from raw item factors, applying reversals
# flagged in Scales.csv (single source of truth) at report time.
d <- add_scale_scores(d)
#q<-base.loaddata.factorlevels()
#save(q, file="q_20190802")
#load(file="../../2018 Statewide Survey/Analysis/Rscripts/CrossTabTables/q_20190802")
q<-read.csv(file="../../Data/DataAggregation1/FactorLevels_aggregated.csv") %>% filter(Year==2025)
l=read.csv(file="../../Data/DataAggregation1/Labels.csv")

```

```{r createFunctions}
CreateFlex<-function(x, mergeOnFirst=FALSE, firstColLabel=FALSE) {
  require(officer)
  require(flextable)
  
  bigborder=officer:: fp_border(color="black", width = 1.5)
  smallborder=officer:: fp_border(color="black", width=1.0)
  # width for the leading column: narrow when it holds a short item label
  w1 <- if (firstColLabel) 0.4 else 1.2
  
  myFlex<-  flextable(x) %>%
    theme_zebra()
  
  if(mergeOnFirst==TRUE) {
    #merge first column cells  
    myFlex <-myFlex %>%
        merge_v(j=1, part="body") 
      #when a short label leads, also merge the adjacent wording column
      if (firstColLabel) {
        myFlex <- myFlex %>% merge_v(j=2, part="body")
      }
      #add border below merged cells in first column
      myFlex<-myFlex %>%
        border(border.bottom = smallborder, i=rle(cumsum(myFlex$body$spans$columns[,1] ))$values, part="body") 
  }
  
  myFlex <- myFlex %>%
    #border_outer(officer:: fp_border(color="black", width = 1.5), part="all") %>%
    #add border above and below footer
    border(border.bottom = bigborder, border.top = bigborder, part = "header") %>%
    #add border at bottom of body
    border(border.bottom = bigborder, i=nrow(myFlex$body$spans$rows), part = "body") %>%
    padding(j=1, padding.left=3) %>%
    flextable::align(align="left", part="all") %>%
    fontsize(part = "header", size = 10) %>%
    fontsize(part="body", size=8) %>%
    bold(part="header") %>%
    #autofit() %>%
    width(j = 1, width = w1) %>%
    set_table_properties(layout = "autofit", width = 1)

  # widen the wording column when a short label column leads
  if (firstColLabel) {
    myFlex <- myFlex %>% width(j = 2, width = 1.2)
  }

      
  myFlex
}


```

`r officer::run_pagebreak()`
# Introduction

The use of harvest regulations is one of the most-commonly used management tools in the management of sport fisheries.  Harvest regulations can be applied to fisheries over a region-wide or state-wide scale, or they can be applied to specific waterbodies or fisheries in a site-specific manner.  While site-specific regulations are often more effective at addressing local concerns, region-wide and state-wide regulations can provide consistency and broader management benefits.  Fisheries managers, adminstrators, and the general public often disagree on the best mix of wide-scale and site-specific regulations due to percieved complexity, compliance, enforcement, and other social issues.  The 2025 Statwide License Angler Survey (LAS) included a series of questions that were designed to assess angler attitudes toward the use of harvest regulations, particularly among different spatial scales (see Appendix A for the full list of questions).

These questions were designed to cover a range of opinions and attitudes towards regulations.  As the questions are new and under their first iteration of use, no a priori scale structure was imposed on the questions.  The following report describes the development of a scale structure for the regulation questions, the reliability of the resulting scales, and the relationship of the scale results to other survey parameters.

`r officer::run_pagebreak()`
# Methods

Logistic implementation of the 2025 LAS is described in Bosr (2026).  Analysis of survey returns, response bias, and weight stratigies is found in Hurley (2026).  The twelve regulation items (Items A–L) were administered as a single block of 5-point statements with responses of: 1 = Strongly disagree, 2 = Slightly disagree, 3 = Neither agree nor disagree, 4 = Slightly agree, and 5 = Strongly agree (Appendix ???). The questions were written as balanced between three scale constructs including multi-directionality.  However, this analysis treats the list of items without an a priori scale structure.  Any reversal of answer directionality is determined by survey responses and scale development analysis.

## Scale development

```{r regdev_setup, include=FALSE}
library(psych)
library(lavaan)
library(nnet)
library(car)
library(patchwork)
library(survey)

reg_items <- paste0("Q31", letters[1:12])

# Numeric 1-5 item matrix and complete-case subset
reg_num <- as.data.frame(lapply(d[reg_items], as.integer))
names(reg_num) <- reg_items
cc        <- stats::complete.cases(reg_num)
reg_cc    <- reg_num[cc, ]
n_total   <- nrow(reg_num)
n_cc      <- nrow(reg_cc)
pct_cc    <- round(100 * n_cc / n_total, 1)

# Item wording lookup
item_text <- q %>%
  dplyr::filter(grepl("^Q31[a-z]$", Field)) %>%
  dplyr::distinct(Field, Question)
lab <- function(f) item_text$Question[match(f, item_text$Field)]

# Scale definitions (empirical)
comp_i <- c("Q31e", "Q31g", "Q31h")
site_i <- c("Q31j", "Q31k", "Q31l")
unif_i <- c("Q31a", "Q31b", "Q31d", "Q31f", "Q31i")

# ---- Factorability & polychoric correlations ----
Rpoly <- polychoric(reg_cc)$rho
kmo   <- KMO(Rpoly)
bart  <- cortest.bartlett(Rpoly, n = n_cc)

# ---- Parallel analysis (number retained) ----
set.seed(4127)
pa <- fa.parallel(Rpoly, n.obs = n_cc, fa = "fa", fm = "ml", plot = FALSE)
n_fact <- pa$nfact

# ---- 3-factor EFA ----
fa3 <- fa(Rpoly, nfactors = 3, fm = "ml", rotate = "oblimin", n.obs = n_cc)
L   <- unclass(fa3$loadings)
# Map statistical factors to substantive scales by representative items
f_comp <- which.max(abs(L["Q31h", ]))
f_site <- which.max(abs(L["Q31k", ]))
f_unif <- which.max(abs(L["Q31d", ]))
fa_fit_tli   <- round(fa3$TLI, 3)
fa_fit_rmsea <- round(fa3$RMSEA[1], 3)

# ---- Reliability per scale ----
rel_one <- function(items) {
  a  <- psych::alpha(reg_cc[, items], warnings = FALSE)
  om <- tryCatch(suppressWarnings(
          psych::omega(reg_cc[, items], nfactors = 1, plot = FALSE,
                       poly = TRUE)$omega.tot), error = function(e) NA_real_)
  list(alpha = a$total$raw_alpha, omega = om, item = a$item.stats$r.drop,
       drop = a$alpha.drop$raw_alpha)
}
rel_comp <- rel_one(comp_i)
rel_site <- rel_one(site_i)
rel_unif <- rel_one(unif_i)

# ---- CFA: 1-factor (bipolar) vs 2-factor (correlated) on 8 policy items ----
pol_i <- c(unif_i, site_i)
pol   <- reg_cc[, pol_i]
pol[] <- lapply(pol, ordered)
m1 <- paste("policy =~", paste(pol_i, collapse = " + "))
m2 <- paste0("uniform =~ ", paste(unif_i, collapse = " + "), "\n",
             "site =~ ",    paste(site_i, collapse = " + "))
fit1 <- cfa(m1, data = pol, estimator = "WLSMV", ordered = pol_i)
fit2 <- cfa(m2, data = pol, estimator = "WLSMV", ordered = pol_i)
fm <- function(fit) fitMeasures(fit,
  c("cfi.scaled","tli.scaled","rmsea.scaled","srmr"))
fm1 <- fm(fit1); fm2 <- fm(fit2)
lrt <- lavTestLRT(fit1, fit2, method = "satorra.2000")
latcor <- lavInspect(fit2, "cor.lv")["uniform", "site"]

# ---- Composite (bipolar) scale & scores ----
comprehension <- rowMeans(reg_cc[, comp_i])
site_score    <- rowMeans(reg_cc[, site_i])
uniform_score <- rowMeans(reg_cc[, unif_i])
orientation   <- rowMeans(cbind(6 - reg_cc[, unif_i], reg_cc[, site_i]))
alpha_orient  <- psych::alpha(cbind(6 - reg_cc[, unif_i], reg_cc[, site_i]),
                              warnings = FALSE)$total$raw_alpha

# ---- Analysis frame with demographics / covariates / weights ----
af <- data.frame(
  comprehension, site_score, uniform_score, orientation,
  Resi    = d$Resi[cc],
  gender  = d$E2[cc],
  Age     = d$Age[cc],
  avidity = suppressWarnings(as.numeric(as.character(d$C1Total_days[cc]))),
  B1      = as.character(d$B1[cc]),
  postWeight = d$postWeight[cc],
  stringsAsFactors = FALSE
)
af$avidity_log <- log1p(af$avidity)
af$quadrant <- factor(dplyr::case_when(
  af$uniform_score >  3 & af$site_score >  3 ~ "Wants both",
  af$uniform_score <= 3 & af$site_score >  3 ~ "Site-specific only",
  af$uniform_score >  3 & af$site_score <= 3 ~ "Statewide only",
  TRUE                                       ~ "Neither"),
  levels = c("Statewide only","Neither","Wants both","Site-specific only"))
af$wants_both <- ifelse(af$quadrant == "Wants both", "Wants both", "Other")

top_fish <- c("Walleye / Sauger","Largemouth bass","Crappie","Channel catfish",
              "Trout","I do not prefer any particular type of fish")
af$fishpref <- dplyr::case_when(
  is.na(af$B1)          ~ "Missing",
  af$B1 %in% top_fish   ~ af$B1,
  TRUE                  ~ "Other species")
af$fishpref <- relevel(factor(af$fishpref),
                       ref = "I do not prefer any particular type of fish")

# ---- Demographic association tests (Wants both vs rest) ----
cram_v <- function(tb) {
  x <- suppressWarnings(chisq.test(tb))
  v <- sqrt(as.numeric(x$statistic) / (sum(tb) * (min(dim(tb)) - 1)))
  list(chi = as.numeric(x$statistic), df = x$parameter, p = x$p.value, v = v)
}
res_t <- cram_v(table(af$wants_both, af$Resi))
gen_t <- cram_v(table(af$wants_both, af$gender))
age_w <- wilcox.test(Age ~ wants_both, data = af)
n1 <- sum(af$wants_both == "Wants both" & !is.na(af$Age))
n0 <- sum(af$wants_both == "Other" & !is.na(af$Age))
age_rrb <- (2 * as.numeric(age_w$statistic) / (n1 * n0)) - 1   # rank-biserial
age_med <- tapply(af$Age, af$wants_both, median, na.rm = TRUE)

# ---- Multinomial: quadrant ~ comprehension (+ covariates) ----
af$quadrant <- relevel(af$quadrant, ref = "Wants both")
m_base <- multinom(quadrant ~ comprehension, data = af, trace = FALSE)
m_full <- multinom(quadrant ~ comprehension + avidity_log + fishpref,
                   data = af, trace = FALSE)
an_base <- car::Anova(m_base)
an_full <- car::Anova(m_full)
or_tab <- data.frame(
  Contrast = paste(rownames(coef(m_base)), "vs Wants both"),
  OR_unadjusted = round(exp(coef(m_base)[, "comprehension"]), 2),
  OR_adjusted   = round(exp(coef(m_full)[, "comprehension"]), 2),
  row.names = NULL)
ci_base <- exp(confint(m_base)["comprehension", , ])
or_tab$CI95 <- apply(round(t(ci_base), 2), 1,
                     function(z) sprintf("[%.2f, %.2f]", z[1], z[2]))

# ---- Weighted quadrant prevalence (design-based) ----
af$quadrant <- factor(af$quadrant,
  levels = c("Site-specific only","Wants both","Statewide only","Neither"))
des <- svydesign(ids = ~1, weights = ~postWeight,
                 data = af[!is.na(af$postWeight), ])
wp  <- svymean(~quadrant, des)
wci <- confint(wp)
wtab <- data.frame(
  Quadrant = levels(af$quadrant),
  `Unweighted %` = round(100 * as.numeric(prop.table(table(af$quadrant))), 1),
  `Weighted %`   = round(100 * as.numeric(coef(wp)), 1),
  `95% CI`       = sprintf("[%.1f, %.1f]", 100*wci[,1], 100*wci[,2]),
  check.names = FALSE, row.names = NULL)
```

Analyses used `r format(n_cc, big.mark=",")` of `r format(n_total, big.mark=",")`
2025 LAS respondents (`r pct_cc`%) who answered all twelve items. Per-item nonresponse was modest and uniform (11–13%), consistent with incidental item skipping rather than structured
non-response. Because the items are ordinal, all correlational and
factor-analytic steps used polychoric correlations. Item and scale structure was explored unweighted, on the rationale that measurement structure is a property of the instrument rather than of the survey response composition.  Appriopiate per-respondant survey weighting is used only for the population-level estimates and comparisons (post-stratified on age group and residency).

# Results

## Dimensionality and the three-scale solution

Before extraction, the correlation matrix was checked for factorability. The
Kaiser–Meyer–Olkin measure of sampling adequacy was
**`r round(kmo$MSA, 2)`**, with all per-item values ≥
`r round(min(kmo$MSAi), 2)`. By Kaiser's conventional benchmarks (< 0.50
unacceptable, 0.70–0.80 middling, 0.80–0.90 *meritorious*, > 0.90 marvelous),
the battery is comfortably in the meritorious range. Bartlett's test of
sphericity rejected the identity-matrix null
(χ²(`r bart$df`) = `r format(round(bart$chisq), big.mark=",")`,
*p* < .001), confirming sufficient common variance to factor.

Horn's parallel analysis—which retains factors whose eigenvalues exceed those
from random data of equivalent dimensions—indicated **`r n_fact` factors**.
The polychoric inter-item correlations (Figure 1) show the same three blocks
visually, and, notably, the policy items split by direction: the
statewide/simplification items correlate positively among themselves and
negatively with the site-specific items.

```{r regdev_heatmap, fig.cap="Figure 1. Polychoric inter-item correlations among the twelve regulation items.", fig.width=7.5, fig.height=6.5}
as.data.frame(Rpoly) |>
  tibble::rownames_to_column("item1") |>
  tidyr::pivot_longer(-item1, names_to = "item2", values_to = "r") |>
  ggplot(aes(item1, item2, fill = r)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%.2f", r)), size = 2.5) +
  scale_fill_gradient2(low = "#2166ac", mid = "white", high = "#b2182b",
                       midpoint = 0, limits = c(-1, 1)) +
  labs(x = NULL, y = NULL, fill = "r") +
  theme_minimal(base_size = 11) +
  theme(panel.grid = element_blank())
```

A three-factor model was estimated by maximum likelihood with oblique (oblimin)
rotation, allowing the factors to correlate. The rotated pattern (Table 1) is
simple and interpretable: eleven of twelve items load saliently
(|loading| ≥ .40) on exactly one factor, with no consequential cross-loadings.
The factors correspond to **regulation comprehension/confidence**
(Items E, G, H), **site-specific support** (Items J, K, L), and
**statewide/simplification preference** (Items A, B, D, F, I).

```{r regdev_loadings}
fac_idx  <- c(f_comp, f_site, f_unif)
ord_items <- c(comp_i, site_i, unif_i)
load_tbl <- data.frame(
  Item = lab(ord_items),
  Comprehension = round(L[ord_items, f_comp], 2),
  `Site-specific` = round(L[ord_items, f_site], 2),
  `Statewide` = round(L[ord_items, f_unif], 2),
  h2 = round(fa3$communality[ord_items], 2),
  check.names = FALSE)
for (j in 2:4) load_tbl[abs(load_tbl[[j]]) < .30, j] <- NA
CreateFlex(load_tbl)
```

*Table 1. Oblimin-rotated maximum-likelihood factor loadings (loadings < .30
suppressed); h² = communality. ML extraction on the polychoric matrix.*

One item—**Item C** ("Anglers are willing to follow complex regulations to
produce high-quality fisheries")—failed to cohere with any factor (no loading
≥ .30; its largest polychoric correlation with any other item was 0.39). It
appears to tap a distinct notion of compliance willingness that the remaining
items do not, and retaining it would degrade rather than define a scale.
**Item C was therefore excluded from all scale scores** and is reported only at
the item level (above). The three-factor model accounted for
`r round(sum(fa3$Vaccounted["Proportion Var", ]) * 100)`% of the common
variance; overall approximate fit was acceptable for an exploratory solution
(TLI = `r fa_fit_tli`, RMSEA = `r fa_fit_rmsea`), with the residual misfit
attributable largely to the orphan item and a minor secondary loading on Item A.

## Reliability

Internal consistency was estimated with Cronbach's α and McDonald's ω
(Table 2). Conventionally, α ≥ .70 is considered acceptable and ≥ .80 good; ω
is reported alongside because it does not assume tau-equivalence and is the
preferred coefficient for congeneric items. All three scales meet or approach
the "good" threshold, and no item-deletion would materially raise any
coefficient, so all items were retained.

```{r regdev_reliability}
rel_tbl <- data.frame(
  Scale = c("Comprehension / confidence", "Site-specific support",
            "Statewide / simplification preference"),
  Items = c(length(comp_i), length(site_i), length(unif_i)),
  `Cronbach alpha` = round(c(rel_comp$alpha, rel_site$alpha, rel_unif$alpha), 3),
  `McDonald omega`  = round(c(rel_comp$omega, rel_site$omega, rel_unif$omega), 3),
  `Item-total r (range)` = c(
    sprintf("%.2f-%.2f", min(rel_comp$item), max(rel_comp$item)),
    sprintf("%.2f-%.2f", min(rel_site$item), max(rel_site$item)),
    sprintf("%.2f-%.2f", min(rel_unif$item), max(rel_unif$item))),
  check.names = FALSE)
CreateFlex(rel_tbl)
```

*Table 2. Internal-consistency reliability for the three derived scales.*

## Two correlated scales versus a single bipolar composite

Because the statewide and site-specific items are negatively related, a natural
question is whether the eight policy items measure **one** bipolar dimension
(statewide regulation at one pole, site-specificity at the other) or **two** distinct but
correlated dimensions. This was tested directly with confirmatory factor
analysis on the eight policy items, using the WLSMV estimator appropriate for
ordinal indicators, comparing a one-factor model against a two-factor
correlated model (Table 3).

```{r regdev_cfa}
cfa_tbl <- data.frame(
  Model = c("1-factor (bipolar)", "2-factor (correlated)"),
  CFI   = round(c(fm1["cfi.scaled"], fm2["cfi.scaled"]), 3),
  TLI   = round(c(fm1["tli.scaled"], fm2["tli.scaled"]), 3),
  RMSEA = round(c(fm1["rmsea.scaled"], fm2["rmsea.scaled"]), 3),
  SRMR  = round(c(fm1["srmr"], fm2["srmr"]), 3),
  row.names = NULL)
CreateFlex(cfa_tbl)
```

*Table 3. CFA fit for competing structures of the eight policy items
(WLSMV, robust/scaled indices).*

Against standard cutoffs (good fit: CFI/TLI ≥ .95, RMSEA ≤ .06, SRMR ≤ .08;
acceptable: CFI/TLI ≥ .90, RMSEA ≤ .08), the one-factor model fits poorly
(CFI = `r round(fm1["cfi.scaled"],2)`, RMSEA = `r round(fm1["rmsea.scaled"],2)`),
whereas the two-factor model is far better
(CFI = `r round(fm2["cfi.scaled"],2)`, RMSEA = `r round(fm2["rmsea.scaled"],2)`).
A robust scaled chi-square difference test strongly favors two factors
(Δχ²(`r lrt[2,"Df diff"]`) = `r format(round(lrt[2,"Chisq diff"]), big.mark=",")`,
*p* < .001). The disattenuated latent correlation between the two policy factors
is `r round(latcor, 2)`—substantial, but well short of the −1 a true single
bipolar axis would require (the two poles share only about
`r round(latcor^2 * 100)`% of their variance).

Because the indicators are ordinal and estimation used the mean- and
variance-adjusted WLSMV estimator, this difference test follows the Satorra
(2000) procedure—the appropriate robust correction for categorical-data
estimators; the more familiar Satorra–Bentler (2010) correction applies only to
continuous robust maximum likelihood (MLM/MLR) and is not valid here.

The practical consequence is visible when respondents are scored both ways
(Figure 2). Under the two-scale framing (left), the data do not collapse onto
the anti-diagonal that a pure bipolar dimension implies; a large group scores
high on **both** scales. The single reversed composite (right), though
internally consistent (α = `r round(alpha_orient, 2)`), averages these
respondents toward the middle and conceals that pattern.

```{r regdev_framing, fig.cap="Figure 2. Two-scale framing (left) versus single reversed composite (right). Red line marks where a strictly bipolar dimension would place respondents.", fig.width=7.5, fig.height=4}
pA <- ggplot(af, aes(uniform_score, site_score)) +
  geom_jitter(width = .12, height = .12, alpha = .12, size = .8) +
  geom_hline(yintercept = 3, linetype = 2, colour = "grey40") +
  geom_vline(xintercept = 3, linetype = 2, colour = "grey40") +
  geom_abline(slope = -1, intercept = 6, colour = "#b2182b") +
  labs(title = "Two-scale framing",
       x = "Statewide preference (mean)", y = "Site-specific support (mean)") +
  theme_minimal(base_size = 10)
pB <- ggplot(af, aes(orientation)) +
  geom_histogram(binwidth = .25, fill = "grey50", colour = "white") +
  geom_vline(xintercept = 3, linetype = 2, colour = "grey40") +
  labs(title = "Single composite framing",
       subtitle = "Higher = pro site-specific",
       x = "Site-specific orientation (8-item mean)", y = "Anglers") +
  theme_minimal(base_size = 10)
pA + pB
```

**Recommendation.** The evidence supports retaining **two correlated policy
scales** rather than a single composite. Beyond the statistical case, the
two-scale representation preserves the most managerially interesting group—the
anglers who simultaneously value local tailoring and worry about complexity—who
are otherwise erased. The composite remains available (encoded as
`reg_orientation`) for occasions that call for a single summary number, with the
caveat that it compresses a genuinely two-dimensional attitude.

# Discussion

## Self-rated comprehension and the policy quadrants

To connect the comprehension scale to the policy debate, respondents were
cross-classified at the scale midpoints (3.0) into four quadrants: *Site-specific
only*, *Statewide only*, *Wants both* (high on both), and *Neither* (low on both).
A multinomial logistic regression predicting quadrant membership from
comprehension (Table 4, Figure 3) shows a strong, monotonic gradient
(likelihood-ratio χ²(`r an_base["comprehension","Df"]`) =
`r round(an_base["comprehension","LR Chisq"], 1)`, *p* < .001).

```{r regdev_multinom}
CreateFlex(or_tab[, c("Contrast","OR_unadjusted","CI95")])
```

*Table 4. Odds ratios for a one-point increase in comprehension, relative to the
"Wants both" reference group.*

```{r regdev_box, fig.cap="Figure 3. Regulation comprehension by policy quadrant (red point = mean).", fig.width=7, fig.height=4.5}
af |>
  dplyr::mutate(quad = factor(quadrant,
    levels = c("Statewide only","Neither","Wants both","Site-specific only"))) |>
  ggplot(aes(quad, comprehension)) +
  geom_boxplot(outlier.alpha = .15, width = .5) +
  stat_summary(fun = mean, geom = "point", colour = "#b2182b", size = 2) +
  labs(x = NULL, y = "Comprehension / confidence (mean of Items E, G, H)") +
  theme_minimal(base_size = 11)
```

Each one-point rise in comprehension nearly doubles the odds of being
*Site-specific only* rather than *Wants both*
(OR = `r or_tab$OR_unadjusted[or_tab$Contrast=="Site-specific only vs Wants both"]`)
and sharply lowers the odds of being *Statewide only*
(OR = `r or_tab$OR_unadjusted[or_tab$Contrast=="Statewide only vs Wants both"]`).
**For managers and administrators, this is the actionable finding:** support for
the more complex, locally tailored regulatory approach rises with anglers'
confidence that they understand the rules. Investments that make regulations
easier to find, read, and apply are therefore not merely a customer-service
nicety—they plausibly expand the constituency comfortable with the
site-specific management that biologists often need. The relationship is
cross-sectional and should not be read causally, but its size and consistency
make comprehension a natural lever to monitor and test.

## Fishing avidity and species preference

A reasonable concern is that the comprehension–policy link is a by-product of
how much or what people fish. Adding fishing avidity (log of total days fished
in 2025) and target-species preference to the model leaves the comprehension
effect essentially unchanged (Table 5): the adjusted odds ratios match the
unadjusted ones to two decimals, and comprehension remains the dominant term
(LR χ²(`r an_full["comprehension","Df"]`) =
`r round(an_full["comprehension","LR Chisq"], 1)`, *p* < .001).

```{r regdev_adjust}
CreateFlex(or_tab[, c("Contrast","OR_unadjusted","OR_adjusted")])
```

*Table 5. Comprehension odds ratios before and after adjusting for avidity and
species preference.*

The two covariates behave differently from one another. Fishing avidity is
**not** associated with policy quadrant
(LR χ²(`r an_full["avidity_log","Df"]`) =
`r round(an_full["avidity_log","LR Chisq"], 1)`,
*p* = `r round(an_full["avidity_log","Pr(>Chisq)"], 2)`): how often an angler
fishes does not predict where they stand. Species preference **is** associated
(LR χ²(`r an_full["fishpref","Df"]`) =
`r round(an_full["fishpref","LR Chisq"], 1)`, *p* < .001), though the practical
differences are modest; most groups fall within a few points of one another.
The clearest departure is among **trout anglers**, who lean toward statewide regulation
more than other groups—a pattern worth noting for managers given the
site-specific nature of much of Nebraska's trout management.

Demographically, the "wants both" segment is unremarkable. It does not differ
from other anglers in residency
(χ²(`r res_t$df`) = `r round(res_t$chi, 2)`,
*p* = `r round(res_t$p, 2)`; Cramér's *V* = `r round(res_t$v, 3)`) or gender
(χ²(`r gen_t$df`) = `r round(gen_t$chi, 2)`,
*p* = `r round(gen_t$p, 2)`; *V* = `r round(gen_t$v, 3)`), and is only
trivially older (median `r age_med["Wants both"]` vs `r age_med["Other"]` years;
Wilcoxon *p* = `r round(age_w$p.value, 3)`, rank-biserial *r* =
`r round(age_rrb, 2)`). The ambivalence is broad-based rather than confined to
any subgroup, which argues against treating it as a niche position.

## Standalone Item C

Item C ("Anglers are willing to follow complex regulations to produce
high-quality fisheries") was excluded from the scales because it failed to load
cleanly on any factor. Its behavior is nonetheless informative, and because it
speaks to a stated *behavioral* willingness rather than a policy preference, it
is worth examining as an external correlate of the derived scales.

```{r regdev_q31c}
af$Q31c <- reg_cc$Q31c
q31c_tab <- af |>
  dplyr::group_by(quadrant) |>
  dplyr::summarise(n = dplyr::n(),
                   Mean = round(mean(Q31c), 2),
                   SD = round(sd(Q31c), 2), .groups = "drop") |>
  dplyr::arrange(dplyr::desc(Mean))
kw <- kruskal.test(Q31c ~ quadrant, data = af)
sp <- sapply(af[c("comprehension","site_score","uniform_score","orientation")],
             function(x) round(cor(af$Q31c, x, method = "spearman"), 2))
CreateFlex(as.data.frame(q31c_tab))
```

*Table 7. Mean agreement with Item C by policy quadrant (1 = strongly disagree,
5 = strongly agree).*

Agreement with Item C is unevenly distributed across the quadrants
(Kruskal-Wallis χ²(`r kw$parameter`) = `r round(kw$statistic, 1)`, *p* < .001;
Figure 5). It is highest among the *Site-specific only* group
(`r q31c_tab$Mean[q31c_tab$quadrant=="Site-specific only"]`) and lowest among
the *Statewide only* group
(`r q31c_tab$Mean[q31c_tab$quadrant=="Statewide only"]`). Consistent with this,
Item C correlates positively with both the comprehension scale
(Spearman ρ = `r sp["comprehension"]`) and the site-specific support scale
(ρ = `r sp["site_score"]`), and weakly negatively with statewide preference
(ρ = `r sp["uniform_score"]`).

```{r regdev_q31c_fig, fig.cap="Figure 5. Mean agreement with Item C by policy quadrant (bars are 95% confidence intervals).", fig.width=7, fig.height=4}
af |>
  dplyr::mutate(quad = factor(quadrant,
    levels = c("Statewide only","Neither","Wants both","Site-specific only"))) |>
  dplyr::group_by(quad) |>
  dplyr::summarise(m = mean(Q31c), se = sd(Q31c)/sqrt(dplyr::n()),
                   .groups = "drop") |>
  ggplot(aes(quad, m)) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = m - 1.96*se, ymax = m + 1.96*se), width = .15) +
  labs(x = NULL, y = "Mean agreement with Item C (1-5)") +
  theme_minimal(base_size = 11)
```

This dual association explains why Item C resisted assignment to a single factor:
it draws simultaneously on feeling competent with the rules and on valuing
locally tailored management, the two constructs that the exploratory analysis
kept distinct. Substantively, Item C functions less like a scale indicator than
like a downstream attitude the scales help account for. **For managers, the
implication is direct and encouraging:** the anglers most willing to comply with
complex, site-specific rules in pursuit of better fishing are precisely those
who understand the regulations and already endorse tailored management. This
reinforces the earlier conclusion that improving regulatory comprehension is a
plausible route not only to broader acceptance of site-specific regulation but
to greater willingness to follow it. As with the other correlational results,
the cross-sectional design precludes causal claims.

## Population sizes of the quadrants

Finally, the quadrants were projected to the licensed-angler population using
the survey raking weights (post-stratified on age group and residency). A
design-based estimator (Taylor-linearized standard errors) yields the weighted
prevalences and 95% confidence intervals in Table 6 and Figure 4. Weighting
shifts the estimates only slightly relative to the raw sample, indicating that
attitude composition is not strongly confounded with the age/residency margins
used in raking.

```{r regdev_weighted}
CreateFlex(wtab)
```

*Table 6. Unweighted and weighted (raked) quadrant prevalence with design-based
95% confidence intervals.*

```{r regdev_wbar, fig.cap="Figure 4. Weighted population prevalence of the four policy quadrants (design-based 95% CIs).", fig.width=7, fig.height=4}
data.frame(Quadrant = factor(levels(af$quadrant), levels = levels(af$quadrant)),
           est = 100*as.numeric(coef(wp)),
           lo  = 100*wci[,1], hi = 100*wci[,2]) |>
  ggplot(aes(Quadrant, est)) +
  geom_col(fill = "grey55", width = .65) +
  geom_errorbar(aes(ymin = lo, ymax = hi), width = .2) +
  labs(x = NULL, y = "Weighted % of anglers") +
  theme_minimal(base_size = 11)
```

Roughly **`r round(wtab$"Weighted %"[wtab$Quadrant=="Site-specific only"])`%**
of Nebraska anglers endorse site-specific regulation without favoring
statewide regulation, while a comparable
**`r round(wtab$"Weighted %"[wtab$Quadrant=="Wants both"])`%** want both
simplicity and local tailoring. Only about
**`r round(wtab$"Weighted %"[wtab$Quadrant=="Statewide only"])`%** prefer
statewide regulation alone. For decision-makers, the headline is that outright opposition
to site-specific regulation is a minority position, but a plurality of anglers
hold the more nuanced "both" view—suggesting that communication emphasizing
*why* particular waters carry particular rules, paired with genuine effort to
keep the overall system legible, is likely to resonate more broadly than either
pure simplification or unexplained complexity.

## Limitations

Several limitations qualify these results. First, the data are
**cross-sectional**: comprehension, policy preference, and their correlates were
measured at a single point, so the associations reported here—most importantly
the comprehension–policy gradient—describe co-occurrence rather than cause.
Higher comprehension may foster openness to complexity, anglers predisposed
toward site-specific management may simply invest more in learning the rules, or
both may share a common driver such as engagement or experience; this design
cannot adjudicate among them. Second, target-species preference (B1) was
**missing for roughly 31% of the analytic sample**. Missing cases were retained
as their own category to preserve power and avoid list-wise loss, but if that
missingness is related to species choice the fish-preference estimates could be
biased; the central comprehension finding does not depend on B1 and is
unaffected. Third, the analysis rests on a **single survey year (2025)**, so the
scale structure and prevalence estimates should be treated as provisional;
confirmatory cross-validation in a future administration would be needed to
establish measurement invariance over time and confirm the three-factor
solution is stable rather than sample-specific. Finally, scale scores were
formed as unit-weighted item means, a deliberate and transparent simplification
rather than latent-variable scores; modest departures from equal item weighting
would not materially change the substantive conclusions.

# Implications

#Appendices

`r paste(trimws(GetQuestion(q, Q31, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.reversed, "  ", caption.raked, sep="")`

```{r Q31_percentA}
myFields<-d %>% dplyr::select(contains("Q31")) %>% select(-contains("Answered")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  tempD<-data.frame(Item=myFields[i], CreateTableA_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
  tempD$ItemLetter<-toupper(sub("^Q31", "", myFields[i]))
  tempD<-SubstitueQuesForResponse(tempD,q, !!rlang::sym(myFields[i]), 2025, responseField="Item")
}
op<-MarkReversedItems(op, q, 2025, responseField="Item")
op<-op %>% dplyr::rename(Statement = Item, Item = ItemLetter) %>% dplyr::relocate(Item, Statement)
CreateFlex(op, mergeOnFirst = TRUE, firstColLabel = TRUE)
```

`r paste(trimws(GetQuestion(q, Q31, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.reversed, "  ", caption.raked, sep="")`

```{r Q31_percentB}
myFields<-d %>% dplyr::select(contains("Q31")) %>% select(-contains("Answered")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  tempD<-data.frame(Item=myFields[i], CreateTableB_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
  tempD$ItemLetter<-toupper(sub("^Q31", "", myFields[i]))
  tempD<-SubstitueQuesForResponse(tempD,q, !!rlang::sym(myFields[i]), 2025, responseField="Item")
}
op<-MarkReversedItems(op, q, 2025, responseField="Item")
op<-op %>% dplyr::rename(Statement = Item, Item = ItemLetter) %>% dplyr::relocate(Item, Statement)
CreateFlex(op, mergeOnFirst = TRUE, firstColLabel = TRUE)
```

`r paste(trimws(GetQuestion(q, Q31, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.reversed, "  ", caption.raked, sep="")`

```{r Q31_means}
myFieldsQ31<-d %>% dplyr::select(contains("Q31")) %>% select(-contains("Answered")) %>% names()
tblA<-CreateTableA_means(d, myFieldsQ31)
tblA$Item<-toupper(sub("^Q31", "", as.character(tblA$Response)))
tblA<-SubstitueQuesForResponse(tblA, q, Q31, 2025)
tblA<-MarkReversedItems(tblA, q, 2025)
tblA<-tblA %>% dplyr::rename(Statement = Response) %>% dplyr::relocate(Item, Statement)
CreateFlex(tblA, firstColLabel = TRUE)
```


`r paste(trimws(GetQuestion(q, Q31, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.reversed, "  ", caption.raked, sep="")`

```{r}
tblB<-CreateTableB_means(d, myFieldsQ31)
tblB$Item<-toupper(sub("^Q31", "", as.character(tblB$Response)))
tblB<-SubstitueQuesForResponse(tblB, q, Q31, 2025)
tblB<-MarkReversedItems(tblB, q, 2025)
tblB<-tblB %>% dplyr::rename(Statement = Response) %>% dplyr::relocate(Item, Statement)
CreateFlex(tblB, firstColLabel = TRUE)
```
