---
#title: "2025 Licensed Angler Survey Regulation Questions"
#date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  officedown::rdocx_document:
    #reference_docx: double_spaced_template.docx
    toc: true
  #word_document: default
always_allow_html: yes
---

```{r setup, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, fig.width=7.5, fig.height=7}

knitr::opts_chunk$set(echo=FALSE, include=TRUE, warning=FALSE, error=FALSE, message=FALSE,  ft.align="left")
library(tictoc)
tic("Report Took ")
options(stringsAsFactors = FALSE)

#devtools::install_github("davidgohel/officer")

#devtools::install_github("davidgohel/officedown")

library(officedown)
library(rmarkdown)
library(tidyverse)
library(knitr)
library(flextable)
library(stringr)
library(likert)

setwd("D:/Survey/Analysis/CrossTabTables/")

source("..\\BaseFunctions_2025_UPDATED.R") #load file of common functions
source("CrossTabTableFunctions.R") #load file of cross tab report functions

```

```{r getData, echo=FALSE}

setwd("D:/Survey/Analysis/CrossTabTables/")

#load data

load(file="../../Data/DataAggregation1/aggregateData_20260624.rData")
d<-d %>% filter(surveyYear==2025)

# Rebuild scale/subscale scores from raw item factors, applying reversals

# flagged in Scales.csv (single source of truth) at report time.

d <- add_scale_scores(d)

#q<-base.loaddata.factorlevels()

#save(q, file="q_20190802")

#load(file="../../2018 Statewide Survey/Analysis/Rscripts/CrossTabTables/q_20190802")

q<-read.csv(file="../../Data/DataAggregation1/FactorLevels_aggregated.csv") %>% filter(Year==2025)
l=read.csv(file="../../Data/DataAggregation1/Labels.csv")

```

```{r createFunctions}

CreateFlex<-function(x, mergeOnFirst=FALSE, firstColLabel=FALSE) {
  require(officer)
  require(flextable)

  bigborder=officer:: fp_border(color="black", width = 1.5)
  smallborder=officer:: fp_border(color="black", width=1.0)
  # width for the leading column: narrow when it holds a short item label
  w1 <- if (firstColLabel) 0.4 else 1.2

  myFlex<-  flextable(x) %>%
    theme_zebra()

  if(mergeOnFirst==TRUE) {
    #merge first column cells
    myFlex <-myFlex %>%
        merge_v(j=1, part="body")
      #when a short label leads, also merge the adjacent wording column
      if (firstColLabel) {
        myFlex <- myFlex %>% merge_v(j=2, part="body")
      }
      #add border below merged cells in first column
      myFlex<-myFlex %>%
        border(border.bottom = smallborder, i=rle(cumsum(myFlex$body$spans$columns[,1] ))$values, part="body")
  }

  myFlex <- myFlex %>%
    #border_outer(officer:: fp_border(color="black", width = 1.5), part="all") %>%
    #add border above and below footer
    border(border.bottom = bigborder, border.top = bigborder, part = "header") %>%
    #add border at bottom of body
    border(border.bottom = bigborder, i=nrow(myFlex$body$spans$rows), part = "body") %>%
    padding(j=1, padding.left=3) %>%
    flextable::align(align="left", part="all") %>%
    fontsize(part = "header", size = 10) %>%
    fontsize(part="body", size=8) %>%
    bold(part="header") %>%
    #autofit() %>%
    width(j = 1, width = w1) %>%
    set_table_properties(layout = "autofit", width = 1)

  # widen the wording column when a short label column leads
  if (firstColLabel) {
    myFlex <- myFlex %>% width(j = 2, width = 1.2)
  }

  myFlex
}

```

`r officer::run_pagebreak()`

# Introduction

The use of harvest regulations is one of the most-commonly used tools in the management of sport fisheries.  Harvest regulations can be applied to fisheries over a region-wide or state-wide scale, or they can be applied to specific waterbodies or fisheries in a site-specific manner.  While site-specific regulations are often more effective at addressing local concerns, region-wide and state-wide regulations can provide consistency and broader management benefits.  Fisheries managers, adminstrators, and the general public often disagree on the best mix of wide-scale and site-specific regulations due to percieved complexity, compliance, enforcement, and other social issues.  The 2025 Statwide License Angler Survey (LAS) included a series of questions that were designed to assess angler attitudes toward the use of harvest regulations, particularly among different spatial scales (see Appendix A for the full list of questions).

These questions were designed to cover a range of opinions and attitudes towards regulations.  As the questions are new and under their first iteration of use, no a priori scale structure was imposed on the questions.  The following report describes the development of a scale structure for the regulation questions, the reliability of the resulting scales, and the relationship of the scale results to other survey parameters.

`r officer::run_pagebreak()`

# Methods

Logistic implementation of the 2025 LAS is described in Bosr (2026).  Analysis of survey returns, response bias, and weighting stratigies are found in Hurley (2026).  The twelve regulation items (Items A–L) were administered as a single block of 5-point statements with responses of: 1 = Strongly disagree, 2 = Slightly disagree, 3 = Neither agree nor disagree, 4 = Slightly agree, and 5 = Strongly agree (Appendix A). The questions were written as balanced between three scale constructs including multi-directionality.  However, this analysis treats the list of items without an a priori scale structure.  Any reversal of answer directionality was determined by survey responses and the scale development analysis.

```{r regdev_setup, include=FALSE}

library(psych)
library(lavaan)
library(nnet)
library(car)
library(patchwork)
library(survey)

reg_items <- paste0("Q31", letters[1:12])

# Numeric 1-5 item matrix and complete-case subset

reg_num <- as.data.frame(lapply(d[reg_items], as.integer))
names(reg_num) <- reg_items
cc        <- stats::complete.cases(reg_num)
reg_cc    <- reg_num[cc, ]
n_total   <- nrow(reg_num)
n_cc      <- nrow(reg_cc)
pct_cc    <- round(100 * n_cc / n_total, 1)

# Item wording lookup

item_text <- q %>%
  dplyr::filter(grepl("^Q31[a-z]$", Field)) %>%
  dplyr::distinct(Field, Question)
lab <- function(f) item_text$Question[match(f, item_text$Field)]

# Scale definitions (empirical)

comp_i <- c("Q31e", "Q31g", "Q31h")
site_i <- c("Q31j", "Q31k", "Q31l")
unif_i <- c("Q31a", "Q31b", "Q31d", "Q31f", "Q31i")

# ---- Factorability & polychoric correlations ----

Rpoly <- polychoric(reg_cc)$rho
kmo   <- KMO(Rpoly)
bart  <- cortest.bartlett(Rpoly, n = n_cc)

# ---- Parallel analysis (number retained) ----

set.seed(4127)
pa <- fa.parallel(Rpoly, n.obs = n_cc, fa = "fa", fm = "ml", plot = FALSE)
n_fact <- pa$nfact

# ---- 3-factor EFA ----

fa3 <- fa(Rpoly, nfactors = 3, fm = "ml", rotate = "oblimin", n.obs = n_cc)
L   <- unclass(fa3$loadings)

# Map statistical factors to substantive scales by representative items

f_comp <- which.max(abs(L["Q31h", ]))
f_site <- which.max(abs(L["Q31k", ]))
f_unif <- which.max(abs(L["Q31d", ]))
fa_fit_tli   <- round(fa3$TLI, 3)
fa_fit_rmsea <- round(fa3$RMSEA[1], 3)

# ---- Reliability per scale ----

rel_one <- function(items) {
  a  <- psych::alpha(reg_cc[, items], warnings = FALSE)
  om <- tryCatch(suppressWarnings(
          psych::omega(reg_cc[, items], nfactors = 1, plot = FALSE,
                       poly = TRUE)$omega.tot), error = function(e) NA_real_)
  list(alpha = a$total$raw_alpha, omega = om, item = a$item.stats$r.drop,
       drop = a$alpha.drop$raw_alpha)
}
rel_comp <- rel_one(comp_i)
rel_site <- rel_one(site_i)
rel_unif <- rel_one(unif_i)

# ---- CFA: 1-factor (bipolar) vs 2-factor (correlated) on 8 policy items ----

pol_i <- c(unif_i, site_i)
pol   <- reg_cc[, pol_i]
pol[] <- lapply(pol, ordered)
m1 <- paste("policy =~", paste(pol_i, collapse = " + "))
m2 <- paste0("uniform =~ ", paste(unif_i, collapse = " + "), "\n",
             "site =~ ",    paste(site_i, collapse = " + "))
fit1 <- cfa(m1, data = pol, estimator = "WLSMV", ordered = pol_i)
fit2 <- cfa(m2, data = pol, estimator = "WLSMV", ordered = pol_i)
fm <- function(fit) fitMeasures(fit,
  c("cfi.scaled","tli.scaled","rmsea.scaled","srmr"))
fm1 <- fm(fit1); fm2 <- fm(fit2)
lrt <- lavTestLRT(fit1, fit2, method = "satorra.2000")
latcor <- lavInspect(fit2, "cor.lv")["uniform", "site"]

# ---- Composite (bipolar) scale & scores ----

comprehension <- rowMeans(reg_cc[, comp_i])
site_score    <- rowMeans(reg_cc[, site_i])
uniform_score <- rowMeans(reg_cc[, unif_i])
orientation   <- rowMeans(cbind(6 - reg_cc[, unif_i], reg_cc[, site_i]))
alpha_orient  <- psych::alpha(cbind(6 - reg_cc[, unif_i], reg_cc[, site_i]),
                              warnings = FALSE)$total$raw_alpha

# ---- Analysis frame with demographics / covariates / weights ----

af <- data.frame(
  comprehension, site_score, uniform_score, orientation,
  Resi    = d$Resi[cc],
  gender  = d$E2[cc],
  Age     = d$Age[cc],
  avidity = suppressWarnings(as.numeric(as.character(d$C1Total_days[cc]))),
  B1      = as.character(d$B1[cc]),
  postWeight = d$postWeight[cc],
  stringsAsFactors = FALSE
)
af$avidity_log <- log1p(af$avidity)
af$quadrant <- factor(dplyr::case_when(
  af$uniform_score >  3 & af$site_score >  3 ~ "Wants both",
  af$uniform_score <= 3 & af$site_score >  3 ~ "Site-specific only",
  af$uniform_score >  3 & af$site_score <= 3 ~ "Statewide only",
  TRUE                                       ~ "Neither"),
  levels = c("Statewide only","Neither","Wants both","Site-specific only"))
af$wants_both <- ifelse(af$quadrant == "Wants both", "Wants both", "Other")

top_fish <- c("Walleye / Sauger","Largemouth bass","Crappie","Channel catfish",
              "Trout","I do not prefer any particular type of fish")
af$fishpref <- dplyr::case_when(
  is.na(af$B1)          ~ "Missing",
  af$B1 %in% top_fish   ~ af$B1,
  TRUE                  ~ "Other species")
af$fishpref <- relevel(factor(af$fishpref),
                       ref = "I do not prefer any particular type of fish")

# ---- Demographic association tests (Wants both vs rest) ----

cram_v <- function(tb) {
  x <- suppressWarnings(chisq.test(tb))
  v <- sqrt(as.numeric(x$statistic) / (sum(tb) * (min(dim(tb)) - 1)))
  list(chi = as.numeric(x$statistic), df = x$parameter, p = x$p.value, v = v)
}
res_t <- cram_v(table(af$wants_both, af$Resi))
gen_t <- cram_v(table(af$wants_both, af$gender))
age_w <- wilcox.test(Age ~ wants_both, data = af)
n1 <- sum(af$wants_both == "Wants both" & !is.na(af$Age))
n0 <- sum(af$wants_both == "Other" & !is.na(af$Age))
age_rrb <- (2 * as.numeric(age_w$statistic) / (n1 * n0)) - 1   # rank-biserial
age_med <- tapply(af$Age, af$wants_both, median, na.rm = TRUE)

# ---- Multinomial: quadrant ~ comprehension (+ covariates) ----

af$quadrant <- relevel(af$quadrant, ref = "Wants both")
m_base <- multinom(quadrant ~ comprehension, data = af, trace = FALSE)
m_full <- multinom(quadrant ~ comprehension + avidity_log + fishpref,
                   data = af, trace = FALSE)
an_base <- car::Anova(m_base)
an_full <- car::Anova(m_full)
or_tab <- data.frame(
  Contrast = paste(rownames(coef(m_base)), "vs Wants both"),
  OR_unadjusted = round(exp(coef(m_base)[, "comprehension"]), 2),
  OR_adjusted   = round(exp(coef(m_full)[, "comprehension"]), 2),
  row.names = NULL)
ci_base <- exp(confint(m_base)["comprehension", , ])
or_tab$CI95 <- apply(round(t(ci_base), 2), 1,
                     function(z) sprintf("[%.2f, %.2f]", z[1], z[2]))

# ---- Weighted quadrant prevalence (design-based) ----

af$quadrant <- factor(af$quadrant,
  levels = c("Site-specific only","Wants both","Statewide only","Neither"))
des <- svydesign(ids = ~1, weights = ~postWeight,
                 data = af[!is.na(af$postWeight), ])
wp  <- svymean(~quadrant, des)
wci <- confint(wp)
wtab <- data.frame(
  Quadrant = levels(af$quadrant),
  `Unweighted %` = round(100 * as.numeric(prop.table(table(af$quadrant))), 1),
  `Weighted %`   = round(100 * as.numeric(coef(wp)), 1),
  `95% CI`       = sprintf("[%.1f, %.1f]", 100*wci[,1], 100*wci[,2]),
  check.names = FALSE, row.names = NULL)

```

Analyses used `r format(n_cc, big.mark=",")` of `r format(n_total, big.mark=",")` 2025 LAS respondents (`r pct_cc`%) who answered all twelve items. Per-item nonresponse was modest and uniform (11–13%), consistent with incidental item skipping rather than structured
non-response. All correlational and factor-analytic steps used polychoric correlations due to the ordinal nature of the items. Item and scale structure was explored unweighted on the rationale that measurement structure is a property of the instrument rather than of the survey response composition.  Appriopiate per-respondant survey weighting suggested by Hurley (2026) was used only for the population-level estimates and comparisons (post-stratified on age group and residency).

# Results

## Dimensionality and the three-scale solution

Before extraction, the correlation matrix was checked for factorability. The
Kaiser–Meyer–Olkin measure of sampling adequacy was
`r round(kmo$MSA, 2)`, with all per-item values ≥
`r round(min(kmo$MSAi), 2)`. By Kaiser's (1974) conventional benchmarks (< 0.50
unacceptable, 0.70–0.79 middling, 0.80–0.89 *meritorious*, ≥ 0.90 marvelous),
the items are comfortably in the meritorious range. Bartlett's test of
sphericity rejected the hypothesis that the items represent an identity-matrix
(χ²(`r bart$df`) = `r format(round(bart$chisq), big.mark=",")`,
*p* < .001).  These results confirm that sufficient common variance exists to factor.

Horn's parallel analysis (which retains factors whose eigenvalues exceed those
from random data of equivalent dimensions) indicated `r n_fact` factors in the items (Figure 1).
The polychoric inter-item correlations (Figure 2) show the same three blocks
visually and that the two policy blocks split by direction: the
simplification items correlate positively among themselves and
negatively with the site-specific items.

```{r regdev_scree, fig.cap="Figure 1. Horn's parallel analysis scree plot. Actual factor eigenvalues (solid line) exceed mean eigenvalues from 100 random datasets of equivalent dimensions (dashed line) for the first three factors, supporting retention of a 3-factor solution.", fig.width=6, fig.height=4}

data.frame(
  Factor    = 1:6,
  Actual    = pa$fa.values[1:6],
  Simulated = pa$fa.sim[1:6]
) |>
  tidyr::pivot_longer(-Factor, names_to = "Source", values_to = "Eigenvalue") |>
  ggplot(aes(Factor, Eigenvalue, color = Source, linetype = Source)) +
  geom_hline(yintercept = 0, color = "grey80") +
  geom_vline(xintercept = 3.5, linetype = "dashed", color = "grey60") +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2.5) +
  scale_color_manual(values = c(Actual = "#1b4f8a", Simulated = "#c0392b")) +
  scale_linetype_manual(values = c(Actual = "solid", Simulated = "dashed")) +
  scale_x_continuous(breaks = 1:6) +
  labs(x = "Factor", y = "Eigenvalue", color = NULL, linetype = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom")

```

```{r regdev_heatmap, fig.cap="Figure 2. Polychoric inter-item correlations among the twelve regulation items.", fig.width=7.5, fig.height=6.5}

as.data.frame(Rpoly) |>
  tibble::rownames_to_column("item1") |>
  dplyr::mutate(item1 = toupper(sub("^Q31", "", item1))) |>
  tidyr::pivot_longer(-item1, names_to = "item2", values_to = "r") |>
  dplyr::mutate(item2 = toupper(sub("^Q31", "", item2))) |>
  ggplot(aes(item1, item2, fill = r)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%.2f", r)), size = 2.5) +
  scale_fill_gradient2(low = "#2166ac", mid = "white", high = "#b2182b",
                       midpoint = 0, limits = c(-1, 1)) +
  labs(x = NULL, y = NULL, fill = "r") +
  theme_minimal(base_size = 11) +
  theme(panel.grid = element_blank())

```

A three-factor model was also estimated by maximum likelihood with oblique rotation. The rotated pattern (Table 1) is simple and interpretable.  Eleven of twelve items load saliently
(|loading| ≥ .40) on exactly one factor with no consequential cross-loadings.  The factors correspond to regulation comprehension and confidence (*comprehension*; Items E, G, H), site-specific support (*site-specific*; Items J, K, L), and simplification preference (*simplification*; Items A, B, D, F, I).

```{r regdev_loadings}

fac_idx  <- c(f_comp, f_site, f_unif)
ord_items <- c(comp_i, site_i, unif_i)
load_tbl <- data.frame(
  Item = toupper(sub("^Q31", "", ord_items)),
  Statement = lab(ord_items),
  Comprehension = round(L[ord_items, f_comp], 2),
  `Site-specific` = round(L[ord_items, f_site], 2),
  `Simplification` = round(L[ord_items, f_unif], 2),
  h2 = round(fa3$communality[ord_items], 2),
  check.names = FALSE)
for (j in 3:5) load_tbl[abs(load_tbl[[j]]) < .30, j] <- NA
CreateFlex(load_tbl, firstColLabel = TRUE)|>
  compose(part = "header", j = "h2",
          value = as_paragraph(as_chunk("h"), as_sup("2")))

```

*Table 1. Oblimin-rotated factor loadings from maximum-likelihood extraction on the polychoric correlation matrix (loadings < .30 suppressed; Item C excluded — see text); h² = communality. TLI = `r fa_fit_tli`, RMSEA = `r fa_fit_rmsea`.*

Item C - "Anglers are willing to follow complex regulations to
produce high-quality fisheries" — failed to relate with any factor (no loading
≥ .30; largest polychoric correlation = 0.39). It instead appears to tap the idea of complience that the remaining items do not.  Retaining it would degrade rather than improve any of the other scales.  Item C was excluded from all scale scores and is reported only at
the item level.

The three-factor model accounted for `r round(sum(fa3$Vaccounted["Proportion Var", ]) * 100)`% of the variance of the items.  Overall approximate fit was acceptable for an exploratory solution (TLI = `r fa_fit_tli`, RMSEA = `r fa_fit_rmsea`), with the residual misfit attributable largely to the orphan item and a minor secondary loading on Item A.

## Reliability

Internal consistency was estimated with Cronbach's α and McDonald's ω
(Table 2). Conventionally, α ≥ .70 is considered acceptable and ≥ .80 good (Nunnally & Bernstein, 1994); ω
is reported alongside because it does not assume tau-equivalence and is the
preferred coefficient for congeneric items (McDonald, 1999; McNeish, 2018). All three scales meet or approach
the "good" threshold, and no item deletion would materially raise any
coefficient, so all items were retained.

```{r regdev_reliability}

rel_tbl <- data.frame(
  Scale = c("Comprehension", "Site-specific",
            "Simplification"),
  Items = c(length(comp_i), length(site_i), length(unif_i)),
  `Cronbach alpha` = round(c(rel_comp$alpha, rel_site$alpha, rel_unif$alpha), 3),
  `McDonald omega`  = round(c(rel_comp$omega, rel_site$omega, rel_unif$omega), 3),
  check.names = FALSE)
CreateFlex(rel_tbl)

```

*Table 2. Internal-consistency reliability for the three derived scales.*

## Two correlated scales versus a single bipolar composite

Because the simplified and site-specific items are negatively related, a natural
question is whether the eight policy items measure one bipolar dimension
(simplification at one pole, site-specificity at the other) or two distinct but
correlated dimensions. The three-factor EFA structure established in the
previous section is suggested by this analysis; the confirmatory analysis here addresses a
narrower question specifically about the two policy-orientation factors —
whether the simplification and site-specific items, which load on separate EFA
factors, nonetheless reduce to a single, more-easily understood bipolar dimension.  This was tested with confirmatory factor
analysis on the eight policy items, using the WLSMV estimator appropriate for
ordinal indicators, comparing a one-factor model against a two-factor
correlated model (Table 3).

```{r regdev_cfa}

cfa_tbl <- data.frame(
  Model = c("1-factor (bipolar)", "2-factor (correlated)"),
  CFI   = round(c(fm1["cfi.scaled"], fm2["cfi.scaled"]), 3),
  TLI   = round(c(fm1["tli.scaled"], fm2["tli.scaled"]), 3),
  RMSEA = round(c(fm1["rmsea.scaled"], fm2["rmsea.scaled"]), 3),
  SRMR  = round(c(fm1["srmr"], fm2["srmr"]), 3),
  row.names = NULL)
CreateFlex(cfa_tbl)

```

*Table 3. CFA fit for competing structures of the eight policy items
(WLSMV, robust/scaled indices).*

Against standard cutoffs (good fit: CFI/TLI ≥ .95, RMSEA ≤ .06, SRMR ≤ .08;
acceptable: CFI/TLI ≥ .90, RMSEA ≤ .08; Hu & Bentler, 1999), the one-factor model fits poorly
(CFI = `r round(fm1["cfi.scaled"],2)`, RMSEA = `r round(fm1["rmsea.scaled"],2)`),
whereas the two-factor model is far better
(CFI = `r round(fm2["cfi.scaled"],2)`, RMSEA = `r round(fm2["rmsea.scaled"],2)`).
A robust scaled chi-square difference test strongly favors two factors
(Δχ²(`r lrt[2,"Df diff"]`) = `r format(round(lrt[2,"Chisq diff"]), big.mark=",")`,
*p* < .001). The two-factor model estimates the latent correlation between the two policy
factors at `r round(latcor, 2)`—substantial, but well short of the −1 that a
true single bipolar axis would require (the two poles share only about
`r round(latcor^2 * 100)`% of their variance).

The practical difference between a two-scale and single-scale approach to the support of the different regulation complexity levels is visible when respondents are scored both ways (Figure 3). Under the two-scale framing the data do not collapse onto the diagonal that a pure bipolar dimension implies; a large group scores high on both scales. The single reversed composite, though internally consistent (α = `r round(alpha_orient, 2)`), averages these
respondents toward the middle and conceals that pattern.

```{r regdev_framing, fig.cap="Figure 3. Two-scale framing (left) versus single reversed composite (right). Red line marks where a strictly bipolar dimension would place respondents.", fig.width=7.5, fig.height=4}

pA <- ggplot(af, aes(uniform_score, site_score)) +
  geom_jitter(width = .12, height = .12, alpha = .12, size = .8) +
  geom_hline(yintercept = 3, linetype = 2, colour = "grey40") +
  geom_vline(xintercept = 3, linetype = 2, colour = "grey40") +
  geom_abline(slope = -1, intercept = 6, colour = "#b2182b") +
  labs(title = "Two-scale framing",
       x = "Simplification mean", y = "Site-specific mean") +
  theme_minimal(base_size = 10)
pB <- ggplot(af, aes(orientation)) +
  geom_histogram(binwidth = .25, fill = "grey50", colour = "white") +
  geom_vline(xintercept = 3, linetype = 2, colour = "grey40") +
  labs(title = "Single composite framing",
       subtitle = "Higher value = site-specific support",
       x = "Site-specific mean", y = "Number respondents") +
  theme_minimal(base_size = 10)
pA + pB

```

The evidence supports retaining two policy scales (site-specific and simplification) rather than a single composite. Beyond the statistical case, the two-scale representation preserves the most interesting group, the anglers who simultaneously value local tailoring and worry about complexity, who are otherwise erased. The composite scale can remain available for occasions that call for a single summary number, with the caveat that it compresses a genuinely  two-dimensional attitude.

# Discussion

## Interaction of comprehension and policy scales

To connect the comprehension scale to the policy debate, respondents were
split at the scale midpoints (3.0) into four quadrants: Site-specific
only, Simplification only, Wants both (high on both), and Neither (low on both).
A multinomial logistic regression predicting quadrant membership from
comprehension (Table 4, Figure 4) shows a strong, monotonic gradient
(likelihood-ratio χ²(`r an_base["comprehension","Df"]`) =
`r round(an_base["comprehension","LR Chisq"], 1)`, *p* < .001).

```{r regdev_multinom}

or_tab |>
  dplyr::mutate(`Odds Ratio` = paste0(OR_unadjusted, " ", CI95)) |>
  dplyr::select(Contrast, `Odds Ratio`) |>
  CreateFlex()

```

*Table 4. Odds ratios for a one-point increase in comprehension, relative to the
"Wants both" reference group.*

```{r regdev_box, fig.cap="Figure 4. Mean comprehension by policy quadrant.  Error bars represent 95% confidence interval.", fig.width=7, fig.height=4.5}

af |>
  dplyr::mutate(quad = factor(quadrant,
    levels = c("Statewide only","Neither","Wants both","Site-specific only"))) |>
  ggplot(aes(quad, comprehension)) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.15) +
  stat_summary(fun = mean, geom = "point", size = 2.5) +
  labs(x = NULL, y = "Comprehension scale mean") +
  theme_minimal(base_size = 11)

```

Each one-point rise in comprehension nearly doubles the odds of being
"Site-specific only" rather than "Wants both" (OR = `r or_tab$OR_unadjusted[or_tab$Contrast=="Site-specific only vs Wants both"]`)
and sharply lowers the odds of being "Statewide only"
(OR = `r or_tab$OR_unadjusted[or_tab$Contrast=="Statewide only vs Wants both"]`).
For fishery managers, the actionable finding is that support for
more complex, locally tailored regulations rises with anglers'
confidence that they understand the rules. Investments that make regulations
easier to find, read, and apply are therefore not merely a customer-service function but may plausibly expand the constituency comfortable with the
site-specific management that biologists often need.

## Fishing avidity and species preference

A reasonable consideration is that the comprehension–policy link is a by-product of
how much or for what people fish. Adding fishing avidity (log of total days fished
in 2025) and target-species preference to the model leaves the comprehension
effect essentially unchanged (Table 5): the adjusted odds ratios match the
unadjusted ones to two decimals, and comprehension remains the dominant term
(LR χ²(`r an_full["comprehension","Df"]`) =
`r round(an_full["comprehension","LR Chisq"], 1)`, *p* < .001).

```{r regdev_adjust}

or_tab |>
  dplyr::select(Contrast, `Odds ratio - original` = OR_unadjusted, `Odds ration - adjusted` = OR_adjusted) |>
  CreateFlex()

```

*Table 5. Comprehension odds ratios before and after adjusting for avidity and
species preference.*

The two covariates behave differently from one another. Fishing avidity is
not associated with policy quadrant in the multinomial model (LR χ²(`r an_full["avidity_log","Df"]`) =
`r round(an_full["avidity_log","LR Chisq"], 1)`,
*p* = `r round(an_full["avidity_log","Pr(>Chisq)"], 2)`): how often an angler
fishes does not predict where they stand.  However Species preference is associated
(LR χ²(`r an_full["fishpref","Df"]`) =
`r round(an_full["fishpref","LR Chisq"], 1)`, *p* < .001), though the practical
differences are modest; most groups fall within a few points of one another (Figure 5).
The clearest departure is among trout anglers, who lean toward simplified regulations
more than other groups (Figure 5).  This pattern is worth noting for managers given the
site-specific nature of much of Nebraska's trout management.

```{r regdev_specpref, fig.cap="Figure 5. Policy quadrant membership by target species preference (anglers with missing or unspecified species preference excluded), sorted by proportion in the Statewide-only quadrant. Trout anglers (outlined) show the strongest lean toward simplifed regulations.", fig.width=7, fig.height=4.5}

plot_df <- af |>
  dplyr::filter(!fishpref %in% c("Missing", "Other species")) |>
  dplyr::mutate(
    fishpref = dplyr::if_else(
      fishpref == "I do not prefer any particular type of fish",
      "No preference", fishpref),
    quadrant = factor(quadrant,
      levels = c("Statewide only","Neither","Wants both","Site-specific only"))
  ) |>
  dplyr::count(fishpref, quadrant) |>
  dplyr::group_by(fishpref) |>
  dplyr::mutate(pct = n / sum(n)) |>
  dplyr::ungroup()

sp_order <- plot_df |>
  dplyr::filter(quadrant == "Statewide only") |>
  dplyr::arrange(pct) |>
  dplyr::pull(fishpref)

plot_df |>
  dplyr::mutate(
    fishpref = factor(fishpref, levels = sp_order),
    is_trout = fishpref == "Trout"
  ) |>
  ggplot(aes(pct, fishpref, fill = quadrant, color = is_trout, linewidth = is_trout)) +
  geom_col(width = 0.7) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0, 0)) +
  scale_fill_manual(values = c(
    "Statewide only"     = "#d6604d",
    "Neither"            = "#f4a582",
    "Wants both"         = "#92c5de",
    "Site-specific only" = "#2166ac"),
    name = NULL) +
  scale_color_manual(values = c("TRUE" = "black", "FALSE" = NA), guide = "none") +
  scale_linewidth_manual(values = c("TRUE" = 0.8, "FALSE" = 0), guide = "none") +
  labs(x = "Proportion of anglers", y = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom",
        panel.grid.major.y = element_blank())

```

Demographically, the "wants both" segment is unremarkable. It does not differ
from other anglers in residency
(χ²(`r res_t$df`) = `r round(res_t$chi, 2)`,
*p* = `r round(res_t$p, 2)`; Cramér's *V* = `r round(res_t$v, 3)`) or gender
(χ²(`r gen_t$df`) = `r round(gen_t$chi, 2)`,
*p* = `r round(gen_t$p, 2)`; *V* = `r round(gen_t$v, 3)`), and is only
trivially older (median `r age_med["Wants both"]` vs `r age_med["Other"]` years;
Wilcoxon *p* = `r round(age_w$p.value, 3)`, rank-biserial *r* =
`r round(age_rrb, 2)`).
Because the "wants both" segment is demographically unremarkable, the appetite for both flexibility and simplicity should be understood as a mainstream attitude rather than a position of any demographic subgroup.  Coupled with the comprehension scale relationships, support of this group for site-specific regulations also appears to be mallable with education and enforcement actions.

## Standalone Item C

Item C ("Anglers are willing to follow complex regulations to produce
high-quality fisheries") was excluded from the scales because it failed to load
cleanly on any factor. While it doesn't factor into the three scales presented, its responses are still worth examining outside of scale developement because it speaks to a stated behavioral willingness rather than a policy preference.

```{r regdev_q31c}

af$Q31c <- reg_cc$Q31c
q31c_tab <- af |>
  dplyr::group_by(quadrant) |>
  dplyr::summarise(n = dplyr::n(),
                   Mean = round(mean(Q31c), 2),
                   me = qt(0.975, dplyr::n() - 1) * sd(Q31c) / sqrt(dplyr::n()),
                   `95% CI` = sprintf("%.2f \u00b1 %.2f", Mean, round(me, 2)),
                   .groups = "drop") |>
  dplyr::select(-me) |>
  dplyr::arrange(dplyr::desc(Mean))
kw <- kruskal.test(Q31c ~ quadrant, data = af)
sp <- sapply(af[c("comprehension","site_score","uniform_score","orientation")],
             function(x) round(cor(af$Q31c, x, method = "spearman"), 2))
CreateFlex(as.data.frame(q31c_tab))

```

*Table 7. Mean agreement with Item C by policy quadrant.*

Agreement with Item C is unevenly distributed across the quadrants
(Kruskal-Wallis χ²(`r kw$parameter`) = `r round(kw$statistic, 1)`, *p* < .001;
Figure 7). It is highest among the Site-specific only group (`r q31c_tab$Mean[q31c_tab$quadrant=="Site-specific only"]`) and lowest among the Statewide only group
(`r q31c_tab$Mean[q31c_tab$quadrant=="Statewide only"]`). Consistent with this,
Item C correlates positively with both the comprehension scale (Spearman ρ = `r sp["comprehension"]`) and the site-specific scale (ρ = `r sp["site_score"]`), and weakly negatively with simplification (ρ = `r sp["uniform_score"]`).

```{r regdev_q31c_fig, fig.cap="Figure 7. Mean agreement with Item C by policy quadrant.  Error bars represent 95% confidence intervals.", fig.width=7, fig.height=4}

af |>
  dplyr::mutate(quad = factor(quadrant,
    levels = c("Statewide only","Neither","Wants both","Site-specific only"))) |>
  dplyr::group_by(quad) |>
  dplyr::summarise(m = mean(Q31c), se = sd(Q31c)/sqrt(dplyr::n()),
                   .groups = "drop") |>
  ggplot(aes(quad, m)) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = m - 1.96*se, ymax = m + 1.96*se), width = .15) +
  labs(x = NULL, y = "Item C mean") +
  theme_minimal(base_size = 11)

```

This dual association explains why Item C resisted assignment to a single factor:
it draws simultaneously on feeling competent with the rules and on valuing
locally tailored management, the two constructs that the exploratory analysis
kept distinct. Item C functions less like a scale indicator than
like a downstream attitude the scales help account for. For fishery managers, the
implication is direct and encouraging. The anglers most willing to comply with
complex, site-specific rules in pursuit of better fishing are those
who understand the regulations and already endorse tailored management. This
reinforces the earlier conclusion that improving regulatory comprehension is a
plausible route not only to broader acceptance of site-specific regulation but
to greater willingness to follow it. However, this is a single item and repeated measures on future application of this instrument may be needed to confirm this construct.

## Population sizes of the quadrants

Finally, the quadrants were projected to the licensed-angler population using
the survey respondant weights (post-stratified on age group and residency; Hurley 2026). A
design-based estimator (Taylor-linearized standard errors) yields the weighted
prevalences and 95% confidence intervals in Table 6 and Figure 6. Weighting
shifts the estimates only slightly relative to the raw sample, indicating that
attitude composition is not strongly confounded with the age or residency margins
used in weighting.

```{r regdev_weighted}

wtab |>
  dplyr::mutate(
    p_uw = `Unweighted %` / 100,
    n_tot = sum(table(af$quadrant)),
    `Unweighted %` = sprintf("%.1f \u00b1 %.1f", `Unweighted %`,
                              round(1.96 * sqrt(p_uw * (1 - p_uw) / n_tot) * 100, 1)),
    `Weighted %`   = sprintf("%.1f \u00b1 %.1f", `Weighted %`,
                              round((100*wci[,2] - 100*wci[,1]) / 2, 1))
  ) |>
  dplyr::select(Quadrant, `Unweighted %`, `Weighted %`) |>
  CreateFlex()

```

*Table 6. Unweighted and weighted (raked) quadrant prevalence with design-based
95% confidence intervals.*

```{r regdev_wbar, fig.cap="Figure 6. Weighted population prevalence of the four policy quadrants (design-based 95% CIs).", fig.width=7, fig.height=4}

data.frame(Quadrant = factor(levels(af$quadrant), levels = levels(af$quadrant)),
           est = 100*as.numeric(coef(wp)),
           lo  = 100*wci[,1], hi = 100*wci[,2]) |>
  ggplot(aes(Quadrant, est)) +
  geom_col(fill = "grey55", width = .65) +
  geom_errorbar(aes(ymin = lo, ymax = hi), width = .2) +
  labs(x = NULL, y = "Weighted % of anglers") +
  theme_minimal(base_size = 11)

```

Roughly `r round(wtab$"Weighted %"[wtab$Quadrant=="Site-specific only"])`%
of Nebraska anglers endorse site-specific regulation without favoring
statewide regulation, while a comparable
`r round(wtab$"Weighted %"[wtab$Quadrant=="Wants both"])`% want both
simplicity and local tailoring. Only about
`r round(wtab$"Weighted %"[wtab$Quadrant=="Statewide only"])`% prefer
statewide regulations alone. For decision-makers, the message is that outright opposition
to site-specific regulation is a minority position, but another group of anglers
hold the more nuanced "both" view which suggests that communication emphasizing
why particular waters carry particular regulations, paired with genuine effort to
keep the overall system comprehendible, and adaquate education and enforcement actions are likely to resonate more broadly than either pure simplification or unexplained complexity.

## Limitations

Some limitations could apply to these results. The scales derived in this study including comprehension, site-specific preference, simplification preference, and their combinations were measured in a single cross-sectional effort.  It is possible that the associations found can be purely correlative here and should taken as informative but not as causational.  Higher comprehension may foster openness to complexity, or anglers predisposed
toward site-specific management may simply invest more in learning the rules, or both may be true.  Anglers may share a common driver such as engagement or experience or education and this analysis cannot differentiate among them.
These results also rely on stated versus realized preferences.  Any given respondant may score highly on site-specific or simplified scales, yet when faced with a concrete regulation implimentation may exhibit a different realized response driven by situation specfic parameters.  Results presented reflect population analysis of generalized, stated opinions and preferences
The analysis also rests on a single survey year (2025) and angler population sampling so the scale structure and prevalence estimates should be treated as provisional or potentially transitional,  Confirmatory cross-validation in a future survey efforts would be needed to establish measurement over time and confirm the three-factor solution is stable rather than sample-specific.

# Implications

## Fisheries regulations

From a broad persepective, 2025 LAS respondants expressed more support for site-specific approaches over simplified, regional approaches to regulating fisheries.  However, the smaller, no inconsequential amount of respondents that did favor simplified regulations indicates that that discontent may be expressed regardless of approach used.  The tipping point for policy application appears to lie with a sizable portion of respondants who are willing to support either approach.  The critical consideration to move respondants towards site-specific regulations appears to be the ability to comprehend both the regulations themselves and the logic behind them as well as trust in the managers that set the recommendations.  With proper educational and outreach efforts, this large, middle-group of respondants will likely lend the support needed for any regulation change or implementation.

## Scale development.

The simplification preference scale warrants attention in future survey iterations: all five of its items are negatively worded (reversed), meaning angler agreement consistently signals preference for simpler, statewide rules. While the scale performs reliably (ω = `r rel_tbl[rel_tbl$Scale == "Simplification preference", "McDonald omega"]`), all-same-direction item blocks are susceptible to acquiescence bias — a tendency to agree with statements regardless of content. Future development should introduce positively worded counterparts to create a more balanced item pool.  Additionally, additional questions to complement Item C could help create a useful fourth scale looking at perception of angler behaviors.

While they score well on factor loading and consistance, the comprehension and site-specific scales are also relatively narrow at three items. Broadening it with additional items tapping angler confidence with specific regulatory formats and additional site-specific examples may improve not on cosmetic balance but also content coverage providing a more stable platform for longitudinal monitoring.

# Appendex A

`r paste(trimws(GetQuestion(q, Q31, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.reversed, "  ", caption.raked, sep="")`

```{r Q31_percentA}

myFields<-d %>% dplyr::select(contains("Q31")) %>% select(-contains("Answered")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  tempD<-data.frame(Item=myFields[i], CreateTableA_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
  tempD$ItemLetter<-toupper(sub("^Q31", "", myFields[i]))
  tempD<-SubstitueQuesForResponse(tempD,q, !!rlang::sym(myFields[i]), 2025, responseField="Item")
}
op<-MarkReversedItems(op, q, 2025, responseField="Item")
op<-op %>% dplyr::rename(Statement = Item, Item = ItemLetter) %>% dplyr::relocate(Item, Statement)
CreateFlex(op, mergeOnFirst = TRUE, firstColLabel = TRUE)

```

`r paste(trimws(GetQuestion(q, Q31, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.reversed, "  ", caption.raked, sep="")`

```{r Q31_percentB}

myFields<-d %>% dplyr::select(contains("Q31")) %>% select(-contains("Answered")) %>% names()
op<-foreach(i=1:length(myFields), .combine="rbind") %do% {
  tempD<-data.frame(Item=myFields[i], CreateTableB_selectOne_percent(d %>% filter(!is.na(get(myFields[i]))), myFields[i]), check.names = FALSE)
  tempD$ItemLetter<-toupper(sub("^Q31", "", myFields[i]))
  tempD<-SubstitueQuesForResponse(tempD,q, !!rlang::sym(myFields[i]), 2025, responseField="Item")
}
op<-MarkReversedItems(op, q, 2025, responseField="Item")
op<-op %>% dplyr::rename(Statement = Item, Item = ItemLetter) %>% dplyr::relocate(Item, Statement)
CreateFlex(op, mergeOnFirst = TRUE, firstColLabel = TRUE)

```

`r paste(trimws(GetQuestion(q, Q31, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.reversed, "  ", caption.raked, sep="")`

```{r Q31_means}

myFieldsQ31<-d %>% dplyr::select(contains("Q31")) %>% select(-contains("Answered")) %>% names()
tblA<-CreateTableA_means(d, myFieldsQ31)
tblA$Item<-toupper(sub("^Q31", "", as.character(tblA$Response)))
tblA<-SubstitueQuesForResponse(tblA, q, Q31, 2025)
tblA<-MarkReversedItems(tblA, q, 2025)
tblA<-tblA %>% dplyr::rename(Statement = Response) %>% dplyr::relocate(Item, Statement)
CreateFlex(tblA, firstColLabel = TRUE)

```

`r paste(trimws(GetQuestion(q, Q31, 2025)), "  ", caption.means, "  ", labels.agree, "  ", caption.reversed, "  ", caption.raked, sep="")`

```{r}

tblB<-CreateTableB_means(d, myFieldsQ31)
tblB$Item<-toupper(sub("^Q31", "", as.character(tblB$Response)))
tblB<-SubstitueQuesForResponse(tblB, q, Q31, 2025)
tblB<-MarkReversedItems(tblB, q, 2025)
tblB<-tblB %>% dplyr::rename(Statement = Response) %>% dplyr::relocate(Item, Statement)
CreateFlex(tblB, firstColLabel = TRUE)

```

# References

Bureau of Soci0logical Research. 2026. Fishing Nebraska 2025-2026 Methodology Report. University of Nebraska-Lincoln.
Hu, L. T., & Bentler, P. M. (1999). Cutoff criteria for fit indexes in covariance structure analysis: Conventional criteria versus new alternatives. Structural Equation Modeling, 6(1), 1–55.
Hurley, Keith. 2026. 2026 Nebraska Licensed Angler Survey - Respondents and Responses. Nebraska Game and Parks Commission. (Hurley 2026).
Kaiser, H. F. (1974). An index of factorial simplicity. Psychometrika, 39(1), 31–36.
McDonald, R. P. (1999). Test theory: A unified treatment. Lawrence Erlbaum Associates.
McNeish, D. (2018). Thanks coefficient alpha, we'll take it from here. Psychological Methods, 23(3), 412–433.
Nunnally, J. C., & Bernstein, I. H. (1994). Psychometric theory (3rd ed.). McGraw-Hill.